### 2018-03-14 decorrelation.tex
First commit with work from emails

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RevTeX 4.1 LaTeX
% Kevin C. Young
% Scalable & Secure Systems Research (08961)
% Thu Mar  5 15:29:19 PST 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}

\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}

%-------------Header begins here----------------------------------------
\begin{document}
\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}

\author{Kevin C. Young}
\email[Corresponding author: ]{kyoung@sandia.gov}
\affiliation{Sandia National Laboratories, Livermore, CA}

\author{Anthony Polloreno}
% \email[Email: ]{apolloreno}
\affiliation{Rigetti Quantum Computing, Berkeley, CA}

\date{\today}

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical.  Recent work by Preskill and others has shown that the arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

\pacs{}

\maketitle

\section{Outline}
\begin{enumerate}
    \item Introduction
    \item Method
    \item Results
    \item Discussion
    \item Acknowledgments
\end{enumerate}

\section{Introduction}

Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical.  Recent work by Preskill and others has shown that the arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.

We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).  BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.  That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}.  A balanced family is one which satisfies, for some small $\alpha$,
\begin{equation}\label{eq:1}
    \frac{1}{N}\sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
\end{equation}

Where $DPN[\alpha](\rho)$ is a depolarizing noise channel with strength $\alpha$. On average, the unitary approximations implement the target unitary followed by a small depolarizing channel. The task of constructing the BCSs will fall to optimal control.

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations. A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (ie, a clockwise and counter clockwise rotation of the qubit).  In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error.  When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random.  This has the effect of decorrelating the over-rotation error.  As we show, these techniques may be generalized to multi-qubit errors.

\section{Optimal Control Problem}
Generating BCSs can be done in a variety of ways. For simplicity in this paper we use the GRAPE algorithm to generate candidate pulseshapes to approximate the target gate, but one could use any quantum optimal control technique find a family of controls. In our numerical experiment, we set our target control infidelity to $\epsilon=1\mathrm{e}{-3}$ and model the stochastic error on the controls as normally distributed random variables, so that each time-varying control $c_i(t)$ has an associated error $\delta_i \mathtt{\sim} \mathcal{N}(0, .001)$
Thus we have the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = H_0 + \sum_{i=0}^n (c_i(t) + \delta_i)H_i
\end{equation}
for control Hamiltonians $H_i$ and free evolution Hamiltonian $H_0$. In the update step for GRAPE, we modify the gradient to be that of the weighted average performance, with the integrals approximated via Gaussian quadrature:
\begin{equation}
   \mathcal{T}[\int p(\vec{\delta})e^{-iH(t)t}dtd\vec{\delta}]\\
\end{equation}
where $p(\vec{\delta})$ is a multivariate Gaussian distribution.
Doing this ensures that our family of controls perform moderately well over a range of stochastic errors.

After using GRAPE to produce a collection of controls, we now must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}
  \begin{align}
   &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
   &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
   &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{align}
\end{equation}

This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming. We present numerical results for one qubit and two qubits gates in the following sections.

\section{1Q Gates}
We assume a model of our Hamiltonian for one qubit control to be:

$$ H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y) $$

\section{2Q Gate}
We assume a model of our Hamiltonian for two qubit control to be:
$$H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)$$

\begin{align*}
    \left( U^\dagger V \right)
\end{align*}

$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
% \bibliography{decorrelation.bib}

\end{document}

### 2018-03-14 decorrelation.tex
adding bib, and first pass at some way of writing algorithms

@@
 \usepackage{hyperref}
+\usepackage{algorithm, algorithmicx}
+\usepackage{algpseudocode}
 \hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
@@
 Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
-\begin{equation}
 \begin{align}
@@
 \end{align}
-\end{equation}
 
 This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming. We present numerical results for one qubit and two qubits gates in the following sections.
+
+\section{GRAPE}
+First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary.
+Naively this can be done by defining a cost function $J(U) = Tr\{U_TU\}$, where $U_T$ is the target unitary, and $U = \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$.
+One can then define the \textit{control matrix} $u_{ij}$, denoting the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian.
+Then we see that we can maximize our cost function via the chain rule, i.e.
+performing the following update loop for some threshold value $\delta$:
+
+\begin{algorithmic}
+\Procedure{find\_controls}{U, $\delta$, $u_{ij}$}
+\While{$J(U) < (1-\delta$)}
+\State $u_{ij}$ $\rightarrow$ $u_{ij} + \epsilon\frac{\partial J(U)}{\partial u_{ij}}$
+\State $U \rightarrow \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$
+\EndWhile
+\EndProcedure
+\end{algorithmic}
+
+In general these gradients can be computed via simple back propagation with the chain rule, however in \cite{Khaneja2005} Khaneja et al.
+derives a simple update formula that is correct to first order.
+So long as the discretization in time is fine enough,this will be a good approximation.
 
@@
 
-$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
-$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
-% \bibliography{decorrelation.bib}
-
+%$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
+%$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
+\bibliography{decorrelation.bib}
 \end{document}

### 2018-03-17 decorrelation.tex
added images, added some comments to the tex file, added a readme in the image folder

@@
 \usepackage{hyperref}
-\usepackage{algorithm, algorithmicx}
-\usepackage{algpseudocode}
+\usepackage{algorithm}
+\usepackage{algpseudocode, caption}
 \hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
@@
 \newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
+\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
 \newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
@@
 
+\begin{algorithm}[H]
+\floatname{algorithm}{Procedure}
+  \caption*{\textsc{\textbf{Gradient Ascent}}}
    \begin{algorithmic}
-\Procedure{find\_controls}{U, $\delta$, $u_{ij}$}
 \While{$J(U) < (1-\delta$)}
@@
 \EndWhile
-\EndProcedure
+
    \end{algorithmic}
+\end{algorithm}
 
-In general these gradients can be computed via simple back propagation with the chain rule, however in \cite{Khaneja2005} Khaneja et al.
-derives a simple update formula that is correct to first order.
-So long as the discretization in time is fine enough,this will be a good approximation.
+In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters via the chain rule.
+However, in \cite{Khaneja2005} Khaneja et al.
+derive a simple update formula that is correct to first order, in particular one can show that:
+\begin{align}
+\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
+\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
+\end{align}
+
+In this paper we have modified the update step to use instead use approximately the following gradient:
+\begin{align}
+\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta})}{\partial u_{ij}} d\vec{\delta}
+\end{align}
+again with $p(\vec{\delta})$ Gaussian. In particular, this ensures that the optimizer will attempt to find controls that are not only good at zero detuning, but also for small noise values.
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{x2.png}
+\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}.
+A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
+B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
+\end{figure*}
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{y2.png}
+\caption{In the above we have used our method to produce a BCS for a $RY(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}.
+A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
+B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
+\end{figure*}
 
@@
 
-$$ H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y) $$
+\begin{equation}\label{eq:1Qham}
+H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
+\end{equation}
+We assume variances of $\sigma = .001$ on all control parameters, and we use a control time of $\pi$, with 100 steps of discretization.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated.
+%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{2Q.png}
+\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}.
+A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
+B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
+\end{figure*}
 
@@
 We assume a model of our Hamiltonian for two qubit control to be:
-$$H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)$$
-
-\begin{align*}
-    \left( U^\dagger V \right)
-\end{align*}
+\begin{equation} \label{eq:2Qham}
+H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)
+\end{equation}
+We assume that the standard deviations are $\sigma = .001$ on all parameters, and that the control time is 4 $\pi$, with discretization of 500 steps.
+In addition, we assume that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are correlated.
+Namely, because in many systems like superconducting qubits, the difference between these pulses amounts to a phase shift in the signal, so that things like amplitude drift will be shared and correlated.
+%It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe
 

### 2018-05-07 decorrelation/decorrelation.tex
Fixing a lot of comments from Kevin's first round of reviewing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RevTeX 4.1 LaTeX
% Kevin C. Young
% Scalable & Secure Systems Research (08961)
% Thu Mar  5 15:29:19 PST 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}

\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}

%-------------Header begins here----------------------------------------
\begin{document}
\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}

\author{Kevin C. Young}
\email[Corresponding author: ]{kyoung@sandia.gov}
\affiliation{Sandia National Laboratories, Livermore, CA}

\author{Anthony Polloreno}
% \email[Email: ]{apolloreno}
\affiliation{Rigetti Computing, Berkeley, CA}

\date{\today}

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical. Recent work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

\pacs{}

\maketitle

\section{Introduction}

%Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical.  Recent work by Preskill and others has shown that the arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.

Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}. These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates assumptions made by the models used in proofs.

As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
\begin{equation}\label{eq:0}
  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
\end{equation}
where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process. In a standard nearest-neighbors topology, like those found in super-conducting qubit architectures, these terms might arise from an effective model where high-frequency degrees of freedom are intergrated out to yield high-weight operators. These noise channels are one way in which the assumptions used in proofs of thresholds may be violated.

Another assumption that is instrumental in proving many threshold theorems is Markovianity \cite{Kitaev1997}. There are many ways in which devices can behave in non-Markovian ways, and NISQ devices have already been shown to be subject to drift in controls, \cite{Kelly2018} and in general non-Markovian noise \cite{BlumeKohout2017}. Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise. [WHY IS WHAT WE'RE DOING BETTER?]

To remedy these problems, we take a different approach and propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs). BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian. That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}. A balanced family is one which satisfies, for some small $\alpha$,
\begin{equation}\label{eq:1}
  \frac{1}{N}\sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
\end{equation}

Where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$. (For the rest of this paper, we will refer to them just as depolarizing channels.) Such a channel is defined as:
\begin{equation}\label{eq:2}
  DPN[\alpha](\rho) \rightarrow (1-\alpha)\rho + \alpha\sum p_i \sigma_i\rho\sigma_i
\end{equation}
with $p_i$ summing to one. This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel. The task of constructing the BCSs will fall to optimal control.

This techique can be used to turn coherent error into incoherent error and correlated error into uncorrelated error. The former gives the benefit that the error incurred from incoherent errors compound linearly, while coherent errors compound quadratically. The latter gives the benefit of reducing non-Markovian effects. This is a particularly useful property of BCSs, as diagnosing non-Markovianity in a gateset is challenging, but essential to perform reliable quantum computation. Many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.

For example, randomized benchmarking and tomography will report incorrect answers without any syndrome, [CITATION NEEDED], and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian. Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate.

\section{GRAPE}\label{GRAPE}
Generating BCSs can be done in a variety of ways, using any quantum optimal control technique \cite{Caneva2011, Machnes2018} to find a family of controls. For simplicity in this paper we use the GRAPE algorithm to generate candidate pulseshapes to approximate the target gate. First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$. Defining our uncontrolled Hamiltonian as $H_0$, our control Hamiltonians as $H_{i\neq 0}$, and our \textit{control matrix} $u_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write our approximate unitary at any timestep as
\begin{equation}\label{eq:3}
  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}u_{ij}H_{ij}\}
\end{equation}
Then, to measure the simularity of our approxiate unitary $U_n$, and our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U_n\}$.

To optimize this cost function we can perform the following standard update loop for some threshold value $\varepsilon > 0$ and step size $\delta > 0$:
\begin{algorithm}[H]
\floatname{algorithm}
  \caption{\textsc{\textbf{Gradient Ascent}}}
  \begin{algorithmic}
    \While{$J(U_n) < (1-\varepsilon$)}
    \State $u_{ij} \rightarrow u_{ij} + \delta\frac{\partial J(U)}{\partial u_{ij}}$
    \For{$1 \leq i \leq n$}
    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}u_{ij}H_i)\}$
    \EndFor
    \State $U \rightarrow \prod_1^nU_i$
    \EndWhile 
  \end{algorithmic}
\end{algorithm}

In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule. However, in \cite{Khaneja2005} Khaneja et al. derive a simple update formula that is correct to first order. In particular one can show that:
\begin{align}
\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
\end{align}

In this paper we have modified the update step to use instead use approximately the following gradient:
\begin{align}\label{quadrature}
\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
\end{align}
with $p(\vec{\delta})$ Gaussian distributed. This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral approximately in this paper by using Gaussian quadrature. Doing this ensures that the family of controls produced by our routine perform moderately well over a range of stochastic errors.

\section{Optimal Control Problem}\label{ocp}
To explore the utility of BCSs, we consider the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = H_0 + \sum_{i=1}^n (c_i(t) + \delta_i(t))H_i
\end{equation}
for control Hamiltonians $H_{i\neq0}$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$ are random variables. Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time. Correlations between different $\delta_i$ could arise if two of the control have the same noise source, e.g. $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope.

After using GRAPE to produce a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{split}
\end{equation}

This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming.[CITATION NEEDED]

Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls. Therefore we can view our approach as a regularization of this method, where we have imposed the condition that our final channel must arise from a BCS.[IS THIS ACTUALLY A REGULARIZATION? DOES IT IMPOSE SOME KIND OF SPARSITY] In doing so, we move from using a convex optimization routine to compute the diamond norm to needing to computing a sum. In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.

\begin{figure}
  \centering
  \includegraphics[width=.75\columnwidth]{simple_example.png}
  \caption{An example of a BCS. The red path is a $\pi$ pulse over-rotating clockwise, while the blue path is a $\pi$ pulse over-rotating counter-clockwise. The purple path is the average of the two.}
  \label{fig:simple_example}
\end{figure}

\section{A Simple Example}
As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations. A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit). In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error. When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random. This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}). In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically. In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent ou gates in the vectorized superoperator representation, then:

\begin{equation}
  \begin{gathered}
    \frac{1}{2}(X_{\pi + \epsilon} + \bar X_{\pi + \epsilon}) \\  
    = (\sin^2{\frac{\pi + \epsilon}{2}}I + \cos^2{\frac{\pi + \epsilon}{2}}X)X \\
    \approx ((1 - \epsilon^2)I + \epsilon^2X)X
  \end{gathered}
\end{equation}

Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $\bar X_\pi$  form a BCS, with $\alpha\approx\epsilon^2$.

\section{1Q Gates}\label{1Q Gates}
 In this section, we present numerical results on generating one-qubit gates that together with $RZ(\theta$) rotations are universal for one-qubit computation. Our control Hamiltonian is given as: 
\begin{equation}\label{eq:1Qham}
  H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
$\epsilon$ is a normally distributed random variable, centered at $0$ with standard deviation $.001$, corresponding to a time varying Stark shift on the qubit. $\delta$ is also a normally distributed random variable with the same parameters, and is meant to represent random fluctuations in the control electronics, such as diurnal variations resulting from temperature instability. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
[ADD ANALYSIS OF PLOTS]
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{x2.png}
\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{y2.png}
\caption{In the above we have used our method to produce a BCS for a $RY(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

\section{2Q Gates}\label{2Q Gates}
 In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation. Our control Hamiltonian is given as: 
\begin{equation} \label{eq:2Qham}
H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)
\end{equation}
We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
[ADD ANALYSIS OF PLOTS]
%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

%It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe

%$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
%$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
\bibliography{decorrelation.bib}
\end{document}

### 2018-07-09 decorrelation/decorrelation.tex
some updates

@@
 
+\author{Anthony Polloreno}
+% \email[Email: ]{apolloreno}
+\affiliation{Rigetti Computing, Berkeley, CA}
+
 \author{Kevin C. Young}
@@
 \affiliation{Sandia National Laboratories, Livermore, CA}
-
-\author{Anthony Polloreno}
-% \email[Email: ]{apolloreno}
-\affiliation{Rigetti Computing, Berkeley, CA}
 
@@
 \section{Optimal Control Problem}\label{ocp}
+\subsection{Random Gate Synthesis}
 To explore the utility of BCSs, we consider the following Hamiltonian:
@@
 \end{equation}
-for control Hamiltonians $H_{i\neq0}$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$ are random variables.
+for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$.
 Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time.
-Correlations between different $\delta_i$ could arise if two of the control have the same noise source, e.g.
-$X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope.
-
-After using GRAPE to produce a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}).
+Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
+Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
+\subsection{Channel Approximation}
+After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}).
 To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate.
@@
 \begin{equation} \label{eq:2Qham}
-H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)
+H = \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} + \sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j))
 \end{equation}

### 2018-07-19 decorrelation/decorrelation.tex
Adding in experimental results, and more references and comments, still very rough

@@
 
-%Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated.
-While convenient for simulation, these error models are often unphysical.
-Recent work by Preskill and others has shown that the arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold.
-The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations.
-We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
-
 Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}.
@@
 Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise.
-[WHY IS WHAT WE'RE DOING BETTER?]
+Indeed, other have even implemented these routines natively in hardware \cite{Ware2018}.
+These routines all require some level of sophistication.
+In the case of \cite{Campbell2017}, the analysis assumes Solovay-Kitaev [CITATION]-like decomposition of unitaries, and treats Pauli and Clifford gates as being free to implement, which is far from the reality of modern quantum computers.
+In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations.
+In general, this cannot be done efficiently for non-Clifford operations, and in addition, this introduces a linear-time precompilation overhead for shot of the circuit.
 
@@
 Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate.
+Unlike \cite{Ware2018}, \cite{Wallman2016}, and \citep{Campbell2017}, this routine can be implemented in the firmware of the quantum computer, and requires only an instruction for a random choice - no pre or post processing is required.
 
@@
 
-\section{1Q Gates}\label{1Q Gates}
+\section{Numerical Results}\label{numerical}
+\subsection{1Q Gates}\label{1Q Gates}
  In this section, we present numerical results on generating one-qubit gates that together with $RZ(\theta$) rotations are universal for one-qubit computation. Our control Hamiltonian is given as: 
@@
 
-\section{2Q Gates}\label{2Q Gates}
+\subsection{2Q Gates}\label{2Q Gates}
  In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation.
@@
 
+\section{Experimental Results}\label{experimental}
+To demonstrate the realizability of this routine, we implemented it on a superconducting qubit, to calibrate an $RX(\frac{\pi}{2})$ pulse.
+The qubit being used had a 20.5 $\mu$s T1, and a 11.00 $\mu$s T2, and the pulse shapes being considered were 30ns long top hat pulse sequences, generated via a set-and-hold signal generator using the amplitudes shown in \ref{fig:pulseshapes}.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=.75\columnwidth]{pulseshapes.png}
+  \caption{The pulseshapes used in the routine.
+The original pulse was generated by iteratively applying $RX(\frac{\pi}{2})$ pulses, fitting the resulting sinusoid, and updating the controls.
+The variants were generated via optimal control, seeding the GRAPE algorithm with the initial pulse.}
+  \label{fig:pulseshapes}
+\end{figure}
+
+In this example we generated 10 candidate pulses using the GRAPE algorithm with a high convergence tolerance, with the intention that the optimizer would find solutions with some degree of noticeable coherent error.
+For each pulseshape, which enacts some unitary $U_i$, we performed an RPE-like experiment [REF RPE] where the $\sigma_y$ and $\sigma_z$ expectations values were measured at the end of a sequence of $n$ applications of $U_i$, where n ranged from 1 to 100, and each circuit was sampled 1000 times.
+The results are plotted in [REF SUBPLOTS OF \ref{fig:rebit}].
+Then, using the same optimization tool chain as in \ref{numerical}, we picked out the coeffients $p_i$ such that $p_i, U_i$ are a BCS, and performed the same experiment, but where for each shot of the experiment, we precompiled a different circuit.
+In particular, in our sampling procedure, circuit $U_{i_0}, U_{i_1}, ..., U_{i_{n-1}}$ occurs with probability $p_{i_0}p_{i_1}...p_{i_{n-1}}$.
+While in this example high fidelity, low coherent error controls can be produced [REFERENCE SUBPLOT OF \ref{fig:pulseshapes}], this demonstrates that this method can reduce coherent errors drastically.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=.75\columnwidth]{example.png}
+  \caption{An experimental implementation of our routine.
+We should include an array of images, maybe similar to this one, and then comment that in the image representing the BCS (above) that the noise is dominantly incoherent.
+The colors, ranging from purple to red, correspond to the depth into the sequence, where the darkest purple point is at the top of the rebit at $\ket{0}$.
+As the color becomes more red, the gate is applied more times, and consequently in the BCS example, moves the qubit's state vector closer to the maximally mixed state at the origin.
+The angle was computed by taking the arctangent of the $\sigma_y$ and $\sigma_z$ expectations, while the ther radius was computed by adding the two expectations in quadrature.}
+  \label{fig:rebit}
+\end{figure}
+
+\section{Conclusion}
+We have shown numerically and experimentally that drawing from a collection of implementations of a gate with the correct probabilties can reduce coherent error by an order of magnitude, while increasing incoherent error by a smaller amount, at virtually no cost to gate fidelity.
+We have demonstrated that these approximate controls can be generated through optimal control, and that the minimization problem is tractable.
+In addition, we have shown that it is possible to perform the routine on existing quantum hardware.
+Future directions for this work include moving the random gate selection from a precompilation step onto runtime FPGA logic, investigating other optimzation routines such as [GOAT, CRAB], and using more precise benchmarking routines such as GST [REF GST] to more quantitatively investigate the performance of these routines.
+The code used in this paper is available at [REF MY GITHUB].
+
 %It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe

### 2018-07-19 decorrelation/decorrelation.tex
updating, including references, cleaning up a bit

@@
 These routines all require some level of sophistication.
-In the case of \cite{Campbell2017}, the analysis assumes Solovay-Kitaev [CITATION]-like decomposition of unitaries, and treats Pauli and Clifford gates as being free to implement, which is far from the reality of modern quantum computers.
+In the case of \cite{Campbell2017}, the analysis assumes some algorithm for decomposing arbitray unitaries, and treats Pauli and Clifford gates as being free to implement in those decompositions, which is far from the reality of modern quantum computers.
 In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations.
@@
 
-For example, randomized benchmarking and tomography will report incorrect answers without any syndrome, [CITATION NEEDED], and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian.
+For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian.
 Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate.
-Unlike \cite{Ware2018}, \cite{Wallman2016}, and \citep{Campbell2017}, this routine can be implemented in the firmware of the quantum computer, and requires only an instruction for a random choice - no pre or post processing is required.
+Unlike \cite{Ware2018}, \cite{Wallman2016}, and \citep{Campbell2017}, this routine can be implemented natively in the control electronics of a quantum computer, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.
 
@@
 
-This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming.[CITATION NEEDED]
+This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming\cite{wright1999numerical}.
 
 Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
-Therefore we can view our approach as a regularization of this method, where we have imposed the condition that our final channel must arise from a BCS.[IS THIS ACTUALLY A REGULARIZATION?
-DOES IT IMPOSE SOME KIND OF SPARSITY] In doing so, we move from using a convex optimization routine to compute the diamond norm to needing to computing a sum.
+Our routine, on the other hand, uses a convex optimization routine to compute the diamond norm to needing to computing a sum.
 In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.
@@
 In this example we generated 10 candidate pulses using the GRAPE algorithm with a high convergence tolerance, with the intention that the optimizer would find solutions with some degree of noticeable coherent error.
-For each pulseshape, which enacts some unitary $U_i$, we performed an RPE-like experiment [REF RPE] where the $\sigma_y$ and $\sigma_z$ expectations values were measured at the end of a sequence of $n$ applications of $U_i$, where n ranged from 1 to 100, and each circuit was sampled 1000 times.
+For each pulseshape, which enacts some unitary $U_i$, we performed an RPE-like experiment\cite{Kimmel2015} where the $\sigma_y$ and $\sigma_z$ expectations values were measured at the end of a sequence of $n$ applications of $U_i$, where n ranged from 1 to 100, and each circuit was sampled 1000 times.
 The results are plotted in [REF SUBPLOTS OF \ref{fig:rebit}].
@@
 In addition, we have shown that it is possible to perform the routine on existing quantum hardware.
-Future directions for this work include moving the random gate selection from a precompilation step onto runtime FPGA logic, investigating other optimzation routines such as [GOAT, CRAB], and using more precise benchmarking routines such as GST [REF GST] to more quantitatively investigate the performance of these routines.
-The code used in this paper is available at [REF MY GITHUB].
+Future directions for this work include moving the random gate selection from a precompilation step onto runtime FPGA logic, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more precise benchmarking routines such as GST\cite{BlumeKohout2017} to more quantitatively investigate the performance of these routines.
+The code used in this paper is available at \cite{decorrelating_errors}.
 
+\section{Acknowledgements}
 %It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe

### 2018-07-23 decorrelation/decorrelation.tex
changin out a picture, changing text, adding in needcites

@@
 While convenient for simulation, these error models are often unphysical.
-Recent work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold.
+Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold.
 The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations.
@@
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}.
-These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates assumptions made by the models used in proofs.
+Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}\needcite.
+These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} , independance of errors \needcite , and even the magnitude of the noise \needcite .
+With these assumptions violated, promises about system performance cannot be made as easily.
 
-As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
-\begin{equation}\label{eq:0}
-  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
-\end{equation}
-where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process.
+%As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
+%\begin{equation}\label{eq:0}
+%  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
+%\end{equation}
+%where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process.
 In a standard nearest-neighbors topology, like those found in super-conducting qubit architectures, these terms might arise from an effective model where high-frequency degrees of freedom are intergrated out to yield high-weight operators.
@@
 
-Another assumption that is instrumental in proving many threshold theorems is Markovianity \cite{Kitaev1997}.
-There are many ways in which devices can behave in non-Markovian ways, and NISQ devices have already been shown to be subject to drift in controls, \cite{Kelly2018} and in general non-Markovian noise \cite{BlumeKohout2017}.
+As examples of these deviations from the theory, there are many ways in which devices can behave in non-Markovian ways, such as drift in controls, \cite{Kelly2018} and general non-Markovian noise \cite{BlumeKohout2017}.
+Even if a given system behaves in a Markovian way, many models make simplifying assumptions about the noise on that system - such as positing that it has a simple structure.
+Because of its  classical simulability, the channel that is often chosen is the Pauli channel \needcite .
+From there, one can ask what models can honestly be represented by using these simple models \needcite, but the fundamental problem with this approach is the pessimism that comes along with it.
+As we get closer to having real, usable systems, we want models that not only give us guarantees, but faithfully represent our system.
+
 Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise.
-Indeed, other have even implemented these routines natively in hardware \cite{Ware2018}.
-These routines all require some level of sophistication.
-In the case of \cite{Campbell2017}, the analysis assumes some algorithm for decomposing arbitray unitaries, and treats Pauli and Clifford gates as being free to implement in those decompositions, which is far from the reality of modern quantum computers.
+Given a process that is generated by a sequence of channels with some unknown, potentially channel depdenent error, the realization has been made that coherent error in the process can be averaged away into incoherent error, at the cost of an additional compilation step.
+Some of these routines have even been demonstrated experiementally \cite{Ware2018}, and been shown to reduce the off diagonal elements in the Pauli Liouville representation \needcite of the channels.
+
+A common feature of these routines is that take advantage of the fact that processes are generally enacted as a sequence of gates.
+By inserting a potentially expensive classical pre-compilation step, they can exploit sequence structure of a process to average away coherent error.
+In the case of \cite{Campbell2017}, the analysis takes the point of view of treating Pauli and Clifford gates as being free, which is out of reach of modern quantum computers\needcite.
 In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations.
-In general, this cannot be done efficiently for non-Clifford operations, and in addition, this introduces a linear-time precompilation overhead for shot of the circuit.
+In general, this cannot be done efficiently for non-Clifford operations, and there for this routine is demanding given the severe circuit depth constraints of modern quantum computers.\needcite
 
-To remedy these problems, we take a different approach and propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).
+To remedy these problems, we take a different approach at the gate synthesis level.
+We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).
 BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.
@@
 Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate.
-Unlike \cite{Ware2018}, \cite{Wallman2016}, and \citep{Campbell2017}, this routine can be implemented natively in the control electronics of a quantum computer, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.
+Unlike in \cite{Wallman2016, Campbell2017, Ware2018} this routine can be implemented natively in control electronics, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.
 
@@
 In particular one can show that:
-\begin{align}
+\begin{equation}\label{eq:update}
+  \begin{split}
 \frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
 \braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
-\end{align}
-
-In this paper we have modified the update step to use instead use approximately the following gradient:
-\begin{align}\label{quadrature}
-\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
-\end{align}
-with $p(\vec{\delta})$ Gaussian distributed.
-This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral approximately in this paper by using Gaussian quadrature.
-Doing this ensures that the family of controls produced by our routine perform moderately well over a range of stochastic errors.
+  \end{split}
+\end{equation}
 
@@
 \begin{equation}\label{eq:2}
-  H(t) = H_0 + \sum_{i=1}^n (c_i(t) + \delta_i(t))H_i
+  H(t) = \delta_0H_0 + \sum_{i=1}^n (1 + \delta_i)c_i(t)H_i
 \end{equation}
-for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$.
-Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time.
-Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
+for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
+Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequeny, and phase of the laser might drift over time.
+\needcite(Blueprint for a microwave trapped ion quantum computer) Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
 Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
+\needcite
+
+Given such a Hamiltonian, a threshold approximation fidelity $\mathcal{F}$, and a target gate $U_T$, we can use the technique described in \ref{GRAPE} to generate candidate pulse sequences that enact unitaries $U_i$ that approximate $U_T$, such that $Tr(U_T^{\dagger}U_i) \ge \mathcal{F}$.
+
+In this paper we have modified the update step in \ref{eq:update} to instead use approximately the following gradient:
+\begin{align}\label{quadrature}
+\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
+\end{align}
+with $p(\vec{\delta})$ Gaussian distributed.
+This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral in this paper by using Gaussian quadrature.\needcite Doing this ensures that the family of controls produced by our routine, $U_i$, perform moderately well over a range of control errors that might occur.
+
 \subsection{Channel Approximation}
@@
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
-Our routine, on the other hand, uses a convex optimization routine to compute the diamond norm to needing to computing a sum.
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires optimizing over the diamond norm, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
+Our routine, on the other hand, optimizes over an easy to compute sum.
 In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.
@@
 In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically.
-In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent ou gates in the vectorized superoperator representation, then:
+In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:
 
@@
   \begin{gathered}
-    \frac{1}{2}(X_{\pi + \epsilon} + \bar X_{\pi + \epsilon}) \\  
-    = (\sin^2{\frac{\pi + \epsilon}{2}}I + \cos^2{\frac{\pi + \epsilon}{2}}X)X \\
-    \approx ((1 - \epsilon^2)I + \epsilon^2X)X
+    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + \bar X^*_{\pi + \epsilon}\otimes \bar X_{\pi + \epsilon}) \\  
+    = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
+    \approx ((1 - \epsilon^2)I\otimes I + \epsilon^2X\otimes X)X\otimes X
   \end{gathered}
@@
 \end{equation}
-$\epsilon$ is a normally distributed random variable, centered at $0$ with standard deviation $.001$, corresponding to a time varying Stark shift on the qubit.
-$\delta$ is also a normally distributed random variable with the same parameters, and is meant to represent random fluctuations in the control electronics, such as diurnal variations resulting from temperature instability.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
-[ADD ANALYSIS OF PLOTS]
+where $\epsilon \sim \delta \sim \mathcal{N}(0, .001)$ We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
+In our simulation we chose an total evolution time of $T=\pi$, and a number of steps $N=100$, with a threshold infidelity of $1E-3$.
 \begin{figure*}
@@
 \begin{equation} \label{eq:2Qham}
-H = \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} + \sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j))
+\begin{split}
+H = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
+&+ \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} 
+\end{split}
 \end{equation}
 We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
-[ADD ANALYSIS OF PLOTS]
-%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
+In this simulation we again had a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
 \begin{figure*}[t]

### 2018-08-01 decorrelation/decorrelation.tex
updates

@@
 Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}\needcite.
-These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} , independance of errors \needcite , and even the magnitude of the noise \needcite .
-With these assumptions violated, promises about system performance cannot be made as easily.
+These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds\needcite, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors \needcite.
+With these assumptions violated, promises about system performance and correctness are difficult to make.
 
@@
 
-As examples of these deviations from the theory, there are many ways in which devices can behave in non-Markovian ways, such as drift in controls, \cite{Kelly2018} and general non-Markovian noise \cite{BlumeKohout2017}.
-Even if a given system behaves in a Markovian way, many models make simplifying assumptions about the noise on that system - such as positing that it has a simple structure.
-Because of its  classical simulability, the channel that is often chosen is the Pauli channel \needcite .
-From there, one can ask what models can honestly be represented by using these simple models \needcite, but the fundamental problem with this approach is the pessimism that comes along with it.
-As we get closer to having real, usable systems, we want models that not only give us guarantees, but faithfully represent our system.
+There are many ways in which devices can behave in non-Markovian ways,\cite{Kelly2018, BlumeKohout2017}, and even if a system is Markovian, many models make simplifying assumptions about the noise on that system - such as positing that it has a simple structure.
+For instance Pauli channels are often chosen\needcite due to their classical simulability\needcite.
+Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system by \textit{honestly} representing them \cite{Puzzuoli2014}.
+This approach is correct and rigorous, but scales poorly.
 
-Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to try to remove correlated noise.
-Given a process that is generated by a sequence of channels with some unknown, potentially channel depdenent error, the realization has been made that coherent error in the process can be averaged away into incoherent error, at the cost of an additional compilation step.
-Some of these routines have even been demonstrated experiementally \cite{Ware2018}, and been shown to reduce the off diagonal elements in the Pauli Liouville representation \needcite of the channels.
+Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to remove correlated noise.
+Given a process that is generated by a sequence of channels with some unknown, potentially channel depdenent error, coherent errors can be averaged away into incoherent error, at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
+Some of these routines have been demonstrated experimentally \cite{Ware2018}, and been shown to reduce the coherence of noise.
 
-A common feature of these routines is that take advantage of the fact that processes are generally enacted as a sequence of gates.
+%A common feature of these routines is that take advantage of the fact that processes are generally enacted as a sequence of gates.
 By inserting a potentially expensive classical pre-compilation step, they can exploit sequence structure of a process to average away coherent error.
@@
 
-To remedy these problems, we take a different approach at the gate synthesis level.
+In this Letter, we take a different approach to address these problems at the gate synthesis level.
 We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).
@@
 
-This techique can be used to turn coherent error into incoherent error and correlated error into uncorrelated error.
-The former gives the benefit that the error incurred from incoherent errors compound linearly, while coherent errors compound quadratically.
-The latter gives the benefit of reducing non-Markovian effects.
-This is a particularly useful property of BCSs, as diagnosing non-Markovianity in a gateset is challenging, but essential to perform reliable quantum computation.
-Many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.
+This techique can be used to turn coherent error into incoherent error therefore correlated error into uncorrelated error.
+One benefit of this is that non-Markovian noise will be made to be more Markovian.
+This is particularly useful because many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.
 
 For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian.
-Because BCSs change the error to a depolorizing channel, the correlations in the noise can be massively reduced, and the process can be made much closer to Markovian, at no real cost to the fidelity of the implemented gate.
-Unlike in \cite{Wallman2016, Campbell2017, Ware2018} this routine can be implemented natively in control electronics, and only requires that the onboard sequencer has the abiltiy to generate random numbers - no pre or post processing is required.
+Because BCSs change the error to a depolorizing channel, the correlations in the noise can be reduced, and the process can be made much closer to Markovian, and as we will show, this comes at no real cost to the fidelity of the implemented gate.
+Finally, unlike in \cite{Wallman2016, Campbell2017, Ware2018} we note that this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse shapes - no classical preprocessing or runtime frame tracking is required.
 
@@
 To demonstrate the realizability of this routine, we implemented it on a superconducting qubit, to calibrate an $RX(\frac{\pi}{2})$ pulse.
-The qubit being used had a 20.5 $\mu$s T1, and a 11.00 $\mu$s T2, and the pulse shapes being considered were 30ns long top hat pulse sequences, generated via a set-and-hold signal generator using the amplitudes shown in \ref{fig:pulseshapes}.
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=.75\columnwidth]{pulseshapes.png}
-  \caption{The pulseshapes used in the routine.
-The original pulse was generated by iteratively applying $RX(\frac{\pi}{2})$ pulses, fitting the resulting sinusoid, and updating the controls.
-The variants were generated via optimal control, seeding the GRAPE algorithm with the initial pulse.}
-  \label{fig:pulseshapes}
-\end{figure}
+The qubit being used had a 20.5 $\mu$s T1, and a 11.00 $\mu$s T2, and the pulse shapes being considered were 30ns long top hat pulse sequences, generated via a set-and-hold signal generator using the amplitudes shown in
 

### 2018-08-01 decorrelation/decorrelation.tex
changes

@@
 \usepackage{algpseudocode}
+\usepackage{subcaption}
 \hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
@@
 \begin{document}
+\tableofcontents
 \title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}
@@
 
-\section{GRAPE}\label{GRAPE}
+\section{A Simple Example}
+As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations.
+A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
+In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error.
+When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random.
+This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
+In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically.
+In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:
+
+\begin{equation}
+  \begin{gathered}
+    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + \bar X^*_{\pi + \epsilon}\otimes \bar X_{\pi + \epsilon}) \\  
+    = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
+    \approx ((1 - \epsilon^2)I\otimes I + \epsilon^2X\otimes X)X\otimes X
+  \end{gathered}
+\end{equation}
+
+Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $\bar X_\pi$  form a BCS, with $\alpha\approx\epsilon^2$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.75\columnwidth]{simple_example.png}
+  \caption{An example of a BCS. The red path is a $\pi$ pulse over-rotating clockwise, while the blue path is a $\pi$ pulse over-rotating counter-clockwise. The purple path is the average of the two.}
+  \label{fig:simple_example}
+\end{figure}
+\section{Optimal Control Problems}\label{ocp}
+\subsection{Random Gate Synthesis}
 Generating BCSs can be done in a variety of ways, using any quantum optimal control technique \cite{Caneva2011, Machnes2018} to find a family of controls.
@@
 
-\section{Optimal Control Problem}\label{ocp}
-\subsection{Random Gate Synthesis}
-To explore the utility of BCSs, we consider the following Hamiltonian:
-\begin{equation}\label{eq:2}
-  H(t) = \delta_0H_0 + \sum_{i=1}^n (1 + \delta_i)c_i(t)H_i
-\end{equation}
-for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
-Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequeny, and phase of the laser might drift over time.
-\needcite(Blueprint for a microwave trapped ion quantum computer) Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
-Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
-\needcite
-
 Given such a Hamiltonian, a threshold approximation fidelity $\mathcal{F}$, and a target gate $U_T$, we can use the technique described in \ref{GRAPE} to generate candidate pulse sequences that enact unitaries $U_i$ that approximate $U_T$, such that $Tr(U_T^{\dagger}U_i) \ge \mathcal{F}$.
@@
 
-\subsection{Channel Approximation}
+Concretely we consider a Hamiltonian of the following form:
+\begin{equation}\label{eq:2}
+  H(t) = \delta_0H_0 + \sum_{i=1}^n (1 + \delta_i)c_i(t)H_i
+\end{equation}
+for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
+Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequency, and phase of the laser might drift over time.\cite{Lekitsch2017} Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
+Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
+\needcite
+
+\subsection{BCS Approximation}
 After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}).
 To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate.
-If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations.
+If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations.
 In particular, we see that we can write a convex sum over these channels as:
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-  \includegraphics[width=.75\columnwidth]{simple_example.png}
-  \caption{An example of a BCS. The red path is a $\pi$ pulse over-rotating clockwise, while the blue path is a $\pi$ pulse over-rotating counter-clockwise. The purple path is the average of the two.}
-  \label{fig:simple_example}
-\end{figure}
+\begin{subfigure}[t]{.5\linewidth}
+\includegraphics[width=\textwidth]{1q0.png}
+\caption{This is one example of a 1D slice varying over one control.}
+\end{subfigure}%
+~
+\begin{subfigure}[t]{.5\linewidth}
+\includegraphics[width=\textwidth]{1q1.png}
+\caption{This is another example of a 1D slice varying over one control.}
+\end{subfigure}
+  \label{fig:1qnum}
+\end{figure*}
 
-\section{A Simple Example}
-As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations.
-A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
-In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error.
-When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random.
-This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
-In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically.
-In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:
-
-\begin{equation}
-  \begin{gathered}
-    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + \bar X^*_{\pi + \epsilon}\otimes \bar X_{\pi + \epsilon}) \\  
-    = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
-    \approx ((1 - \epsilon^2)I\otimes I + \epsilon^2X\otimes X)X\otimes X
-  \end{gathered}
-\end{equation}
-
-Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $\bar X_\pi$  form a BCS, with $\alpha\approx\epsilon^2$.
-
+\begin{figure*}
+\centering
+\begin{subfigure}[t]{.5\linewidth}
+\includegraphics[width=\textwidth]{control_dpn_all0.png}
+\caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
+\end{subfigure}%
+~
+\begin{subfigure}[t]{.5\linewidth}
+\includegraphics[width=\textwidth]{control_dpn_all2.png}
+\caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
+\end{subfigure}
+  \label{fig:2qnum}
+\end{figure*}
 \section{Numerical Results}\label{numerical}
@@
 In our simulation we chose an total evolution time of $T=\pi$, and a number of steps $N=100$, with a threshold infidelity of $1E-3$.
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{x2.png}
-\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}.
-A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
-B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
-\end{figure*}
 
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{y2.png}
-\caption{In the above we have used our method to produce a BCS for a $RY(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}.
-A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
-B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
-\end{figure*}
+The results can be seen in \ref{fig:1qnum}, where we have plotted each control as a function of one detuning value, fixing the others to zero.
+In the top half of each plot, we show the variation in the sum of the absolute valua of the off diagonal elements of the Pauli-Liouville Representation, while in the lower plot we see the variation in fidelity.
+While the controls were optimized by considering Gaussian noise with $\sigma=.001$ for each control, we have plotted the performance of the controls over a wider range to show more structure.
+We see over an order of magnitude improvement in the sum of the absolute values of the off-diagonal elements, while the fidelity remains above the specified target.
 
@@
 In this simulation we again had a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\textwidth]{2Q.png}
-\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}.
-A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$.
-B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
-\end{figure*}
+
+As in \ref{1qnum}, the results of these numerics can be visualized in \ref{fig2num}.
+Notably, even in the two qubit case where optimization over many controls becomes more difficult, we see a decrease in the magnitude of the off-diagonal terms by over an order of magnitude.
 
@@
 To demonstrate the realizability of this routine, we implemented it on a superconducting qubit, to calibrate an $RX(\frac{\pi}{2})$ pulse.
-The qubit being used had a 20.5 $\mu$s T1, and a 11.00 $\mu$s T2, and the pulse shapes being considered were 30ns long top hat pulse sequences, generated via a set-and-hold signal generator using the amplitudes shown in
+The qubit being used had a FILL IN $\mu$s T1, and a FILL IN $\mu$s T2.
 
-In this example we generated 10 candidate pulses using the GRAPE algorithm with a high convergence tolerance, with the intention that the optimizer would find solutions with some degree of noticeable coherent error.
-For each pulseshape, which enacts some unitary $U_i$, we performed an RPE-like experiment\cite{Kimmel2015} where the $\sigma_y$ and $\sigma_z$ expectations values were measured at the end of a sequence of $n$ applications of $U_i$, where n ranged from 1 to 100, and each circuit was sampled 1000 times.
-The results are plotted in [REF SUBPLOTS OF \ref{fig:rebit}].
-Then, using the same optimization tool chain as in \ref{numerical}, we picked out the coeffients $p_i$ such that $p_i, U_i$ are a BCS, and performed the same experiment, but where for each shot of the experiment, we precompiled a different circuit.
-In particular, in our sampling procedure, circuit $U_{i_0}, U_{i_1}, ..., U_{i_{n-1}}$ occurs with probability $p_{i_0}p_{i_1}...p_{i_{n-1}}$.
-While in this example high fidelity, low coherent error controls can be produced [REFERENCE SUBPLOT OF \ref{fig:pulseshapes}], this demonstrates that this method can reduce coherent errors drastically.
+In this example we intentionally over and under-calibrated four pulseshapes.
+For each of these pulseshapes, in addition to their BCS and the calibrated pulse, we then ran a randomized benchmarking experiment.\needcite The results are plotted in \ref{fig:rb}.
+In each case, our Clifford sequences were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+In the superconducting qubit architecture used, these gates are implemented using the same pulse envelope definition.
+It was shown in \cite{Ball2016} that for a particular error model, non-Markovian, or \textit{quasi-static}, noise can result in more general Gamma Distributed noise, while Markovian noise, such as depolarizing noise, should result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence depth.
+Our results are consistent with this, as demonstrated by the long tails in the four leftmost plots that vanish in the bottom right plot.
 
@@
   \centering
-  \includegraphics[width=.75\columnwidth]{example.png}
-  \caption{An experimental implementation of our routine.
-We should include an array of images, maybe similar to this one, and then comment that in the image representing the BCS (above) that the noise is dominantly incoherent.
-The colors, ranging from purple to red, correspond to the depth into the sequence, where the darkest purple point is at the top of the rebit at $\ket{0}$.
-As the color becomes more red, the gate is applied more times, and consequently in the BCS example, moves the qubit's state vector closer to the maximally mixed state at the origin.
-The angle was computed by taking the arctangent of the $\sigma_y$ and $\sigma_z$ expectations, while the ther radius was computed by adding the two expectations in quadrature.}
-  \label{fig:rebit}
+  \includegraphics[width=\columnwidth]{placeholder_rb.png}
+  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
+  \label{fig:rb}
 \end{figure}

### 2018-08-01 decorrelation/decorrelation.tex
one more pass through

@@
 \hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
-%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
-%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
-%   urlcolor{blue}}
-
 \newcommand{\tr}{{\rm Tr\thinspace}}
@@
 \author{Anthony Polloreno}
-% \email[Email: ]{apolloreno}
+\email[Email: ]{anthony@rigetti.com}
 \affiliation{Rigetti Computing, Berkeley, CA}
@@
 
-%As an example, many models assume that errors are local, however systems can have spatially correlated error on more than two qubits that arise from multi-qubit terms in the Hamiltonian, such as:
-%\begin{equation}\label{eq:0}
-%  H(t) = \sum_{n}\sum_{i}\sum_{j=x,y,z} a^{\textbf{i}}_{\textbf{j}}(t)(\sigma_{j_1}^{i_1}\otimes\sigma_{j_2}^{i_2}\otimes ... \otimes \sigma_{j_n}^{i_n})
-%\end{equation}
-%where $a^{\textbf{i}}_{\textbf{j}}$ is a stochastic process.
-In a standard nearest-neighbors topology, like those found in super-conducting qubit architectures, these terms might arise from an effective model where high-frequency degrees of freedom are intergrated out to yield high-weight operators.
-These noise channels are one way in which the assumptions used in proofs of thresholds may be violated.
-
-There are many ways in which devices can behave in non-Markovian ways,\cite{Kelly2018, BlumeKohout2017}, and even if a system is Markovian, many models make simplifying assumptions about the noise on that system - such as positing that it has a simple structure.
-For instance Pauli channels are often chosen\needcite due to their classical simulability\needcite.
+There are many ways in which device noise can be non-Markovian ways,\cite{Kelly2018, BlumeKohout2017}, even when the noise in a system is Markovian, many models make simplifying assumptions about the noise on that system.
+For instance Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite their unrealistic form.
 Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system by \textit{honestly} representing them \cite{Puzzuoli2014}.
@@
 Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to remove correlated noise.
-Given a process that is generated by a sequence of channels with some unknown, potentially channel depdenent error, coherent errors can be averaged away into incoherent error, at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
+Given a process that is generated by a sequence of channels with some unknown, potentially channel dependent error, coherent errors can be averaged away into incoherent error, at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
 Some of these routines have been demonstrated experimentally \cite{Ware2018}, and been shown to reduce the coherence of noise.
-
-%A common feature of these routines is that take advantage of the fact that processes are generally enacted as a sequence of gates.
-By inserting a potentially expensive classical pre-compilation step, they can exploit sequence structure of a process to average away coherent error.
-In the case of \cite{Campbell2017}, the analysis takes the point of view of treating Pauli and Clifford gates as being free, which is out of reach of modern quantum computers\needcite.
-In \cite{Wallman2016} and the implementation in \cite{Ware2018}, the random frames are implemented in each sequence by precompiling the inserted Pauli frame rotations with the Clifford operations.
-In general, this cannot be done efficiently for non-Clifford operations, and there for this routine is demanding given the severe circuit depth constraints of modern quantum computers.\needcite
 
@@
 We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).
-BCSs are families of control solutions that all approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.
+BCSs are families of control solutions that approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.
 That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}.
@@
 Where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$.
-(For the rest of this paper, we will refer to them just as depolarizing channels.) Such a channel is defined as:
+(For the rest of this paper, we will refer to them as just depolarizing channels.) Such a channel is defined as:
 \begin{equation}\label{eq:2}
@@
 
-This techique can be used to turn coherent error into incoherent error therefore correlated error into uncorrelated error.
-One benefit of this is that non-Markovian noise will be made to be more Markovian.
-This is particularly useful because many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.
+This techique can be used to turn coherent error into incoherent errorr, correlated error into uncorrelated error, and therefore non-Markovian noise into more Markovian noise.
+This is particularly, since many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.
 
 For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian.
-Because BCSs change the error to a depolorizing channel, the correlations in the noise can be reduced, and the process can be made much closer to Markovian, and as we will show, this comes at no real cost to the fidelity of the implemented gate.
-Finally, unlike in \cite{Wallman2016, Campbell2017, Ware2018} we note that this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse shapes - no classical preprocessing or runtime frame tracking is required.
+Because BCSs can make error channels look more depolarizing, the correlations in the noise can be reduced, and the process can be made much closer to Markovian.
+In addition, we will show that this comes at no real cost to the fidelity of the implemented gate.
+Finally, unlike in \cite{Wallman2016, Campbell2017, Ware2018} this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse shapes - no classical preprocessing or runtime frame tracking is required.
 
@@
   \includegraphics[width=.75\columnwidth]{simple_example.png}
-  \caption{An example of a BCS. The red path is a $\pi$ pulse over-rotating clockwise, while the blue path is a $\pi$ pulse over-rotating counter-clockwise. The purple path is the average of the two.}
+  \caption{THIS FIGURE SHOULD BE REPLACED}
   \label{fig:simple_example}
@@
 \begin{equation}\label{eq:3}
-  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}u_{ij}H_{ij}\}
+  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}u_{ij}H_{j}\}
 \end{equation}
-Then, to measure the simularity of our approxiate unitary $U_n$, and our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U_n\}$.
+Then, to measure the simularity of our approxiate unitary $U_n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U_n\}$.
 
@@
     \For{$1 \leq i \leq n$}
-    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}u_{ij}H_i)\}$
+    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}u_{ij}H_j)\}$
     \EndFor
-    \State $U \rightarrow \prod_1^nU_i$
+    \State $U \rightarrow \prod_{i=1}^nU_i$
     \EndWhile 
@@
 
-Given such a Hamiltonian, a threshold approximation fidelity $\mathcal{F}$, and a target gate $U_T$, we can use the technique described in \ref{GRAPE} to generate candidate pulse sequences that enact unitaries $U_i$ that approximate $U_T$, such that $Tr(U_T^{\dagger}U_i) \ge \mathcal{F}$.
-
-In this paper we have modified the update step in \ref{eq:update} to instead use approximately the following gradient:
+In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we have modified the update step in \ref{eq:update} to instead use approximately the following gradient:
 \begin{align}\label{quadrature}
@@
 Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequency, and phase of the laser might drift over time.\cite{Lekitsch2017} Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
-Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
+Examples of shared noise sources include $RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
 \needcite
@@
   \begin{split}
-    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
+    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{\substack{i,j \\ i\neq j}}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
     &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
@@
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires optimizing over the diamond norm, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
-Our routine, on the other hand, optimizes over an easy to compute sum.
-In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates in sections \ref{1Q Gates} and \ref{2Q Gates}.
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires optimizing over the diamond norm, and in particular does not have the restriction that the optimal channel be decomposed into a given family of controls.
+Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined in terms of our collection of pulseshapes.
 

### 2018-08-02 decorrelation/decorrelation.tex
more references and changes

@@
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}\needcite.
-These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds\needcite, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors \needcite.
+Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}.
+These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\needcite.
 With these assumptions violated, promises about system performance and correctness are difficult to make.
 
-There are many ways in which device noise can be non-Markovian ways,\cite{Kelly2018, BlumeKohout2017}, even when the noise in a system is Markovian, many models make simplifying assumptions about the noise on that system.
-For instance Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite their unrealistic form.
+There are many ways in which device noise can fail to be Markovian,\cite{Kelly2018, BlumeKohout2017}, and even when the noise \textit{is} Markovian, many models make simplifying assumptions about the structure of the noise.
+For instance, Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite their unrealistic form.
 Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system by \textit{honestly} representing them \cite{Puzzuoli2014}.
@@
 
-Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit composition to remove correlated noise.
-Given a process that is generated by a sequence of channels with some unknown, potentially channel dependent error, coherent errors can be averaged away into incoherent error, at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
-Some of these routines have been demonstrated experimentally \cite{Ware2018}, and been shown to reduce the coherence of noise.
+Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit compilation to remove correlated noise.
+Given a process that is generated by a sequence of channels with some unknown and potentially channel dependent error, coherent errors can be averaged away into incoherent error.
+Indeed, some of these routines have been demonstrated experimentally \cite{Ware2018}, and been shown to reduce the coherence of noise.
+However, this benefit comes at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
 
@@
 In this example we intentionally over and under-calibrated four pulseshapes.
-For each of these pulseshapes, in addition to their BCS and the calibrated pulse, we then ran a randomized benchmarking experiment.\needcite The results are plotted in \ref{fig:rb}.
+For each of these pulseshapes, in addition to their BCS and the calibrated pulse, we then ran a randomized benchmarking experiment.\cite{Magesan2011} The results are plotted in \ref{fig:rb}.
 In each case, our Clifford sequences were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Work}
 We have shown numerically and experimentally that drawing from a collection of implementations of a gate with the correct probabilties can reduce coherent error by an order of magnitude, while increasing incoherent error by a smaller amount, at virtually no cost to gate fidelity.
 We have demonstrated that these approximate controls can be generated through optimal control, and that the minimization problem is tractable.
-In addition, we have shown that it is possible to perform the routine on existing quantum hardware.
-Future directions for this work include moving the random gate selection from a precompilation step onto runtime FPGA logic, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more precise benchmarking routines such as GST\cite{BlumeKohout2017} to more quantitatively investigate the performance of these routines.
-The code used in this paper is available at \cite{decorrelating_errors}.
+In addition, we have shown that it is possible to perform the routine on existing hardware.
+The code used to generate the numerical results in this paper is available at \cite{decorrelating_errors}.
+
+Future directions for this work include moving the random gate selection from a precompilation step to a runtime logic, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more precise benchmarking routines such as GST\cite{BlumeKohout2017} to more quantitatively investigate the performance of these routines.
+
+In addition, the numerical work in the paper assumed access to a model of the system.
+In general, an experimenter may not have a model readily available to describe the system, maybe due to on-chip crosstalk, or even if they do have access to such a model, it might be computationally intractable to simulate.
+In both of these situations, numerical generation of candidate pulseshapes and the minimization become infeasible.
+One approach would to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to minimize the magnitude of off-diagonal terms as measured by simple pulse sequences that amplify those elements of the process matrix.\needcite
 
 \section{Acknowledgements}
-%It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe
 
-%$$ \epsilon, \delta \midtilde \sim \mathcal{N}(0, .001) $$
-%$$\epsilon_0, \epsilon_1, \delta_0, \delta_1 \midtilde \sim \mathcal{N}(0, .001)$$
 \bibliography{decorrelation.bib}

### 2018-08-06 data/raw_data/GRAPE.py
adding in raw data with notebook

@@ -1,0 +1,435 @@
+import itertools
+import numpy as np
+import scipy
+import scipy.optimize as optimize
+import matplotlib.pyplot as plt
+from numpy.polynomial.hermite import hermgauss
+import multiprocessing
+from functools import reduce
+from mpi4py import MPI
+
+COMM = MPI.COMM_WORLD
+
+
+def split(container, count):
+    """
+    Simple function splitting a container into equal length chunks.
+    Order is not preserved but this is potentially an advantage depending on
+    the use case.
+    """
+    return [container[_i::count] for _i in range(count)]
+
+
+def adjoint(operator):
+    """
+    Computes the adjoint of a given matrix.
+
+    :param numpy.array operator: Array to compute the adjoint of.
+    :return: The adjoint of operator.
+    :rtype: numpy.array
+    """
+    return np.conj(operator).T
+
+
+def control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt):
+    """
+    Given an controllable and a non-controllable hamiltonian, with controls and the time step size,
+    computes the unitaries that give the time evolution. e.g.
+
+    control_unitaries(I, [X], [[0],[1],[0],[1]], np.pi)
+    [I, X, I, X]
+
+    :param numpy.array ambient_hamiltonian: A square 2D array, corresponding to the uncontrollable
+     part of the system hamiltonian.
+    :param list control_hamiltonians: A list of square 2D numpy.arrays, corresponding to the
+     controllable terms in the hamiltonian. This should be as long as the second dimension of
+     controls.
+    :param numpy.array controls: A 2D numpy.array, whose rows represent time steps, and whose
+     jth column corresponds to the control amplitude for the jth element of control_hamiltonians.
+    :param float dt: The time to evolve each row of controls for.
+    :return: The list of unitaries corresponding to the discretized evolution of the system.
+    :rtype: list
+    """
+    if len(controls.shape) == 1:
+        controls = controls.reshape(-1, len(control_hamiltonians))
+    unitaries = []
+    for row in controls:
+        step_hamiltonian = [control * control_hamiltonians[i] for i, control in enumerate(row)]
+        evolution = scipy.linalg.expm(
+            -1.j * dt * (np.sum(ambient_hamiltonian, axis=0) + np.sum(step_hamiltonian, axis=0)))
+        unitaries.append(evolution)
+    return unitaries
+
+
+def grape_perf(ambient_hamiltonian, control_hamiltonians, controls, dt, target_operator):
+    """
[…]

### 2018-08-06 data/raw_data/pauli_channel_approximation.py

@@ -1,0 +1,863 @@
+import numpy as np
+import matplotlib.pyplot as plt
+plt.switch_backend('agg')
+from GRAPE import GRAPE, control_unitaries, adjoint, average_over_noise
+import numpy as np
+from scipy.optimize import minimize
+import scipy
+import dill
+import itertools
+from copy import deepcopy
+from functools import reduce
+import subprocess
+import os.path
+import multiprocessing
+from mpi4py import MPI
+import sys
+import time as timemod
+COMM = MPI.COMM_WORLD
+#Note ambient hamiltonian as been changed to a list of hamiltonians, but the name remains unchanged.
+
+I = np.eye(2)
+X = np.array([[0, 1], [1, 0]])
+Y = np.array([[0, -1.j], [1.j, 0]])
+Z = np.array([[1, 0], [0, -1]])
+PAULIS = [I, X, Y, Z]
+
+from itertools import product
+def generate_indices(num_points, order_desired):
+    num_indices = len(order_desired)
+    tuples = product(range(num_points), repeat=num_indices)
+    indices = [sum([num_points**(num_indices - 1 - order_desired[i]) * t[i] for i in range(num_indices)]) for t in tuples]
+    return indices
+
+def error_unitary(unitary, target):
+    """
+    Constructs the superoperator for the error unitary corresponding propagating forward by target,
+     and back by unitary.
+
+    :param np.array unitary: Control unitary realized in the computational basis.
+    :param np.array target: The desired unitary in the computational basis.
+    :return: The superoperator corresponding to the unitary postrotational error.
+    :rtype: numpy.array
+    """
+    error = adjoint(unitary).dot(target)
+    return np.kron(np.conj(error), error)
+
+
+def off_diagonal_projection(sop):
+    """
+    Computes a quantity proportional to the sum of the magnitudes of terms corresponding to non-stochastic evolution.
+
+    :param numpy.ndarry sop: Representation our operator as a superoperator, e.g. operating on vectorized density
+     matrices.
+    """
+    basis = PAULIS
+    for _ in range(int(np.log2(sop.shape[0]) / 2.0) - 1):
+        basis = [np.kron(base, pauli) for pauli in PAULIS for base in basis]
+    off_diagonal = 0
+    for i, base1 in enumerate(basis):
+        for j, base2 in enumerate(basis):
+            if i != j:
[…]

### 2018-08-08 decorrelation/decorrelation.tex
cleaned up figures and file structure
A few paper updates

@@
 \usepackage{algpseudocode}
-\usepackage{subcaption}
-\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
+\usepackage{graphicx}
+% \usepackage[justification=justified,font=small]{caption}
+\graphicspath{{./figures/}}
+\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
 \newcommand{\tr}{{\rm Tr\thinspace}}
@@
 \begin{document}
-\tableofcontents
+% \tableofcontents
 \title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}
@@
 \author{Kevin C. Young}
-\email[Corresponding author: ]{kyoung@sandia.gov}
+% \email[Corresponding author: ]{kyoung@sandia.gov}
 \affiliation{Sandia National Laboratories, Livermore, CA}
@@
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006}.
-These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\needcite.
+Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006} \kcy{more recent citations}.
+These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\needcite.
 With these assumptions violated, promises about system performance and correctness are difficult to make.
@@
 Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system by \textit{honestly} representing them \cite{Puzzuoli2014}.
-This approach is correct and rigorous, but scales poorly.
+This approach is correct and rigorous, but produces overly-pessimistic bounds on device performance.
 
-Other authors have tried to address these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit compilation to remove correlated noise.
+Other authors have addressed these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit compilation to remove correlated noise.
 Given a process that is generated by a sequence of channels with some unknown and potentially channel dependent error, coherent errors can be averaged away into incoherent error.
@@
 However, this benefit comes at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{simple_example.pdf}
+  \caption{An example of a balanced control solution.
+Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
+Each time the gate is used, one of these implementations is chosen at random.
+The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
+  \label{fig:simple_example}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=.75\columnwidth]{simple_example.png}
-  \caption{THIS FIGURE SHOULD BE REPLACED}
-  \label{fig:simple_example}
-\end{figure}
 \section{Optimal Control Problems}\label{ocp}
@@
 
-\begin{figure*}
-\centering
-\begin{subfigure}[t]{.5\linewidth}
-\includegraphics[width=\textwidth]{1q0.png}
-\caption{This is one example of a 1D slice varying over one control.}
-\end{subfigure}%
-~
-\begin{subfigure}[t]{.5\linewidth}
-\includegraphics[width=\textwidth]{1q1.png}
-\caption{This is another example of a 1D slice varying over one control.}
-\end{subfigure}
-  \label{fig:1qnum}
-\end{figure*}
+% \begin{figure*}
+% \centering
+% \begin{subfigure}[t]{.5\linewidth}
+% \includegraphics[width=\textwidth]{1q0.png}
+% \caption{This is one example of a 1D slice varying over one control.}
+% \end{subfigure}%
+% ~
+% \begin{subfigure}[t]{.5\linewidth}
+% \includegraphics[width=\textwidth]{1q1.png}
+% \caption{This is another example of a 1D slice varying over one control.}
+% \end{subfigure}
+%   \label{fig:1qnum}
+% \end{figure*}
 
-\begin{figure*}
-\centering
-\begin{subfigure}[t]{.5\linewidth}
-\includegraphics[width=\textwidth]{control_dpn_all0.png}
-\caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
-\end{subfigure}%
-~
-\begin{subfigure}[t]{.5\linewidth}
-\includegraphics[width=\textwidth]{control_dpn_all2.png}
-\caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
-\end{subfigure}
-  \label{fig:2qnum}
-\end{figure*}
+% \begin{figure*}
+% \centering
+% \begin{subfigure}[t]{.5\linewidth}
+% \includegraphics[width=\textwidth]{control_dpn_all0.png}
+% \caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
+% \end{subfigure}%
+% ~
+% \begin{subfigure}[t]{.5\linewidth}
+% \includegraphics[width=\textwidth]{control_dpn_all2.png}
+% \caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
+% \end{subfigure}
+%   \label{fig:2qnum}
+% \end{figure*}
 \section{Numerical Results}\label{numerical}
@@
 \section{Acknowledgements}
-
+Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S.
+Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
 \bibliography{decorrelation.bib}

### 2018-09-20 decorrelation/decorrelation.tex
RB Plots Updated
some changes to the text

@@
 \newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
-
+\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
 %-------------Header begins here----------------------------------------
@@
 The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations.
-We propose to introduce similar methods to effect the spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
+We propose to introduce similar methods at the gate synthesis level to effect the $\amp{Why are we calling this spatial?}$spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
 \end{abstract}
@@
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006} \kcy{more recent citations}.
+Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006} $\kcy{more recent citations}$.
 These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\needcite.
@@
 
-There are many ways in which device noise can fail to be Markovian,\cite{Kelly2018, BlumeKohout2017}, and even when the noise \textit{is} Markovian, many models make simplifying assumptions about the structure of the noise.
-For instance, Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite their unrealistic form.
-Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system by \textit{honestly} representing them \cite{Puzzuoli2014}.
+Moreover, there are many ways in which device noise can fail to be Markovian, \cite{Kelly2018, BlumeKohout2017, Klimov2018}, and even when the noise \textit{is} Markovian, many models make simplifying assumptions about the structure of the noise.
+For instance, Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite most noise sources being poorly approximated by Pauli channels.\needcite.
+Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system\cite{Puzzuoli2014}.
 This approach is correct and rigorous, but produces overly-pessimistic bounds on device performance.
 
-Other authors have addressed these problems \cite{Wallman2016, Campbell2017, Heim2016} by using circuit compilation to remove correlated noise.
-Given a process that is generated by a sequence of channels with some unknown and potentially channel dependent error, coherent errors can be averaged away into incoherent error.
-Indeed, some of these routines have been demonstrated experimentally \cite{Ware2018}, and been shown to reduce the coherence of noise.
-However, this benefit comes at the cost of additional compilation steps, which may in general increase circuit depth and require more sophisticated classical preprocessing.
+Some characterization routines take a different approach, and assume that the noise is well-behaved.
+For example, randomized benchmarking and tomography will simple report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian.
+
+Other authors have considering the problem of coherent error at the logical gate level, considering over rotations that might arise from gate approximation \cite{Campbell2017, 1612.01011}, and others have considered methods of \textit{twirling} error, such that it turns into a Pauli channel through random compilation methods\cite{Wallman2016, Ware2018}.
 
@@
 
-In this Letter, we take a different approach to address these problems at the gate synthesis level.
-We propose to inject additional decorrelating randomness into the system through the use of \emph{balanced control solutions} (BCSs).
+In this Letter, we take a different approach to address the issues of coherent and non-Markovian error.
+We propose to inject additional decorrelating randomness into the system during gate synthesis through the use of \emph{balanced control solutions} (BCSs).
 BCSs are families of control solutions that approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.
@@
 
-This techique can be used to turn coherent error into incoherent errorr, correlated error into uncorrelated error, and therefore non-Markovian noise into more Markovian noise.
-This is particularly, since many routines exist that can assess the quality of a gateset, however in the presence of non-Markovianity most of them become unreliable.
-
-For example, randomized benchmarking and tomography will report incorrect answers without any syndrome \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian, but will fail to diagnose in what way it was non-Markovian.
-Because BCSs can make error channels look more depolarizing, the correlations in the noise can be reduced, and the process can be made much closer to Markovian.
-In addition, we will show that this comes at no real cost to the fidelity of the implemented gate.
-Finally, unlike in \cite{Wallman2016, Campbell2017, Ware2018} this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse shapes - no classical preprocessing or runtime frame tracking is required.
+Because BCSs produce error channels that are depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g.
+drift.
+In addition, we will give numerical results showing that the fidelity of the new approximation to $U$ is not much worse than the fidelities of the constituent controls.
 
@@
 \section{Experimental Results}\label{experimental}
-To demonstrate the realizability of this routine, we implemented it on a superconducting qubit, to calibrate an $RX(\frac{\pi}{2})$ pulse.
-The qubit being used had a FILL IN $\mu$s T1, and a FILL IN $\mu$s T2.
-
-In this example we intentionally over and under-calibrated four pulseshapes.
-For each of these pulseshapes, in addition to their BCS and the calibrated pulse, we then ran a randomized benchmarking experiment.\cite{Magesan2011} The results are plotted in \ref{fig:rb}.
+Here we present experimental results from implementing our routine on a superconducting transmon qubit.
+In this experiment we intentionally over and under-calibrated four pulses enacting approximate RX($\frac{\pi}{2})$) rotations.
+For each instatiation of the rotation, in addition to the BCS for the four pulses and a calibrated pulse, we ran a randomized benchmarking experiment.\cite{Magesan2011} The results are plotted in \ref{fig:rb}.
 In each case, our Clifford sequences were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In the superconducting qubit architecture used, these gates are implemented using the same pulse envelope definition.
-It was shown in \cite{Ball2016} that for a particular error model, non-Markovian, or \textit{quasi-static}, noise can result in more general Gamma Distributed noise, while Markovian noise, such as depolarizing noise, should result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence depth.
-Our results are consistent with this, as demonstrated by the long tails in the four leftmost plots that vanish in the bottom right plot.
+In the superconducting qubit architecture used, these gates are implemented using the same pulse envelope definition, and are therefore subject to the same miscalibration errors.
+It was shown in \cite{Ball2016} that for particular non-Markovian (\textit{quasi-static}) error models, noise will manifest as gamma distributed points for each sequence length.
+On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
+Our results are consistent with this $\amp{explain how, given new plot}$
 
@@
 \section{Conclusion and Future Work}
-We have shown numerically and experimentally that drawing from a collection of implementations of a gate with the correct probabilties can reduce coherent error by an order of magnitude, while increasing incoherent error by a smaller amount, at virtually no cost to gate fidelity.
+We have shown both numerically and experimentally that drawing from a collection of different synthesized version of a gate with  optimized probabilties can reduce coherent error by at least an order of magnitude, at virtually no cost to gate fidelity.
 We have demonstrated that these approximate controls can be generated through optimal control, and that the minimization problem is tractable.
 In addition, we have shown that it is possible to perform the routine on existing hardware.
-The code used to generate the numerical results in this paper is available at \cite{decorrelating_errors}.
+We note that unlike in \cite{Wallman2016, Campbell2017, Ware2018} this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse definitions.
+In particular, no classical preprocessing or runtime frame tracking is required.
 
@@
 
-In addition, the numerical work in the paper assumed access to a model of the system.
-In general, an experimenter may not have a model readily available to describe the system, maybe due to on-chip crosstalk, or even if they do have access to such a model, it might be computationally intractable to simulate.
+In addition, the numerical work in the paper assumes access to a model of the system.
+In general, an experimentalist may not have a model readily available to describe the system, e.g.
+in the presence of unknown on-chip crosstalk.
+Even if they do have access to such a model, it might be computationally intractable to simulate.
 In both of these situations, numerical generation of candidate pulseshapes and the minimization become infeasible.
-One approach would to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to minimize the magnitude of off-diagonal terms as measured by simple pulse sequences that amplify those elements of the process matrix.\needcite
+One approach would then be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to minimize the magnitude of off-diagonal terms as measured by simple pulse sequences that amplify those elements of the process matrix.\needcite The code used to generate the numerical results in this paper is available at \cite{decorrelating_errors}.
 

### 2018-09-22 decorrelation/decorrelation.tex
Updating Notebook with diamond norm computations, and updating the tex document a  bit

@@
 The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations.
-We propose to introduce similar methods at the gate synthesis level to effect the $\amp{Why are we calling this spatial?}$spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
+We propose to introduce similar methods at the gate synthesis level to effect the temporal decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
 \end{abstract}
@@
 \end{equation}
-with $p_i$ summing to one.
-This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel.
-The task of constructing the BCSs will fall to optimal control.
+with $p_i$ summing to one. This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel.
 
-Because BCSs produce error channels that are depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g.
+One property of BCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BCS to $U_T$ is also no larger than $\epsilon^2$.
+This follows from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}.
+This tells us that we can lower bound the worst case performance of a BCS, and because  depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g.
 drift.
-In addition, we will give numerical results showing that the fidelity of the new approximation to $U$ is not much worse than the fidelities of the constituent controls.
+In this paper, the task of constructing the BCSs will fall to optimal control.
+We will give numerical results showing that the fidelity of the new approximation to $U_T$ is of the same order as the constituent controls.
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{placeholder_rb.png}
+  \includegraphics[width=\columnwidth]{rb_data.pdf}
   \caption{Randomized benchmarking experiments ran using different pulse definitions.

### 2018-09-24 decorrelation/decorrelation.tex
updates to the paper

--- 2018-09-20 decorrelation/decorrelation.tex
@@
 \newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
+\setlength{\jot}{10pt}
 %-------------Header begins here----------------------------------------
@@
 % \tableofcontents
-\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}
+\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis - A BOCS of Control Solutions}
 
@@
 While convenient for simulation, these error models are often unphysical.
-Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold.
-The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations.
-We propose to introduce similar methods at the gate synthesis level to effect the $\amp{Why are we calling this spatial?}$spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
+Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial and temporal correlation, provided the correlation is sufficiently weak and decays sufficiently quickly, but at the cost of a significantly lower threshold.
+The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing noise correlations.
+We propose to introduce similar methods at the gate synthesis level to effect the decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
+We show numerically and experimentally on a superconducting qubit that these methods can reduce the magnitude of the diamond norm of the error by at least an order of magnitude.
 \end{abstract}
@@
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006} $\kcy{more recent citations}$.
-These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\needcite.
-With these assumptions violated, promises about system performance and correctness are difficult to make.
+Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006, 1609.00510, https://doi.org/10.7907/z96m34sc, Kubica2018, Wang2003, Campbell2017}.
+These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\cite{Knill1998}.
+With these assumptions violated, many properties of system performance and correctness can no longer be guaranteed.
 
-Moreover, there are many ways in which device noise can fail to be Markovian, \cite{Kelly2018, BlumeKohout2017, Klimov2018}, and even when the noise \textit{is} Markovian, many models make simplifying assumptions about the structure of the noise.
-For instance, Pauli channels are often used to model systems\needcite due to their classical simulability\needcite, despite most noise sources being poorly approximated by Pauli channels.\needcite.
-Some authors have then taken the approach of using these easily-understood models to upper bound the error in a real system\cite{Puzzuoli2014}.
+To make matters worse, the ways in which a quantum computer can fail to meet these assumptions are manifold\cite{Kelly2018, BlumeKohout2017, Klimov2018}, and even when the noise is Markovian, many models and existing work make strong simplifying assumptions about the structure of the noise.
+As an example, Pauli channels are often used to model systems due to their classical simulability\cite{quant-ph/9807006}, even in the absence of physical motivation\cite{Aliferis2007, Knill2005, Wang2011, DuclosCianci2010, Wootton2012, Bombin2012, Puzzuoli2014, aliferis2008accuracy}.
+Because of this, a common approach is to attempt to use those thresholds to give a loose lower bound for thresholds with lower noise\cite{Puzzuoli2014}.
 This approach is correct and rigorous, but produces overly-pessimistic bounds on device performance.
 
-Some characterization routines take a different approach, and assume that the noise is well-behaved.
-For example, randomized benchmarking and tomography will simple report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013}, and gateset tomography will report that the gateset failed to be Markovian.
+Relatedly, many characterization routines assume that the noise is well-behaved so that they can make non-trivial assertions about performance.
+If these assumptions are violated, the utility of many of these algorithms is drastically reduced.
+For example, randomized benchmarking and tomography will report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013}.
+Slightly more helpful, gate-set tomography will report that the gateset failed to be Markovian, however figuring out how to bring it back to the space of the Markovianity can be challenging.
 
-Other authors have considering the problem of coherent error at the logical gate level, considering over rotations that might arise from gate approximation \cite{Campbell2017, 1612.01011}, and others have considered methods of \textit{twirling} error, such that it turns into a Pauli channel through random compilation methods\cite{Wallman2016, Ware2018}.
+Many authors have approached these problems at varying levels of abstraction, each with their own benefits and short-comings.
+At the level of unitary synthesis, authors have considered randomizing over errors that might arise from gate approximations like Solovay-Kitaev \cite{Campbell2017, 1612.01011}.
+While this affords the ability to prove theorems that guarantee quadratic improvements to performance, they do not offer routines which are accessible and implementable with current coherence times.
+At the level of compilation, Frame Randomization\cite{Wallman2016, Ware2018}can be used to average over noise by \textit{twirling} error over an appropriately selected unitary 2-design.\cite{roy2009unitary} This has the advantage of being implementable\cite{Ware2018}, but it can require intensive use of classical resources, such as precompilation and generation of many waveform variants, and becomes more difficult when the gates being used are not in the Clifford group, as is the case in various quantum computing architectures.
+The general theme of these results is that of randomized decoupling\cite{Viola2005, Viola}.
+By introducing classical randomness into quantum computations, both coherent and non-Markovian can be transformed to incoherent, independent, Markovian noise, to varying degrees.
+In this paper, we explore a different method of solving these problems.
+We propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{balanced optimal control solutions} (BOCSs).
 
@@
 
-In this Letter, we take a different approach to address the issues of coherent and non-Markovian error.
-We propose to inject additional decorrelating randomness into the system during gate synthesis through the use of \emph{balanced control solutions} (BCSs).
-BCSs are families of control solutions that approximate the same target gate, but with balanced errors for any given instance of the noise Hamiltonian.
-That is, for a target gate, $U_T$, we seek a family of control solutions, $c_i(t)$, each implementing an approximation $U_i$ to the target gate, such that the family of unitary approximations is \emph{balanced}.
+\section{Theory}
+ BOCSs are families of control solutions, $c_i(t)$, where each member of the family approximates the same target gate with slightly different errors, for any given instance a noise Hamiltonian.
+That is, for a target unitary operator $U_T$, we seek a family of approximating $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \delta)}$ to the target gate, such that the family of unitary approximations is \emph{balanced}.
 A balanced family is one which satisfies, for some small $\alpha$,
@@
 
-Where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$.
+where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$.
 (For the rest of this paper, we will refer to them as just depolarizing channels.) Such a channel is defined as:
@@
 with $p_i$ summing to one.
-This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel.
-The task of constructing the BCSs will fall to optimal control.
+This means that a for a family of controls that are a BOCS, there exists a weighting $p_i$, such that when the unitary approximations are averaged over with that weighting, they implement the target unitary followed by a depolarizing channel.
 
-Because BCSs produce error channels that are depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g.
-drift.
-In addition, we will give numerical results showing that the fidelity of the new approximation to $U$ is not much worse than the fidelities of the constituent controls.
+Thus, one property of BOCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BOCS to $U_T$ is also no larger than $\epsilon^2$.
+This follows from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, and tells us that we can lower bound the worst case performance of a BOCS by the square of the error on each member of the BOCS, and linearly in the error of the weighted average.
+Because a set of parameters always exist that result in quadratically smaller error, it is then clear that in priniple BOCSs can always quadratically decrease the error in our approximation (in diamond norm).
+Moreover, in the setting where our system's performance is non-Markovian, e.g.
+drift, optimizing our BOCSs over a range of control parameters can reduce the non-Markovianity of the noise.
+As the name suggests, the task of generating BOCSs in this paper will fall to optimal control.
 
 \section{A Simple Example}
-As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations.
-A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
-In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error.
-When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random.
+As a somewhat trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
+A BOCS may consist of an $X_\pi$ pulse, as well as an $X_{-\pi}$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
+In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $X_{-\pi}$ pulse will result in an \emph{under}-rotation error.
+When it comes time to perform the target gate in a quantum circuit, one member of the BOCS is chosen uniformly at random.
 This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
-In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically.
-In particular, if we choose the weights in \ref{eq:1} such that $\omega_i=1$, and we choose to represent our gates in the vectorized superoperator representation, then:
+In this simple example, we can analytically find a solution to Equation \ref{eq:1}.
+Specifically, by choosing weights $\omega_i=1$, we see:
 
@@
   \begin{gathered}
-    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + \bar X^*_{\pi + \epsilon}\otimes \bar X_{\pi + \epsilon}) \\
+    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + X^*_{-(\pi + \epsilon)}\otimes X_{-(\pi + \epsilon})) \\
     = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
-    \approx ((1 - \epsilon^2)I\otimes I + \epsilon^2X\otimes X)X\otimes X
+    \approx DPN[\epsilon^2]X\otimes X
   \end{gathered}
@@
 
-Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $\bar X_\pi$  form a BCS, with $\alpha\approx\epsilon^2$.
+Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $X_{-\pi}$  form a BOCS, with $\alpha\approx\epsilon^2$.
 
@@
 \subsection{Random Gate Synthesis}
-Generating BCSs can be done in a variety of ways, using any quantum optimal control technique \cite{Caneva2011, Machnes2018} to find a family of controls.
-For simplicity in this paper we use the GRAPE algorithm to generate candidate pulseshapes to approximate the target gate.
+Generating BOCSs can be done in a variety of ways, using any  of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}.
+For our numerics, we chose to use the GRAPE algorithm to generate candidate pulseshapes to approximate the target gate.
 First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$.
-Defining our uncontrolled Hamiltonian as $H_0$, our control Hamiltonians as $H_{i\neq 0}$, and our \textit{control matrix} $u_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write our approximate unitary at any timestep as
+Defining our uncontrolled Hamiltonian as $H_0$, our control Hamiltonians as $H_{i\neq 0}$, and our \textit{control matrix} $c_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write our approximate unitary at any timestep as
 \begin{equation}\label{eq:3}
-  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}u_{ij}H_{j}\}
+  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}c_{ij}H_{j}\}
 \end{equation}
@@
     \While{$J(U_n) < (1-\varepsilon$)}
-    \State $u_{ij} \rightarrow u_{ij} + \delta\frac{\partial J(U)}{\partial u_{ij}}$
+    \State $c_{ij} \rightarrow c_{ij} + \delta\frac{\partial J(U)}{\partial c_{ij}}$
     \For{$1 \leq i \leq n$}
-    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}u_{ij}H_j)\}$
+    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}c_{ij}H_j)\}$
     \EndFor
@@
 
-In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we have modified the update step in \ref{eq:update} to instead use approximately the following gradient:
+In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we consider the controls to have quasi-static Gaussian distributed errors, so to generate controls that are robust drift in these controls we modify our gradient to instead be:
 \begin{align}\label{quadrature}
+\frac{\partial \tilde J(U)}{\partial u_{ij}} =
 \int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
 \end{align}
-with $p(\vec{\delta})$ Gaussian distributed.
-This technique has been used in previous works such as \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors, and we approximate this integral in this paper by using Gaussian quadrature.\needcite Doing this ensures that the family of controls produced by our routine, $U_i$, perform moderately well over a range of control errors that might occur.
+with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
+To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomial.
 
-Concretely we consider a Hamiltonian of the following form:
+Concretely, we consider a Hamiltonian of the following form:
 \begin{equation}\label{eq:2}
@@
 for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
-Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequency, and phase of the laser might drift over time.\cite{Lekitsch2017} Correlations between different $\delta_i$ might arise if two of the controls have the same noise source.
-Examples of shared noise sources include $RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
-\needcite
+Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequency, or phase of the laser might drift over time\cite{Kelly2018, Lekitsch2017}.
+Correlations between different $\delta_i$ might arise, for instance, if two of the controls have the same noise source, e.g.
+$RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and suffer from the same diurnal temperature drift of control electronics.
 
-\subsection{BCS Approximation}
-After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}).
+\subsection{BOCS Approximation}
+After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BOCS as described in Equation \ref{eq:1}.
 To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate.
-If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations.
-In particular, we see that we can write a convex sum over these channels as:
+The we see that for any stochastic application of these channels, the resulting map is given by:
 \begin{align}
- \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
-\end{align}
-Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
+ \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}_i^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}_i
+\end{align} If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} errors.
+Thus to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
 \begin{equation}\label{eq:minimization}
+\setlength{\jot}{0pt}
   \begin{split}
@@
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires optimizing over the diamond norm, and in particular does not have the restriction that the optimal channel be decomposed into a given family of controls.
-Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined in terms of our collection of pulseshapes.
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the more computationally challenging task of optimizing over the diamond norm, and does not constrain the resulting channel to be decomposable into a given family of controls.
+Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined in terms of given collection of pulseshapes.
 
@@
 \section{Numerical Results}\label{numerical}
+In the following two subsections, we present numerical results of our routine, first for a one qubit example, and then for a two-qubit example.
+The code and BOCSs generated for both examples is available online at \cite{decorrelating_errors}.
 \subsection{1Q Gates}\label{1Q Gates}
- In this section, we present numerical results on generating one-qubit gates that together with $RZ(\theta$) rotations are universal for one-qubit computation. Our control Hamiltonian is given as:
+ For the one-qubit case, we consider generating BOCSs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, that together with $RZ(\theta$) rotations are universal for one-qubit computation.
+(In particular, choosing just one of these two gates would be sufficient.) Our control Hamiltonian is given as:
 \begin{equation}\label{eq:1Qham}
@@
 \end{equation}
-where $\epsilon \sim \delta \sim \mathcal{N}(0, .001)$ We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
-In our simulation we chose an total evolution time of $T=\pi$, and a number of steps $N=100$, with a threshold infidelity of $1E-3$.
+where $\epsilon, \delta \sim \mathcal{N}(0, .001)$ We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
+In our simulation we chose an total evolution time of $T=\pi$, a number of steps $N=100$, and a threshold infidelity of $1E-3$ for generating the control solutions with GRAPE.
 
-The results can be seen in \ref{fig:1qnum}, where we have plotted each control as a function of one detuning value, fixing the others to zero.
+%The results can be seen in \ref{fig:1qnum}, where we have plotted each control as a function of one detuning value, fixing the others to zero.
 In the top half of each plot, we show the variation in the sum of the absolute valua of the off diagonal elements of the Pauli-Liouville Representation, while in the lower plot we see the variation in fidelity.
@@
 \subsection{2Q Gates}\label{2Q Gates}
- In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation.
+ For a two-qubit example, we again consider the single qubit gates $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ on both qubits, along with single qubit $RZ(\theta)$ rotations.
+The entangling operation we chose is $ZZ(\frac{\pi}{2})$, which together with the single-qubit operations is universal for quantum computation.
 Our control Hamiltonian is given as:
@@
 H = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})}
+&+ \Delta c(t) \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})}
 \end{split}
 \end{equation}
-We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
+We again consider $\epsilon_j, \delta_j, \delta \sim .001$.
 In this simulation we again had a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
 
-As in \ref{1qnum}, the results of these numerics can be visualized in \ref{fig2num}.
-Notably, even in the two qubit case where optimization over many controls becomes more difficult, we see a decrease in the magnitude of the off-diagonal terms by over an order of magnitude.
+%0.0507,  0.0307, -0.0493, -0.0693, with total area under the curve given by 0.7853981633974484, 
+\section{Experimental Results}\label{experimental}
+Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit.
+In particular we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
+To implement a BOCS on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for an approximately calibrated 50$\mu$s $X_{\frac{\pi}{2}}$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$ pulse.
 
-\section{Experimental Results}\label{experimental}
-Here we present experimental results from implementing our routine on a superconducting transmon qubit.
-In this experiment we intentionally over and under-calibrated four pulses enacting approximate RX($\frac{\pi}{2})$) rotations.
-For each instatiation of the rotation, in addition to the BCS for the four pulses and a calibrated pulse, we ran a randomized benchmarking experiment.\cite{Magesan2011} The results are plotted in \ref{fig:rb}.
-In each case, our Clifford sequences were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In the superconducting qubit architecture used, these gates are implemented using the same pulse envelope definition, and are therefore subject to the same miscalibration errors.
+Using Equation \ref{eq:minimization}, we then generated the optimal (Is this convex?) weights $\omega_i$, and ran a randomized benchmarking experiment for each over- and under-calibrated pulse, the calibrated pulse, and the stochastic channel given by drawing from the members of the BOCS with $\omega_i$ on each application of the gate.
+We used $N=1000$ shots per experiment and $K=10$ sequences per sequence length, out to length $L=64$\cite{Magesan2011}.
+In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+In our implementation, these gates are implemented using the same pulse envelope definitions with the same control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to the same miscalibration errors.
  It was shown in \cite{Ball2016} that for particular non-Markovian (\textit{quasi-static}) error models, noise will manifest as gamma distributed points for each sequence length.
 On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-Our results are consistent with this $\amp{explain how, given new plot}$
+As can be seen in the results shown in Figure \ref{fig:rb} for sequence lengths $L=64$, we see that the coherently miscalibrated controls having long tails, consistent with gamma distributed random variables, while the calibrated andn randomized implementations both have much shorter tails, consistent with gaussian distributed random variables.
 
@@
 \section{Conclusion and Future Work}
-We have shown both numerically and experimentally that drawing from a collection of different synthesized version of a gate with  optimized probabilties can reduce coherent error by at least an order of magnitude, at virtually no cost to gate fidelity.
-We have demonstrated that these approximate controls can be generated through optimal control, and that the minimization problem is tractable.
-In addition, we have shown that it is possible to perform the routine on existing hardware.
-We note that unlike in \cite{Wallman2016, Campbell2017, Ware2018} this method of coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse definitions.
+We have shown numerically that using a balanced optimal control solution (BOCS) can reduce the error on a quantum channel by at least an order of magnitude in diamond norm robustly - that is, over a wide range noise values.
+In addition, we have given evidence that using a BOCS can convert coherent error in a family of miscalibrated controls into incoherent error, at virtually no cost to gate fidelity.
+In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
+
+%Contrasting with \cite{Ware2018}, we see that this method of non-Markovian and coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse definitions.
 In particular, no classical preprocessing or runtime frame tracking is required.
 
-Future directions for this work include moving the random gate selection from a precompilation step to a runtime logic, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more precise benchmarking routines such as GST\cite{BlumeKohout2017} to more quantitatively investigate the performance of these routines.
-
-In addition, the numerical work in the paper assumes access to a model of the system.
+Future directions for this work include moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Finally, the numerical work in the paper assumes access to a model of the system.
 In general, an experimentalist may not have a model readily available to describe the system, e.g.
-in the presence of unknown on-chip crosstalk.
-Even if they do have access to such a model, it might be computationally intractable to simulate.
-In both of these situations, numerical generation of candidate pulseshapes and the minimization become infeasible.
-One approach would then be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to minimize the magnitude of off-diagonal terms as measured by simple pulse sequences that amplify those elements of the process matrix.\needcite The code used to generate the numerical results in this paper is available at \cite{decorrelating_errors}.
+in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
+Even if a model is available, it might be computationally intractable to simulate, i.e.
+for more than a few qubits, or for non-adiabatic physics.
+In these situations, both numerical model-driver generation of candidate pulseshapes and the minimization become infeasible.
+One approach would then be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
+While performing optimization this way would be slow (requiring full tomography, in general, to reconstruct the off-diagonal elements of the process matrix), it might be feasible to instead run simple pulse sequences that are sensitive to known parameters of interest, and use those to drive the optimization, perhaps in some iterative fashion.
+By picking out elements of the process matrix in this way, one could reduce the magnitude of coherent error, and avoid doing a full process tomography at each step.\needcite
 

### 2018-09-25 decorrelation/decorrelation.tex
Minor changes to the example

--- 2018-09-20 decorrelation/decorrelation.tex
@@
 \section{A Simple Example}
-As a somewhat trivial example, consider a single-qubit rotation-angle error, such as result from stochastic laser amplitude fluctuations.
-A BCS may consist of an $X_\pi$ pulse, as well as an $\bar X_\pi$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
-In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $\bar X_\pi$ pulse results in an \emph{under}-rotation error.
-When it comes time to perform the target gate in a quantum circuit, one member of the BCS is chosen uniformly at random.
-This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
+As a somewhat trivial example, consider a single-qubit $X_\pi$ gate.
+We will assume that the control hardware implementing this gate is slightly miscalibrated, leading to an over-rotation by angle $\theta$.
+The diamond distance between this channel and the ideal implementation is $\theta$.
+If the gate were repeated $N$ total times, the target qubit would experience an accumulated over-rotation of $N\theta$.
+As shown in Fig.~\ref{fig:simple_example}, a balanced implementation of this gate may consist of two implimentations: 1) the original $X_\theta = \exp(-i (\pi/2+\theta)\sigma_x)$ and 2) the conjugate $X_\theta^\dagger = \exp(-i (\pi/2+\theta)\sigma_x)$.
+Each time the gate is required in a quantum circuit, one member of this balanced set is chosen uniformly at random.
+After $N$ applications of this gate, the mean over-rotation angle is zero, with a standard deviation of $\sqrt{N}\theta$.
+This is equivalent to the perfect gate followed by a stochastic Pauli $X$ error with rate $\theta^2$.
+The diamond norm of the channel is $\theta^2$, This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
 In this simple example, we can solve the minimization problem given by equation \ref{eq:minimization} analytically.

### 2018-09-25 decorrelation/decorrelation.tex

--- 2018-09-24 decorrelation/decorrelation.tex
@@
 \documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
-
 \usepackage{amsfonts,amsmath,amssymb,amsthm}
@@
 % \tableofcontents
-\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis - A BOCS of Control Solutions}
+\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}
 
@@
 Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006, 1609.00510, https://doi.org/10.7907/z96m34sc, Kubica2018, Wang2003, Campbell2017}.
-These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above thresholds, but that also violates fundamental assumptions made by the models used in these results, such as Markovianity \cite{Kitaev1997} and independence of errors\cite{Knill1998}.
+These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above known thresholds, but that also violates fundamental assumptions made by the models used in these results\cite{Kelly2018, BlumeKohout2017, Klimov2018}, such as Markovianity \cite{Kitaev1997} and independence of errors\cite{Knill1998}.
 With these assumptions violated, many properties of system performance and correctness can no longer be guaranteed.
 
-To make matters worse, the ways in which a quantum computer can fail to meet these assumptions are manifold\cite{Kelly2018, BlumeKohout2017, Klimov2018}, and even when the noise is Markovian, many models and existing work make strong simplifying assumptions about the structure of the noise.
-As an example, Pauli channels are often used to model systems due to their classical simulability\cite{quant-ph/9807006}, even in the absence of physical motivation\cite{Aliferis2007, Knill2005, Wang2011, DuclosCianci2010, Wootton2012, Bombin2012, Puzzuoli2014, aliferis2008accuracy}.
-Because of this, a common approach is to attempt to use those thresholds to give a loose lower bound for thresholds with lower noise\cite{Puzzuoli2014}.
-This approach is correct and rigorous, but produces overly-pessimistic bounds on device performance.
+Moreover, even when noise can be accurately modeled as Markovian, many existing works make further simplifying approximations about its structure to make problems tractable.
+For example, Pauli channels are often used to model systems due to their classical simulability\cite{quant-ph/9807006}, even in the absence of physical motivation\cite{Aliferis2007, Knill2005, Wang2011, DuclosCianci2010, Wootton2012, Bombin2012, Puzzuoli2014, aliferis2008accuracy}.
+One approach, then, would be to use these thresholds to give a loose lower bound for thresholds in other systems\cite{Puzzuoli2014}.
+Such an approach is correct and rigorous, but will produce overly-pessimistic bounds that may not be reflective of numerically demonstrated performnace.
 
-Relatedly, many characterization routines assume that the noise is well-behaved so that they can make non-trivial assertions about performance.
-If these assumptions are violated, the utility of many of these algorithms is drastically reduced.
+Many characterization routines also make assumptions about the form of noise, and if these assumptions are violated the utility and correctness of these routines may be reduced.
 For example, randomized benchmarking and tomography will report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013}.
-Slightly more helpful, gate-set tomography will report that the gateset failed to be Markovian, however figuring out how to bring it back to the space of the Markovianity can be challenging.
+Slightly more helpful, gate-set tomography will report that a system fails to be Markovian, without saying in what way..
 
-Many authors have approached these problems at varying levels of abstraction, each with their own benefits and short-comings.
-At the level of unitary synthesis, authors have considered randomizing over errors that might arise from gate approximations like Solovay-Kitaev \cite{Campbell2017, 1612.01011}.
+Other authors have approached these problems at varying levels of abstraction, each with their own benefits and short-comings.
+At the level of unitary synthesis, one can consider randomizing over errors that might arise from gate approximations like the Solovay-Kitaev decomposition \cite{Campbell2017, 1612.01011}.
 While this affords the ability to prove theorems that guarantee quadratic improvements to performance, they do not offer routines which are accessible and implementable with current coherence times.
-At the level of compilation, Frame Randomization\cite{Wallman2016, Ware2018}can be used to average over noise by \textit{twirling} error over an appropriately selected unitary 2-design.\cite{roy2009unitary} This has the advantage of being implementable\cite{Ware2018}, but it can require intensive use of classical resources, such as precompilation and generation of many waveform variants, and becomes more difficult when the gates being used are not in the Clifford group, as is the case in various quantum computing architectures.
-The general theme of these results is that of randomized decoupling\cite{Viola2005, Viola}.
-By introducing classical randomness into quantum computations, both coherent and non-Markovian can be transformed to incoherent, independent, Markovian noise, to varying degrees.
+In addition, present quantum computing work focusses primarily on gate synthesis, rather than unitary synthesis.
+
+At the level of compilation, Frame Randomization\cite{Wallman2016, Ware2018} can be used to average over noise by twirling error over an appropriately selected unitary 2-design.\cite{roy2009unitary} This has the advantage of being realizable in existing systems\cite{Ware2018}, but it can require intensive use of classical resources, such as precompilation and generation of many waveform variants, and becomes more difficult when the gates being used are not in the Clifford group, as is the case in various quantum computing architectures.
+
+The general theme of these results is randomized decoupling\cite{Viola2005, Viola} -- by introducing classical randomness into quantum computations, both coherent and non-Markovian noise can be transformed to incoherent, independent, and Markovian noise.
 In this paper, we explore a different method of solving these problems.
 We propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{balanced optimal control solutions} (BOCSs).
+The task of generating BOCSs will fall to optimal control.
 
@@
  BOCSs are families of control solutions, $c_i(t)$, where each member of the family approximates the same target gate with slightly different errors, for any given instance a noise Hamiltonian.
-That is, for a target unitary operator $U_T$, we seek a family of approximating $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \delta)}$ to the target gate, such that the family of unitary approximations is \emph{balanced}.
-A balanced family is one which satisfies, for some small $\alpha$,
+That is, for a target gate $U_T$, we seek a family of approximating gates $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \delta)}$ such that the family of unitary approximations is \emph{balanced}.
+A family of controls is balanced if there is a weighting $\omega_i$ of its members such that produces a \textit{balanced channel}, satisfying for some small $\alpha$,
 \begin{equation}\label{eq:1}
@@
 
-where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$.
-(For the rest of this paper, we will refer to them as just depolarizing channels.) Such a channel is defined as:
+where $\omega_i > 0$ and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. Such a channel is defined as:
 \begin{equation}\label{eq:2}
@@
 with $p_i$ summing to one.
-This means that a for a family of controls that are a BOCS, there exists a weighting $p_i$, such that when the unitary approximations are averaged over with that weighting, they implement the target unitary followed by a depolarizing channel.
 
-Thus, one property of BOCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BOCS to $U_T$ is also no larger than $\epsilon^2$.
-This follows from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, and tells us that we can lower bound the worst case performance of a BOCS by the square of the error on each member of the BOCS, and linearly in the error of the weighted average.
-Because a set of parameters always exist that result in quadratically smaller error, it is then clear that in priniple BOCSs can always quadratically decrease the error in our approximation (in diamond norm).
+Thus, following from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, one property of BOCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BOCS to $U_T$ is also no larger than $\epsilon^2$.
+Because any sufficiently populated BOCS will have a set of controls that result in error of order $\mathcal{O}(\epsilon^2)$ on their balanced channel, it is then clear that in priniple BOCSs can always quadratically decrease the error in our approximation (in diamond norm).
 Moreover, in the setting where our system's performance is non-Markovian, e.g.
-drift, optimizing our BOCSs over a range of control parameters can reduce the non-Markovianity of the noise.
-As the name suggests, the task of generating BOCSs in this paper will fall to optimal control.
+drift, optimizing our BOCSs \textit{robustly} over a range of control parameters can reduce the non-Markovianity of the noise.
 
@@
 \end{equation}
-Then, to measure the simularity of our approxiate unitary $U_n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U_n\}$.
+Then, to measure the simularity of our approxiate unitary $U$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
 
@@
   \begin{algorithmic}
-    \While{$J(U_n) < (1-\varepsilon$)}
+    \While{$J(U) < (1-\varepsilon$)}
     \State $c_{ij} \rightarrow c_{ij} + \delta\frac{\partial J(U)}{\partial c_{ij}}$
@@
 
-In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we consider the controls to have quasi-static Gaussian distributed errors, so to generate controls that are robust drift in these controls we modify our gradient to instead be:
+In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we consider the controls to have quasi-static\cite{Ball2016}(non-Markovian) Gaussian distributed errors, so to generate controls that are robust to this error we modify our gradient to instead be:
 \begin{align}\label{quadrature}
@@
 with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
-To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomial.
+To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomial\cite{abramowiz1972handbook}.
 
@@
 for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
-Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time, or a trapped ion quantum computer where the intensity, frequency, or phase of the laser might drift over time\cite{Kelly2018, Lekitsch2017}.
+Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses or qubit transition frequencies vary over time, or a trapped ion quantum computer where the intensity, frequency, or phase of the laser might drift\cite{Kelly2018, Klimov2018, Lekitsch2017}.
 Correlations between different $\delta_i$ might arise, for instance, if two of the controls have the same noise source, e.g.
-$RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and suffer from the same diurnal temperature drift of control electronics.
+$RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and all of the lab equipment may suffer from the same temperature drift of control electronics.
 
 \subsection{BOCS Approximation}
-After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BOCS as described in Equation \ref{eq:1}.
+After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_i$ such that the collection of controls form a BOCS as described in Equation \ref{eq:1}.
 To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate.
@@
  \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}_i^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}_i
-\end{align} If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} errors.
+\end{align} If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} errors\cite{Ware2018}.
 Thus to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
@@
 Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the more computationally challenging task of optimizing over the diamond norm, and does not constrain the resulting channel to be decomposable into a given family of controls.
-Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined in terms of given collection of pulseshapes.
+Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined explicitly in terms of given family of controls.
 
@@
 % \end{figure*}
+
 \section{Numerical Results}\label{numerical}
 In the following two subsections, we present numerical results of our routine, first for a one qubit example, and then for a two-qubit example.
-The code and BOCSs generated for both examples is available online at \cite{decorrelating_errors}.
+The code and BOCSs generated for both examples are available online at \cite{decorrelating_errors}.
 \subsection{1Q Gates}\label{1Q Gates}
- For the one-qubit case, we consider generating BOCSs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, that together with $RZ(\theta$) rotations are universal for one-qubit computation.
+ For the one-qubit case, we generate BOCSs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, that together with $RZ(\theta$) rotations are universal for one-qubit computation.
 (In particular, choosing just one of these two gates would be sufficient.) Our control Hamiltonian is given as:
@@
  For a two-qubit example, we again consider the single qubit gates $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ on both qubits, along with single qubit $RZ(\theta)$ rotations.
-The entangling operation we chose is $ZZ(\frac{\pi}{2})$, which together with the single-qubit operations is universal for quantum computation.
+The entangling operation we chose is $ZZ(\frac{\pi}{2})$, which together with the single-qubit operations are universal for quantum computation.
 Our control Hamiltonian is given as:
@@
 H = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ \Delta c(t) \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})}
+&+ (1+\delta)c(t) \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})}
 \end{split}
@@
 We again consider $\epsilon_j, \delta_j, \delta \sim .001$.
-In this simulation we again had a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
+In this simulation we again used a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
 
@@
 In particular we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a BOCS on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for an approximately calibrated 50$\mu$s $X_{\frac{\pi}{2}}$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$ pulse.
+To implement a BOCS on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
-Using Equation \ref{eq:minimization}, we then generated the optimal (Is this convex?) weights $\omega_i$, and ran a randomized benchmarking experiment for each over- and under-calibrated pulse, the calibrated pulse, and the stochastic channel given by drawing from the members of the BOCS with $\omega_i$ on each application of the gate.
-We used $N=1000$ shots per experiment and $K=10$ sequences per sequence length, out to length $L=64$\cite{Magesan2011}.
+Using Equation \ref{eq:minimization}, we then generated the optimal (IS THIS CONVEX?) weights $\omega_i$.
+To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.
+We used $N=1000$ shots per experiment and $K=10$ sequences per sequence length, for sequence lengths up to $L=64$\cite{Magesan2011}.
 In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In our implementation, these gates are implemented using the same pulse envelope definitions with the same control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to the same miscalibration errors.
- It was shown in \cite{Ball2016} that for particular non-Markovian (\textit{quasi-static}) error models, noise will manifest as gamma distributed points for each sequence length.
+In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
+The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
+In this experiment, fitting the randomized benchmarking data with scipy's curve\_fit using the Trust Region Reflective method reports one-qubit gate fidelities of $99.4\%$ for the calibrated pulse, $98.8\%$ for Pulse1, $99.4\%$ for Pulse2, $98.9\%$ for Pulse3, $98.6\%$ for Pulse4, and $99.0\%$ for the Randomized pulse.
+As one can see from looking at Figure \ref{fig:rb}, despite all controls performing comparably to the Calibrated control, only the Randomized control has similarly tight error bars.
+In the cases of each miscalibrated pulse, the error bars extend significantly, in often asymmetric ways, making usage of chi-square statistics, and errors on the fit less straightforward.
+
+This is consistent with the result shown in \cite{Ball2016} that for particular non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
 On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-As can be seen in the results shown in Figure \ref{fig:rb} for sequence lengths $L=64$, we see that the coherently miscalibrated controls having long tails, consistent with gamma distributed random variables, while the calibrated andn randomized implementations both have much shorter tails, consistent with gaussian distributed random variables.
+We see that the coherently miscalibrated controls have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
 
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using a balanced optimal control solution (BOCS) can reduce the error on a quantum channel by at least an order of magnitude in diamond norm robustly - that is, over a wide range noise values.
-In addition, we have given evidence that using a BOCS can convert coherent error in a family of miscalibrated controls into incoherent error, at virtually no cost to gate fidelity.
+We have shown numerically that using a balanced optimal control solution (BOCS) can reduce non-Markovian coherent error on a quantum channel by at least an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
@@
 
-Future directions for this work include moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimzation routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
-Finally, the numerical work in the paper assumes access to a model of the system.
-In general, an experimentalist may not have a model readily available to describe the system, e.g.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+
+Another interesting area of research would be using model-free approaches.
+The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
 in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
-Even if a model is available, it might be computationally intractable to simulate, i.e.
-for more than a few qubits, or for non-adiabatic physics.
-In these situations, both numerical model-driver generation of candidate pulseshapes and the minimization become infeasible.
-One approach would then be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
-While performing optimization this way would be slow (requiring full tomography, in general, to reconstruct the off-diagonal elements of the process matrix), it might be feasible to instead run simple pulse sequences that are sensitive to known parameters of interest, and use those to drive the optimization, perhaps in some iterative fashion.
-By picking out elements of the process matrix in this way, one could reduce the magnitude of coherent error, and avoid doing a full process tomography at each step.\needcite
+Moreover, even if a model is available, it might be computationally inconvenient to simulate, i.e.
+for more than a few qubits, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
+
+In these situations, one approach would be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
+While performing optimization this way would still be slow (requiring full process tomography, in general, to reconstruct the process matrix of a candidate balanced channel), one could intead select pulse sequences that are sensitive to known parameters of interest in the Hamiltonian and just run the minimization with respect to those terms.
+(e.g.
+if we suspect there is unwanted $Z\otimes Z$ crosstalk between qubits.)
 

### 2018-09-26 decorrelation/decorrelation.tex
adding small blurb about least squares, citation still needed

@@
 
-This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming\cite{wright1999numerical}.
+In the numerics section below, this was solved with a constrained minimization algorithm (Sequential Least Squares Programming\cite{wright1999numerical}).
+However, it can be solved more efficiently as a least squares problem.
+In particular, consider the $M^2-M$ off diagonal elements $\mathcal{E}_i$.
+Vectorize their squares, and concatenate the resulting vectors, for each $\mathcal{E}_i$.
+Then we just need to find $\omega$ that produces the smallest $\vec{b}$ in the following underconstrainted least squares problem:
+\begin{center}
+$A\omega= \vec{b}$
+\end{center}
+where:
+\begin{center}
+
+A = $\begin{pmatrix}
+\mathcal{E}_{0_{10}} & \mathcal{E}_{1_{10}} & \cdots & \mathcal{E}_{N-1_{10}}\\
+\mathcal{E}_{0_{20}} & \mathcal{E}_{1_{20}} & \cdots &\mathcal{E}_{N-1_{20}}\\
+\vdots & \vdots & \ddots & \\
+\mathcal{E}_{0_{M-1 M}} &\mathcal{E}_{1_{M-1 M}} & & \mathcal{E}_{N-1_{M-1 M}}
+\end{pmatrix}
+$
+\end{center}
+In particular, we want the solution $\omega$ such that $||\vec{b}||_2^2$ is minimized.
+This is readily given by the solution to a constrained least squares minimization problem as $\frac{1}{N}(\tilde{A^{-1}}_{AVG})^{-1}\tilde{A^{-1}}_{i_{AVG}}$.\needcite\url{http://eeweb.poly.edu/iselesni/lecture_notes/least_squares/least_squares_SP.pdf}
 
@@
 
-Using Equation \ref{eq:minimization}, we then generated the optimal (IS THIS CONVEX?) weights $\omega_i$.
+Using Equation \ref{eq:minimization}, we then generated the optimal weighting $\omega_i$.
 To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.
@@
 
-In these situations, one approach would be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
+In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
 While performing optimization this way would still be slow (requiring full process tomography, in general, to reconstruct the process matrix of a candidate balanced channel), one could intead select pulse sequences that are sensitive to known parameters of interest in the Hamiltonian and just run the minimization with respect to those terms.

### 2018-09-30 decorrelation/decorrelation.tex
small incomplete changes to the text, extending small example to talk about robustness

@@
 \setlength{\jot}{10pt}
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{lem}[thm]{Lemma}
+\usepackage{lipsum}
+
 %-------------Header begins here----------------------------------------
@@
 
-Thus, following from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, one property of BOCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BOCS to $U_T$ is also no larger than $\epsilon^2$.
-Because any sufficiently populated BOCS will have a set of controls that result in error of order $\mathcal{O}(\epsilon^2)$ on their balanced channel, it is then clear that in priniple BOCSs can always quadratically decrease the error in our approximation (in diamond norm).
-Moreover, in the setting where our system's performance is non-Markovian, e.g.
-drift, optimizing our BOCSs \textit{robustly} over a range of control parameters can reduce the non-Markovianity of the noise.
+We will be interested in the case where $\alpha \approx \epsilon^2$, with $\epsilon$ being the infidelity of each $U_i$ to $U_T$.
+Indeed, from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{H_i\}]$, where Conv is the convex hull of its arguments and $H_i$ are the generating Hamiltonians for the controls, then we know such a balanced channel exists.
+In this case, following from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, we can bound the the diamond distance from a BOCS to $U_T$ by $\epsilon^2$.
+Thus for suitable BOCSs, we can quadratically decrease the error in our approximation in diamond norm.
 
 \section{A Simple Example}
-As a somewhat trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
+As a trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
 A BOCS may consist of an $X_\pi$ pulse, as well as an $X_{-\pi}$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
@@
 Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $X_{-\pi}$  form a BOCS, with $\alpha\approx\epsilon^2$.
+
+Moreover, if we consider the amplitudes to not only be miscalibrated, but also non-Markovian (i.e.
+such that for each circuit the error map can be approximated by $X(\epsilon \pm \delta$, where $\delta\sim\mathcal{N}(0, \sigma^2)$), we see that for correlated noise we get a reduction on the impact of $\delta$.
+Indeed, we see that the error is a $X\otimes X$ term with  coefficient:
+
+\begin{equation}
+  \begin{gathered}
+  2\epsilon^2 + 4\delta\epsilon + 2\delta^2
+  \end{gathered}
+\end{equation}
+
+Thus, the drift in controls can also be supressed by a quadratic factor in some cases.
 

### 2018-10-15 decorrelation/decorrelation.tex
updates to text

--- 2018-09-25 decorrelation/decorrelation.tex
@@
 \usepackage{graphicx}
-% \usepackage[justification=justified,font=small]{caption}
 \graphicspath{{./figures/}}
@@
 \newcommand{\T}{\mathsf{T}}
-
 \newcommand{\erf}[1]{Eq.~(\ref{#1})}
@@
 The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing noise correlations.
-We propose to introduce similar methods at the gate synthesis level to effect the decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
-We show numerically and experimentally on a superconducting qubit that these methods can reduce the magnitude of the diamond norm of the error by at least an order of magnitude.
+We propose to introduce similar methods at the physical gate synthesis level to effect the decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
+We discuss and show numerically that these controls can be made robust to drift, and experimentally demonstrate our approach on a superconducting qubit.
 \end{abstract}
@@
 Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006, 1609.00510, https://doi.org/10.7907/z96m34sc, Kubica2018, Wang2003, Campbell2017}.
-These results show that quantum computation is feasible in principle, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above known thresholds, but that also violates fundamental assumptions made by the models used in these results\cite{Kelly2018, BlumeKohout2017, Klimov2018}, such as Markovianity \cite{Kitaev1997} and independence of errors\cite{Knill1998}.
-With these assumptions violated, many properties of system performance and correctness can no longer be guaranteed.
+These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above known thresholds, but that also violates fundamental assumptions made by the models used in these results\cite{Kelly2018, BlumeKohout2017, Klimov2018}, such as independence of errors\cite{Knill1998} and Markovianity \cite{Kitaev1997}.
 
-Moreover, even when noise can be accurately modeled as Markovian, many existing works make further simplifying approximations about its structure to make problems tractable.
+When noise can be accurately modeled as Markovian, existing work often makes approximations to make problems tractable.
 For example, Pauli channels are often used to model systems due to their classical simulability\cite{quant-ph/9807006}, even in the absence of physical motivation\cite{Aliferis2007, Knill2005, Wang2011, DuclosCianci2010, Wootton2012, Bombin2012, Puzzuoli2014, aliferis2008accuracy}.
 One approach, then, would be to use these thresholds to give a loose lower bound for thresholds in other systems\cite{Puzzuoli2014}.
-Such an approach is correct and rigorous, but will produce overly-pessimistic bounds that may not be reflective of numerically demonstrated performnace.
+Such an approach will produce overly-pessimistic bounds that may not be reflective of a system's actual performance.
 
-Many characterization routines also make assumptions about the form of noise, and if these assumptions are violated the utility and correctness of these routines may be reduced.
-For example, randomized benchmarking and tomography will report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013}.
-Slightly more helpful, gate-set tomography will report that a system fails to be Markovian, without saying in what way..
+When noise is non-Markovian, the situation is much worse.
+Not only will the Markovian models used in threshold calculations be wrong, but assumptions that underpin characterization routines will be violated.
+Randomized benchmarking and tomography will report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013} and gate-set tomography will report that a system fails to be Markovian, but without saying in what way.
 
-Other authors have approached these problems at varying levels of abstraction, each with their own benefits and short-comings.
-At the level of unitary synthesis, one can consider randomizing over errors that might arise from gate approximations like the Solovay-Kitaev decomposition \cite{Campbell2017, 1612.01011}.
-While this affords the ability to prove theorems that guarantee quadratic improvements to performance, they do not offer routines which are accessible and implementable with current coherence times.
-In addition, present quantum computing work focusses primarily on gate synthesis, rather than unitary synthesis.
+An early proposal for fixing these problems is randomized decoupling\cite{Viola2005, Viola} -- by introducing classical randomness into quantum computations, both coherent and non-Markovian noise can be transformed to incoherent, independent, and Markovian noise.
 
-At the level of compilation, Frame Randomization\cite{Wallman2016, Ware2018} can be used to average over noise by twirling error over an appropriately selected unitary 2-design.\cite{roy2009unitary} This has the advantage of being realizable in existing systems\cite{Ware2018}, but it can require intensive use of classical resources, such as precompilation and generation of many waveform variants, and becomes more difficult when the gates being used are not in the Clifford group, as is the case in various quantum computing architectures.
+One particular way of realizing randomized decoupling is Frame Randomization\cite{Wallman2016, Ware2018}.
+Frame Randomization can be used to average over noise by twirling error over an appropriately selected unitary 2-design, by inserting an additional precompilation step in the execution of quantum circuits.\cite{roy2009unitary} This has been demonstrated in existing systems\cite{Ware2018}, but can require intensive use of classical processors and waveform memory, and becomes more difficult when the gates being used are not in the Clifford group\needcite, as is the case in various quantum computing architectures.\needcite
 
-The general theme of these results is randomized decoupling\cite{Viola2005, Viola} -- by introducing classical randomness into quantum computations, both coherent and non-Markovian noise can be transformed to incoherent, independent, and Markovian noise.
-In this paper, we explore a different method of solving these problems.
-We propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{balanced optimal control solutions} (BOCSs).
-The task of generating BOCSs will fall to optimal control.
+Another approach is to consider constructing a family of unitaries that approximate a given gate, and averaging over them.
+In \cite{Campbell2017}, Campbell considers coherent error arising from unitary synthesis approximations algorithms like the Solovay-Kitaev Algorithm \cite{1612.01011}.
+He presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle.
+In that work, the primary emphasis was on resource counting, and diamond-norm error-bounds at level of unitary synthesis.
+In this paper, we explore a different but related problem: synthesizing physical controls and making them robust to drift.
+
+We propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
+The task of generating RBCs will fall to optimal control.
 
@@
 \section{Theory}
- BOCSs are families of control solutions, $c_i(t)$, where each member of the family approximates the same target gate with slightly different errors, for any given instance a noise Hamiltonian.
-That is, for a target gate $U_T$, we seek a family of approximating gates $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \delta)}$ such that the family of unitary approximations is \emph{balanced}.
-A family of controls is balanced if there is a weighting $\omega_i$ of its members such that produces a \textit{balanced channel}, satisfying for some small $\alpha$,
+ Consider a family of control solutions, $c_i(t)$, where each member of the family approximates the same target gate with slightly different errors.
+That is, for a target gate $U_T$, the family consists of gates $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \vec{\delta})}$, where $\vec{\delta}$ are \textit{quasi-static}\cite{Ball2016} parameters of the Hamiltonian.
+Such a family of unitary approximations is called a \emph{balanced control} if there is a weight vector $\vec{\omega}$ that satisfies the following for some small $\alpha$,
 \begin{equation}\label{eq:1}
@@
 
-where $\omega_i > 0$ and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. Such a channel is defined as:
+where $\vec{\omega}$ must be a proper probability distribution and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. Such a channel is defined as:
 \begin{equation}\label{eq:2}
@@
 
-Thus, following from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}, one property of BOCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BOCS to $U_T$ is also no larger than $\epsilon^2$.
-Because any sufficiently populated BOCS will have a set of controls that result in error of order $\mathcal{O}(\epsilon^2)$ on their balanced channel, it is then clear that in priniple BOCSs can always quadratically decrease the error in our approximation (in diamond norm).
-Moreover, in the setting where our system's performance is non-Markovian, e.g.
-drift, optimizing our BOCSs \textit{robustly} over a range of control parameters can reduce the non-Markovianity of the noise.
+This is equivalent to the condition given by Campbell\cite{Campbell2017}, that there exist a weight such that
+
+\begin{equation}\label{eq:campbell-condition}
+\sum \omega_j H_j(t, \vec{\delta})|_{\delta=\vec{0}} = 0
+\end{equation}
+However, we will be interested in a stronger condition.
+A balanced control is said to be \textit{robust to order $\ell$} if a generalized form of Equation \ref{eq:campbell-condition} holds, namely if for all $j \leq \ell$:
+\begin{equation}\label{eq:RBC}
+D_\ell = \sum_j \omega_j \frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}H_j(t,\vec{\delta})|_{\delta=\vec{0}}  = 0
+\end{equation}
+
+These conditions imply that an $\ell^{th}$ order RBC ($\ell$RBC) is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
+To see this, write the error on each gate in the RBC as $U_j(\vec{\delta}) = exp(-i(\tilde{H}_j(\vec{0}) + \frac{\partial}{\partial\delta_i}\tilde{H}_j(d\delta_i) +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \tilde{H}_j(d\delta_i d\delta_k) + ...)U_T$, where $\tilde{H}(\delta)$ generates the error $U_j(\vec{\delta})U_T^{\dagger}$ over variations in $\vec{\delta}$.
+In this way, an $\ell$RBC satisfies Equation \ref{eq:1} to $\ell^{th}$ order.
+
+In all of the above, we will be interested in the case where $\alpha \approx \epsilon^2$, with $\epsilon$ being diamond distance from each member of the RBC to $U_T$.
+Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments then we know that $\vec{\omega}$ exists that satisfies Equation \ref{eq:1}.
+Then, following from the mixing lemma proven by both Campbell and Hastings\cite{1612.01011}, we can bound the the diamond distance from a balanced control to $U_T$ by $\epsilon^2$.
+Moreover, by following a generalized version of the algorithm Campbell presents in \cite{Campbell2017}, we can find families of controls that are $\ell$RBCs, for any $\ell$.
 
 \section{A Simple Example}
-As a somewhat trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
-A BOCS may consist of an $X_\pi$ pulse, as well as an $X_{-\pi}$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
+As a trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
+An RBC may consist of an $X_\pi$ pulse, as well as an $X_{-\pi}$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
 In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $X_{-\pi}$ pulse will result in an \emph{under}-rotation error.
-When it comes time to perform the target gate in a quantum circuit, one member of the BOCS is chosen uniformly at random.
+When it comes time to perform the target gate in a quantum circuit, one member of the RBC is chosen uniformly at random.
 This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
 In this simple example, we can analytically find a solution to Equation \ref{eq:1}.
-Specifically, by choosing weights $\omega_i=1$, we see:
+Specifically, by choosing weights $\omega_i=\frac{1}{2}$, we see:
 
@@
   \begin{gathered}
-    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + X^*_{-(\pi + \epsilon)}\otimes X_{-(\pi + \epsilon})) \\
+    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + X^*_{-(\pi + \epsilon)}\otimes X_{-(\pi + \epsilon)})) \\
     = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
@@
 
-Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $X_{-\pi}$  form a BOCS, with $\alpha\approx\epsilon^2$.
+Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $X_{-\pi}$  form a 0RBC, with $\alpha\approx\epsilon^2$.
+
+If we consider the amplitudes to not only be miscalibrated, but also non-Markovian (i.e. such that $\epsilon$ is drifting), we find the following channel, for any drift $\delta$:
+
+\begin{equation}
+  \begin{gathered}
+  DPN[(\epsilon + \delta)^2]X\otimes X
+  \end{gathered}
+\end{equation}
+
+Thus, the noise is always depolarizing, for every $\ell > 0$, this family of controls is an $\ell$RBC, and by injecting additional randomness the error rate is supressed quadratically.
 
@@
 \subsection{Random Gate Synthesis}
-Generating BOCSs can be done in a variety of ways, using any  of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}.
-For our numerics, we chose to use the GRAPE algorithm to generate candidate pulseshapes to approximate the target gate.
+ Generating RBCs can be done in a variety of ways, in this paper we consider using optimal control.
+In particular, one could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}.
+For our numerics, we chose to use the GRAPE algorithm.
 First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$.
-Defining our uncontrolled Hamiltonian as $H_0$, our control Hamiltonians as $H_{i\neq 0}$, and our \textit{control matrix} $c_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write our approximate unitary at any timestep as
+Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write an approximate unitary for any timestep of evolution as:
 \begin{equation}\label{eq:3}
@@
 \end{equation}
-Then, to measure the simularity of our approxiate unitary $U$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
+Then, to measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
 
@@
 
-In our numerical results in Section \ref{1Q Gates} and \ref{2Q Gates}, we consider the controls to have quasi-static\cite{Ball2016}(non-Markovian) Gaussian distributed errors, so to generate controls that are robust to this error we modify our gradient to instead be:
+Because we our trying to generate high-order RBCs, we want to generate controls that perform well over a wide range of parameter values ($\delta$).
+To do this, we modified the gradient in GRAPE to instead be:
 \begin{align}\label{quadrature}
@@
 with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
-To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomial\cite{abramowiz1972handbook}.
+To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomials\cite{abramowiz1972handbook}.
 
-Concretely, we consider a Hamiltonian of the following form:
-\begin{equation}\label{eq:2}
-  H(t) = \delta_0H_0 + \sum_{i=1}^n (1 + \delta_i)c_i(t)H_i
-\end{equation}
-for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and random variables $\delta_i$, that model some small uncertainty in parameters in the Hamiltonian.
-Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses or qubit transition frequencies vary over time, or a trapped ion quantum computer where the intensity, frequency, or phase of the laser might drift\cite{Kelly2018, Klimov2018, Lekitsch2017}.
-Correlations between different $\delta_i$ might arise, for instance, if two of the controls have the same noise source, e.g.
-$RX$ and $RY$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and all of the lab equipment may suffer from the same temperature drift of control electronics.
-
-\subsection{BOCS Approximation}
-After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_i$ such that the collection of controls form a BOCS as described in Equation \ref{eq:1}.
-To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate.
-The we see that for any stochastic application of these channels, the resulting map is given by:
-\begin{align}
- \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}_i^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}_i
-\end{align} If we consider the Pauli-Liouville representation\cite{Kimmel2014} of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} errors\cite{Ware2018}.
-Thus to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
+\subsection{RBC Approximation}
+After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_i$ such that the collection of controls form an $\ell$RBC as described in Equation \ref{eq:RBC}.
+To do this, for each control $U_i(\vec{\delta})$ we find the unitary error channel $\mathcal{E}_i(\vec{\delta})$ such that $\mathcal{E}_i(\vec{\delta})U_i(\vec{\delta})=U_T$, where $U_T$ is the target gate.
+By taking the logarithm of these error maps, we then get a family of Hamiltonians $\tilde{H}_j(\delta)$, and conside the following quadratic program whose solutions satisfies the robustness conditions given in Equation \ref{eq:RBC}.
+Namely:
 \begin{equation}\label{eq:minimization}
-\setlength{\jot}{0pt}
   \begin{split}
-    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{\substack{i,j \\ i\neq j}}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
-    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
-    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
+    &\textbf{minimize: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell,\ D_i=0\\
+   	&\phantom{\textbf{subject to: }}\sum \omega_j = 1\\
+   	&\phantom{\textbf{subject to: }}\sum 0 \le \omega_j \le 1    
   \end{split}
 \end{equation}
+%These constraints for each $P_i$ can be broken into $2_{\ell-1}$ constraints, one for the imaginary components, and one for the real component.
+Alternatively, one can express the Hamiltonians as vectors in $\mathbb{R}^{2^n}$
 
-This can be solved with a constrained minimization algorithm, such as Sequential Least Squares Programming\cite{wright1999numerical}.
+The question still remains -- when does this quadratic program have a solution.
+Naturally, if the control family is too small a solution won't exist.
+In addition, as in \cite{Campbell2017}, we need  $0\in $ Conv$[\{\frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}\tilde{H}_j(t,\vec{\delta})|_{\vec{\delta}=0}\}]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust unitaries.
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the more computationally challenging task of optimizing over the diamond norm, and does not constrain the resulting channel to be decomposable into a given family of controls.
-Our routine, on the other hand, optimizes over an easy to compute sum, and produces a channel defined explicitly in terms of given family of controls.
+%In addition, for the constraints to be feasible, it is clear that the following condition is necessary: take $dim(\omega)=\Omega$, and $dim(\delta)=\Delta$.
+Each constraint is a matrix with $\Delta^i2^n$ elements.
+Thus we need at least $\Delta^i2^n$ linearly independent controls to even span the space of feasible weight vectors.
+On the other hand, even if the controls span the space, this is not sufficient because they must contain the origin in their complex hull.
+This can be achieved via a generalization of Campbell's Algorithm and by modifying the oracle query to ask for controls whose derivatives also satisfy certain properties.
+
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework it does not constrain the resulting channel to be decomposable into a given family of controls.
+Our routine, on the other hand, produces a channel defined explicitly in terms of given family of controls.
 
@@
 In the following two subsections, we present numerical results of our routine, first for a one qubit example, and then for a two-qubit example.
-The code and BOCSs generated for both examples are available online at \cite{decorrelating_errors}.
+The code and RBCs generated for both examples are available online at \cite{decorrelating_errors}.
 \subsection{1Q Gates}\label{1Q Gates}
- For the one-qubit case, we generate BOCSs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, that together with $RZ(\theta$) rotations are universal for one-qubit computation.
-(In particular, choosing just one of these two gates would be sufficient.) Our control Hamiltonian is given as:
+ For the one-qubit case, we generate a 1RBCs for $RX(\frac{\pi}{2})$. Our control Hamiltonian is given as:
 \begin{equation}\label{eq:1Qham}
-  H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
+  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
 \end{equation}
-where $\epsilon, \delta \sim \mathcal{N}(0, .001)$ We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
-In our simulation we chose an total evolution time of $T=\pi$, a number of steps $N=100$, and a threshold infidelity of $1E-3$ for generating the control solutions with GRAPE.
+where we take  when generating the members of the RBC.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
+When generating the controls, we chose an total evolution time of $T=\pi$, a number of steps $N=100$, and a threshold infidelity of $1E-3$, with $\epsilon, \delta \sim \mathcal{N}(0, .001)$.
+The results can be seen in \ref{fig:num}.
+In particular, over a wide region about the origin, the diamond norm can be seen to have been reduced by over an order of magnitude.
 
+\begin{figure}\label{fig:num}
+  \centering
+  \includegraphics[width=\columnwidth]{placeholdernumerical.pdf}
+  \caption{Placeholder image until we figure out what to plot. This currently shows that for one of the control the diamond norm decreased by over an order of magnitude. The labels need to be bigger.}
+  \label{fig:rb}
+\end{figure}
 %The results can be seen in \ref{fig:1qnum}, where we have plotted each control as a function of one detuning value, fixing the others to zero.
@@
 \subsection{2Q Gates}\label{2Q Gates}
- For a two-qubit example, we again consider the single qubit gates $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ on both qubits, along with single qubit $RZ(\theta)$ rotations.
-The entangling operation we chose is $ZZ(\frac{\pi}{2})$, which together with the single-qubit operations are universal for quantum computation.
-Our control Hamiltonian is given as:
+ For a two-qubit example, we chose $ZZ(\frac{\pi}{2})=\exp{(-i\frac{\pi}{4}\sigma_z\otimes\sigma_z)}$. Our control Hamiltonian is given as:
 \begin{equation} \label{eq:2Qham}
 \begin{split}
-H = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ (1+\delta)c(t) \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})}
+H(\vec{\epsilon}, \vec{\delta}, \eta, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
+&+ (1+\eta)c(t) \exp{(-i\frac{\pi}{4}\sigma_z^1\otimes\sigma_z^2})
 \end{split}
 \end{equation}
-We again consider $\epsilon_j, \delta_j, \delta \sim .001$.
-In this simulation we again used a threshold infidelity of $1E-3$, but we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example, however the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
+We again consider $\epsilon_j, \delta_j, \eta \sim .001$, however and a threshold infidelity of $1E-3$, however we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
+The results also show a reduction of an order of magnitude in diamond norm about the origin, and for a wide neighborhood around it.
 
@@
 In particular we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a BOCS on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement a RBC on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
-Using Equation \ref{eq:minimization}, we then generated the optimal (IS THIS CONVEX?) weights $\omega_i$.
+ Using Equation \ref{eq:minimization}, we then generated the optimal weighting $\omega_i$.
 To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.
@@
 The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-In this experiment, fitting the randomized benchmarking data with scipy's curve\_fit using the Trust Region Reflective method reports one-qubit gate fidelities of $99.4\%$ for the calibrated pulse, $98.8\%$ for Pulse1, $99.4\%$ for Pulse2, $98.9\%$ for Pulse3, $98.6\%$ for Pulse4, and $99.0\%$ for the Randomized pulse.
-As one can see from looking at Figure \ref{fig:rb}, despite all controls performing comparably to the Calibrated control, only the Randomized control has similarly tight error bars.
+
+%with scipy's curve\_fit using the Trust Region Reflective method 
+In this experiment, fitting the randomized benchmarking data reports one-qubit gate fidelities of $99.4\%$ for the calibrated pulse, $98.8\%$ for Pulse1, $99.4\%$ for Pulse2, $98.9\%$ for Pulse3, $98.6\%$ for Pulse4, and $99.0\%$ for the Randomized pulse.
+However, as one can see from looking at Figure \ref{fig:rb}, despite all controls performing comparably to the Calibrated control, only the Randomized control has similarly tight error bars.
 In the cases of each miscalibrated pulse, the error bars extend significantly, in often asymmetric ways, making usage of chi-square statistics, and errors on the fit less straightforward.
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using a balanced optimal control solution (BOCS) can reduce non-Markovian coherent error on a quantum channel by at least an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+We have shown numerically that using RBCs can reduce non-Markovian, coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
@@
 Moreover, even if a model is available, it might be computationally inconvenient to simulate, i.e.
-for more than a few qubits, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
+for more than a few qubits.%, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
 
-In these situations, one approach would be to use \textit{in situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
-While performing optimization this way would still be slow (requiring full process tomography, in general, to reconstruct the process matrix of a candidate balanced channel), one could intead select pulse sequences that are sensitive to known parameters of interest in the Hamiltonian and just run the minimization with respect to those terms.
-(e.g.
-if we suspect there is unwanted $Z\otimes Z$ crosstalk between qubits.)
+In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
+While performing a complete optimization in this way would still be slow, requiring full process tomography, one could intead optimize via partial tomography.
+By selecting pre-- and post --rotations that correspond to measuring pauli moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
 

### 2018-10-23 decorrelation/decorrelation.tex
including a bit more detail, feel free to revert this commit

@@
 One particular way of realizing randomized decoupling is Frame Randomization\cite{Wallman2016, Ware2018}.
-Frame Randomization can be used to average over noise by twirling error over an appropriately selected unitary 2-design, by inserting an additional precompilation step in the execution of quantum circuits.\cite{roy2009unitary} This has been demonstrated in existing systems\cite{Ware2018}, but can require intensive use of classical processors and waveform memory, and becomes more difficult when the gates being used are not in the Clifford group\needcite, as is the case in various quantum computing architectures.\needcite
+Frame Randomization can be used to average over noise by twirling error over an appropriately selected unitary 2-design, by inserting an additional precompilation step in the execution of quantum circuits.\cite{roy2009unitary} This has been demonstrated in existing systems\cite{Ware2018}, but can require intensive use of classical processors and waveform memory.
 
-Another approach is to consider constructing a family of unitaries that approximate a given gate, and averaging over them.
-In \cite{Campbell2017}, Campbell considers coherent error arising from unitary synthesis approximations algorithms like the Solovay-Kitaev Algorithm \cite{1612.01011}.
-He presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle.
-In that work, the primary emphasis was on resource counting, and diamond-norm error-bounds at level of unitary synthesis.
-In this paper, we explore a different but related problem: synthesizing physical controls and making them robust to drift.
-
-We propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
-The task of generating RBCs will fall to optimal control.
+Another way of performing randomized deocupling is through mixing unitaries.
+In \cite{Campbell2017}, Campbell presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle.
+In Campbell's work, he discusses such an oracle could be implemented via unitary synthesis approximations algorithms\cite{1612.01011}, and considers estimating and reducing resources costs that might arise during circuit compilation.
+In this paper we will we explore a different but related problem: synthesizing physical controls and making them robust to drift.
+Using optimal control routines as our oracle , we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
 
@@
 
-\section{Theory}
- Consider a family of control solutions, $c_i(t)$, where each member of the family approximates the same target gate with slightly different errors.
-That is, for a target gate $U_T$, the family consists of gates $U_i = \mathcal{T}e^{-i\int c_i(t)H(t, \vec{\delta})}$, where $\vec{\delta}$ are \textit{quasi-static}\cite{Ball2016} parameters of the Hamiltonian.
-Such a family of unitary approximations is called a \emph{balanced control} if there is a weight vector $\vec{\omega}$ that satisfies the following for some small $\alpha$,
+\section{Robustly Balanced Controls}
+ Consider the problem of trying to approximate a target unitary operation, $U_T$. Define a control solution $c_i(t)$ by  \begin{equation} 
+\mathcal{T}e^{-i\int c_i(t)H(t, \vec{\delta})} = U_i \approx U_T
+ \end{equation}
+ where $\vec{\delta}$ are meant to be \textit{quasi-static}\cite{Ball2016} parameters of a Hamiltonian, $H(t, \vec{\delta})$.
+A family of control solutions is called a \emph{balanced control} if there is probability distribution $\vec{\omega}$ that satisfies the following for some small $\alpha$,
 \begin{equation}\label{eq:1}
-  \frac{1}{N}\sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
+  \sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
 \end{equation}
 
-where $\vec{\omega}$ must be a proper probability distribution and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. Such a channel is defined as:
+where $\vec{\omega}$ must be a proper probability distribution and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. A depolarizing channel is defined as:
 \begin{equation}\label{eq:2}
@@
 
-This is equivalent to the condition given by Campbell\cite{Campbell2017}, that there exist a weight such that
+This is equivalent to the condition given by Campbell in \cite{Campbell2017}, that there exist a weight such that
 
@@
 \end{equation}
-However, we will be interested in a stronger condition.
-A balanced control is said to be \textit{robust to order $\ell$} if a generalized form of Equation \ref{eq:campbell-condition} holds, namely if for all $j \leq \ell$:
+however we will generalize this condition to define an RBC.
+A balanced control is said to be robust to order $\ell$ if a generalized form of Equation \ref{eq:campbell-condition} holds, namely if for all $1 \leq j \leq \ell$:
 \begin{equation}\label{eq:RBC}
-D_\ell = \sum_j \omega_j \frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}H_j(t,\vec{\delta})|_{\delta=\vec{0}}  = 0
+\begin{gathered}
+\sum_k\omega_k(\sum_{n=0}^j D^n_k)^j = 0\\
+D^n_k = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}...\partial\delta{i_n}}H_k(t,\vec{\delta})|_{\delta=\vec{0}}
+\end{gathered}
 \end{equation}
-
+Where the first sum is meant to result from Taylor expansion, and therefore will require matrix reshaping.
 These conditions imply that an $\ell^{th}$ order RBC ($\ell$RBC) is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
 To see this, write the error on each gate in the RBC as $U_j(\vec{\delta}) = exp(-i(\tilde{H}_j(\vec{0}) + \frac{\partial}{\partial\delta_i}\tilde{H}_j(d\delta_i) +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \tilde{H}_j(d\delta_i d\delta_k) + ...)U_T$, where $\tilde{H}(\delta)$ generates the error $U_j(\vec{\delta})U_T^{\dagger}$ over variations in $\vec{\delta}$.
-In this way, an $\ell$RBC satisfies Equation \ref{eq:1} to $\ell^{th}$ order.
+Then, by Taylor expanding $U_j(\vec{\delta})U_T^{\dagger}$ one finds that the the first $\ell$ derivatives of an $\ell RBC$ will be zero.
 
@@
 Naturally, if the control family is too small a solution won't exist.
-In addition, as in \cite{Campbell2017}, we need  $0\in $ Conv$[\{\frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}\tilde{H}_j(t,\vec{\delta})|_{\vec{\delta}=0}\}]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust unitaries.
+As in \cite{Campbell2017}, we need  $0\in $ Conv$[\{\frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}\tilde{H}_j(t,\vec{\delta})|_{\vec{\delta}=0}\}]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
+Finally one would like to ensure that the control family produced is not too large - that is given the family of controls, we would like to regularize the cost function to enforce sparsity.
+In this case, lasso regularization is insufficient as we already constrain the one norm of the vector we optimize over to be unity.
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and remains a convex problem.
 

### 2018-10-23 data/raw_data/GRAPE.py
everything on my machine

@@ -56,7 +56,7 @@ def control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt):
     for row in controls:
         step_hamiltonian = [control * control_hamiltonians[i] for i, control in enumerate(row)]
         evolution = scipy.linalg.expm(
-            -1.j * dt * (np.sum(ambient_hamiltonian, axis=0) + np.sum(step_hamiltonian, axis=0)))
+            -1.j * dt * (sum(ambient_hamiltonian) + np.sum(step_hamiltonian, axis=0)))
         unitaries.append(evolution)
     return unitaries
 
@@ -83,7 +83,8 @@ def grape_perf(ambient_hamiltonian, control_hamiltonians, controls, dt, target_o
     unitaries = control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt)
     final_unitary = reduce(np.dot, list(reversed(unitaries)), np.eye(unitaries[0].shape[0]))
     overlap = np.trace(adjoint(target_operator).dot(final_unitary))
-    return -overlap * np.conj(overlap)
+    perf = -overlap * np.conj(overlap)
+    return np.real(perf)
 
 
 def grape_gradient(ambient_hamiltonian, control_hamiltonians, controls, dt, target_operator):
@@ -147,7 +148,7 @@ def comp_avg_perf(pair):
 
 
 def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
-                       controls, detunings, dt, target_operator, deg=2, num_processors=7):
+                       controls, detunings, dt, target_operator, deg=3, num_processors=7):
     """
     Average the given func over noise using gaussian quadrature.
 
@@ -281,32 +282,16 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
                                            target_operator)
         grad = lambda controls: grape_gradient(ambient_hamiltonian, control_hamiltonians, controls,
                                                dt, target_operator)
+    import numpy as np
+    perf = lambda controls: grape_perf(ambient_hamiltonian*0, control_hamiltonians, controls, dt,
+                                       target_operator)
     dimension = np.shape(ambient_hamiltonian[0])[0]
     disp = True
     ftol = (1 - threshold)
     options = {"ftol": ftol,
                "disp": disp}
-
-
-    # num_samples = 10
-    # # We'll assume one control
-    # fwhm = 2.5
[…]

### 2018-10-23 data/raw_data/pauli_channel_approximation.py

@@ -78,8 +78,7 @@ class PCA(object):
 
     def __init__(self, num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
                  num_steps, time, threshold, detunings):
-        #self.seed = 138
-        self.seed = np.random.randint(1000)
+        self.seed = 139
         np.random.seed(self.seed)
         self.start = timemod.time()
         controlset = []
@@ -98,20 +97,14 @@ class PCA(object):
                            num_steps, time, threshold, random_detunings)
             controlset.append(result.reshape(-1, len(control_hamiltonians)))
             # controlset.append(np.array([1] * num_steps).reshape(-1, 1))
-        # self.controlset = np.array(controlset) + np.random.normal(0, .001,
-        #                                                           size=(np.array(controlset).shape))
-        controlset = np.array(controlset)
-        nums = np.array([.06, .04, -.04, -.06]) - .0093
-        a = np.array([np.array([[nums[0]/controlset.shape[1]] * controlset.shape[1], [nums[1]/controlset.shape[1]] * controlset.shape[1],
-                                                  [nums[2] / controlset.shape[1]] * controlset.shape[1], [nums[3] / controlset.shape[1]] * controlset.shape[1]]).T]).T
-        self.controlset = controlset + a
+        self.controlset = controlset
 
         self.detunings = detunings
         self.target_operator = target_operator
         self.dt = dt
         self.ambient_hamiltonian = ambient_hamiltonian
         self.control_hamiltonians = control_hamiltonians
-        self.assign_probs()
+        #self.assign_probs()
 
     def assign_probs(self):
         # Initialize random probabilities
@@ -193,189 +186,18 @@ class PCA(object):
         print(new_probs)
         return res.fun
 
-    # def plot_everything(self, num_processors=6, num_points=10):
-    #     """Plots the depolarizing noise and gate fidelity over all detunings, varying over the list
-    #      provided by itertools."""
-    #
-    #     values_to_plot = []
-    #     corr = []
-    #     import time
-    #     start = time.time()
-    #     for i, detuning in enumerate(self.detunings):
-    #         # values = (np.geomspace(1, 2**(num_points - 1), num_points) - 1)/(2**(num_points-1) -
-    #         #                                                                  1) * detuning[0]*200
[…]

### 2018-10-25 code/GRAPE.py
moving over code, and two notebooks with plots

@@ -1,0 +1,326 @@
+import itertools
+import numpy as np
+import scipy
+import scipy.optimize as optimize
+from numpy.polynomial.hermite import hermgauss
+from functools import reduce
+from mpi4py import MPI
+
+COMM = MPI.COMM_WORLD
+
+
+def split(container, count):
+    """
+    Simple function splitting a container into equal length chunks.
+    Order is not preserved but this is potentially an advantage depending on
+    the use case.
+    """
+    return [list(container)[_i::count] for _i in range(count)]
+
+
+def adjoint(operator):
+    """
+    Computes the adjoint of a given matrix.
+
+    :param numpy.array operator: Array to compute the adjoint of.
+    :return: The adjoint of operator.
+    :rtype: numpy.array
+    """
+    return np.conj(operator).T
+
+
+def control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt):
+    """
+    Given an controllable and a non-controllable hamiltonian, with controls and the time step size,
+    computes the unitaries that give the time evolution. e.g.
+
+    control_unitaries(I, [X], [[0],[1],[0],[1]], np.pi)
+    [I, X, I, X]
+
+    :param numpy.array ambient_hamiltonian: A square 2D array, corresponding to the uncontrollable
+     part of the system hamiltonian.
+    :param list control_hamiltonians: A list of square 2D numpy.arrays, corresponding to the
+     controllable terms in the hamiltonian. This should be as long as the second dimension of
+     controls.
+    :param numpy.array controls: A 2D numpy.array, whose rows represent time steps, and whose
+     jth column corresponds to the control amplitude for the jth element of control_hamiltonians.
+    :param float dt: The time to evolve each row of controls for.
+    :return: The list of unitaries corresponding to the discretized evolution of the system.
+    :rtype: list
+    """
+    if len(controls.shape) == 1:
+        controls = controls.reshape(-1, len(control_hamiltonians))
+    unitaries = []
+    for row in controls:
+        step_hamiltonian = [control * control_hamiltonians[i] for i, control in enumerate(row)]
+        evolution = scipy.linalg.expm(
+            -1.j * dt * (sum(ambient_hamiltonian) + np.sum(step_hamiltonian, axis=0)))
+        unitaries.append(evolution)
+    return unitaries
+
+
+def grape_perf(ambient_hamiltonian, control_hamiltonians, controls, dt, target_operator):
+    """
+    Evaluate the performance function :math: `\phi_4` as described in Khaneja et al.'s paper.
+
[…]

### 2018-10-25 code/convex.py

@@ -1,0 +1,156 @@
+from scipy.misc import derivative
+from itertools import product
+from functools import reduce
+from copy import deepcopy
+from GRAPE import control_unitaries
+from scipy.linalg import logm
+import cvxpy as cp
+import numpy as np
+
+DEFAULT_TOL = 1e-8
+
+
+def error(combo, controls, target_operator, control_hamiltonians, ambient_hamiltonian0, dt):
+    """Return the Hamiltonian that when exponentiated gives the error unitary from the target."""
+    adjoint_target = np.conj(target_operator.T)
+    newcontrols = deepcopy(controls)
+    ambient_hamiltonian = [deepcopy(ah).astype("float") for ah in ambient_hamiltonian0]
+    for cnum, value in enumerate(combo):
+        cnum -= len(ambient_hamiltonian0)
+        if cnum >= 0:
+            newcontrols[:, cnum] = newcontrols[:, cnum] * (1 + value)
+        if cnum < 0:
+            assert cnum == -1, "For one qubit, there is only one amb. term we consider."
+            idx = len(ambient_hamiltonian) - abs(cnum)
+            ambient_hamiltonian[idx] *= float(value)
+    # just check the first one
+    assert np.isclose(ambient_hamiltonian[0], np.conj(ambient_hamiltonian[0].T)).all()
+    for h in control_hamiltonians:
+        assert np.isclose(h, np.conj(h.T)).all()
+    step_unitaries = control_unitaries(ambient_hamiltonian,
+                                       control_hamiltonians,
+                                       newcontrols,
+                                       dt)
+    for u in step_unitaries:
+        assert np.isclose(np.conj(u.T).dot(u), np.eye(2)).all(), np.conj(u.T).dot(u)
+    unitary = reduce(lambda a, b: a.dot(b), step_unitaries)
+    error_gen = logm(adjoint_target.dot(unitary))
+    entry = (error_gen[0, 0] - error_gen[1, 1])/2
+    error_gen[0, 0] = entry
+    error_gen[1, 1] = -entry
+    return -1.j * error_gen
+
+
+def deg_deriv(controlset, target, control_hamiltonians, ambient_hamiltonian0, dt, deg):
+    ds = []
+    for control in controlset:
[…]

### 2018-10-25 code/pauli_channel_approximation.py

@@ -1,0 +1,227 @@
+import matplotlib.pyplot as plt
+plt.switch_backend('agg')
+from GRAPE import GRAPE, control_unitaries, adjoint
+import numpy as np
+import dill
+from functools import reduce
+from tqdm import tqdm
+import time as timemod
+from convex import all_derivs, optimal_weights, optimal_weights_1st_order
+from mpi4py import MPI
+import scipy
+import os
+from itertools import product
+
+COMM = MPI.COMM_WORLD
+
+I = np.eye(2)
+X = np.array([[0, 1], [1, 0]])
+Y = np.array([[0, -1.j], [1.j, 0]])
+Z = np.array([[1, 0], [0, -1]])
+PAULIS = [I, X, Y, Z]
+
+
+def generate_indices(num_points, order_desired):
+    num_indices = len(order_desired)
+    tuples = product(range(num_points), repeat=num_indices)
+    indices = [sum([num_points**(num_indices - 1 - order_desired[i]) * t[i] for i in range(num_indices)]) for t in tuples]
+    return indices
+
+
+def error_unitary(unitary, target):
+    """
+    Constructs the superoperator for the error unitary corresponding propagating forward by target,
+     and back by unitary.
+
+    :param np.array unitary: Control unitary realized in the computational basis.
+    :param np.array target: The desired unitary in the computational basis.
+    :return: The superoperator corresponding to the unitary postrotational error.
+    :rtype: numpy.array
+    """
+    error = adjoint(unitary).dot(target)
+    return np.kron(np.conj(error), error)
+
+
+def off_diagonal_projection(sop):
+    """
+    Computes a quantity proportional to the sum of the magnitudes of terms corresponding to non-stochastic evolution.
+
+    :param numpy.ndarry sop: Representation our operator as a superoperator, e.g. operating on vectorized density
+     matrices.
+    """
+    basis = PAULIS
+    for _ in range(int(np.log2(sop.shape[0]) / 2.0) - 1):
+        basis = [np.kron(base, pauli) for pauli in PAULIS for base in basis]
+    off_diagonal = 0
+    for i, base1 in enumerate(basis):
+        for j, base2 in enumerate(basis):
+            if i != j:
+                off_diagonal += np.abs(np.trace(adjoint(np.kron(base1, base2)).dot(sop))) ** 2
+    return off_diagonal
+
+
[…]

### 2018-10-27 decorrelation/decorrelation.tex

@@
 Moreover, by following a generalized version of the algorithm Campbell presents in \cite{Campbell2017}, we can find families of controls that are $\ell$RBCs, for any $\ell$.
-
+In this setting, we can relax Equation \ref{eq:RBC}, to be
+\begin{equation}\label{eq:RBC-relaxed}
+\begin{gathered}
+\sum_k\omega_kD^n_k = 0\\
+\end{gathered}
+\end{equation}
+In this context, since we are assuming that the derivatives are all of norm $\epsilon$, the above condition guarantees that the error unitary be no worse than $\sum^n\epsilon^2\delta^n$ near the origin -- all orders can be quadratically supressed.
 \section{A Simple Example}

### 2018-10-27 code/convex.py
repeated combo indices, and adding in special cases to dispatch on 1 and 2 q stuff

@@ -15,12 +15,19 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
     adjoint_target = np.conj(target_operator.T)
     newcontrols = deepcopy(controls)
     ambient_hamiltonian = [deepcopy(ah).astype("float") for ah in ambient_hamiltonian0]
+    combo = list(combo)
+    if len(combo) == 2:
+        combo = combo + combo[-1:]
+    else:
+        assert len(combo) == 5
+        combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo + combo[4:]
+        assert len(combo) == 7
+    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
     for cnum, value in enumerate(combo):
         cnum -= len(ambient_hamiltonian0)
         if cnum >= 0:
             newcontrols[:, cnum] = newcontrols[:, cnum] * (1 + value)
         if cnum < 0:
-            assert cnum == -1, "For one qubit, there is only one amb. term we consider."
             idx = len(ambient_hamiltonian) - abs(cnum)
             ambient_hamiltonian[idx] *= float(value)
     # just check the first one
@@ -32,7 +39,7 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
                                        newcontrols,
                                        dt)
     for u in step_unitaries:
-        assert np.isclose(np.conj(u.T).dot(u), np.eye(2)).all(), np.conj(u.T).dot(u)
+        assert np.isclose(np.conj(u.T).dot(u), np.eye(int(np.sqrt(target_operator.size)))).all(), np.conj(u.T).dot(u)
     unitary = reduce(lambda a, b: a.dot(b), step_unitaries)
     error_gen = logm(adjoint_target.dot(unitary))
     entry = (error_gen[0, 0] - error_gen[1, 1])/2
@@ -43,8 +50,12 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
 
 def deg_deriv(controlset, target, control_hamiltonians, ambient_hamiltonian0, dt, deg):
     ds = []
+    if target.shape == (2,2):
+        point = np.array([0, 0])
+    else:
[…]

### 2018-10-27 code/pauli_channel_approximation.py

@@ -161,6 +161,34 @@ def compute_dpn_and_fid(data):
 
     return projs, fidelities
 
+#
+# if __name__ == "__main__":
+#     COMM = MPI.COMM_WORLD
+#     I = np.eye(2)
+#     X = np.array([[0, 1], [1, 0]])
+#     Y = np.array([[0, -1.j], [1.j, 0]])
+#     Z = np.array([[1, 0], [0, -1]])
+#     ambient_hamiltonian = [Z]
+#     control_hamiltonians = [X, Y]
+#     detunings = [(1E-3, 1), (1E-3,  2)]
+#     target_operator = scipy.linalg.sqrtm(X)
+#     time = np.pi
+#     num_steps = 25
+#     threshold = 1 - .001
+#     num_controls = 750
+#     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
+#               num_steps, time, threshold, detunings)
+#
+#     if COMM.rank == 0:
+#         i = 0
+#         while os.path.exists("pickled_controls%s.pkl" % i):
+#             i += 1
+#         fh = open("pickled_controls%s.pkl" % i, "wb")
+#         dill.dump(pca, fh)
+#         pca.assign_weights()
+#         dill.dump(pca, fh)
+#         fh.close()
+
 
 if __name__ == "__main__":
     COMM = MPI.COMM_WORLD
@@ -168,60 +196,32 @@ if __name__ == "__main__":
     X = np.array([[0, 1], [1, 0]])
     Y = np.array([[0, -1.j], [1.j, 0]])
     Z = np.array([[1, 0], [0, -1]])
-    ambient_hamiltonian = [Z]
-    control_hamiltonians = [X, Y]
-    detunings = [(1E-3, 1), (1E-3,  2)]
-    target_operator = scipy.linalg.sqrtm(X)
-    time = np.pi
-    num_steps = 25
+    #CNOT = np.array([[1, 0, 0, 0], [0, -1, 0, 0], [0, 0, -1, 0], [0, 0, 0, 1]])
+    IZ = np.kron(I, Z)
+    ZI = np.kron(Z, I)
+    XI = np.kron(X, I)
+    IX = np.kron(I, X)
+    IY = np.kron(I, Y)
+    YI = np.kron(Y, I)
+    ZZ = np.kron(Z, Z)
+    entangle_ZZ = np.array([[1, 0, 0, 0], [0, 1.j, 0, 0], [0, 0, 1.j, 0], [0, 0, 0, 1]])
[…]

### 2018-10-27 code/convex.py
everything appears to be working - facotred out the extended first degree terms, and cleaned up pca generation a bit towards making it easy for kevin to run

@@ -20,7 +20,7 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
         combo = combo + combo[-1:]
     else:
         assert len(combo) == 5
-        combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo + combo[4:]
+        combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo[4:]
         assert len(combo) == 7
     assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
     for cnum, value in enumerate(combo):
@@ -111,8 +111,8 @@ def optimal_weights_1st_order(derivs, l, tol=DEFAULT_TOL):
         for ham_const in equalities:
             constraints += [np.real(ham_const) * omega == 0]
             constraints += [np.imag(ham_const) * omega == 0]
-
-        first_order = compute_first_order_term(derivs)
+        first_order = ham_consts[-1]
+        #first_order = compute_first_order_term(derivs)
         objective = cp.Minimize(cp.norm(np.real(first_order) * omega) + cp.norm(np.imag(first_order) * omega) + t)
         prob = cp.Problem(objective, constraints)
         result = prob.solve(solver=cp.CVXOPT, abstol=tol, abstol_inacc=tol)

### 2018-10-27 code/pauli_channel_approximation.py

@@ -106,6 +106,7 @@ class PCA(object):
         self.derivs = derivs
         self.weights = weights
         self.weights_0 = weights_0
+        print("Assigned weights.")
 
 
 def compute_dpn_and_fid(data):
@@ -161,42 +162,41 @@ def compute_dpn_and_fid(data):
 
     return projs, fidelities
 
-#
-# if __name__ == "__main__":
-#     COMM = MPI.COMM_WORLD
-#     I = np.eye(2)
-#     X = np.array([[0, 1], [1, 0]])
-#     Y = np.array([[0, -1.j], [1.j, 0]])
-#     Z = np.array([[1, 0], [0, -1]])
-#     ambient_hamiltonian = [Z]
-#     control_hamiltonians = [X, Y]
-#     detunings = [(1E-3, 1), (1E-3,  2)]
-#     target_operator = scipy.linalg.sqrtm(X)
-#     time = np.pi
-#     num_steps = 25
-#     threshold = 1 - .001
-#     num_controls = 750
-#     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
-#               num_steps, time, threshold, detunings)
-#
-#     if COMM.rank == 0:
-#         i = 0
-#         while os.path.exists("pickled_controls%s.pkl" % i):
-#             i += 1
-#         fh = open("pickled_controls%s.pkl" % i, "wb")
-#         dill.dump(pca, fh)
-#         pca.assign_weights()
-#         dill.dump(pca, fh)
-#         fh.close()
 
-
-if __name__ == "__main__":
+def gen_1q():
     COMM = MPI.COMM_WORLD
     I = np.eye(2)
     X = np.array([[0, 1], [1, 0]])
     Y = np.array([[0, -1.j], [1.j, 0]])
     Z = np.array([[1, 0], [0, -1]])
-    #CNOT = np.array([[1, 0, 0, 0], [0, -1, 0, 0], [0, 0, -1, 0], [0, 0, 0, 1]])
+    ambient_hamiltonian = [Z]
+    control_hamiltonians = [X, Y]
+    detunings = [(1E-3, 1), (1E-3,  2)]
+    target_operator = scipy.linalg.sqrtm(X)
+    time = np.pi
+    num_steps = 25
+    threshold = 1 - .001
+    num_controls = 750
[…]

### 2018-10-27 code/convex.py
notebooks updated, and code should be set to generate 2Q results

@@ -8,6 +8,7 @@ import cvxpy as cp
 import numpy as np
 
 DEFAULT_TOL = 1e-8
+# Not being used right now.
 
 
 def error(combo, controls, target_operator, control_hamiltonians, ambient_hamiltonian0, dt):
@@ -100,6 +101,8 @@ def optimal_weights_1st_order(derivs, l, tol=DEFAULT_TOL):
     mini = float('inf')
     res = None
     for i in range(len(derivs[0])):
+        if i % 100:
+            print(f"Done with convex problem {i} out of {len(derivs[0])}")
         ham_consts = []
         for deriv in derivs:
             ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
@@ -115,7 +118,7 @@ def optimal_weights_1st_order(derivs, l, tol=DEFAULT_TOL):
         #first_order = compute_first_order_term(derivs)
         objective = cp.Minimize(cp.norm(np.real(first_order) * omega) + cp.norm(np.imag(first_order) * omega) + t)
         prob = cp.Problem(objective, constraints)
-        result = prob.solve(solver=cp.CVXOPT, abstol=tol, abstol_inacc=tol)
+        result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER)# abstol=tol, abstol_inacc=tol)
         if result < mini and omega.value is not None:
             mini = result
             res = omega.value
@@ -148,6 +151,8 @@ def optimal_weights(derivs, l, tol=DEFAULT_TOL):
     mini = float('inf')
     res = None
     for i in range(len(derivs[0])):
+        if i % 100:
+            print(f"Done with convex problem {i} out of {len(derivs[0])}")
         ham_consts = []
         for deriv in derivs:
             ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
@@ -161,7 +166,7 @@ def optimal_weights(derivs, l, tol=DEFAULT_TOL):
             constraints += [np.imag(ham_const)*omega == 0]
         objective = cp.Minimize(cp.norm(np.real(ham_consts[-1])*omega) + cp.norm(np.imag(ham_consts[-1])*omega) + t)
         prob = cp.Problem(objective, constraints)
-        result = prob.solve(solver=cp.CVXOPT, abstol=tol, abstol_inacc=tol)
+        result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER)# abstol=tol, abstol_inacc=tol)
[…]

### 2018-10-27 code/pauli_channel_approximation.py

@@ -184,9 +184,11 @@ def gen_1q():
         i = 0
         while os.path.exists("pickled_controls%s.pkl" % i):
             i += 1
-        fh = open("pickled_controls%s.pkl" % i, "wb")
+        fh = open("just_pickled_controls%s.pkl" % i, "wb")
         dill.dump(pca, fh)
         pca.assign_weights()
+        fh.close()
+        fh = open("pickled_controls%s.pkl" % i, "wb")
         dill.dump(pca, fh)
         fh.close()
 
@@ -210,21 +212,23 @@ def gen_2q():
     detunings = [(.001, 1), (.001, 1), (.001, 2), (.001, 2), (.001, 1)]
     target_operator = entangle_ZZ
     time = 2. * np.pi
-    num_steps = 50
+    num_steps = 40
     threshold = 1 - .001
-    num_controls = 1
+    num_controls = 200
     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
               num_steps, time, threshold, detunings)
     if COMM.rank == 0:
-        # print("TOOK {}".format(pca.time))
-        import os
         i = 0
         while os.path.exists("pickled_controls%s.pkl" % i):
             i += 1
+        fh = open("just_pickled_controls%s.pkl" % i, "wb")
+        dill.dump(pca, fh)
+        pca.assign_weights()
+        fh.close()
         fh = open("pickled_controls%s.pkl" % i, "wb")
         dill.dump(pca, fh)
         fh.close()
 
 
 if __name__ == '__main__':
-    gen_1q()
+    gen_2q()

### 2018-10-28 code/pauli_channel_approximation.py
adjusted pauli_channel_approximationbecause my python wasn't build with tkinter

@@ -1,5 +1,6 @@
+import matplotlib
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
-plt.switch_backend('agg')
 from GRAPE import GRAPE, control_unitaries, adjoint
 import numpy as np
 import dill

### 2018-10-28 decorrelation/decorrelation.tex
Added some notes and todos to tex file

@@
 \begin{abstract}
-Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated.
-While convenient for simulation, these error models are often unphysical.
-Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial and temporal correlation, provided the correlation is sufficiently weak and decays sufficiently quickly, but at the cost of a significantly lower threshold.
-The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing noise correlations.
-We propose to introduce similar methods at the physical gate synthesis level to effect the decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
-We discuss and show numerically that these controls can be made robust to drift, and experimentally demonstrate our approach on a superconducting qubit.
+Coherent errors in quantum operations are ubiquitous.
+Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate.
+Furthermore, coherent errors are considerably more difficult to model than stochastic errors, and understanding their impact on a generic quantum circuit or algorithm can be challenging.
+In this talk, we discuss using robust optimal control techniques to construct many different implementations of a target gates, each with a different coherent error.
+As Hastings and Campbell have recently shown, randomly sampling over that ensemble yields an effective quantum channel that well approximates our target, but with dramatically suppressed coherent error.
+Our results extend those of Hastings and Campbell to include robustness to drifting external control parameters.
+We have implemented these constructions using a superconducting qubits and will discuss randomized benchmarking results consistent with a marked reduction in coherent error.
 \end{abstract}
@@
 \section{Introduction}
+\note{Point to work by Hastings and Cambell, discuss robust controls, what is the problem that we're trying to solve.
+Here's the basic idea.
+We're dealing with robust controls, and we implement them on the Rigetti 19Q-Acorn chip.
+Do we want to talk about threshold theorems?
+Read Laflamme and Flamia papers and see if they are relevant.
+Keep discussion of nonmarkovianty and correlation of errors.
+Include discussion of drift.}
 
@@
 \section{Robustly Balanced Controls}
+\note{Include the figure with the arrows and the derivation of the higher order terms and discussion that the optimal control that we're using is sufficient often to guarantee that the bare hamiltonian is asmall, so that we can take the expansion only to first order in delta in the easy way.
+Discuss the impact on diamond norm.
+We are going to use the mixing theorem from Campbell, so we'll have to quote that result.
+}
  Consider the problem of trying to approximate a target unitary operation, $U_T$. Define a control solution $c_i(t)$ by  \begin{equation}
@@
 \section{A Simple Example}
+\note{This particular instance is NOT robust, but we can construct one that IS. }
 As a trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
@@
 To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomials\cite{abramowiz1972handbook}.
+\note{Discuss how this is a proxy for the higher-order derivatives being small. Discuss the difference between the step control functions and the cost function in the optimization.}
 

### 2018-10-28 decorrelation/decorrelation.tex
some changes to the paper, still not done yet

--- 2018-10-27 decorrelation/decorrelation.tex
@@
 % \tableofcontents
-\title{Decorrelating Errors in Quantum Gates by Random Gate Synthesis}
+\title{Robust Decorrelation of Errors in Quantum Gates by Random Gate Synthesis}
 
@@
 \subsection{Random Gate Synthesis}
- Generating RBCs can be done in a variety of ways, in this paper we consider using optimal control.
-In particular, one could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}.
-For our numerics, we chose to use the GRAPE algorithm.
-First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$.
-Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing control amplitude associated with the $i^{th}$ time step and the $j^{th}$ hamiltonian, we can write an approximate unitary for any timestep of evolution as:
+ In this paper, we consider using optimal control to generate RBCs.
+One could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}, and for our numerics we chose to use the GRAPE algorithm.
+First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$, given a Hamiltonian with controlled and uncontrolled terms.
+Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ Hamiltonian, we can write an the unitary for any timestep of evolution as:
 \begin{equation}\label{eq:3}
@@
 \end{equation}
-Then, to measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
+To measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
 
@@
 However, in \cite{Khaneja2005} Khaneja et al.
-derive a simple update formula that is correct to first order.
+derive an update formula that is correct to first order, and efficient to compute.
 In particular one can show that:
@@
 
-Because we our trying to generate high-order RBCs, we want to generate controls that perform well over a wide range of parameter values ($\delta$).
-To do this, we modified the gradient in GRAPE to instead be:
+Because we our trying to generate high-order RBCs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
 \begin{align}\label{quadrature}
@@
 with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
-To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost functions as a low order polynomials\cite{abramowiz1972handbook}.
+To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost function as a low order polynomial\cite{abramowiz1972handbook} (in particular degree 5).
+Note that despite updating the gradient, we did not change the cost function.
+The termination condition for the gradient ascent loop is still just that the controls perform well in the absence of drift.
+This is not a fundamental requirement of the routine, but rather was done to make finding solutions with $J(U) < 1 - \epsilon$  less computationally taxing.
 
@@
 After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_i$ such that the collection of controls form an $\ell$RBC as described in Equation \ref{eq:RBC}.
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework it does not constrain the resulting channel to be decomposable into a given family of controls.
+The following routine, however, will produce a channel defined explicitly in terms of given family of controls.
 To do this, for each control $U_i(\vec{\delta})$ we find the unitary error channel $\mathcal{E}_i(\vec{\delta})$ such that $\mathcal{E}_i(\vec{\delta})U_i(\vec{\delta})=U_T$, where $U_T$ is the target gate.
-By taking the logarithm of these error maps, we then get a family of Hamiltonians $\tilde{H}_j(\delta)$, and conside the following quadratic program whose solutions satisfies the robustness conditions given in Equation \ref{eq:RBC}.
-Namely:
+By taking the logarithm of these error maps, we then get a family of Hamiltonians $\tilde{H}_j(\delta)$, and consider the following quadratic program whose solutions satisfy the robustness conditions given in Equation \ref{eq:RBC}:
 \begin{equation}\label{eq:minimization}
   \begin{split}
-    &\textbf{minimize: } ||D_{\ell}^T\omega||\\
-    &\textbf{subject to: } \forall i<\ell,\ D_i=0\\
-   	&\phantom{\textbf{subject to: }}\sum \omega_j = 1\\
-   	&\phantom{\textbf{subject to: }}\sum 0 \le \omega_j \le 1    
+    &\underset{\omega\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
   \end{split}
@@
 
-The question still remains -- when does this quadratic program have a solution.
-Naturally, if the control family is too small a solution won't exist.
-As in \cite{Campbell2017}, we need  $0\in $ Conv$[\{\frac{\partial^{\ell}}{\partial\delta_{i_1}...\partial\delta{i_\ell}}\tilde{H}_j(t,\vec{\delta})|_{\vec{\delta}=0}\}]$.
+If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
 This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
-Finally one would like to ensure that the control family produced is not too large - that is given the family of controls, we would like to regularize the cost function to enforce sparsity.
-In this case, lasso regularization is insufficient as we already constrain the one norm of the vector we optimize over to be unity.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and remains a convex problem.
+In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
+We would also like to ensure that the control family produced is not too large, as this would make the approach much less practical.
+Given the family of controls, we would like to regularize the cost function to enforce sparsity.
+In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via convex programming by extending Equation \ref{eq:minimization}:
+\begin{equation} 
+\begin{split}
+\underset{n\in[N]}{\textbf{minimize}}\{\\
+    &\underset{\omega\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
+    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\\}
+\end{split}
+\end{equation}, where $\lambda$ is a hyperparameter to be optimized over. In practice, we have found that this can lead to 2RBCs with less than ten controls.
 
@@
 This can be achieved via a generalization of Campbell's Algorithm and by modifying the oracle query to ask for controls whose derivatives also satisfy certain properties.
-
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework it does not constrain the resulting channel to be decomposable into a given family of controls.
-Our routine, on the other hand, produces a channel defined explicitly in terms of given family of controls.
 
@@
 
- Using Equation \ref{eq:minimization}, we then generated the optimal weighting $\omega_i$.
+WE NO LONGER USED THIS ROUTINE, SINCE WE WERE MINIMIZING THE OFF DIAGONAL ELEMENTS.
+Using Equation \ref{eq:minimization}, we then generated the optimal weighting $\omega_j$.
 To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.
@@
 %with scipy's curve\_fit using the Trust Region Reflective method 
-In this experiment, fitting the randomized benchmarking data reports one-qubit gate fidelities of $99.4\%$ for the calibrated pulse, $98.8\%$ for Pulse1, $99.4\%$ for Pulse2, $98.9\%$ for Pulse3, $98.6\%$ for Pulse4, and $99.0\%$ for the Randomized pulse.
-However, as one can see from looking at Figure \ref{fig:rb}, despite all controls performing comparably to the Calibrated control, only the Randomized control has similarly tight error bars.
-In the cases of each miscalibrated pulse, the error bars extend significantly, in often asymmetric ways, making usage of chi-square statistics, and errors on the fit less straightforward.
-
-This is consistent with the result shown in \cite{Ball2016} that for particular non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
+In this experiment, fitting the randomized benchmarking data reports one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the Randomized pulse.
+In the cases of each miscalibrated pulse, the error bars extend significantly, which is consistent with the results shown in \cite{Ball2016} that for particular non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
 On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.

### 2018-10-28 code/pauli_channel_approximation.py
fixing MPI support with docs

@@ -176,7 +176,7 @@ def gen_1q():
     time = np.pi
     num_steps = 25
     threshold = 1 - .001
-    num_controls = 750
+    num_controls = 10
     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
               num_steps, time, threshold, detunings)
 
@@ -231,4 +231,4 @@ def gen_2q():
 
 
 if __name__ == '__main__':
-    gen_2q()
+    gen_1q()

### 2018-10-28 code/GRAPE.py
deg 2 -> deg 3

@@ -139,7 +139,7 @@ def comp_avg_perf(pair):
 
 
 def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
-                       controls, detunings, dt, target_operator, deg=2):
+                       controls, detunings, dt, target_operator, deg=3):
     """
     Average the given func over noise using gaussian quadrature.
 
@@ -216,7 +216,7 @@ def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
                                      detunings, dt, target_operator)))
     # Gather results on rank 0.
     results = MPI.COMM_WORLD.allgather(results)
-
+    #print(f"Number of results on {COMM.rank} is now {len(results)}")
     # if COMM.rank == 0:
     #     # Flatten list of lists.
     results = [_i for temp in results for _i in temp]

### 2018-10-29 decorrelation/decorrelation.tex
more changes to the paper, adding caps where we need to fill in data

--- 2018-10-28 decorrelation/decorrelation.tex
@@
 \begin{equation}\label{eq:1}
-  \sum_{i=1}^N \omega_i U_i \rho U_i^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
+  \sum_{i=1}^N \omega_j U_j \rho U_j^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
 \end{equation}
@@
 In this simple example, we can analytically find a solution to Equation \ref{eq:1}.
-Specifically, by choosing weights $\omega_i=\frac{1}{2}$, we see:
+Specifically, by choosing weights $\omega_j=\frac{1}{2}$, we see:
 
@@
 \subsection{RBC Approximation}
-After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_i$ such that the collection of controls form an $\ell$RBC as described in Equation \ref{eq:RBC}.
+After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_j$ such that the collection of controls form an $\ell$RBC as described in Equation \ref{eq:RBC}.
 Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework it does not constrain the resulting channel to be decomposable into a given family of controls.
@@
   \begin{split}
-    &\underset{\omega\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
     &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
@@
 In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
-We would also like to ensure that the control family produced is not too large, as this would make the approach much less practical.
-Given the family of controls, we would like to regularize the cost function to enforce sparsity.
+
+To make sure the routine remains practical, we would like to regularize our objective function to enforce sparsity.
 In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via convex programming by extending Equation \ref{eq:minimization}:
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
 \begin{equation} 
 \begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{\\
-    &\underset{\omega\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
+\underset{n\in[N]}{\textbf{minimize}}\{
+    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
     &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\\}
+    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
 \end{split}
-\end{equation}, where $\lambda$ is a hyperparameter to be optimized over. In practice, we have found that this can lead to 2RBCs with less than ten controls.
+\end{equation} where $\lambda$ is a hyperparameter to be optimized over. In practice, for $\lambda=1E-4$, we have found that this can lead to 1RBCs with fewer than ten members.
 
@@
 We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
-When generating the controls, we chose an total evolution time of $T=\pi$, a number of steps $N=100$, and a threshold infidelity of $1E-3$, with $\epsilon, \delta \sim \mathcal{N}(0, .001)$.
+When generating the controls, we chose an total evolution time of $T=FILL IN$, a number of steps $N=FILL IN$, a Gaussian quadrature degree of $d=FILL IN$, and a threshold infidelity of $1E-3$, with $\epsilon, \delta \sim \mathcal{N}(0, .001)$.
 The results can be seen in \ref{fig:num}.
-In particular, over a wide region about the origin, the diamond norm can be seen to have been reduced by over an order of magnitude.
+In particular, over a wide region about the origin, the diamond norm can be seen to have been reduced by over an order of magnitude from the members of the RBC, and the 1RBC is performs moderately worse at the origin, while outperforming the 0RBC for larger detunings.
 
@@
 \end{equation}
-We again consider $\epsilon_j, \delta_j, \eta \sim .001$, however and a threshold infidelity of $1E-3$, however we increased the total evolution time to $T=4\pi$, and increased the number of steps to $N=400$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
+We again consider $\epsilon_j, \delta_j, \eta \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$, however we increased the total evolution time to $T=FILL IN$, and increased the number of steps to $N=FILL IN$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
 The results also show a reduction of an order of magnitude in diamond norm about the origin, and for a wide neighborhood around it.
@@
 In particular we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a RBC on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement an RBC on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
-WE NO LONGER USED THIS ROUTINE, SINCE WE WERE MINIMIZING THE OFF DIAGONAL ELEMENTS.
-Using Equation \ref{eq:minimization}, we then generated the optimal weighting $\omega_j$.
+ Using a similar routine to Equation \ref{eq:minimization}, we then generated the optimal weightings $\omega$.
+Instead of performing the convex optimization routine, we used the COBYLA minimizer in \texttt{scipy.optimize} to perform constrained minimization of the off-diagonal elements of the produced channel.
+This is a form of Sequential Quadratic
+Programming\cite{wright1999numerical}, and is equivalent to the convex optimization problem given for producing a 0RBC.
 To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.

### 2018-10-29 code/pauli_channel_approximation.py
Fixed a bug where PCA was called without a 'dirname' argument. The call was redundent, so I commented it out.

@@ -222,8 +222,8 @@ def gen_2q():
     num_steps = 40
     threshold = 1 - .001
     num_controls = 200
-    pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
-              num_steps, time, threshold, detunings)
+    #pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
+    #          num_steps, time, threshold, detunings)
     dirname = None
     if COMM.rank == 0:
         i = 0

### 2018-10-30 code/pauli_channel_approximation.py
updating pauli_channel_approx to run the right thing this time

@@ -232,4 +232,4 @@ def gen_2q():
 
 
 if __name__ == '__main__':
-    gen_1q()
+    gen_2q()

### 2018-10-30 code/pauli_channel_approximation.py
saving controls as we go!

@@ -75,7 +75,8 @@ class PCA(object):
      most like Pauli Channels."""
 
     def __init__(self, num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
-                 num_steps, time, threshold, detunings):
+                 num_steps, time, threshold, detunings, dirname):
+        COMM = MPI.COMM_WORLD
         self.seed = 138
         np.random.seed(self.seed)
         self.start = timemod.time()
@@ -92,6 +93,8 @@ class PCA(object):
             result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
                            num_steps, time, threshold, random_detunings)
             controlset.append(result.reshape(-1, len(control_hamiltonians)))
+            if COMM.rank == 0:
+                dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
         self.controlset = controlset
         self.detunings = detunings
         self.target_operator = target_operator
@@ -177,19 +180,22 @@ def gen_1q():
     time = np.pi
     num_steps = 25
     threshold = 1 - .001
-    num_controls = 10
-    pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
-              num_steps, time, threshold, detunings)
-
+    num_controls = 4
+    dirname = None
     if COMM.rank == 0:
         i = 0
         while os.path.exists("pickled_controls%s.pkl" % i):
             i += 1
-        fh = open("just_pickled_controls%s.pkl" % i, "wb")
+        dirname = f'controls_{i}'
+        os.mkdir(dirname)
+    pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
+              num_steps, time, threshold, detunings, dirname)
+    if COMM.rank == 0:
+        fh = open(os.path.join(dirname, "just_pickled_controls%s.pkl" % i), 'wb')
         dill.dump(pca, fh)
         pca.assign_weights()
         fh.close()
-        fh = open("pickled_controls%s.pkl" % i, "wb")
+        fh = open(os.path.join(dirname, "pickled_controls%s.pkl" % i), "wb")
         dill.dump(pca, fh)
         fh.close()
 
@@ -232,4 +238,4 @@ def gen_2q():
 
 
 if __name__ == '__main__':
-    gen_2q()
+    gen_1q()

### 2018-10-30 code/pauli_channel_approximation.py
changes for 2q

@@ -224,18 +224,24 @@ def gen_2q():
     num_controls = 200
     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
               num_steps, time, threshold, detunings)
+    dirname = None
     if COMM.rank == 0:
         i = 0
         while os.path.exists("pickled_controls%s.pkl" % i):
             i += 1
-        fh = open("just_pickled_controls%s.pkl" % i, "wb")
+        dirname = f'controls_{i}'
+        os.mkdir(dirname)
+    pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
+              num_steps, time, threshold, detunings, dirname)
+    if COMM.rank == 0:
+        fh = open(os.path.join(dirname, "just_pickled_controls%s.pkl" % i), 'wb')
         dill.dump(pca, fh)
         pca.assign_weights()
         fh.close()
-        fh = open("pickled_controls%s.pkl" % i, "wb")
+        fh = open(os.path.join(dirname, "pickled_controls%s.pkl" % i), "wb")
         dill.dump(pca, fh)
         fh.close()
 
 
 if __name__ == '__main__':
-    gen_1q()
+    gen_2q()

### 2018-10-30 code/GRAPE.py
removing a few print statements

@@ -139,7 +139,7 @@ def comp_avg_perf(pair):
 
 
 def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
-                       controls, detunings, dt, target_operator, deg=3):
+                       controls, detunings, dt, target_operator, deg=2):
     """
     Average the given func over noise using gaussian quadrature.
 
@@ -210,7 +210,7 @@ def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
     results = []
     for job in jobs:
 
-        #print("{} has {} jobs, doing job {}".format(COMM.rank, len(jobs), job[0]))
+        print("{} has {} jobs, doing job {}".format(COMM.rank, len(jobs), job))
         results.append(comp_avg_perf((
                                      job, controls, func, ambient_hamiltonian, control_hamiltonians,
                                      detunings, dt, target_operator)))
@@ -282,8 +282,8 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
 
     avg_perf = perf(result.x)
 
-    print("PERF AT ZERO: {}".format(perf_at_zero/(dimension ** 2)))
-    print("Avg perf: {}".format(-avg_perf/(dimension ** 2)))
+    #print("PERF AT ZERO: {}".format(perf_at_zero/(dimension ** 2)))
+    #print("Avg perf: {}".format(-avg_perf/(dimension ** 2)))
 
     import sys
     sys.stdout.flush()
@@ -297,8 +297,8 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
                                   result.x, dt,
                                   target_operator)
         avg_perf = perf(result.x)
-        print("PERF AT ZERO: {}".format(perf_at_zero / (dimension ** 2)))
-        print("Avg perf: {}".format(-avg_perf / (dimension ** 2)))
+        #print("PERF AT ZERO: {}".format(perf_at_zero / (dimension ** 2)))
+        #print("Avg perf: {}".format(-avg_perf / (dimension ** 2)))
         sys.stdout.flush()
     return result.x
 
@@ -320,8 +320,8 @@ if __name__ == "__main__":
               detunings=[.0001] * (len(control_hamiltonians) + len(ambient_hamiltonian)),
               threshold=.9)
     controls = x.reshape(-1, len(control_hamiltonians))
-    print(reduce(lambda a, b: a.dot(b),
[…]

### 2018-10-30 code/pauli_channel_approximation.py

@@ -84,7 +84,7 @@ class PCA(object):
         dt = time / num_steps
         self.num_controls = num_controls
         for i in tqdm(range(num_controls)):
-            print("CONTROL {}".format(i))
+            #print("CONTROL {}".format(i))
             random_detunings = []
             for detuning in detunings:
                 random_detunings.append((detuning[0], detuning[1]))
@@ -110,7 +110,7 @@ class PCA(object):
         self.derivs = derivs
         self.weights = weights
         self.weights_0 = weights_0
-        print("Assigned weights.")
+        #print("Assigned weights.")
 
 
 def compute_dpn_and_fid(data):
@@ -219,7 +219,7 @@ def gen_2q():
     detunings = [(.001, 1), (.001, 1), (.001, 2), (.001, 2), (.001, 1)]
     target_operator = entangle_ZZ
     time = 2. * np.pi
-    num_steps = 40
+    num_steps = 50
     threshold = 1 - .001
     num_controls = 200
     #pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
@@ -230,7 +230,8 @@ def gen_2q():
         while os.path.exists("pickled_controls%s.pkl" % i):
             i += 1
         dirname = f'controls_{i}'
-        os.mkdir(dirname)
+        if not os.path.exists(dirname):
+            os.mkdir(dirname)
     pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
               num_steps, time, threshold, detunings, dirname)
     if COMM.rank == 0:

### 2018-10-30 code/GRAPE.py
better logging

@@ -210,7 +210,7 @@ def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
     results = []
     for job in jobs:
 
-        print("{} has {} jobs, doing job {}".format(COMM.rank, len(jobs), job))
+        #print("{} has {} jobs, doing job {}".format(COMM.rank, len(jobs), job))
         results.append(comp_avg_perf((
                                      job, controls, func, ambient_hamiltonian, control_hamiltonians,
                                      detunings, dt, target_operator)))
@@ -226,7 +226,7 @@ def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
 
 
 def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps, time,
-          threshold=1 - 1E-3, detunings=None):
+          threshold=1 - 1E-3, detunings=None, iteration=0):
     """
     Perform the GRAPE algorithm to approximate target_gate in num_steps with time given by time,
     using ambient_hamiltonian as the uncontrolled hamiltonian and control_hamiltonians as the
@@ -289,6 +289,7 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
     sys.stdout.flush()
 
     while -perf_at_zero/(dimension ** 2) < threshold:
+        print(f"\n\n\nRetrying control {iteration}\n\n\n")
         controls = (2.0 * np.random.rand(1, int(len(control_hamiltonians) * num_steps)) - 1.0) * .1
         result = optimize.minimize(fun=perf, x0=controls, jac=grad, method='tnc', options=options,
                                    bounds=bounds)

### 2018-10-30 code/pauli_channel_approximation.py

@@ -91,7 +91,7 @@ class PCA(object):
             import sys
             sys.stdout.flush()
             result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
-                           num_steps, time, threshold, random_detunings)
+                           num_steps, time, threshold, random_detunings, i)
             controlset.append(result.reshape(-1, len(control_hamiltonians)))
             if COMM.rank == 0:
                 dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))

### 2018-10-30 code/GRAPE.py
removing scipy print statements

@@ -261,7 +261,7 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
                                                target_operator)
 
     dimension = np.shape(ambient_hamiltonian[0])[0]
-    disp = True
+    disp = False
     ftol = (1 - threshold)
     options = {"ftol": ftol,
                "disp": disp}

### 2018-10-30 code/pauli_channel_approximation.py
decreasing num_steps and num_controls

@@ -219,9 +219,9 @@ def gen_2q():
     detunings = [(.001, 1), (.001, 1), (.001, 2), (.001, 2), (.001, 1)]
     target_operator = entangle_ZZ
     time = 2. * np.pi
-    num_steps = 50
+    num_steps = 20
     threshold = 1 - .001
-    num_controls = 200
+    num_controls = 100
     #pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,
     #          num_steps, time, threshold, detunings)
     dirname = None

### 2018-10-31 code/GRAPE.py
small changes for ooperating params

@@ -290,6 +290,7 @@ def GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator, num_steps,
 
     while -perf_at_zero/(dimension ** 2) < threshold:
         print(f"\n\n\nRetrying control {iteration}\n\n\n")
+        sys.stdout.flush()
         controls = (2.0 * np.random.rand(1, int(len(control_hamiltonians) * num_steps)) - 1.0) * .1
         result = optimize.minimize(fun=perf, x0=controls, jac=grad, method='tnc', options=options,
                                    bounds=bounds)

### 2018-10-31 code/pauli_channel_approximation.py

@@ -219,7 +219,7 @@ def gen_2q():
     detunings = [(.001, 1), (.001, 1), (.001, 2), (.001, 2), (.001, 1)]
     target_operator = entangle_ZZ
     time = 2. * np.pi
-    num_steps = 20
+    num_steps = 40
     threshold = 1 - .001
     num_controls = 100
     #pca = PCA(num_controls, ambient_hamiltonian, control_hamiltonians, target_operator,

### 2018-10-31 code/GRAPE.py
changing parallelization to be over controls, rather than averaging...

@@ -157,73 +157,71 @@ def average_over_noise(func, ambient_hamiltonian, control_hamiltonians,
     :rtype: rtype of func
     """
     controls = controls.reshape(-1, len(control_hamiltonians))
-
-    if COMM.rank == 0:
-        corr = []
-        if type(detunings[0]) != tuple:
-            pass
-        else:
-            new_detunings = []
-            for i, detune in enumerate(detunings):
-                new_detunings.append(detune[0])
-                for _ in range(detune[1]):
-                    corr.append(i)  # use the ith detuning more than once
-            detunings = new_detunings
-        points, weights = hermgauss(deg)
-        nonzero_detunings = np.where(np.array(detunings) != 0)[0]
-        zero_detunings = np.where(np.array(detunings) == 0)[0]
-
-        pairs = [list(zip(np.sqrt(detuning) * points, weights)) for i, detuning in
-                 enumerate(np.array(detunings)[nonzero_detunings])]
-        for index in zero_detunings:
-            pairs.insert(index, [(0, 1)])
-        combinations = itertools.product(*pairs)
-        # Expand them if there are correlations
-        if corr:
-            new_combinations = []
-            for combo in combinations:
-                new_combo = []
-                last_number = -1
-                for index in corr:
-                    if index == last_number:
-                        new_number = False
-                    else:
-                        new_number = True
-                    last_number = index
-                    pair = combo[index]
-                    if not new_number:
-                        pair = (pair[0], 1)
-                    new_combo.append(pair)
-                new_combinations.append(new_combo)
-            combinations = new_combinations
-        jobs = combinations
-        # Split into however many cores are available.
-        jobs = split(jobs, COMM.size)
+    #
+    # if COMM.rank == 0:
+    corr = []
+    if type(detunings[0]) != tuple:
+        pass
     else:
-        jobs = None
+        new_detunings = []
+        for i, detune in enumerate(detunings):
+            new_detunings.append(detune[0])
+            for _ in range(detune[1]):
+                corr.append(i)  # use the ith detuning more than once
+        detunings = new_detunings
+    points, weights = hermgauss(deg)
+    nonzero_detunings = np.where(np.array(detunings) != 0)[0]
+    zero_detunings = np.where(np.array(detunings) == 0)[0]
+
+    pairs = [list(zip(np.sqrt(detuning) * points, weights)) for i, detuning in
+             enumerate(np.array(detunings)[nonzero_detunings])]
[…]

### 2018-10-31 code/pauli_channel_approximation.py

@@ -83,8 +83,12 @@ class PCA(object):
         controlset = []
         dt = time / num_steps
         self.num_controls = num_controls
-        for i in tqdm(range(num_controls)):
-            #print("CONTROL {}".format(i))
+        for i in range(num_controls):
+            if (i + 1) // COMM.size != COMM.rank:
+                continue
+            print(f'{COMM.rank} doing control {i}')
+            np.random.seed(self.seed + i)
+            print("CONTROL {}".format(i))
             random_detunings = []
             for detuning in detunings:
                 random_detunings.append((detuning[0], detuning[1]))
@@ -93,14 +97,16 @@ class PCA(object):
             result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
                            num_steps, time, threshold, random_detunings, i)
             controlset.append(result.reshape(-1, len(control_hamiltonians)))
-            if COMM.rank == 0:
-                dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
-        self.controlset = controlset
-        self.detunings = detunings
-        self.target_operator = target_operator
-        self.dt = dt
-        self.ambient_hamiltonian = ambient_hamiltonian
-        self.control_hamiltonians = control_hamiltonians
+            dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
+        controlset = MPI.COMM_WORLD.gather(controlset, root=0)
+        if COMM.rank == 0:
+            controlset = [item for sublist in controlset for item in sublist]
+            self.controlset = controlset
+            self.detunings = detunings
+            self.target_operator = target_operator
+            self.dt = dt
+            self.ambient_hamiltonian = ambient_hamiltonian
+            self.control_hamiltonians = control_hamiltonians
 
     def assign_weights(self, l1=0, l2=1E-3):
         derivs = all_derivs(self.controlset, self.target_operator, self.control_hamiltonians, self.ambient_hamiltonian,
@@ -110,7 +116,7 @@ class PCA(object):
         self.derivs = derivs
         self.weights = weights
         self.weights_0 = weights_0
-        #print("Assigned weights.")
+        print("Assigned weights.")
 
 
 def compute_dpn_and_fid(data):
[…]

### 2018-10-31 code/pauli_channel_approximation.py
correct parallelization, could use better logging

@@ -84,11 +84,10 @@ class PCA(object):
         dt = time / num_steps
         self.num_controls = num_controls
         for i in range(num_controls):
-            if (i + 1) // COMM.size != COMM.rank:
+            if (i % COMM.size) != COMM.rank:
                 continue
             print(f'{COMM.rank} doing control {i}')
             np.random.seed(self.seed + i)
-            print("CONTROL {}".format(i))
             random_detunings = []
             for detuning in detunings:
                 random_detunings.append((detuning[0], detuning[1]))
@@ -98,6 +97,7 @@ class PCA(object):
                            num_steps, time, threshold, random_detunings, i)
             controlset.append(result.reshape(-1, len(control_hamiltonians)))
             dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
+        print(f'controlset has {len(controlset)} members')
         controlset = MPI.COMM_WORLD.gather(controlset, root=0)
         if COMM.rank == 0:
             controlset = [item for sublist in controlset for item in sublist]
@@ -251,4 +251,4 @@ def gen_2q():
 
 
 if __name__ == '__main__':
-    gen_2q()
+    gen_1q()

### 2018-10-31 code/pauli_channel_approximation.py
changing to run 2q

@@ -251,4 +251,4 @@ def gen_2q():
 
 
 if __name__ == '__main__':
-    gen_1q()
+    gen_2q()

### 2018-10-31 code/pauli_channel_approximation.py
moving directory name generation out of rank=0 loop branch in gen2q

@@ -83,30 +83,30 @@ class PCA(object):
         controlset = []
         dt = time / num_steps
         self.num_controls = num_controls
-        for i in range(num_controls):
-            if (i % COMM.size) != COMM.rank:
-                continue
-            print(f'{COMM.rank} doing control {i}')
-            np.random.seed(self.seed + i)
-            random_detunings = []
-            for detuning in detunings:
-                random_detunings.append((detuning[0], detuning[1]))
-            import sys
-            sys.stdout.flush()
-            result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
-                           num_steps, time, threshold, random_detunings, i)
-            controlset.append(result.reshape(-1, len(control_hamiltonians)))
-            dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
-        print(f'controlset has {len(controlset)} members')
-        controlset = MPI.COMM_WORLD.gather(controlset, root=0)
-        if COMM.rank == 0:
-            controlset = [item for sublist in controlset for item in sublist]
-            self.controlset = controlset
-            self.detunings = detunings
-            self.target_operator = target_operator
-            self.dt = dt
-            self.ambient_hamiltonian = ambient_hamiltonian
-            self.control_hamiltonians = control_hamiltonians
+        # for i in range(num_controls):
+        #     if (i % COMM.size) != COMM.rank:
+        #         continue
+        #     print(f'{COMM.rank} doing control {i}')
+        #     np.random.seed(self.seed + i)
+        #     random_detunings = []
+        #     for detuning in detunings:
+        #         random_detunings.append((detuning[0], detuning[1]))
+        #     import sys
+        #     sys.stdout.flush()
+        #     result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
+        #                    num_steps, time, threshold, random_detunings, i)
+        #     controlset.append(result.reshape(-1, len(control_hamiltonians)))
+        #     dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
+        # print(f'controlset has {len(controlset)} members')
+        # controlset = MPI.COMM_WORLD.gather(controlset, root=0)
+        # if COMM.rank == 0:
[…]

### 2018-10-31 code/pauli_channel_approximation.py
uncommenting important code

@@ -83,25 +83,25 @@ class PCA(object):
         controlset = []
         dt = time / num_steps
         self.num_controls = num_controls
-        # for i in range(num_controls):
-        #     if (i % COMM.size) != COMM.rank:
-        #         continue
-        #     print(f'{COMM.rank} doing control {i}')
-        #     np.random.seed(self.seed + i)
-        #     random_detunings = []
-        #     for detuning in detunings:
-        #         random_detunings.append((detuning[0], detuning[1]))
-        #     import sys
-        #     sys.stdout.flush()
-        #     result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
-        #                    num_steps, time, threshold, random_detunings, i)
-        #     controlset.append(result.reshape(-1, len(control_hamiltonians)))
-        #     dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
-        # print(f'controlset has {len(controlset)} members')
-        # controlset = MPI.COMM_WORLD.gather(controlset, root=0)
-        # if COMM.rank == 0:
-        #     controlset = [item for sublist in controlset for item in sublist]
-        #     self.controlset = controlset
+        for i in range(num_controls):
+            if (i % COMM.size) != COMM.rank:
+                continue
+            print(f'{COMM.rank} doing control {i}')
+            np.random.seed(self.seed + i)
+            random_detunings = []
+            for detuning in detunings:
+                random_detunings.append((detuning[0], detuning[1]))
+            import sys
+            sys.stdout.flush()
+            result = GRAPE(ambient_hamiltonian, control_hamiltonians, target_operator,
+                           num_steps, time, threshold, random_detunings, i)
+            controlset.append(result.reshape(-1, len(control_hamiltonians)))
+            dill.dump(result.reshape(-1, len(control_hamiltonians)), open(os.path.join(dirname, f'control_{i}'), 'wb'))
+        print(f'controlset has {len(controlset)} members')
+        controlset = MPI.COMM_WORLD.gather(controlset, root=0)
+        if COMM.rank == 0:
+            controlset = [item for sublist in controlset for item in sublist]
+            self.controlset = controlset
         self.detunings = detunings
         self.target_operator = target_operator
         self.dt = dt
@@ -228,8 +228,6 @@ def gen_2q():
     num_steps = 40
     threshold = 1 - .001
     num_controls = 100
[…]

### 2018-11-15 code/convex.py
changes before reverting

@@ -164,7 +164,7 @@ def optimal_weights_1st_order_no_constraints(derivs, l, tol=DEFAULT_TOL):
     first_order = ham_consts[-1]
     objective = cp.Minimize(cp.norm(np.real(first_order) * omega) + cp.norm(np.imag(first_order) * omega))
     prob = cp.Problem(objective, constraints)
-    result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER, abstol=tol, abstol_inacc=tol)
+    result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER)#, abstol=tol, abstol_inacc=tol)
     return omega.value
 
 
@@ -209,8 +209,10 @@ def optimal_weights(derivs, l, tol=DEFAULT_TOL):
             constraints += [np.imag(ham_const)*omega == 0]
         objective = cp.Minimize(cp.norm(np.real(ham_consts[-1])*omega) + cp.norm(np.imag(ham_consts[-1])*omega) + t)
         prob = cp.Problem(objective, constraints)
-        result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER, abstol=tol, abstol_inacc=tol)
+        result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER)#, abstol=tol, abstol_inacc=tol)
         if result < mini and omega.value is not None:
             mini = result
             res = omega.value
     return res
+
+

### 2018-11-15 code/pauli_channel_approximation.py

@@ -109,18 +109,21 @@ class PCA(object):
         self.ambient_hamiltonian = ambient_hamiltonian
         self.control_hamiltonians = control_hamiltonians
 
-    def assign_weights(self, l1=1E-3, l2=1E-3):
+    def assign_weights_0(self, l2=1E-3):
         derivs = all_derivs(self.controlset, self.target_operator, self.control_hamiltonians, self.ambient_hamiltonian,
                             self.dt, 1)
         for i, d in enumerate(derivs):
             if i == 1:
                 derivs[i] = np.delete(d, np.s_[2], 1)
-        weights = optimal_weights_1st_order(derivs, l1)
         weights_0 = optimal_weights(derivs[:1], l2)
         self.derivs = derivs
-        self.weights = weights
         self.weights_0 = weights_0
-        print("Tried assigning weights.")
+        print("Tried assigning zeroth order weights.")
+
+    def assign_weights(self, l1=1E-3):
+        weights = optimal_weights_1st_order(self.derivs, l1)
+        self.weights = weights
+        print("Tried assigning order weights.")
 
 
 def compute_dpn_and_fid(data):

### 2018-11-15 decorrelation/decorrelation.tex
adding notebook, and udpating paper with a short paragraph about 2q results

@@
 In this paper we will we explore a different but related problem: synthesizing physical controls and making them robust to drift.
-Using optimal control routines as our oracle , we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
+Using optimal control routines as our oracle, we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
 
@@
 \subsection{2Q Gates}\label{2Q Gates}
- For a two-qubit example, we chose $ZZ(\frac{\pi}{2})=\exp{(-i\frac{\pi}{4}\sigma_z\otimes\sigma_z)}$. Our control Hamiltonian is given as:
+ For a two-qubit example, we chose $iSWAP$. Our control Hamiltonian is given as:
 \begin{equation} \label{eq:2Qham}
@@
 H(\vec{\epsilon}, \vec{\delta}, \eta, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ (1+\eta)c(t) \exp{(-i\frac{\pi}{4}\sigma_z^1\otimes\sigma_z^2})
+&+ k(XX + YY)
 \end{split}
 \end{equation}
-We again consider $\epsilon_j, \delta_j, \eta \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$, however we increased the total evolution time to $T=FILL IN$, and increased the number of steps to $N=FILL IN$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
-The results also show a reduction of an order of magnitude in diamond norm about the origin, and for a wide neighborhood around it.
+We again consider $\epsilon_j, \delta_j \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$.
+In the two qubit case, however, the evolution time was constrained by the interaction Hamiltonian.
+In particular, we required a time of FILLIN so that GRAPE could find controls that performed a high fidelity iSWAP.
+Due to the na\"ivety of GRAPE, however, all the controls generated have nearly the same sensitivity to $\epsilon_j$.
+If we want to generate an $\ell RBC$ for $\ell > 0$, we need to ensure that the derivatives of the controls produced by our routine are both small and various enough that they can be combined in a way that averages to zero.
+To this end, we manually produced a collection of so-called bang-bang decoupling sequences.
+An example of such a sequence is show in FILL IN A FIGURE HERE.
+These controls all are constructed in such a way that one of the two qubits is flipped for some duration of the gate, during which a fraction of accrued RZ errors from frequency detuning errors on either qubit can be echoed away.
+When the convex solver is given these controls, it finds an optimal weighting that performs comparably with the one qubit example.
 

### 2018-11-23 code/convex.py
a notebook with a baby 2q result

@@ -24,6 +24,7 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
         combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo[4:]
         assert len(combo) == 7
     assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
+    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
     for cnum, value in enumerate(combo):
         cnum -= len(ambient_hamiltonian0)
         if cnum >= 0:
@@ -60,7 +61,8 @@ def deg_deriv(controlset, target, control_hamiltonians, ambient_hamiltonian0, dt
         point = np.array([0, 0])
     else:
         point = np.array([0, 0, 0, 0, 0])
-    for control in controlset:
+    for i, control in enumerate(controlset):
+        print("Control {} derivative.".format(i))
         d = compute_ith_derivative(lambda x: error(x, control, target, control_hamiltonians, ambient_hamiltonian0, dt), point, tuple(), deg, target.size)
         ds.append(d)
     ds = np.array(ds)
@@ -279,7 +281,7 @@ def compute_first_order_term(derivs):
 def optimal_weights(derivs, l, tol=DEFAULT_TOL):
     mini = float('inf')
     res = None
-    for i in range(len(derivs[0])):
+    for i in range(1):#range(len(derivs[0])):
         try:
             if i % 10 == 0:
                 print(f"Done with convex problem {i} out of {len(derivs[0])}")
@@ -288,13 +290,13 @@ def optimal_weights(derivs, l, tol=DEFAULT_TOL):
                 ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
             omega = cp.Variable(len(derivs[0]))
             t = cp.Variable(1)
-            constraints = [0 <= omega, omega <= 1/l, sum(omega) == 1/l, t >= 0]
+            constraints = [0 <= omega, omega <= 1, sum(omega) == 1, l*t >= 0]
             constraints += [omega[i] >= cp.inv_pos(t)]
             equalities = ham_consts[:1] # include the min for the first one
             for ham_const in equalities:
                 constraints += [np.real(ham_const) * omega == 0]
                 constraints += [np.imag(ham_const) * omega == 0]
-            objective = cp.Minimize(t/l + cp.norm(np.real(ham_consts[-1]) * omega, 1) + cp.norm(np.imag(ham_consts[-1]) * omega, 1))
[…]

### 2018-11-23 code/diamond.py

@@ -95,7 +95,7 @@ def diamond_norm( jamiolkowski_matrix ):
 
     prob = cvx.Problem(objective, constraints)
     import cvxpy as cp
-    prob.solve(solver="CVXOPT")
+    prob.solve(solver="CVXOPT", kktsolver=cp.ROBUST_KKTSOLVER)
 
     return prob.value
 

### 2018-11-24 code/convex.py
cleaning up optimal weights functions

@@ -6,6 +6,7 @@ from GRAPE import control_unitaries
 from scipy.linalg import logm
 import cvxpy as cp
 import numpy as np
+from scipy.linalg import norm
 
 DEFAULT_TOL = 1e-8
 
@@ -277,81 +278,97 @@ def compute_first_order_term(derivs):
     first_order = hdh + dhh + dh
     return first_order
 
+#
+# def optimal_weights(derivs, l, tol=DEFAULT_TOL):
+#     mini = float('inf')
+#     res = None
+#     for i in range(1):#range(len(derivs[0])):
+#         try:
+#             if i % 10 == 0:
+#                 print(f"Done with convex problem {i} out of {len(derivs[0])}")
+#             ham_consts = []
+#             for deriv in derivs:
+#                 ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
+#             omega = cp.Variable(len(derivs[0]))
+#             t = cp.Variable(1)
+#             constraints = [0 <= omega, omega <= 1, sum(omega) == 1, l*t >= 0]
+#             constraints += [omega[i] >= cp.inv_pos(t)]
+#             equalities = ham_consts[:1] # include the min for the first one
+#             for ham_const in equalities:
+#                 constraints += [np.real(ham_const) * omega == 0]
+#                 constraints += [np.imag(ham_const) * omega == 0]
+#             objective = cp.Minimize(t + cp.norm(np.real(ham_consts[-1]) * omega, 1) + cp.norm(np.imag(ham_consts[-1]) * omega, 1))
+#
+#             # objective = cp.Minimize(
+#             #     cp.norm(np.real(ham_consts[-1]) * omega) + cp.norm(np.imag(ham_consts[-1]) * omega) + t/l) # + cp.norm(np.real(ham_consts[-1]) * omega, 1) + cp.norm(np.imag(ham_consts[-1]) * omega, 1))
+#             prob = cp.Problem(objective, constraints)
+#             result = prob.solve(solver=cp.CVXOPT)# abstol=tol, abstol_inacc=tol, verbose=True)
+#             if result < mini and omega.value is not None:
+#                 mini = result
+#                 res = omega.value
+#         except cp.SolverError:
+#             continue
+#     return res
 
-def optimal_weights(derivs, l, tol=DEFAULT_TOL):
+
+def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=None, sparsity=False):
     mini = float('inf')
[…]

### 2018-11-24 code/convex.py
sqrtx and sqrty working on master, 2q is next

@@ -324,8 +324,8 @@ def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=N
                     ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
                 omega = cp.Variable(len(derivs[0]))
                 t = cp.Variable(1)
-                constraints = [0 <= omega, omega <= 1, sum(omega) == 1, sparsity_param*t >= 0]
-                constraints += [omega[i] >= cp.inv_pos(t)]
+                constraints = [0 <= omega, omega <= 1, sum(omega) == 1, t >= 0]
+                constraints += [omega[i] >= cp.inv_pos(t) * sparsity_param]
                 equalities = ham_consts[:-1]
                 for ham_const in equalities:
                    constraints += [np.real(ham_const) * omega == 0]
@@ -371,4 +371,5 @@ def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=N
         _ = prob.solve(solver=cp.MOSEK, verbose=True)
         res = omega.value
     return res
+
 

### 2018-11-24 code/convex.py
CLOSE TO WHAT WE WANT DONT MOVE

@@ -326,7 +326,7 @@ def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=N
                 t = cp.Variable(1)
                 constraints = [0 <= omega, omega <= 1, sum(omega) == 1, t >= 0]
                 constraints += [omega[i] >= cp.inv_pos(t) * sparsity_param]
-                equalities = ham_consts[:-1]
+                equalities = ham_consts[:1]
                 for ham_const in equalities:
                    constraints += [np.real(ham_const) * omega == 0]
                    constraints += [np.imag(ham_const) * omega == 0]
@@ -335,17 +335,17 @@ def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=N
                                       + cp.norm(np.real(ham_consts[-1]) * omega)
                                       + cp.norm(np.imag(ham_consts[-1]) * omega))
                 if l1_constraint:
-                    real_norm = np.matrix(norm(np.real(ham_consts[-1]), 2, 0))
-                    imag_norm = np.matrix(norm(np.imag(ham_consts[-1]), 2, 0))
-                    objective_argument += l1_param * (real_norm + imag_norm) * omega
+                    ham_norm = np.matrix(norm(np.real(ham_consts[-1]), 1, 0))
+                    objective_argument += cp.norm(l1_param * (ham_norm) * omega, 1)
                 objective = cp.Minimize(objective_argument)
 
                 prob = cp.Problem(objective, constraints)
-                result = prob.solve(solver=cp.MOSEK, verbose=True)
+                result = prob.solve(solver=cp.MOSEK)#, verbose=True)
                 if result < mini and omega.value is not None:
                     mini = result
                     res = omega.value
             except cp.SolverError:
+                print("FAILED")
                 continue
     else:
         ham_consts = []
@@ -353,7 +353,7 @@ def optimal_weights(derivs, l1_constraint=False, l1_param=None, sparsity_param=N
             ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
         omega = cp.Variable(len(derivs[0]))
         constraints = [0 <= omega, omega <= 1, sum(omega) == 1]
-        equalities = ham_consts[:-1]
+        equalities = ham_consts[:1]
         for ham_const in equalities:
             constraints += [np.real(ham_const) * omega == 0]
             constraints += [np.imag(ham_const) * omega == 0]
[…]

### 2018-11-25 decorrelation/numerics.tex
short separate (very rough) blurb about the numerics, and updated plots in the one qubit notebooks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RevTeX 4.1 LaTeX
% Kevin C. Young
% Scalable & Secure Systems Research (08961)
% Thu Mar  5 15:29:19 PST 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\setlength{\jot}{10pt}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\usepackage{lipsum}

\begin{document}

\section{Numerics}
In this section, we numerically assess the performance of 0RBCs and 1RBCs. In particular we consider two tunable qubits, coupled by a resonant exchange interaction, inspired by systems like that in \cite{https://arxiv.org/pdf/1604.03076.pdf}.  For the one-qubit case then, we generate a 1RBC for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$. Our control Hamiltonian is given as:
\begin{equation}\label{eq:1Qham}
  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
where $\epsilon$ corresponds to fluctuations in qubit frequency given by noise on the flux line, and $\delta$ corresponds to fluctuations in the drive amplitude given by noise on the qubit RF drive line. Using the MOSEK solver in cvxpy, and imposing the sparsity constraint in \cite{SPARTSITY}, we generated weights for 0RBCs and 1RBCs, containing just ten controls. The controls were generated via the GRAPE algorithm described in Section \ref{GRAPE SECTION}, assuming Gaussian Noise with mean 0, and standard deviation $.001$. We gave GRAPE a total evolution time of $\pi$, compared with the required $\frac{pi}{2}$ time for the shortest path. We discretized the evolution into 25 steps, and generated 200 controls for the convex solver to choose from. The resutls are shown in \ref{FIGURE1}  and\ref{FIGURE2}. In both cases it can be seen that near the origin the 0RBC and 1RBC outperform the constituent controls by two orders of magnitude in diamond norm, and away from the origin the 0RBC can be seen to increase in diamond norm more quickly than the 1RBC.

\begin{figure}[htb]
  \centering
  \includegraphics[scale=.2]{figures/SQRTX}

\caption{0RBC and 1RBC performance for $RX(\frac{\pi}{2})$, as compared to each other, and members of the control families. At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm. Away from the origin the 1RBC can be seen to be flatter than the 0RBC, outperforming at 1\% error.}
\end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[scale=.2]{figures/SQRTY}
\caption{0RBC and 1RBC performance for $RX(\frac{\pi}{2})$, as compared to each other, and members of the control families. At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm. Away from the origin the 1RBC can be seen to be flatter than the 0RBC, outperforming at .5\% error.}
\end{figure}

For the two qubit example we extend our one qubit model to include a resonant exchange interaction. Our control Hamiltonian is given as:
\begin{equation} \label{eq:2Qham}
\begin{split}
H(\vec{\epsilon}, \vec{\delta}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ k(XX + YY)
\end{split}
\end{equation}

There were several difficulties in considering this particular Hamiltonian, and for more interesting results one might consider a Hamiltonian with a control on the interaction -- such as that of a tunable coupler used in \ref{https://arxiv.org/pdf/1402.7367.pdf}. With that Hamiltonian it is non-trial to construct control solutions that are insensitive to detuning errors on either qubit, since such sequences also tend to decouple the entangling interaction.

Moreover, when attemping to construct control solutions for \ref{eq:2Qham} GRAPE failed to find anything non-trivial. Therefore for this example we constructed analytic bangbang \ref{BANGBANG} sequences that flip both qubits at different times in the sequence to affect a decoupling of detuning errors, while remaining invariant to the eigenspaces of the interaction term. To give the control family a variety of different errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%. A plot of typical control amplitude sequence is given in Figure  \ref{FIGURE}.

Using the same piecewise constant control solution as in the one qubit case, we considered 100 steps, with a total evolution time of $\frac{5\pi}{2}$, the time required for the $XX + YY$ interaction to generate an iSWAP gate in the absence of any other controls. In this case, we treated the $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple the tuning errors as taking only one time step, to avoid significant errors arising from mixing the eigenspaces of the interaction term. In practice this could be accomplished instead by turning off the resonance, performing the $\pi$ pulse, and turning the interaction back on. The particular collection of bang-bang sequences considered were all combinations of of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step. This resulted in a control family of 1024 controls. We did not apply the sparsity constraint to the solutions, however over 100 of the controls have less than $.5$\% of support, so it is feasible that the sparsity constraint could be successfully applied.

The $0RBC$ succesfully finds weights that minimize the 0th order term in the error Hamiltonian to zero within numerical precision, but with nonzero first derivative. Given the 1RBC minimization problem, the solver can also successfully supress the first derivative, while keeping the zeroth order term 0. At the origin, both RBCs can be seen to perform equally well, and better than members of the control family. Away from the origin both RBCs can be seen to perform over half an order of magnitude better in diamond norm than members of the control family, with the 1RBC degrading in quality more slowl than the 0RBC.

There is much more work that can be done investigating other Hamiltonians, for other kinds of noise, and more interesting compositive pulse sequences that might be system dependent. In addition, imposing the $\ell_1$ constraint has the potential to increase performance of $RBC$s when the members of the control family have varied performance (constrasted with the scenario given in Campbell's paper \ref{Campbell} where all controls are assumed to have error bounded by $\epsilon$.) Investigating the trade off between controls with slightly worse error but more interesting derivative may provide more favorable performance increases.

Finally, much of the numerical work here was limited by the same simplicity that makes the GRAPE algorithm useful. Future work could modify the derivative in the GRAPE algorithm to include derivative information to in addition to finding controls with bounded error, GRAPE finds controls with not only bounded derivative, but also derivatives that are wrong in a way that can cancel out the derivatives of other controls in the RBC. These results demonstrate numerically that RBCs are feasible and tractable, and provide an algorithmic way to compute optimal weights for minimizing sensitive to drift.

\end{document}

### 2018-11-26 decorrelation/decorrelation.tex
Added figure

--- 2018-10-29 decorrelation/decorrelation.tex
@@
   \label{fig:simple_example}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace.pdf}
+  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
+These error Hamiltonians lie in a vector space.
+a) Four effective Hamiltonians.
+The origin is not contained in their convex hull, so there are no balanced control solutions.
+b) The origin is contained in the covex hull after adding an additional control solution.
+Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
+c) The error Hamiltonians shown with their derivative with respect to a control parameter.
+As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
+d) The derivatives also lie in a vector space.
+If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order robust balanced control solution.}
+  \label{fig:vectorspace}
 \end{figure}

### 2018-11-28 decorrelation/mixed_unitaries.tex
A few draft updates and new tex document

--- 2018-11-26 decorrelation/decorrelation.tex
@@
 % \tableofcontents
-\title{Robust Decorrelation of Errors in Quantum Gates by Random Gate Synthesis}
+\title{Mixing Unitary Operators for Real and Simulated Quantum Information Processing}
 
@@
 \begin{abstract}
-Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated.
-While convenient for simulation, these error models are often unphysical.
-Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial and temporal correlation, provided the correlation is sufficiently weak and decays sufficiently quickly, but at the cost of a significantly lower threshold.
-The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing noise correlations.
-We propose to introduce similar methods at the physical gate synthesis level to effect the decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
-We discuss and show numerically that these controls can be made robust to drift, and experimentally demonstrate our approach on a superconducting qubit.
+Quantum information processors (QIPs) can suffer from a number of differnt kinds of errors.
 \end{abstract}
@@
 
+% ==============================================================================
+% Section: Introduction
+% ==============================================================================
 \section{Introduction}
+\label{sec:introduction}
 
-Steady progress has been made in the theory of quantum error correction, proving higher thresholds for increasingly general models of noise \cite{Aharonov2006, 1609.00510, https://doi.org/10.7907/z96m34sc, Kubica2018, Wang2003, Campbell2017}.
-These results show that quantum computation is feasible, however recent NISQ \cite{Preskill2018} devices have noise that is not only often above known thresholds, but that also violates fundamental assumptions made by the models used in these results\cite{Kelly2018, BlumeKohout2017, Klimov2018}, such as independence of errors\cite{Knill1998} and Markovianity \cite{Kitaev1997}.
+% ==============================================================================
+% Section: Mixed Unitary Processes
+% ==============================================================================
+\section{Mixed Unitary Processes}
+\label{sec:mixed_unitary_processes}
 
-When noise can be accurately modeled as Markovian, existing work often makes approximations to make problems tractable.
-For example, Pauli channels are often used to model systems due to their classical simulability\cite{quant-ph/9807006}, even in the absence of physical motivation\cite{Aliferis2007, Knill2005, Wang2011, DuclosCianci2010, Wootton2012, Bombin2012, Puzzuoli2014, aliferis2008accuracy}.
-One approach, then, would be to use these thresholds to give a loose lower bound for thresholds in other systems\cite{Puzzuoli2014}.
-Such an approach will produce overly-pessimistic bounds that may not be reflective of a system's actual performance.
+% ==============================================================================
+% Section: Robustly Mixed Unitary Processes
+% ==============================================================================
+\section{Robustly Mixed Unitary Processes}
+\label{sec:robustly_mixed}
 
-When noise is non-Markovian, the situation is much worse.
-Not only will the Markovian models used in threshold calculations be wrong, but assumptions that underpin characterization routines will be violated.
-Randomized benchmarking and tomography will report incorrect answers without any syndrome in the case of non-Markovian noise \cite{Merkel2013} and gate-set tomography will report that a system fails to be Markovian, but without saying in what way.
-
-An early proposal for fixing these problems is randomized decoupling\cite{Viola2005, Viola} -- by introducing classical randomness into quantum computations, both coherent and non-Markovian noise can be transformed to incoherent, independent, and Markovian noise.
-
-One particular way of realizing randomized decoupling is Frame Randomization\cite{Wallman2016, Ware2018}.
-Frame Randomization can be used to average over noise by twirling error over an appropriately selected unitary 2-design, by inserting an additional precompilation step in the execution of quantum circuits.\cite{roy2009unitary} This has been demonstrated in existing systems\cite{Ware2018}, but can require intensive use of classical processors and waveform memory.
-
-Another way of performing randomized deocupling is through mixing unitaries.
-In \cite{Campbell2017}, Campbell presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle.
-In Campbell's work, he discusses such an oracle could be implemented via unitary synthesis approximations algorithms\cite{1612.01011}, and considers estimating and reducing resources costs that might arise during circuit compilation.
-In this paper we will we explore a different but related problem: synthesizing physical controls and making them robust to drift.
-Using optimal control routines as our oracle , we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).
+% ==============================================================================
+% Section: Figures
+% ==============================================================================
+\section{Figures}
+\label{sec:figures}
 
@@
 
-\section{Robustly Balanced Controls}
- Consider the problem of trying to approximate a target unitary operation, $U_T$. Define a control solution $c_i(t)$ by  \begin{equation}
-\mathcal{T}e^{-i\int c_i(t)H(t, \vec{\delta})} = U_i \approx U_T
- \end{equation}
- where $\vec{\delta}$ are meant to be \textit{quasi-static}\cite{Ball2016} parameters of a Hamiltonian, $H(t, \vec{\delta})$.
-A family of control solutions is called a \emph{balanced control} if there is probability distribution $\vec{\omega}$ that satisfies the following for some small $\alpha$,
-\begin{equation}\label{eq:1}
-  \sum_{i=1}^N \omega_j U_j \rho U_j^\dagger = DPN[\alpha]\left(U_T \rho U_T^\dagger \right)
-\end{equation}
-
-where $\vec{\omega}$ must be a proper probability distribution and $DPN[\alpha](\rho)$ is a depolarizing noise channel, with strength $\alpha$. A depolarizing channel is defined as:
-\begin{equation}\label{eq:2}
-  DPN[\alpha](\rho) \rightarrow (1-\alpha)\rho + \alpha\sum p_i \sigma_i\rho\sigma_i
-\end{equation}
-with $p_i$ summing to one.
-
-This is equivalent to the condition given by Campbell in \cite{Campbell2017}, that there exist a weight such that
-
-\begin{equation}\label{eq:campbell-condition}
-\sum \omega_j H_j(t, \vec{\delta})|_{\delta=\vec{0}} = 0
-\end{equation}
-however we will generalize this condition to define an RBC.
-A balanced control is said to be robust to order $\ell$ if a generalized form of Equation \ref{eq:campbell-condition} holds, namely if for all $1 \leq j \leq \ell$:
-\begin{equation}\label{eq:RBC}
-\begin{gathered}
-\sum_k\omega_k(\sum_{n=0}^j D^n_k)^j = 0\\
-D^n_k = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}...\partial\delta{i_n}}H_k(t,\vec{\delta})|_{\delta=\vec{0}}
-\end{gathered}
-\end{equation}
-Where the first sum is meant to result from Taylor expansion, and therefore will require matrix reshaping.
-These conditions imply that an $\ell^{th}$ order RBC ($\ell$RBC) is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
-To see this, write the error on each gate in the RBC as $U_j(\vec{\delta}) = exp(-i(\tilde{H}_j(\vec{0}) + \frac{\partial}{\partial\delta_i}\tilde{H}_j(d\delta_i) +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \tilde{H}_j(d\delta_i d\delta_k) + ...)U_T$, where $\tilde{H}(\delta)$ generates the error $U_j(\vec{\delta})U_T^{\dagger}$ over variations in $\vec{\delta}$.
-Then, by Taylor expanding $U_j(\vec{\delta})U_T^{\dagger}$ one finds that the the first $\ell$ derivatives of an $\ell RBC$ will be zero.
-
-In all of the above, we will be interested in the case where $\alpha \approx \epsilon^2$, with $\epsilon$ being diamond distance from each member of the RBC to $U_T$.
-Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments then we know that $\vec{\omega}$ exists that satisfies Equation \ref{eq:1}.
-Then, following from the mixing lemma proven by both Campbell and Hastings\cite{1612.01011}, we can bound the the diamond distance from a balanced control to $U_T$ by $\epsilon^2$.
-Moreover, by following a generalized version of the algorithm Campbell presents in \cite{Campbell2017}, we can find families of controls that are $\ell$RBCs, for any $\ell$.
-In this setting, we can relax Equation \ref{eq:RBC}, to be
-\begin{equation}\label{eq:RBC-relaxed}
-\begin{gathered}
-\sum_k\omega_kD^n_k = 0\\
-\end{gathered}
-\end{equation}
-In this context, since we are assuming that the derivatives are all of norm $\epsilon$, the above condition guarantees that the error unitary be no worse than $\sum^n\epsilon^2\delta^n$ near the origin -- all orders can be quadratically supressed.
-\section{A Simple Example}
-As a trivial example, consider a single-qubit rotation-angle error, such as from stochastic laser amplitude fluctuations.
-An RBC may consist of an $X_\pi$ pulse, as well as an $X_{-\pi}$ pulse (i.e., a clockwise and counter clockwise rotation of the qubit).
-In the case of excess amplitude, the $X_\pi$ pulse will result in an over-rotation error, while the $X_{-\pi}$ pulse will result in an \emph{under}-rotation error.
-When it comes time to perform the target gate in a quantum circuit, one member of the RBC is chosen uniformly at random.
-This has the effect of decreasing the norm of the noise channel and decorrelating the over-rotation error (Figure \ref{fig:simple_example}).
-In this simple example, we can analytically find a solution to Equation \ref{eq:1}.
-Specifically, by choosing weights $\omega_j=\frac{1}{2}$, we see:
-
-\begin{equation}
-  \begin{gathered}
-    \frac{1}{2}(X^*_{\pi + \epsilon}\otimes X_{\pi + \epsilon} + X^*_{-(\pi + \epsilon)}\otimes X_{-(\pi + \epsilon)})) \\
-    = (\sin^2{\frac{\pi + \epsilon}{2}}I\otimes I + \cos^2{\frac{\pi + \epsilon}{2}}X\otimes X)X\otimes X \\
-    \approx DPN[\epsilon^2]X\otimes X
-  \end{gathered}
-\end{equation}
-
-Therefore, for a rotational error of angle $\epsilon > 0$, we see that $X_\pi$ and  $X_{-\pi}$  form a 0RBC, with $\alpha\approx\epsilon^2$.
-
-If we consider the amplitudes to not only be miscalibrated, but also non-Markovian (i.e. such that $\epsilon$ is drifting), we find the following channel, for any drift $\delta$:
-
-\begin{equation}
-  \begin{gathered}
-  DPN[(\epsilon + \delta)^2]X\otimes X
-  \end{gathered}
-\end{equation}
-
-Thus, the noise is always depolarizing, for every $\ell > 0$, this family of controls is an $\ell$RBC, and by injecting additional randomness the error rate is supressed quadratically.
-
-\section{Optimal Control Problems}\label{ocp}
-\subsection{Random Gate Synthesis}
- In this paper, we consider using optimal control to generate RBCs.
-One could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}, and for our numerics we chose to use the GRAPE algorithm.
-First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$, given a Hamiltonian with controlled and uncontrolled terms.
-Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ Hamiltonian, we can write an the unitary for any timestep of evolution as:
-\begin{equation}\label{eq:3}
-  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}c_{ij}H_{j}\}
-\end{equation}
-To measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
-
-To optimize this cost function we can perform the following standard update loop for some threshold value $\varepsilon > 0$ and step size $\delta > 0$:
-\begin{algorithm}[H]
-\floatname{algorithm}
-  \caption{\textsc{\textbf{Gradient Ascent}}}
-  \begin{algorithmic}
-    \While{$J(U) < (1-\varepsilon$)}
-    \State $c_{ij} \rightarrow c_{ij} + \delta\frac{\partial J(U)}{\partial c_{ij}}$
-    \For{$1 \leq i \leq n$}
-    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}c_{ij}H_j)\}$
-    \EndFor
-    \State $U \rightarrow \prod_{i=1}^nU_i$
-    \EndWhile
-  \end{algorithmic}
-\end{algorithm}
-
-In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule.
-However, in \cite{Khaneja2005} Khaneja et al.
-derive an update formula that is correct to first order, and efficient to compute.
-In particular one can show that:
-\begin{equation}\label{eq:update}
-  \begin{split}
-\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
-\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
-  \end{split}
-\end{equation}
-
-Because we our trying to generate high-order RBCs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
-\begin{align}\label{quadrature}
-\frac{\partial \tilde J(U)}{\partial u_{ij}} =
-\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
-\end{align}
-with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
-To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost function as a low order polynomial\cite{abramowiz1972handbook} (in particular degree 5).
-Note that despite updating the gradient, we did not change the cost function.
-The termination condition for the gradient ascent loop is still just that the controls perform well in the absence of drift.
-This is not a fundamental requirement of the routine, but rather was done to make finding solutions with $J(U) < 1 - \epsilon$  less computationally taxing.
-
-\subsection{RBC Approximation}
-After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $\omega_j$ such that the collection of controls form an $\ell$RBC as described in Equation \ref{eq:RBC}.
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework it does not constrain the resulting channel to be decomposable into a given family of controls.
-The following routine, however, will produce a channel defined explicitly in terms of given family of controls.
-To do this, for each control $U_i(\vec{\delta})$ we find the unitary error channel $\mathcal{E}_i(\vec{\delta})$ such that $\mathcal{E}_i(\vec{\delta})U_i(\vec{\delta})=U_T$, where $U_T$ is the target gate.
-By taking the logarithm of these error maps, we then get a family of Hamiltonians $\tilde{H}_j(\delta)$, and consider the following quadratic program whose solutions satisfy the robustness conditions given in Equation \ref{eq:RBC}:
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
-    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
-  \end{split}
-\end{equation}
-%These constraints for each $P_i$ can be broken into $2_{\ell-1}$ constraints, one for the imaginary components, and one for the real component.
-Alternatively, one can express the Hamiltonians as vectors in $\mathbb{R}^{2^n}$
-
-If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
-In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
-
-To make sure the routine remains practical, we would like to regularize our objective function to enforce sparsity.
-In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
-\begin{equation}
-\begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{
-    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
-    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
-\end{split}
-\end{equation} where $\lambda$ is a hyperparameter to be optimized over. In practice, for $\lambda=1E-4$, we have found that this can lead to 1RBCs with fewer than ten members.
-
-%In addition, for the constraints to be feasible, it is clear that the following condition is necessary: take $dim(\omega)=\Omega$, and $dim(\delta)=\Delta$.
-Each constraint is a matrix with $\Delta^i2^n$ elements.
-Thus we need at least $\Delta^i2^n$ linearly independent controls to even span the space of feasible weight vectors.
-On the other hand, even if the controls span the space, this is not sufficient because they must contain the origin in their complex hull.
-This can be achieved via a generalization of Campbell's Algorithm and by modifying the oracle query to ask for controls whose derivatives also satisfy certain properties.
-
-% \begin{figure*}
-% \centering
-% \begin{subfigure}[t]{.5\linewidth}
-% \includegraphics[width=\textwidth]{1q0.png}
-% \caption{This is one example of a 1D slice varying over one control.}
-% \end{subfigure}%
-% ~
-% \begin{subfigure}[t]{.5\linewidth}
-% \includegraphics[width=\textwidth]{1q1.png}
-% \caption{This is another example of a 1D slice varying over one control.}
-% \end{subfigure}
-%   \label{fig:1qnum}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \begin{subfigure}[t]{.5\linewidth}
-% \includegraphics[width=\textwidth]{control_dpn_all0.png}
-% \caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
-% \end{subfigure}%
-% ~
-% \begin{subfigure}[t]{.5\linewidth}
-% \includegraphics[width=\textwidth]{control_dpn_all2.png}
-% \caption{This is one example of a 1D slice varying over one control. There are five of these in total, but only one is interesting.}
-% \end{subfigure}
-%   \label{fig:2qnum}
-% \end{figure*}
-
-\section{Numerical Results}\label{numerical}
-In the following two subsections, we present numerical results of our routine, first for a one qubit example, and then for a two-qubit example.
-The code and RBCs generated for both examples are available online at \cite{decorrelating_errors}.
-\subsection{1Q Gates}\label{1Q Gates}
- For the one-qubit case, we generate a 1RBCs for $RX(\frac{\pi}{2})$. Our control Hamiltonian is given as:
-\begin{equation}\label{eq:1Qham}
-  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
-\end{equation}
-where we take  when generating the members of the RBC.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as mentioned in Section \ref{ocp}.
-When generating the controls, we chose an total evolution time of $T=FILL IN$, a number of steps $N=FILL IN$, a Gaussian quadrature degree of $d=FILL IN$, and a threshold infidelity of $1E-3$, with $\epsilon, \delta \sim \mathcal{N}(0, .001)$.
-The results can be seen in \ref{fig:num}.
-In particular, over a wide region about the origin, the diamond norm can be seen to have been reduced by over an order of magnitude from the members of the RBC, and the 1RBC is performs moderately worse at the origin, while outperforming the 0RBC for larger detunings.
-
 \begin{figure}\label{fig:num}
@@
 \end{figure}
-%The results can be seen in \ref{fig:1qnum}, where we have plotted each control as a function of one detuning value, fixing the others to zero.
-In the top half of each plot, we show the variation in the sum of the absolute valua of the off diagonal elements of the Pauli-Liouville Representation, while in the lower plot we see the variation in fidelity.
-While the controls were optimized by considering Gaussian noise with $\sigma=.001$ for each control, we have plotted the performance of the controls over a wider range to show more structure.
-We see over an order of magnitude improvement in the sum of the absolute values of the off-diagonal elements, while the fidelity remains above the specified target.
-
-\subsection{2Q Gates}\label{2Q Gates}
- For a two-qubit example, we chose $ZZ(\frac{\pi}{2})=\exp{(-i\frac{\pi}{4}\sigma_z\otimes\sigma_z)}$. Our control Hamiltonian is given as:
-\begin{equation} \label{eq:2Qham}
-\begin{split}
-H(\vec{\epsilon}, \vec{\delta}, \eta, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ (1+\eta)c(t) \exp{(-i\frac{\pi}{4}\sigma_z^1\otimes\sigma_z^2})
-\end{split}
-\end{equation}
-We again consider $\epsilon_j, \delta_j, \eta \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$, however we increased the total evolution time to $T=FILL IN$, and increased the number of steps to $N=FILL IN$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes.
-The results also show a reduction of an order of magnitude in diamond norm about the origin, and for a wide neighborhood around it.
-
-%0.0507,  0.0307, -0.0493, -0.0693, with total area under the curve given by 0.7853981633974484,
-\section{Experimental Results}\label{experimental}
-Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit.
-In particular we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an RBC on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape for a calibrated 50$\mu$s $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
-
- Using a similar routine to Equation \ref{eq:minimization}, we then generated the optimal weightings $\omega$.
-Instead of performing the convex optimization routine, we used the COBYLA minimizer in \texttt{scipy.optimize} to perform constrained minimization of the off-diagonal elements of the produced channel.
-This is a form of Sequential Quadratic
-Programming\cite{wright1999numerical}, and is equivalent to the convex optimization problem given for producing a 0RBC.
-To benchmark the quality of the new balanced channel, we then performed six randomized benchmarking experiments: one for each over- and under-calibrated pulse, one for the calibrated pulse, and one for the balanced channel.
-We used $N=1000$ shots per experiment and $K=10$ sequences per sequence length, for sequence lengths up to $L=64$\cite{Magesan2011}.
-In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
-The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-
-%with scipy's curve\_fit using the Trust Region Reflective method
-In this experiment, fitting the randomized benchmarking data reports one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the Randomized pulse.
-In the cases of each miscalibrated pulse, the error bars extend significantly, which is consistent with the results shown in \cite{Ball2016} that for particular non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
-On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-We see that the coherently miscalibrated controls have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
 
@@
 
-\section{Conclusion and Future Work}
-We have shown numerically that using RBCs can reduce non-Markovian, coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
-In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
-
-%Contrasting with \cite{Ware2018}, we see that this method of non-Markovian and coherent error mitigation is cheap to implement - it only requires a random choice of pulse definition at run time, in addition to the extra storage required to store the pulse definitions.
-In particular, no classical preprocessing or runtime frame tracking is required.
-
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
-
-Another interesting area of research would be using model-free approaches.
-The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
-in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
-Moreover, even if a model is available, it might be computationally inconvenient to simulate, i.e.
-for more than a few qubits.%, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
-
-In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
-While performing a complete optimization in this way would still be slow, requiring full process tomography, one could intead optimize via partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring pauli moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
-
+% ==============================================================================
+% Section: Acknowledgements
+% ==============================================================================
 \section{Acknowledgements}
+\label{sec:acknowledgements}
 Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S.

### 2018-11-28 decorrelation/numerics.tex

@@
   \includegraphics[scale=.2]{figures/SQRTY}
-\caption{0RBC and 1RBC performance for $RX(\frac{\pi}{2})$, as compared to each other, and members of the control families.
+\caption{0RBC and 1RBC performance for $RY(\frac{\pi}{2})$, as compared to each other, and members of the control families.
 At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm.
@@
 
+\begin{figure}[htb]
+  \centering
+  \includegraphics[scale=.1]{figures/2QRBC}
+
+\caption{0RBC and 1RBC performance for $iSWAP$, as compared to each other, and members of the control families.
+At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm, and perform the same as each other.
+Away from the origin the 1RBC can be seen to be flatter for all detunings than the 0RBC.
+The top plot is for frequency drift, while the bottom plot is for RF qubit drive amplitude drift.
+These are for one of the two qubits, but the plots for the other qubit are qualitatively similar.}
+\end{figure}
 \end{document}

### 2018-11-28 decorrelation/techniques.tex

--- 2018-11-25 decorrelation/numerics.tex
@@
 
-\section{Numerics}
-In this section, we numerically assess the performance of 0RBCs and 1RBCs.
-In particular we consider two tunable qubits, coupled by a resonant exchange interaction, inspired by systems like that in \cite{https://arxiv.org/pdf/1604.03076.pdf}.
-For the one-qubit case then, we generate a 1RBC for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$.
-Our control Hamiltonian is given as:
-\begin{equation}\label{eq:1Qham}
-  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
-\end{equation}
-where $\epsilon$ corresponds to fluctuations in qubit frequency given by noise on the flux line, and $\delta$ corresponds to fluctuations in the drive amplitude given by noise on the qubit RF drive line.
-Using the MOSEK solver in cvxpy, and imposing the sparsity constraint in \cite{SPARTSITY}, we generated weights for 0RBCs and 1RBCs, containing just ten controls.
-The controls were generated via the GRAPE algorithm described in Section \ref{GRAPE SECTION}, assuming Gaussian Noise with mean 0, and standard deviation $.001$.
-We gave GRAPE a total evolution time of $\pi$, compared with the required $\frac{pi}{2}$ time for the shortest path.
-We discretized the evolution into 25 steps, and generated 200 controls for the convex solver to choose from.
-The resutls are shown in \ref{FIGURE1}  and\ref{FIGURE2}.
-In both cases it can be seen that near the origin the 0RBC and 1RBC outperform the constituent controls by two orders of magnitude in diamond norm, and away from the origin the 0RBC can be seen to increase in diamond norm more quickly than the 1RBC.
+\section{Choose your own adventure}
+\subsection{1Q}
+In the numerics and experiments run in this paper, a variety of of techniques were employed to guide the convex solver to desired solutions.
+In the one qubit examples we enforced sparsity using the convex optimization problem defined in \cite{NIPS2012_4504} so that the 0RBCs generated would have non-trivial support on only 10 of the 500 controls used.
+In addition we added a hyperparameter to penalize for the l1 norm of the constituent Hamiltonians.
+This was used in the 1RBCs for the one qubit controls so that we could trade off some of the insensitivity of the 1RBC for better performance at the origin.
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[scale=.2]{figures/SQRTX}
-
-\caption{0RBC and 1RBC performance for $RX(\frac{\pi}{2})$, as compared to each other, and members of the control families.
-At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm.
-Away from the origin the 1RBC can be seen to be flatter than the 0RBC, outperforming at 1\% error.}
-\end{figure}
-\begin{figure}[htb]
-  \centering
-  \includegraphics[scale=.2]{figures/SQRTY}
-\caption{0RBC and 1RBC performance for $RX(\frac{\pi}{2})$, as compared to each other, and members of the control families.
-At the origin the RBCs can be see to outperform members of the family by two orders of magnitude in diamond norm.
-Away from the origin the 1RBC can be seen to be flatter than the 0RBC, outperforming at .5\% error.}
-\end{figure}
-
-For the two qubit example we extend our one qubit model to include a resonant exchange interaction. Our control Hamiltonian is given as:
-\begin{equation} \label{eq:2Qham}
+Both the 0RBC and the 1RBC in the one qubit examples were constructed by solving the following equation using MOSEK:
+\begin{equation}\label{eq:minimization}
   \begin{split}
-H(\vec{\epsilon}, \vec{\delta}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ k(XX + YY)
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
   \end{split}
@@
 
-There were several difficulties in considering this particular Hamiltonian, and for more interesting results one might consider a Hamiltonian with a control on the interaction -- such as that of a tunable coupler used in \ref{https://arxiv.org/pdf/1402.7367.pdf}.
-With that Hamiltonian it is non-trial to construct control solutions that are insensitive to detuning errors on either qubit, since such sequences also tend to decouple the entangling interaction.
-
-Moreover, when attemping to construct control solutions for \ref{eq:2Qham} GRAPE failed to find anything non-trivial.
-Therefore for this example we constructed analytic bangbang \ref{BANGBANG} sequences that flip both qubits at different times in the sequence to affect a decoupling of detuning errors, while remaining invariant to the eigenspaces of the interaction term.
+The elements of the one qubit control families were generated using the GRAPE algorithm with N=25 steps and total evolution time of $\pi$.
+The performance function used to terminate the gradient descent was equation (30) in Khaneja's paper - the square of the Hilbert-Schmidt inner product between the GRAPE unitary and the target unitary.
+The gradient, however, is the gaussian quadrature gradient described in the main text.
+In particular, using degree two (which should be accurate for polynomials up to degree 3) Gauss-Hermite quadrature we evaluated the gaussian weighted average gradient for a $\sigma=.001$, on both the qubit drive, and the qubit frequency.
+\subsection{2Q}
+In the two-qubit case the situation was more difficult - GRAPE would not return non-trivial solutions so we manually selected piecewise constant sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
+We then prepared 1024 controls.
+In this case, we treated the $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple the tuning errors as taking only one time step, to avoid significant errors arising from mixing the eigenspaces of the interaction term.
+The particular collection of bang-bang sequences considered were all combinations of of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
 To give the control family a variety of different errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
-A plot of typical control amplitude sequence is given in Figure  \ref{FIGURE}.
-
-Using the same piecewise constant control solution as in the one qubit case, we considered 100 steps, with a total evolution time of $\frac{5\pi}{2}$, the time required for the $XX + YY$ interaction to generate an iSWAP gate in the absence of any other controls.
-In this case, we treated the $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple the tuning errors as taking only one time step, to avoid significant errors arising from mixing the eigenspaces of the interaction term.
-In practice this could be accomplished instead by turning off the resonance, performing the $\pi$ pulse, and turning the interaction back on.
-The particular collection of bang-bang sequences considered were all combinations of of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
-This resulted in a control family of 1024 controls.
-We did not apply the sparsity constraint to the solutions, however over 100 of the controls have less than $.5$\% of support, so it is feasible that the sparsity constraint could be successfully applied.
-
-The $0RBC$ succesfully finds weights that minimize the 0th order term in the error Hamiltonian to zero within numerical precision, but with nonzero first derivative.
-Given the 1RBC minimization problem, the solver can also successfully supress the first derivative, while keeping the zeroth order term 0.
-At the origin, both RBCs can be seen to perform equally well, and better than members of the control family.
-Away from the origin both RBCs can be seen to perform over half an order of magnitude better in diamond norm than members of the control family, with the 1RBC degrading in quality more slowl than the 0RBC.
-
-There is much more work that can be done investigating other Hamiltonians, for other kinds of noise, and more interesting compositive pulse sequences that might be system dependent.
-In addition, imposing the $\ell_1$ constraint has the potential to increase performance of $RBC$s when the members of the control family have varied performance (constrasted with the scenario given in Campbell's paper \ref{Campbell} where all controls are assumed to have error bounded by $\epsilon$.) Investigating the trade off between controls with slightly worse error but more interesting derivative may provide more favorable performance increases.
-
-Finally, much of the numerical work here was limited by the same simplicity that makes the GRAPE algorithm useful.
-Future work could modify the derivative in the GRAPE algorithm to include derivative information to in addition to finding controls with bounded error, GRAPE finds controls with not only bounded derivative, but also derivatives that are wrong in a way that can cancel out the derivatives of other controls in the RBC.
-These results demonstrate numerically that RBCs are feasible and tractable, and provide an algorithmic way to compute optimal weights for minimizing sensitive to drift.
-
+We did not apply the sparsity constraint, or any $\ell 1$ constraints to the solutions, we only applied the minimization problem defined earlier in this document.
+\subsection{Experimental}
+For the experimental data the four controls generated were generated by scaling an approximately calibrated 50$\mu$s Gaussian $\pi$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+Then, using a naive driven qubit model (no noise), we predicted the unitaries that these pulses would generate, calculated their error maps, and used COBYLA in scipy minimize to minimize the off-diagonal elements of the mixed channel.
+Using the weights returned from that, we ran a randomized benchmarking experiment, with the details listed in the main document.
 \end{document}

### 2018-12-07 decorrelation/mixed_unitaries.tex
Added new tex document - mixed_unitaries.tex
Starting to migrate everything into here.

@@
 \newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
-\setlength{\jot}{10pt}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{lem}[thm]{Lemma}
-\usepackage{lipsum}
+
+\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
+\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
+\newcommand{\error}{\ensuremath{{\mathcal{E}}}}
 
@@
 \begin{document}
-% \tableofcontents
-\title{Mixing Unitary Operators for Real and Simulated Quantum Information Processing}
+\title{Advantages of mixed unitary operators for quantum information processing}
 
@@
 \author{Kevin C. Young}
-% \email[Corresponding author: ]{kyoung@sandia.gov}
 \affiliation{Sandia National Laboratories, Livermore, CA}
@@
 \begin{abstract}
-Quantum information processors (QIPs) can suffer from a number of differnt kinds of errors.
+...
 \end{abstract}
@@
 
+The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIP).
+Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices.
+While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum supremacy milestone has yet to be definitively reached.
+The limiting factor, of course, is errors in the quantum gate operations.
+
+The impact of an error in a quantum gate depends strongly on both the nature of the errors.
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations.
+These errors induce repeatable, undesired unitary errors on the state of a QIP.
+Errors of this type are correlated in time and add up coherently, so they are computationally expensive to model and it is difficult to place analytic bounds on circuit performance.
+Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
+These errors can be modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip.
+These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.
+
+Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
+Drifting control parameters or environmental variables can easily have long correlation times that result in errors which is strongly coherent over the length of a quantum circuit.
+While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
+The diamond distance can be used to estimate the failure probability of a quantum circuit, but the diamond distance can grow quadratically with repeated application of gate with coherent errors.
+For long circuits, this can add up extremely quickly.
+Recent work by Hastings and Campbell, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
+This averaging results in quantum processes with diamond distances that grow only linearly  quadratic in the over/under rotation angle of the component gates.
+\note{Clear this up.}
+
+In this article we discuss various applications of mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
+In this article, we discuss an optimal control approach to the mixed unitary control design problem.
+We apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+We further present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Quantum Computing.
+Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
+
+% For instance, the repeated measurements that occur in quantum error correction are suspected to reduce the potential impact of coherent buildup of error.
+Modern devices, however, do not have sufficient numbers of qubits and their errors are above the threshold at which QEC becomes a viable option.
+
 % ==============================================================================
-% Section: Mixed Unitary Processes
+% Section: Representing quantum gates
 % ==============================================================================
-\section{Mixed Unitary Processes}
+\section{Representing quantum gates}
+\label{sec:representing_quantum_gates}
+The standard model for quantum gate operations is as linear maps on the state of some qubits.
+The state is usually represented as a density operator.
+It is often convenient, however, to represent the states instead as a generalized Bloch vector,
+\begin{equation}
+  \vec \rho = \tr(\rho \vec \sigma)
+\end{equation}
+Operations on this Bloch vector can then be represented as \emph{process matrices}, $\target$, and their action on a quantum state given by standard matrix multiplication
+\begin{equation}
+  \rho \rightarrow \target\rho = \error \actual \rho
+\end{equation}
+Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.
+If the error channel is unitary, then the error is coherent.
+An advantage of this particular representation of quantum gates is that Pauli stochastic channels are diagonal, with each entry corresponding to the probability that the associated Pauli error occurs in a given application of the gate.
+
+% ==============================================================================
+% Section: Example Mixed Unitary Processes
+% ==============================================================================
+\section{Example Mixed Unitary Processes}
 \label{sec:mixed_unitary_processes}
+There are often many possibly ways of implementing a target quantum gate.
+Hastings and Campbell consider gates compiled using the Solovey-Kitaev algorithm, for which there are many choices of approximate quantum gate implementations.
+By implementing some number o these implementations at random, we are able to construct a quantum channel that has reduced coherent error.
+As a simple example, we have:
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{simple_example.pdf}
+  \caption{An example of a balanced control solution.
+Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
+Each time the gate is used, one of these implementations is chosen at random.
+The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
+  \label{fig:simple_example}
+\end{figure}
+
+** This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.
 
@@
 \label{sec:robustly_mixed}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace.pdf}
+  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
+These error Hamiltonians lie in a vector space.
+a) Four effective Hamiltonians.
+The origin is not contained in their convex hull, so there are no balanced control solutions.
+b) The origin is contained in the covex hull after adding an additional control solution.
+Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
+c) The error Hamiltonians shown with their derivative with respect to a control parameter.
+As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
+d) The derivatives also lie in a vector space.
+If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order robust balanced control solution.}
+  \label{fig:vectorspace}
+\end{figure}
+
+% ==============================================================================
+% Section: Experimental Results
+% ==============================================================================
+\section{Experimental Results}
+\label{sec:experimental_results}
 

### 2018-12-08 decorrelation/mixed_unitaries.tex
small changes in the text, biggest is changing supremacy -> advantage

@@
 
-The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIP).
+The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
 Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices.
-While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum supremacy milestone has yet to be definitively reached.
+While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone has yet to be definitively reached.
 The limiting factor, of course, is errors in the quantum gate operations.
 
-The impact of an error in a quantum gate depends strongly on both the nature of the errors.
+The impact of an error in a quantum gate depends strongly on both the magnitude and nature of the errors.
 Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations.
@@
 Hastings and Campbell consider gates compiled using the Solovey-Kitaev algorithm, for which there are many choices of approximate quantum gate implementations.
-By implementing some number o these implementations at random, we are able to construct a quantum channel that has reduced coherent error.
+By implementing some number of these implementations at random, we are able to construct a quantum channel that has reduced coherent error.
 As a simple example, we have:

### 2018-12-08 decorrelation/mixed_unitaries.tex
moving over experimental results, and cleaning them up a little

@@
 \label{sec:experimental_results}
+Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit.
+In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
+To implement a MUP on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+
+Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization of the off--diagonal elements of the produced channel.
+This is a form of Sequential Quadratic Programming\cite{wright1999numerical}.
+\note{Explain why this an okay thing to do, or reference the section where we explain it.} To benchmark the quality of the new MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
+In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
+The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
+The complete dataset can be found at  \cite{decorrelating_errors}.
+
+Using \texttt{scipy.optimize.curve\_fit} to fit the randomized benchmarking data to Equation 6 in \cite{Magesan2011} with $B_0$ set to .5, and bounds between (0, 1), we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP.
+In the cases of each miscalibrated pulse, the second moment of the RB number\cite{Proctor2017} for the sampled sequences extends significantly, which is in agreement with the results shown in \cite{Ball2016}.
+Specifically, for non-Markovian error models noise will manifest as gamma distributed points for each sequence length.
+On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
+We see that the coherently miscalibrated controls have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{rb_data.pdf}
+  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
+  \label{fig:rb}
+\end{figure}
 

### 2018-12-08 decorrelation/mixed_unitaries.tex
a few more changes to the experimental section

@@
 In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a MUP on this qubit, four incorrectly calibrated approximately Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
-Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization of the off--diagonal elements of the produced channel.
-This is a form of Sequential Quadratic Programming\cite{wright1999numerical}.
+Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization via Sequential Quadratic Programming\cite{wright1999numerical}, we minimized the off--diagonal elements of the resulting mixed process.
 \note{Explain why this an okay thing to do, or reference the section where we explain it.} To benchmark the quality of the new MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.

### 2018-12-10 decorrelation/mixed_unitaries.tex
Moved over some of the text regarding numerical results

@@
 % ==============================================================================
+% Section: Numerical Results
+% ==============================================================================
+\section{Numerical Results}
+\label{sec:numerical_results}
+In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
+\begin{equation}\label{eq:1Qham}
+  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
+\end{equation}
+We use the GRAPE algorithm as discussed in \ref{sec:GRAPE} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
+The performance function used to terminate the gradient descent was Equation (30) in \cite{Khaneja2005} -- the square of the Hilbert--Schmidt inner product between the generated unitary and the target unitary.
+The gradient, however, is the gaussian quadrature gradient described in \ref{sec:GRAPE}.
+In particular, using degree two (which should be accurate for polynomials up to degree 3) Gauss-Hermite quadrature we evaluated the gaussian weighted average gradient for standard deviation $\sigma=.001$, on both the qubit drive, and the qubit frequency.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as in superconducting qubit systems that share a common RF drive.
+
+Solving the optimization problem defined in  \ref{sec:robustly_mixed} with the MOSEK solver in \texttt{cvxpy} yields a 0MUP with nontrivial (nearly uniform 1\%) support on all the members of the control family.
+However, by imposing the sparsity constraint described in \ref{sec:robustly_mixed} the number of controls can be constrained to be just five.
+When generating a 1MUP we impose an $\ell1$ penalty so that the algorithm favors smaller error Hamiltonians.
+
+In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
+\begin{equation} \label{eq:2Qham}
+\begin{split}
+H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
+&+ \frac{1}{10}(XX + YY)
+\end{split}
+\end{equation}
+
+In this example it was infeasible to use GRAPE to return non-trivial solutions.
+Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
+In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple detuning errors as taking only one time step, to avoid significant errors arising from non-commutativity.
+The specific collection of bang-bang sequences \cite{bang-bang} considered were all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
+To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
+This resulted in 1024 controls, over which we performed the convex optimization described in \ref{sec:robustly_mixed}, with neither sparisty, nor $\ell1$ constraints.
+% ==============================================================================
 % Section: Experimental Results

### 2018-12-10 decorrelation/mixed_unitaries.tex
Updating single qubit numerics photo, and including in figures section

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SQRTX.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit.
+Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$.
+The 0MUP can be seen to outperform the members of the control family by two orders of magnitude at the origin, and the 1MUP by an order of magnitude.
+However, the 1MUP can be seen to be flatter.
+In paritcular, for small detunings, the 1MUP performs better than the 0MUP.}
+  \label{fig:1QMUP}
+\end{figure*}
+
 % ==============================================================================

### 2018-12-12 decorrelation/mixed_unitaries.tex
more text

@@
 
-The impact of an error in a quantum gate depends strongly on both the magnitude and nature of the errors.
-Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations.
-These errors induce repeatable, undesired unitary errors on the state of a QIP.
-Errors of this type are correlated in time and add up coherently, so they are computationally expensive to model and it is difficult to place analytic bounds on circuit performance.
+The impact of an error in a quantum gate depends strongly on both the magnitude and the nature of the errors.
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
+Errors of this type are correlated in time and add up coherently.
+They are are  computationally expensive to model and it is difficult to place analytic bounds on circuit performance.
 Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
-These errors can be modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip.
+Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip.
 These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.
@@
 % ==============================================================================
-% Section: Representing quantum gates
+% Section: Mathematical preliminaries
 % ==============================================================================
-\section{Representing quantum gates}
+\section{Mathematical preliminaries}
 \label{sec:representing_quantum_gates}
-The standard model for quantum gate operations is as linear maps on the state of some qubits.
-The state is usually represented as a density operator.
-It is often convenient, however, to represent the states instead as a generalized Bloch vector,
+Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits.
+Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.
+But if the gates are fairly stable with time and context, then we can describe their action on the qubit state using \emph{process matrices}, linear, Markovian maps on the state of some qubits.
+When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
 \begin{equation}
-  \vec \rho = \tr(\rho \vec \sigma)
+  \vec \rho = \tr(\rho \vec \Sigma),
 \end{equation}
-Operations on this Bloch vector can then be represented as \emph{process matrices}, $\target$, and their action on a quantum state given by standard matrix multiplication
+where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
 \begin{equation}
-  \rho \rightarrow \target\rho = \error \actual \rho
+  \rho \rightarrow \target\rho = \error \actual \rho.
 \end{equation}
 Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.  
-If the error channel is unitary, then the error is coherent.
-An advantage of this particular representation of quantum gates is that Pauli stochastic channels are diagonal, with each entry corresponding to the probability that the associated Pauli error occurs in a given application of the gate.
+\begin{equation}
+	\left( 
+	\begin{array}{c|cccc}
+		1 &  & \vec 0 & \\ 
+		\hrule & &  &  \\
+		\vec{m} &  & R &  \\
+		 &  &  & 
+	\end{array}
+	\right)
+\end{equation}
+
+The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.
+The first column, $\vec{m}$, describes any deviations from unitality, such as could arise from amplitude damping.
+If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
+If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry corresponding to the probability that the associated Pauli error occurs in each application of the gate.
+\note{Be more clear about what "associated" means here}.
+If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
+For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.
+
+** The vec representation may be a little more convenient here? The channel that results is:
+\begin{align}
+	\mathcal{M} 
+		=& \sum_i p_i U^*_i \otimes U_i \\
+		=& \sum_i p_i \exp(i \theta \hat n \cdot \vec\sigma^*) \otimes \exp(-i \theta \hat n \cdot \vec\sigma) \\
+		\simeq & \sum_i p_i (\cos\theta + i \sin\theta H^*)\otimes(\cos\theta -i \sin\theta H) \\
+		\simeq & \sum_i p_i (\cos\theta^2 I\otimes I + \sin\theta^2 H^*\otimes H \\ & + i\sin\theta\cos\theta H^*\otimes I
+								- i\sin\theta\cos\theta I\otimes H )
+\end{align}
+In this case, $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+The result would be a purely stochastic channel.
+
+The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
+Two of the most metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
+These may be represented in terms of the error maps as
+\begin{equation}
+	\vert\vert \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1
+\end{equation}
+\begin{equation}
+	\mathcal{F}(\error) = ...
+\end{equation}
+The diamond norm is generally linear in the over-rotation angle of a quantum operation.
+Also definition of average gate infidelity.
+The AGI is generally quadratic in the over-rotation angle of a quantum operation.
+
+A mixed unitary channel consists of a set of unitary channels, $\actual_i$, and associated weights, $\sum_i p_i = 1$.
+The process matrices for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
+
+Campbell considered the very important problem of minimizing the diamond norm of the resulting error channel.
+\note{Mention the mixing lemma of Campbell and how the Hamiltonians should form a convex set containing the origin \cite{}}.
+This is a particualrly appealing target, because the diamond norm provides useful error metrics on quantum circuits.
+However, it is not the only optimization target that can be chosen.
+If the ultimate goal is to produce a channel whose effect can be easily simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
+
+\eq
 
@@
 \label{sec:mixed_unitary_processes}
-There are often many possibly ways of implementing a target quantum gate.
-Hastings and Campbell consider gates compiled using the Solovey-Kitaev algorithm, for which there are many choices of approximate quantum gate implementations.
-By implementing some number of these implementations at random, we are able to construct a quantum channel that has reduced coherent error.
-As a simple example, we have:
+There are often many possibly ways of implementing any given target quantum gate.
+Hastings and Campbell, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which  many approximate gate compilations are possible.
+By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.
+As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
+The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -epsilon, epsilon, 2\epsilon\}$.
+Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.
+
+\begin{tabular}{cccc}
+	Gate & H_{\rm{eff}} & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
+	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
+	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
+	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
+	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
+\end{tabular}
+
+Make a table of these error channels.
 
@@
 \label{sec:robustly_mixed}
+
+While mixed unitary
 
@@
 
-% ==============================================================================
-% Section: Figures
-% ==============================================================================
-\section{Figures}
-\label{sec:figures}
-
 \begin{figure}

### 2018-12-12 decorrelation/mixed_unitaries.tex
fixing compilation issues

@@
 Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.
+
 \begin{equation}
-	\left( 
-	\begin{array}{c|cccc}
-		1 &  & \vec 0 & \\ 
-		\hrule & &  &  \\
+	\left(\begin{array}{c|cccc}
+		1 &  & \vec0 & \\ 
+		\hline & &  &  \\
 		\vec{m} &  & R &  \\
@@
 
-\eq
+%\eq
 
@@
 As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
-The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -epsilon, epsilon, 2\epsilon\}$.
+The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$.
 Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.
 
+\begin{center}
+
 \begin{tabular}{cccc}
-	Gate & H_{\rm{eff}} & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
+	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
+\hline
 	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
@@
 
+\end{center}
 Make a table of these error channels.

### 2018-12-16 decorrelation/mixed_unitaries.tex
changes to document

@@
 Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-Drifting control parameters or environmental variables can easily have long correlation times that result in errors which is strongly coherent over the length of a quantum circuit.
+Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
 While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.

### 2018-12-16 decorrelation/mixed_unitaries.tex
changes to text

--- 2018-12-12 decorrelation/mixed_unitaries.tex
@@
 \label{sec:robustly_mixed}
+\note{Decide on naming convention, Anthony has used $\ell$ MUP in the rest of the text}
+
+\note{Anthony references this section when discussing minimizing the offdiagonal elements of the error's process matrix.}
+
+\note{Anthony mentions the sparsity constraint, as well as the $\ell_1$ penalty, as being described in this section.}
 
@@
 % ==============================================================================
+
+\section{Random Gate Synthesis}
+\label{sec:random_gate_synthesis}
+ In this paper, we use optimal control to generate the one qubit families of controls for MUPs.
+One could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}, and for our numerics we chose to use the GRAPE algorithm.
+First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$, given a Hamiltonian with controlled and uncontrolled terms.
+Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ Hamiltonian, we can write an the unitary for any timestep of evolution as:
+\begin{equation}\label{eq:3}
+  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}c_{ij}H_{j}\}
+\end{equation}
+To measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
+
+To optimize this cost function we can perform the following standard update loop for some threshold value $\varepsilon > 0$ and step size $\delta > 0$:
+\begin{algorithm}[H]
+\floatname{algorithm}
+  \caption{\textsc{\textbf{Gradient Ascent}}}
+  \begin{algorithmic}
+    \While{$J(U) < (1-\varepsilon$)}
+    \State $c_{ij} \rightarrow c_{ij} + \delta\frac{\partial J(U)}{\partial c_{ij}}$
+    \For{$1 \leq i \leq n$}
+    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}c_{ij}H_j)\}$
+    \EndFor
+    \State $U \rightarrow \prod_{i=1}^nU_i$
+    \EndWhile
+  \end{algorithmic}
+\end{algorithm}
+
+In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule.
+However, in \cite{Khaneja2005} Khaneja et al.
+derive an update formula that is correct to first order, and efficient to compute.
+In particular one can show that:
+\begin{equation}\label{eq:update}
+  \begin{split}
+\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
+\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
+  \end{split}
+\end{equation}
+
+Because we our trying to generate high-order RBCs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
+\begin{align}\label{quadrature}
+\frac{\partial \tilde J(U)}{\partial u_{ij}} =
+\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
+\end{align}
+with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
+To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost function as a low order polynomial\cite{abramowiz1972handbook} (in particular degree 5).
+Note that despite updating the gradient, we did not change the cost function.
+The termination condition for the gradient ascent loop is still just that the controls perform well in the absence of drift.
+This is not a fundamental requirement of the routine, but rather was done to make finding solutions with $J(U) < 1 - \epsilon$  less computationally taxing.
+
+% ==============================================================================
+% Section: Numerical Results
+% ==============================================================================
 \section{Numerical Results}
@@
 \end{equation}
-We use the GRAPE algorithm as discussed in \ref{sec:GRAPE} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
-The performance function used to terminate the gradient descent was Equation (30) in \cite{Khaneja2005} -- the square of the Hilbert--Schmidt inner product between the generated unitary and the target unitary.
-The gradient, however, is the gaussian quadrature gradient described in \ref{sec:GRAPE}.
-In particular, using degree two (which should be accurate for polynomials up to degree 3) Gauss-Hermite quadrature we evaluated the gaussian weighted average gradient for standard deviation $\sigma=.001$, on both the qubit drive, and the qubit frequency.
+We use the GRAPE algorithm as discussed in Section  \ref{sec:random_gate_synthesis} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls, with the Gaussian-weighted gradient averaged over a standard deviation of $\sigma=.001$.
 We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as in superconducting qubit systems that share a common RF drive.
 
-Solving the optimization problem defined in  \ref{sec:robustly_mixed} with the MOSEK solver in \texttt{cvxpy} yields a 0MUP with nontrivial (nearly uniform 1\%) support on all the members of the control family.
-However, by imposing the sparsity constraint described in \ref{sec:robustly_mixed} the number of controls can be constrained to be just five.
-When generating a 1MUP we impose an $\ell1$ penalty so that the algorithm favors smaller error Hamiltonians.
+Solving the optimization problem defined in  \ref{sec:robustly_mixed} yields MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:XMUP} and Figure \ref{fig:YMUP}.
+
+These results demonstrate several properties that make MUPs useful and tractable to generate.
+First, naively generating a 0MUP results in nontrivial support on all the members of the control family.
+However, by rewriting the minimization to impose the sparsity constraint discussed in \ref{sec:robustly_mixed}, we can generate a 0MUP that uses just five of the controls.
+This shows that through adding constraints to our optimization routine, we can make the MUP practically useful, i.e.
+not requiring a prohibitive amount of waveform memory.
+When generating a 1MUP we impose the $\ell_1$ penalty discussed in \ref{sec:robustly_mixed}, so that the algorithm favors smaller error Hamiltonians.
+While the solution in this case was already sparse, enforcing the penalty allows for a smooth trade off between performance at the origin, and robustness to drift.
 
@@
 In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple detuning errors as taking only one time step, to avoid significant errors arising from non-commutativity.
-The specific collection of bang-bang sequences \cite{bang-bang} considered were all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
+The specific collection of bang-bang sequences \cite{bangbang} considered were all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
 To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
-This resulted in 1024 controls, over which we performed the convex optimization described in \ref{sec:robustly_mixed}, with neither sparisty, nor $\ell1$ constraints.
+
+In this example, we find much more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
+Indeed, there are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little variation in the controls.
+Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin, and up to an order of magnitude away from the origin, with the 1MUP performing just as well as the 0MUP, but also being more robust to drift.
+We believe that if we used a two qubit interaction that was controllable, such as tunable couplers, there would be room for more interesting controls and perhaps even better performance improvements.
 % ==============================================================================
@@
 
-Using the COBYLA minimizer in \texttt{scipy.optimize}\cite{scipy} to perform constrained minimization via Sequential Quadratic Programming\cite{wright1999numerical}, we minimized the off--diagonal elements of the resulting mixed process.
-\note{Explain why this an okay thing to do, or reference the section where we explain it.} To benchmark the quality of the new MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+As discussed in Section \ref{sec:robustly_mixed}, we chose here to minimize the off diagonal elements of the process matrix.
+To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
 We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
@@
 The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-The complete dataset can be found at  \cite{decorrelating_errors}.
+Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
 
-Using \texttt{scipy.optimize.curve\_fit} to fit the randomized benchmarking data to Equation 6 in \cite{Magesan2011} with $B_0$ set to .5, and bounds between (0, 1), we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP.
-In the cases of each miscalibrated pulse, the second moment of the RB number\cite{Proctor2017} for the sampled sequences extends significantly, which is in agreement with the results shown in \cite{Ball2016}.
-Specifically, for non-Markovian error models noise will manifest as gamma distributed points for each sequence length.
+Additionally, by minimizing the off-diagonal elements of the process matrix, rather than balancing the Hamiltonian errors, we expect to produce a process with minimal coherent error in the absence of drift.
+To see that this is the case, we cite the results in \cite{Ball2016}.
+For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
 On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-We see that the coherently miscalibrated controls have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
+We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
+Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less coherent error channel.
 
@@
 \end{figure}
+
+% ==============================================================================
+% Section: Figures
+% ==============================================================================
+\section{Figures}
+\label{sec:figures}
 
@@
 
-\begin{figure}\label{fig:num}
-  \centering
-  \includegraphics[width=\columnwidth]{placeholdernumerical.pdf}
-  \caption{Placeholder image until we figure out what to plot. This currently shows that for one of the control the diamond norm decreased by over an order of magnitude. The labels need to be bigger.}
-  \label{fig:rb}
-\end{figure}
-
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{SQRTX.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit.
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RX(\frac{np.pi}{2})$.
 Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$.
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SQRTY.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+The results are quantitatively similar to those for $RX(\frac{\pi}{2})$, but in this case the 0MUP is worse at the origin.
+This can be improved by penalizing for the norms, or by simply trying to find a 1MUP, which both symmeterizes the performance at the origin and makes them better.}
+  \label{fig:XMUP}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{2QRBC.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+Shown with lower alpha values are example members of the control families.
+The 0MUP and 1MUP can be seen to outperform the members of the control family by half an order of magnitude at the origin.
+Away from the origin, the 1MUP can be seen to be flatter.
+Far away from the origin, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.}
+  \label{fig:2MUP}
+\end{figure*}
 % ==============================================================================

### 2018-12-26 decorrelation/mixed_unitaries.tex
more plots, cleaning up convex code and notebooks. experimental and numerical section should be in 80% good shape.

@@
 The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.
-The first column, $\vec{m}$, describes any deviations from unitality, such as could arise from amplitude damping.
+The rest of the first column, $\vec{m}$, describes any deviations from unitality, such as could arise from amplitude damping.
 If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
@@
 The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
-Two of the most metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
+Two of the most common metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
 These may be represented in terms of the error maps as
@@
 Because we our trying to generate high-order RBCs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
-\begin{align}\label{quadrature}
+\begin{align}\label{eq:quadrature}
 \frac{\partial \tilde J(U)}{\partial u_{ij}} =
@@
 \end{equation}
-We use the GRAPE algorithm as discussed in Section  \ref{sec:random_gate_synthesis} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls, with the Gaussian-weighted gradient averaged over a standard deviation of $\sigma=.001$.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as in superconducting qubit systems that share a common RF drive.
+We use the GRAPE algorithm as discussed in Section  \ref{sec:random_gate_synthesis} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls, with a standard deviation of $\sigma=.001$ for the distribution in Equation \ref{eq:quadrature}.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
+Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}.
+These results demonstrate several properties that make MUPs both useful and tractable.
 
-Solving the optimization problem defined in  \ref{sec:robustly_mixed} yields MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:XMUP} and Figure \ref{fig:YMUP}.
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{SQRTY.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+The results are quantitatively similar to those for $RX(\frac{\pi}{2})$, but in this case the 0MUP is worse at the origin.
+This can be improved by penalizing for the norms, or by simply trying to find a 1MUP, which both symmeterizes the performance at the origin and makes them better.}
+  \label{fig:YMUP}
+\end{figure*}
 
-These results demonstrate several properties that make MUPs useful and tractable to generate.
+%\begin{figure*}
+%  \centering
+%  \includegraphics[width=\textwidth]{SQRTX.png}
+%  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RX(\frac{np.pi}{2})$.
+Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$.
+The 0MUP can be seen to outperform the members of the control family by two orders of magnitude at the origin, and the 1MUP by an order of magnitude.
+However, the 1MUP can be seen to be flatter.
+In paritcular, for small detunings, the 1MUP performs better than the 0MUP.}
+%  \label{fig:XMUP}
+%\end{figure*}
+
 First, naively generating a 0MUP results in nontrivial support on all the members of the control family.
-However, by rewriting the minimization to impose the sparsity constraint discussed in \ref{sec:robustly_mixed}, we can generate a 0MUP that uses just five of the controls.
-This shows that through adding constraints to our optimization routine, we can make the MUP practically useful, i.e.
-not requiring a prohibitive amount of waveform memory.
-When generating a 1MUP we impose the $\ell_1$ penalty discussed in \ref{sec:robustly_mixed}, so that the algorithm favors smaller error Hamiltonians.
-While the solution in this case was already sparse, enforcing the penalty allows for a smooth trade off between performance at the origin, and robustness to drift.
+However, by rewriting the minimization to impose the sparsity constraint discussed in Section \ref{sec:robustly_mixed}, we can generate a 0MUP that uses just five of the controls.
+This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
+In both cases we impose the same $\ell_2$ penalty as described in Section \ref{sec:robustly_mixed}, so that the algorithm preferentially selects controls with smaller errors.
+Imposing this constraint allows us to trade off flatness at the origin for performance.
 
@@
 Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
-In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ pulses used to decouple detuning errors as taking only one time step, to avoid significant errors arising from non-commutativity.
-The specific collection of bang-bang sequences \cite{bangbang} considered were all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the first time step, and the same multiple of $8$ steps prior to the last time step.
+In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls.
+An example of such a control is given in Figure \ref{fig:bangbang}.
 To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
 
-In this example, we find much more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
-Indeed, there are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little variation in the controls.
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{bangbang.png}
+  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
+  \label{fig:bangbang}
+\end{figure}
+
+In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
+There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little variation in the controls.
 Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin, and up to an order of magnitude away from the origin, with the 1MUP performing just as well as the 0MUP, but also being more robust to drift.
-We believe that if we used a two qubit interaction that was controllable, such as tunable couplers, there would be room for more interesting controls and perhaps even better performance improvements.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{2QRBC.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+Shown with lower alpha values are example members of the control families.
+The 0MUP and 1MUP can be seen to outperform the members of the control family by half an order of magnitude at the origin.
+Away from the origin, the 1MUP can be seen to be flatter.
+Far away from the origin, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.}
+  \label{fig:2MUP}
+\end{figure*}
+
 % ==============================================================================
@@
 % ==============================================================================
+
 \section{Experimental Results}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{Randomized benchmarking experiments ran using different pulse definitions.
-The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
-  \label{fig:rb}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SQRTX.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RX(\frac{np.pi}{2})$.
-Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$.
-The 0MUP can be seen to outperform the members of the control family by two orders of magnitude at the origin, and the 1MUP by an order of magnitude.
-However, the 1MUP can be seen to be flatter.
-In paritcular, for small detunings, the 1MUP performs better than the 0MUP.}
-  \label{fig:1QMUP}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SQRTY.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are quantitatively similar to those for $RX(\frac{\pi}{2})$, but in this case the 0MUP is worse at the origin.
-This can be improved by penalizing for the norms, or by simply trying to find a 1MUP, which both symmeterizes the performance at the origin and makes them better.}
-  \label{fig:XMUP}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{2QRBC.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
-Shown with lower alpha values are example members of the control families.
-The 0MUP and 1MUP can be seen to outperform the members of the control family by half an order of magnitude at the origin.
-Away from the origin, the 1MUP can be seen to be flatter.
-Far away from the origin, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.}
-  \label{fig:2MUP}
-\end{figure*}
 % ==============================================================================

### 2018-12-26 code/convex.py

@@ -49,9 +49,6 @@ def error(combo, controls, target_operator, control_hamiltonians, ambient_hamilt
     error_gen = logm(adjoint_target.dot(unitary))
     num_states = error_gen.shape[0]
     eye_proj = np.trace(np.dot(np.eye(num_states), error_gen))/num_states
-    # entry = (error_gen[0, 0] - error_gen[1, 1])/2
-    # error_gen[0, 0] = entry
-    # error_gen[1, 1] = -entry
     error_gen -= eye_proj * np.eye(error_gen.shape[0])
     return -1.j * error_gen
 
@@ -105,213 +102,7 @@ def compute_ith_derivative(f, point, args, i, matsize):
     return res
 
 
-def optimal_weights_no_constraints(derivs, l, tol=DEFAULT_TOL):
-    print("Starting optimal weights no constraints")
-    mini = float('inf')
-    res = None
-    ham_consts = []
-    for deriv in derivs:
-        ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
-    omega = cp.Variable(len(derivs[0]))
-    constraints = [0 <= omega, omega <= 1, sum(omega)==1]
-    equalities = ham_consts[:-1]
-    for ham_const in equalities:
-        constraints += [np.real(ham_const)*omega == 0]
-        constraints += [np.imag(ham_const)*omega == 0]
-    objective = cp.Minimize(cp.norm(np.real(ham_consts[-1])*omega) + cp.norm(np.imag(ham_consts[-1])*omega))
-    prob = cp.Problem(objective, constraints)
-    result = prob.solve(solver=cp.CVXOPT, kktsolver=cp.ROBUST_KKTSOLVER,
-                        abstol=tol, abstol_inacc=tol, max_iters=1000, reltol=tol, feastol=tol)
-    return omega.value
-
-
-def optimal_weights_1st_order_no_constraints(derivs, l, tol=DEFAULT_TOL):
-    print("Starting optimal weights no constraints 1st order")
-    mini = float('inf')
-    res = None
-    ham_consts = []
-    for deriv in derivs:
-        ham_consts.append(np.matrix([d.flatten() for d in deriv]).T)
-    omega = cp.Variable(len(derivs[0]))
-    constraints = [0 <= omega, omega <= 1, sum(omega) == 1]
-    equalities = ham_consts[:-1]
-    for ham_const in equalities:
-        constraints += [np.real(ham_const) * omega == 0]
[…]

### 2018-12-26 code/pauli_channel_approximation.py

@@ -5,8 +5,7 @@ import numpy as np
 import dill
 from functools import reduce
 import time as timemod
-from convex import (all_derivs, optimal_weights, optimal_weights_1st_order,
-                    optimal_weights_1st_order_no_constraints, optimal_weights_no_constraints)
+from convex import (all_derivs, optimal_weights)
 from mpi4py import MPI
 import scipy
 import os
@@ -107,25 +106,11 @@ class PCA(object):
         self.ambient_hamiltonian = ambient_hamiltonian
         self.control_hamiltonians = control_hamiltonians
 
-    # def assign_weights_0(self, l2=1E-3):
-    #     # derivs = all_derivs(self.controlset, self.target_operator, self.control_hamiltonians, self.ambient_hamiltonian,
-    #     #                     self.dt, 1)
-    #     # for i, d in enumerate(derivs):
-    #     #     if i == 1:
-    #     #         derivs[i] = np.delete(d, np.s_[2], 1)
-    #     weights_0 = optimal_weights(self.derivs[:1], l2)
-    #     self.weights_0 = weights_0
-    #     print("Tried assigning zeroth order weights.")
-    #
-    # def assign_weights(self, l1=1E-3):
-    #     weights = optimal_weights(self.derivs, l1)
-    #     self.weights = weights
-    #     print("Tried assigning order weights.")
-    def assign_weights(self, l1=0, l2=1E-3):
+    def assign_weights(self):
         derivs = all_derivs(self.controlset, self.target_operator, self.control_hamiltonians, self.ambient_hamiltonian,
                             self.dt, 1)
-        weights = optimal_weights_1st_order(derivs, l1)
-        weights_0 = optimal_weights(derivs[:1], l2)
+        weights_0 = optimal_weights(derivs[:1])
+        weights = optimal_weights(derivs)
         self.derivs = derivs
         self.weights = weights
         self.weights_0 = weights_0
@@ -135,17 +120,11 @@ def compute_dpn_and_fid(data):
     from copy import deepcopy
     import sys
     controlset, ambient_hamiltonian0, combo, dt, control_hamiltonians, target_operator, probs = data
-    print("DOING COMBO {}".format(combo))
     sys.stdout.flush()
     fidelities = []
     projs = []
     sops = []
     controlset_unitaries = []
-    #
-    #
-    # for i, com in enumerate(combo):
-    #     if i != 0 and com != 0:
-    #         return 0
     for controls in controlset:
[…]

### 2018-12-26 decorrelation/mixed_unitaries.tex
pulling over more of the work from the first tex document

@@
 
-\author{Anthony Polloreno}
+\author{Anthony M. Polloreno}
 \email[Email: ]{anthony@rigetti.com}
@@
 In this article we discuss various applications of mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
-In this article, we discuss an optimal control approach to the mixed unitary control design problem.
+We present an optimal control approach to the mixed unitary control design problem.
 We apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
@@
 
-** The vec representation may be a little more convenient here? The channel that results is:
+\note{Consider the vec representation} The channel that results is:
 \begin{align}
@@
 \end{center}
-Make a table of these error channels.
 
@@
 
-** This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.
+\note{This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.}
 
@@
 
-\note{Anthony mentions the sparsity constraint, as well as the $\ell_1$ penalty, as being described in this section.}
+While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
+Because of this drift, the quality of the MUP will degrade.
+Thus, we would like to design mized unitary processes that are \textit{robust} to this drift.
+A mixed unitary process is said to be robust to order $\ell$ if for all $1 \leq j \leq \ell$:
+\begin{equation}\label{eq:MUP}
+\begin{gathered}
+\sum_k\omega_k(\sum_{n=0}^j D^n_k)^j = 0\\
+D^n_k = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}...\partial\delta{i_n}}H_k(t,\vec{\delta})|_{\delta=\vec{0}}
+\end{gathered}
+\end{equation}
+These conditions imply that an $\ell^{th}$ order MUP ($\ell$MUP) is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, write the error on each gate in the MUP as 
+\begin{equation}\label{eq:taylor}
+\begin{gathered}
+U_j(\vec{\delta}) = exp(-i(\tilde{H}_j(\vec{0}) + \frac{\partial}{\partial\delta_i}\tilde{H}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \tilde{H}_j(d\delta_i d\delta_k) + ...)U_T
+\end{gathered}
+\end{equation}
+where $\tilde{H}(\delta)$ generates the error $U_j(\vec{\delta})U_T^{\dagger}$ over variations in $\vec{\delta}$.
+Then, by Taylor expanding $U_j(\vec{\delta})U_T^{\dagger}$ one finds that the the first $\ell$ derivatives of an $\ell RBC$ will be zero.
 
-While mixed unitary
+Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+Then, following from the mixing lemma proven by both Campbell and Hastings\cite{1612.01011}, we can bound the the diamond distance from a balanced control to $U_T$ by $\epsilon^2$.
+We can relax Equation \ref{eq:MUP}, to be
+\begin{equation}\label{eq:RBC-relaxed}
+\begin{gathered}
+\sum_k\omega_kD^n_k = 0\\
+\end{gathered}
+\end{equation}
+In this context, since we are assuming that the derivatives are all of norm $\epsilon$, the above condition guarantees that the error unitary be no worse than $\sum^n\epsilon^2\delta^n$ near the origin -- all orders can be quadratically supressed.
+Figure \ref{fig:vectorspace} gives geometric intuition for robustly mixed unitary processes.
 
@@
 % ==============================================================================
+% Section: Generationg of Robustly Mixed Unitary Processes
+% ==============================================================================
+\section{Generation of Robustly Mixed Unitary Processes}
+\label{sec:generation}
+
+To generate robustly mixed unitary processes, we can solve the following convex optimization problem:
+
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
+  \end{split}
+\end{equation}
+
+If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
+In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
+
+This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the family, does not preferentially select the controls with the least error.
+That is to say, as in Section \ref{sec:mixed_unitary_processes}, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this cost function for a 0MUP.
+To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
+
+\begin{equation}\label{eq:minimization_l2}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
+  \end{split}
+\end{equation}
+with $\eta \geq 0$.
+
+To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
+In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+\begin{equation}
+\begin{split}
+\underset{n\in[N]}{\textbf{minimize}}\{
+    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
+    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
+\end{split}
+\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
+
+% ==============================================================================
 % Section: Numerical Results
@@
 \label{sec:random_gate_synthesis}
- In this paper, we use optimal control to generate the one qubit families of controls for MUPs.
+ In this article, we use optimal control to generate the one qubit families of controls for MUPs.
 One could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}, and for our numerics we chose to use the GRAPE algorithm.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\columnwidth]{rb_data.pdf}
+  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
+  \label{fig:rb}
+\end{figure}
+
 As discussed in Section \ref{sec:robustly_mixed}, we chose here to minimize the off diagonal elements of the process matrix.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{Randomized benchmarking experiments ran using different pulse definitions.
-The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
-  \label{fig:rb}
-\end{figure}
-
-% ==============================================================================
-% Section: Figures
-% ==============================================================================
-\section{Figures}
-\label{sec:figures}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a balanced control solution.
-Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
-Each time the gate is used, one of these implementations is chosen at random.
-The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
-  \label{fig:simple_example}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{vectorspace.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-These error Hamiltonians lie in a vector space.
-a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no balanced control solutions.
-b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
-c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
-d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order robust balanced control solution.}
-  \label{fig:vectorspace}
-\end{figure}
-
 % ==============================================================================

### 2018-12-26 decorrelation/mixed_unitaries.tex
Moving over the conclusion as well

@@
 
-To generate robustly mixed unitary processes, we can solve the following convex optimization problem:
-
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
-    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
-  \end{split}
-\end{equation}
-
-If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
-In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
-
-This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the family, does not preferentially select the controls with the least error.
-That is to say, as in Section \ref{sec:mixed_unitary_processes}, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this cost function for a 0MUP.
-To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
-
-\begin{equation}\label{eq:minimization_l2}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
-  \end{split}
-\end{equation}
-with $\eta \geq 0$.
-
-To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
-In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
-\begin{equation}
-\begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{
-    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
-    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
-\end{split}
-\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
-
-% ==============================================================================
-% Section: Numerical Results
-% ==============================================================================
-
-\section{Random Gate Synthesis}
+\subsection{Random Gate Synthesis}
 \label{sec:random_gate_synthesis}
@@
 This is not a fundamental requirement of the routine, but rather was done to make finding solutions with $J(U) < 1 - \epsilon$  less computationally taxing.
+
+\subsection{Optimal Weighting}
+To generate robustly mixed unitary processes, we can solve the following convex optimization problem:
+
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
+  \end{split}
+\end{equation}
+
+If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
+In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
+
+This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the family, does not preferentially select the controls with the least error.
+That is to say, as in Section \ref{sec:mixed_unitary_processes}, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this cost function for a 0MUP.
+To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
+
+\begin{equation}\label{eq:minimization_l2}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
+  \end{split}
+\end{equation}
+with $\eta \geq 0$.
+
+To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
+In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+\begin{equation}
+\begin{split}
+\underset{n\in[N]}{\textbf{minimize}}\{
+    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
+    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
+\end{split}
+\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
 
@@
 % ==============================================================================
+% Section: Conclusion and Future Work
+% ==============================================================================
+
+\section{Conclusion and Future Work}
+We have shown numerically that using RBCs can reduce non-Markovian, coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
+
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+
+Another interesting area of research would be using model-free approaches.
+The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
+in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
+Moreover, even if a model is available, it might be computationally inconvenient to simulate, i.e.
+for more than a few qubits.%, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
+
+In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
+While performing a complete optimization in this way would still be slow, requiring full process tomography, one could intead optimize via partial tomography.
+By selecting pre-- and post --rotations that correspond to measuring pauli moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
+
+% ==============================================================================
 % Section: Acknowledgements

### 2018-12-26 decorrelation/mixed_unitaries.tex
adding in some reeferences

@@
 The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
-Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices.
-While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone has yet to be definitively reached.
+Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices.
+While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone \cite{1203.5813} has yet to be definitively reached.
 The limiting factor, of course, is errors in the quantum gate operations.

### 2018-12-28 decorrelation/mixed_unitaries.tex
campbell and hastings reference

@@
 For long circuits, this can add up extremely quickly.
-Recent work by Hastings and Campbell, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
+Recent work by Hastings and Campbell\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
 This averaging results in quantum processes with diamond distances that grow only linearly  quadratic in the over/under rotation angle of the component gates.

### 2018-12-28 decorrelation/mixed_unitaries.tex
some more changes to the first part, cleaning up equations and text

@@
 
-\note{Consider the vec representation} The channel that results is:
+The channel that results is:
 \begin{align}
@@
 		=& \sum_i p_i U^*_i \otimes U_i \\
-		=& \sum_i p_i \exp(i \theta \hat n \cdot \vec\sigma^*) \otimes \exp(-i \theta \hat n \cdot \vec\sigma) \\
-		\simeq & \sum_i p_i (\cos\theta + i \sin\theta H^*)\otimes(\cos\theta -i \sin\theta H) \\
-		\simeq & \sum_i p_i (\cos\theta^2 I\otimes I + \sin\theta^2 H^*\otimes H \\ & + i\sin\theta\cos\theta H^*\otimes I
+		=& \sum_i p_i \exp(i \frac{\theta}{2}\hat n \cdot \vec\sigma^*) \otimes \exp(-i \frac{\theta}{2} \hat n \cdot \vec\sigma) \\
+		=& \sum_i p_i (\cos\theta + i \sin\theta H^*)\otimes(\cos\theta -i \sin\theta H) \\
+		=& \sum_i p_i (\cos\theta^2 I\otimes I + \sin\theta^2 H^*\otimes H \\ & + i\sin\theta\cos\theta H^*\otimes I
 								- i\sin\theta\cos\theta I\otimes H )
@@
 \begin{equation}
-	\mathcal{F}(\error) = ...
+	\mathcal{F}(\error) = \frac{Tr(\error^*\otimes\error) + d}{d^2 + d}
 \end{equation}
-The diamond norm is generally linear in the over-rotation angle of a quantum operation.
-Also definition of average gate infidelity.
-The AGI is generally quadratic in the over-rotation angle of a quantum operation.
+The diamond norm is generally linear in the over-rotation angle of a quantum operation, while the AGI is generally quadratic in the over-rotation angle of a quantum operation.
 
 A mixed unitary channel consists of a set of unitary channels, $\actual_i$, and associated weights, $\sum_i p_i = 1$.
-The process matrices for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
+The process matrices for a mixed unitary channel are then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
 
 Campbell considered the very important problem of minimizing the diamond norm of the resulting error channel.
-\note{Mention the mixing lemma of Campbell and how the Hamiltonians should form a convex set containing the origin \cite{}}.
-This is a particualrly appealing target, because the diamond norm provides useful error metrics on quantum circuits.
+Given a collection of component channels with error at most $\epsilon$, Campbell and Hastings gave a sufficient condition for the diamond norm to be minimized to first order in $\epsilon$.
+In their their mixing lemmas\cite{Campbell2017, 1612.01011}, they show that the Hamiltonians should form a convex set containing the origin.
+The diamond norm is a particularly appealing target, because the diamond norm provides useful error metrics on quantum circuits.
 However, it is not the only optimization target that can be chosen.
 If the ultimate goal is to produce a channel whose effect can be easily simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
+Such a channel could be produced by instead minimizing the off-diagonal elements of the process matrix.
 
@@
   \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a balanced control solution.
+  \caption{An example of a mixed unitary process.
 Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
@@
 
+In this case, the MUP that minimizes the diamond norm is given by:
+\begin{equation}
+\frac{1}{2}U_{+\epsilon}^*\otimes U_{+\epsilon} + \frac{1}{2}U_{-\epsilon}^*\otimes U_{-\epsilon}
+\end{equation}
+Additionally, it is clear that because the AGI is linear, the AGI of any convex weighting of these two channels will be $\epsilon^2$.
 \note{This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.}

### 2018-12-28 decorrelation/mixed_unitaries.tex
more structural changes

@@
 \begin{equation}
-	\mathcal{F}(\error) = \frac{Tr(\error^*\otimes\error) + d}{d^2 + d}
+	\mathcal{F}(\error) = \frac{d^2 - \tr{(\error^*\otimes\error)}}{d^2 + d}
 \end{equation}
@@
 \end{center}
+\note{This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.}
 
@@
 Additionally, it is clear that because the AGI is linear, the AGI of any convex weighting of these two channels will be $\epsilon^2$.
-\note{This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.}
+More generally, the problems remains: given a collection of channels, how can one efficiently compute a weighting that minimizes a particular metric.
+
+As discussed in \cite{Campbell2017}, a sufficient condition is:
+\begin{equation}\label{eq:campbell-condition}
+\sum \omega_j H_j = 0
+\end{equation}
+
+This condition can be satisfied by solving the following convex optimization problem:
+
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||H^T\omega||_2\\
+  \end{split}
+\end{equation}
+
+where $H$ is the matrix whose rows are the vectorized Hamiltonians.
+
+This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, does not preferentially select the controls with the least error.
+That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this Equation\ref{eq:minimization}.
+To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
+
+\begin{equation}\label{eq:minimization_l2}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}:  }||H^T\omega||_2 + \eta\sum||H||_2^T\omega\\
+  \end{split}
+\end{equation}
+with $\eta \geq 0$.
+
+%\begin{equation}\label{eq:minimization_l2}
+%  \begin{split}
+%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
+%  \end{split}
+%\end{equation}
+
+To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
+In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+
+\begin{equation}\label{eq:minimization_regularization}
+\begin{split}
+\underset{n\in[N]}{\textbf{minimize}}\{
+    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||H^T\omega|| + t\\
+    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\}
+\end{split}
+\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
+
+%\begin{equation}
+%\begin{split}
+%\underset{n\in[N]}{\textbf{minimize}}\{
+%   &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}%{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\%    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+%    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
+%\end{split}
+%\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
 
@@
 \label{sec:robustly_mixed}
-\note{Decide on naming convention, Anthony has used $\ell$ MUP in the rest of the text}
-
-\note{Anthony references this section when discussing minimizing the offdiagonal elements of the error's process matrix.}
 
@@
 We can relax Equation \ref{eq:MUP}, to be
-\begin{equation}\label{eq:RBC-relaxed}
+\begin{equation}\label{eq:MUP-relaxed}
 \begin{gathered}
@@
 In this context, since we are assuming that the derivatives are all of norm $\epsilon$, the above condition guarantees that the error unitary be no worse than $\sum^n\epsilon^2\delta^n$ near the origin -- all orders can be quadratically supressed.
-Figure \ref{fig:vectorspace} gives geometric intuition for robustly mixed unitary processes.
+Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
 
@@
 
+To generate robustly mixed unitary processes, we can solve the following convex optimization problem, generalizing Equation \ref{eq:minimization}:
+
+\begin{equation}\label{eq:robust_minimization}
+  \begin{split}
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
+    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
+  \end{split}
+\end{equation}
+
+Additionally, this can be extended in the obvious way to use Equations \ref{eq:minimization_l2} and\ref{eq:minimization_regularization}.
+
 % ==============================================================================
-% Section: Generationg of Robustly Mixed Unitary Processes
+% Section: Numerical Results
 % ==============================================================================
-\section{Generation of Robustly Mixed Unitary Processes}
-\label{sec:generation}
-
+\section{Numerical Results}
+\label{sec:numerical_results}
 \subsection{Random Gate Synthesis}
@@
 
-\subsection{Optimal Weighting}
-To generate robustly mixed unitary processes, we can solve the following convex optimization problem:
-
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
-    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
-  \end{split}
-\end{equation}
-
-If the control family is too small a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in particular by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
+If the collection of controls generated this way is too small, a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in this case by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
 In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
 
-This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the family, does not preferentially select the controls with the least error.
-That is to say, as in Section \ref{sec:mixed_unitary_processes}, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this cost function for a 0MUP.
-To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
-
-\begin{equation}\label{eq:minimization_l2}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
-  \end{split}
-\end{equation}
-with $\eta \geq 0$.
-
-To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
-In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
-\begin{equation}
-\begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{
-    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\
-    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
-\end{split}
-\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
-
-% ==============================================================================
-% Section: Numerical Results
-% ==============================================================================
-\section{Numerical Results}
-\label{sec:numerical_results}
+\subsection{One Qubit Performance Analysis}
+\label{one_qubit_performance}
 In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
@@
 Imposing this constraint allows us to trade off flatness at the origin for performance.
-
+\subsection{Two Qubit Performance Analysis}
+\label{two_qubit_performance}
 In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:

### 2018-12-29 decorrelation/mixed_unitaries.tex
changes to notebook plots, and document plots

@@
 \begin{abstract}
-...
+Coherent errors in quantum operations are ubiquitous.
+Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate.
+As Hastings and Campbell have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error.
+Our results extend those of Hastings and Campbell to include robustness to drifting external control parameters.
+We implement these constructions using a superconducting qubit and will discuss randomized benchmarking results consistent with a marked reduction in coherent error.
 \end{abstract}
@@
 Errors of this type are correlated in time and add up coherently.
-They are are  computationally expensive to model and it is difficult to place analytic bounds on circuit performance.
+They are are  computationally expensive to model and it is difficult to place tight analytic bounds on circuit performance.
 Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
@@
 Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-Drifting control parameters or environmental variables can easily have long correlation times that result in errors which is strongly coherent over the length of a quantum circuit.
+Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
 While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
-The diamond distance can be used to estimate the failure probability of a quantum circuit, but the diamond distance can grow quadratically with repeated application of gate with coherent errors.
+The diamond distance can be used to estimate the failure probability of a quantum circuit, but it is in general sensitive to first order upon repeated application of gate with coherent errors.
 For long circuits, this can add up extremely quickly.
-Recent work by Hastings and Campbell\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
-This averaging results in quantum processes with diamond distances that grow only linearly  quadratic in the over/under rotation angle of the component gates.
-\note{Clear this up.}
+Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
+This averaging results in quantum processes with diamond distances that grow only quadratically in the over/under rotation angle of the component gates.
 
 In this article we discuss various applications of mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
-We present an optimal control approach to the mixed unitary control design problem.
-We apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+We present an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
 We further present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Quantum Computing.
@@
 Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.
-But if the gates are fairly stable with time and context, then we can describe their action on the qubit state using \emph{process matrices}, linear, Markovian maps on the state of some qubits.
+But if the gates are fairly stable with time and context\cite{1810.05651}, then we can describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.
 When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
@@
 where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
-\begin{equation}
-  \rho \rightarrow \target\rho = \error \actual \rho.
+\begin{equation}\label{error_def}
+  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
 \end{equation}
-Here $\target_i$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel.
+Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:
 
-\begin{equation}
+\begin{equation}\label{eq:process_matrix}
 	\left(\begin{array}{c|cccc}
@@
 The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.
-The rest of the first column, $\vec{m}$, describes any deviations from unitality, such as could arise from amplitude damping.
+The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping.
 If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
-If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry corresponding to the probability that the associated Pauli error occurs in each application of the gate.
-\note{Be more clear about what "associated" means here}.
+If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry $\error_{ii}$ corresponding to the probability that the associated Pauli error:
+\begin{equation}
+\vec\rho \rightarrow \sigma_i^*\otimes\sigma_i\vec\rho
+\end{equation}
+ occurs in each application of the gate.
+
  If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
@@
 
-The channel that results is:
+For a collection of controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general is:
 \begin{align}
@@
 		=& \sum_i p_i U^*_i \otimes U_i \\
-		=& \sum_i p_i \exp(i \frac{\theta}{2}\hat n \cdot \vec\sigma^*) \otimes \exp(-i \frac{\theta}{2} \hat n \cdot \vec\sigma) \\
-		=& \sum_i p_i (\cos\theta + i \sin\theta H^*)\otimes(\cos\theta -i \sin\theta H) \\
-		=& \sum_i p_i (\cos\theta^2 I\otimes I + \sin\theta^2 H^*\otimes H \\ & + i\sin\theta\cos\theta H^*\otimes I
-								- i\sin\theta\cos\theta I\otimes H )
+		=& \sum_i p_i \exp(i \frac{\theta_i}{2}\hat n_i \cdot \vec\sigma^*) \otimes \exp(-i \frac{\theta_i}{2} \hat n_i \cdot \vec\sigma) \\
+		=& \sum_i p_i (\cos\theta_i + i \sin\theta_i H_i^*)\otimes(\cos\theta_i -i \sin\theta_i H_i) \\
+		=& \sum_i p_i (\cos\theta_i^2 I\otimes I + \sin\theta_i^2 H^*\otimes H_i \\ & + i\sin\theta_i\cos\theta_i H_i^*\otimes I
+								- i\sin\theta_i\cos\theta_i I\otimes H_i )
 \end{align}
@@
 \begin{equation}
-	\mathcal{F}(\error) = \frac{d^2 - \tr{(\error^*\otimes\error)}}{d^2 + d}
+	\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d}
 \end{equation}
-The diamond norm is generally linear in the over-rotation angle of a quantum operation, while the AGI is generally quadratic in the over-rotation angle of a quantum operation.
+The diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
 
-A mixed unitary channel consists of a set of unitary channels, $\actual_i$, and associated weights, $\sum_i p_i = 1$.
-The process matrices for a mixed unitary channel are then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
+A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_i$, and associated weights, $\sum_i p_i = 1$.
+The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
 
-Campbell considered the very important problem of minimizing the diamond norm of the resulting error channel.
-Given a collection of component channels with error at most $\epsilon$, Campbell and Hastings gave a sufficient condition for the diamond norm to be minimized to first order in $\epsilon$.
-In their their mixing lemmas\cite{Campbell2017, 1612.01011}, they show that the Hamiltonians should form a convex set containing the origin.
-The diamond norm is a particularly appealing target, because the diamond norm provides useful error metrics on quantum circuits.
+Campbell\cite{Campbell2017} considered the very important problem of minimizing the diamond norm of the resulting error channel.
+Given a collection of component channels with error at most $\epsilon$, they show that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
+The diamond norm is a particularly appealing target because the it provides useful error metrics on quantum circuits.
 However, it is not the only optimization target that can be chosen.
-If the ultimate goal is to produce a channel whose effect can be easily simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
-Such a channel could be produced by instead minimizing the off-diagonal elements of the process matrix.
-
-%\eq
+If the ultimate goal is to produce a channel whose effect can be efficiently simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
+Such a channel could be produced by instead minimizing the off-diagonal elements in (\ref{eq:process_matrix}).
 
@@
 There are often many possibly ways of implementing any given target quantum gate.
-Hastings and Campbell, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which  many approximate gate compilations are possible.
-By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.
+Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.
 As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
@@
 \end{center}
-\note{This example is really useful and should be expanded. We should discuss the various optimization problems, a mixed unitary strategy, the fidelity of the resulting channel.}
 
@@
 
-As discussed in \cite{Campbell2017}, a sufficient condition is:
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 
-where $H$ is the matrix whose rows are the vectorized Hamiltonians.
+where $H$ is the matrix whose rows are the vectorized Hamiltonians, i.e. for $m$, $n\times n$ Hamiltonians:
+\begin{equation}\label{eq:vectorized_hamiltonians}
+	\left(\begin{array}{cccc}
+		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
+		\vdots\ & \ddots &    \\
+		H_{m_{11}} &  &  H_{m_{nn}} \\ 
+	\end{array} 	
+	\right)
+\end{equation}
 
-This minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, does not preferentially select the controls with the least error.
-That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} minimize this Equation\ref{eq:minimization}.
+While this particular convex optimization problem can be solved through a system of linear equations, casting it as a convex optimization problem allows us to regularize the cost function, and introduce additional constraints.
+In particular, this minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, does not preferentially select the controls with the least error.
+That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} satisfy Equation \ref{eq:minimization}.
 To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}:  }||H^T\omega||_2 + \eta\sum||H||_2^T\omega\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}:  }||H^T\omega||_2 + \eta\sum\omega_j||H_j||_2\\
   \end{split}
@@
 
-To make sure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
+To ensure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
 In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
@@
 Because of this drift, the quality of the MUP will degrade.
-Thus, we would like to design mized unitary processes that are \textit{robust} to this drift.
-A mixed unitary process is said to be robust to order $\ell$ if for all $1 \leq j \leq \ell$:
+Thus, we would like to design MUPs that are \textit{robust} to this drift.
+A mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
 \begin{equation}\label{eq:MUP}
@@
 \end{equation}
-These conditions imply that an $\ell^{th}$ order MUP ($\ell$MUP) is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, write the error on each gate in the MUP as 
+These conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, write the error on each control in the MUP as 
 \begin{equation}\label{eq:taylor}
 \begin{gathered}
-U_j(\vec{\delta}) = exp(-i(\tilde{H}_j(\vec{0}) + \frac{\partial}{\partial\delta_i}\tilde{H}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \tilde{H}_j(d\delta_i d\delta_k) + ...)U_T
+\actual_j(\vec{\delta}) = exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + ...)\target
 \end{gathered}
 \end{equation}
-where $\tilde{H}(\delta)$ generates the error $U_j(\vec{\delta})U_T^{\dagger}$ over variations in $\vec{\delta}$.
-Then, by Taylor expanding $U_j(\vec{\delta})U_T^{\dagger}$ one finds that the the first $\ell$ derivatives of an $\ell RBC$ will be zero.
+where $H(\delta)$ generates $\error$, as in Equation \ref{error_def}.
+By Taylor expanding Equation \ref{eq:taylor} in $\delta$, one finds that the the first $\ell$ derivatives of an $\ell MUP$ will be zero.
 
-Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that $\vec{\omega}$ exists that quadratically decreases the diamond norm.
-Then, following from the mixing lemma proven by both Campbell and Hastings\cite{1612.01011}, we can bound the the diamond distance from a balanced control to $U_T$ by $\epsilon^2$.
-We can relax Equation \ref{eq:MUP}, to be
+Furthermore, if we assume that the derivatives are all of norm $\epsilon$, we can relax Equation \ref{eq:MUP}, to be
 \begin{equation}\label{eq:MUP-relaxed}
@@
 \end{equation}
-In this context, since we are assuming that the derivatives are all of norm $\epsilon$, the above condition guarantees that the error unitary be no worse than $\sum^n\epsilon^2\delta^n$ near the origin -- all orders can be quadratically supressed.
-Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
+This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
+Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
 
@@
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order robust balanced control solution.}
+If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order mixed unitary process.}
   \label{fig:vectorspace}
@@
 \end{equation}
+with $D_k^n$ defined in Equation \ref{eq:MUP}. Equations \ref{eq:minimization_l2} and\ref{eq:minimization_regularization} extend in a straightforward way:
 
-Additionally, this can be extended in the obvious way to use Equations \ref{eq:minimization_l2} and\ref{eq:minimization_regularization}.
+\begin{equation}\label{eq:minimization_regularization}
+\begin{split}
+\underset{n\in[N]}{\textbf{minimize}}\{\\
+    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
+&\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+&\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
+\}
+\end{split}
+\end{equation}
 
@@
 
-If the collection of controls generated this way is too small, a solution won't exist, in particular as in \cite{Campbell2017} we need  $0\in $ Conv$[D_j^i]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm to produce robust controls, in this case by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
+As discussed in Section \ref{sec:robustly_mixed}, for these controls to form an $\ell$MUP, we need $0\in $ Conv$[D_j^i]$.
+This can be accomplished by modifying the oracle in Campbell's algorithm\cite{Campbell2017} to produce robust controls.
+In this case, by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
 In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
@@
 These results demonstrate several properties that make MUPs both useful and tractable.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{SQRTY.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are quantitatively similar to those for $RX(\frac{\pi}{2})$, but in this case the 0MUP is worse at the origin.
-This can be improved by penalizing for the norms, or by simply trying to find a 1MUP, which both symmeterizes the performance at the origin and makes them better.}
-  \label{fig:YMUP}
-\end{figure*}
-
-%\begin{figure*}
-%  \centering
-%  \includegraphics[width=\textwidth]{SQRTX.png}
-%  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RX(\frac{np.pi}{2})$.
-Shown with lower alpha values are example members of the control families, with diamond norms of around $10^{-2}$.
-The 0MUP can be seen to outperform the members of the control family by two orders of magnitude at the origin, and the 1MUP by an order of magnitude.
-However, the 1MUP can be seen to be flatter.
-In paritcular, for small detunings, the 1MUP performs better than the 0MUP.}
-%  \label{fig:XMUP}
-%\end{figure*}
 
@@
   \includegraphics[width=\columnwidth]{bangbang.png}
-  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
+  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
   \label{fig:bangbang}
@@
 In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
-There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little variation in the controls.
-Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin, and up to an order of magnitude away from the origin, with the 1MUP performing just as well as the 0MUP, but also being more robust to drift.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{2QRBC.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
-Shown with lower alpha values are example members of the control families.
-The 0MUP and 1MUP can be seen to outperform the members of the control family by half an order of magnitude at the origin.
-Away from the origin, the 1MUP can be seen to be flatter.
-Far away from the origin, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.}
-  \label{fig:2MUP}
-\end{figure*}
+There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
+Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+For all values of the drifting parameters we see that the 1MUP performs as well or better than 0MUP.
 
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using RBCs can reduce non-Markovian, coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+We have shown numerically that using MUPs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the FPGA, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 
@@
 in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
-Moreover, even if a model is available, it might be computationally inconvenient to simulate, i.e.
-for more than a few qubits.%, or for non-adiabatic gates, where the timestep is required to be much smaller than the gate-time.
+Even if a model is available, it might be computationally inconvenient to simulate, i.e.
+for more than a few qubits.
 
 In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
-While performing a complete optimization in this way would still be slow, requiring full process tomography, one could intead optimize via partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring pauli moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
+While performing a complete optimization in this way would require full process tomography, one could intead optimize via partial tomography.
+By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
 
@@
 Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
+
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=\textwidth]{SQRTY.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+The results are quantitatively similar to those for $RX(\frac{\pi}{2})$.
+In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
+However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+  \label{fig:YMUP}
+\end{figure*}
+
+\begin{figure*}[h]
+  \centering
+  \includegraphics[width=\textwidth]{2QRBC.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+Shown with lower alpha values are example constituent controls.
+The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
+For all detuning values the 1MUP performs as well or better than the 0MUP.
+When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
+  \label{fig:2MUP}
+\end{figure*}
+
 \bibliography{decorrelation.bib}

### 2018-12-29 decorrelation/mixed_unitaries.tex
missed a couple BCSs and RBCs

@@
 
-Because we our trying to generate high-order RBCs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
+Because we our trying to generate high-order MUPs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
 \begin{align}\label{eq:quadrature}
@@
   \caption{Randomized benchmarking experiments ran using different pulse definitions.
-The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
+The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
   \label{fig:rb}

### 2018-12-29 decorrelation/mixed_unitaries.tex
some small formatting changes to equation 22

@@
 \usepackage{graphicx}
+\usepackage{calc}
 \graphicspath{{./figures/}}
@@
 
+\newcommand{\bunderbrace}[2]{%
+  \begin{array}[t]{@{}c@{}}
+  #1\\
+  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
+  \end{array}
+}
+
 \begin{equation}\label{eq:minimization_regularization}
 \begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{\\
-    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
-&\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-&\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
+&\underset{n\in[N]}{\textbf{minimize}}\{\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
+&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+&\ \ \phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
 \}
@@
 Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
+\bibliography{decorrelation.bib}
 
+\newpage
+\onecolumngrid
+% ==============================================================================
+% Section: Appendix
+% ==============================================================================
+\section{Appendix}
+\label{sec:appendix}
 \begin{figure*}[h]
@@
   \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are quantitatively similar to those for $RX(\frac{\pi}{2})$.
+The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
 In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
@@
 
-\bibliography{decorrelation.bib}
 \end{document}

### 2019-01-05 decorrelation/mixed_unitaries.tex
made changes to the text, and the figures

@@
 While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
-The diamond distance can be used to estimate the failure probability of a quantum circuit, but it is in general sensitive to first order upon repeated application of gate with coherent errors.
+The diamond distance can be used to bound the TVD of a quantum circuit, but it is in general sensitive at first order torepeated application of gate with coherent errors.
 For long circuits, this can add up extremely quickly.
-Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates.
-This averaging results in quantum processes with diamond distances that grow only quadratically in the over/under rotation angle of the component gates.
+Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over several distinct implementations of the target quantum gates.
+The resulting effective quantum process has a diamond distancea that grow only quadratically in the over/under rotation angle of the component gates.
 
@@
 Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
+We demonstrate that, depending on the objective, different numerical optimzations may be prefered.
 
@@
 Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.
-But if the gates are fairly stable with time and context\cite{1810.05651}, then we can describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.
+But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.
 When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
@@
 \begin{equation}\label{eq:process_matrix}
+\error =
 	\left(\begin{array}{c|cccc}
-		1 &  & \vec0 & \\ 
+		1 &  & \vec{0}^T & \\ 
 		\hline & &  &  \\
@@
 \end{equation}
-
 The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.
@@
 \begin{equation}
-\vec\rho \rightarrow \sigma_i^*\otimes\sigma_i\vec\rho
+\vec\rho \rightarrow \tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho}
 \end{equation}
@@
 
-For a collection of controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general is:
+For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general is:
 \begin{align}
-	\mathcal{M} 
-		=& \sum_i p_i U^*_i \otimes U_i \\
-		=& \sum_i p_i \exp(i \frac{\theta_i}{2}\hat n_i \cdot \vec\sigma^*) \otimes \exp(-i \frac{\theta_i}{2} \hat n_i \cdot \vec\sigma) \\
-		=& \sum_i p_i (\cos\theta_i + i \sin\theta_i H_i^*)\otimes(\cos\theta_i -i \sin\theta_i H_i) \\
-		=& \sum_i p_i (\cos\theta_i^2 I\otimes I + \sin\theta_i^2 H^*\otimes H_i \\ & + i\sin\theta_i\cos\theta_i H_i^*\otimes I
-								- i\sin\theta_i\cos\theta_i I\otimes H_i )
+	\mathcal{M}_{jk} 
+		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
+		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
+		=& \tr{\sum_i p_i (\sigma_j^{\dagger} (\cos\theta_i + i \sin\theta_i H_i) \sigma_k		(\cos\theta_i - i \sin\theta_i H_i))} \\
+		=&\tr (\sum_i p_i (\sigma_j\sigma_k\cos\theta_i^2 + \sigma_jH_i\sigma_k H_i\sin\theta_i^2 \\ 
+		&+ iH_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j H_i\sin\theta_i\cos\theta_i))
 \end{align}
-In this case, $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+In this case, the first term corresponds to the identity.
+$\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
 The result would be a purely stochastic channel.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace.pdf}
+  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
+These error Hamiltonians lie in a vector space.
+a) Four effective Hamiltonians.
+The origin is not contained in their convex hull, so there are no balanced control solutions.
+b) The origin is contained in the covex hull after adding an additional control solution.
+Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
+c) The error Hamiltonians shown with their derivative with respect to a control parameter.
+As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
+d) The derivatives also lie in a vector space.
+If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order mixed unitary process.}
+  \label{fig:vectorspace}
+\end{figure}
+
+In fact, the problem of minimizing $\sin\theta\cos\theta$ can be seen equivalently as in Figure \ref{fig:vectorspace}.
+The problem can reduced to trying to construct a family of vectors, whose convex hull contains the origin.
 
@@
 \begin{equation}
-	\vert\vert \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1
+	\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq: fid}
 	\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d}
@@
 The diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
+It's interesting, however, to consider how these metrics assess the quality of stochastic quantum processes.
 
-A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_i$, and associated weights, $\sum_i p_i = 1$.
-The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_i p_i \actual_i$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_i p_i \error_i$.
+A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
+The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
+It is clear from Equation \ref{eq: fid} that the AGI is linear, and therefore we see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
+The diamond norm, however, is non-linear, and can in general be smaller for a MUP than any of the processes being mixed.
 
@@
 % ==============================================================================
-\section{Example Mixed Unitary Processes}
+\section{Constructing Useful Unitary Processes}
 \label{sec:mixed_unitary_processes}
+\subsection{Mixed Unitary Processes}
 There are often many possibly ways of implementing any given target quantum gate.
@@
 \end{equation}
-Additionally, it is clear that because the AGI is linear, the AGI of any convex weighting of these two channels will be $\epsilon^2$.
-More generally, the problems remains: given a collection of channels, how can one efficiently compute a weighting that minimizes a particular metric.
+More generally, the problem remains: given a collection of channels, how can one efficiently compute a weighting that minimizes a particular metric?
 
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm to first order is:
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 \end{equation}
-
-This condition can be satisfied by solving the following convex optimization problem:
+In \cite{Campbell2017}, Campbell constructs an algorithm that, using an abstract oracle to produce particular unitary controls, finds a MUP with this property.
+Alternatively, one can use convex optimization to solve this problem.
+Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e.
+for $m$, $n\times n$ Hamiltonians:
+\begin{equation}\label{eq:vectorized_hamiltonians}
+	H = \left(\begin{array}{cccc}
+		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
+		\vdots\ & \ddots &    \\
+		H_{m_{11}} &  &  H_{m_{nn}} \\ 
+	\end{array} 	
+	\right)
+\end{equation}
+Then, if our weighting vector for our MUP is $\omega$, we rewrite this sum as a matrix product, two-norm will be zero if and only if the sum is zero.
+That is we can instead consider solving the following convex optimization problem:
 
@@
 
-where $H$ is the matrix whose rows are the vectorized Hamiltonians, i.e. for $m$, $n\times n$ Hamiltonians:
-\begin{equation}\label{eq:vectorized_hamiltonians}
-	\left(\begin{array}{cccc}
-		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
-		\vdots\ & \ddots &    \\
-		H_{m_{11}} &  &  H_{m_{nn}} \\ 
-	\end{array} 	
-	\right)
-\end{equation}
-
+\subsection{Norm Regularization}
 While this particular convex optimization problem can be solved through a system of linear equations, casting it as a convex optimization problem allows us to regularize the cost function, and introduce additional constraints.
@@
 %\end{equation}
-
+\subsection{Sparsity Constraints}
 To ensure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
@@
 
-%\begin{equation}
-%\begin{split}
-%\underset{n\in[N]}{\textbf{minimize}}\{
-%   &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}%{\textbf{minimize}: } ||D_{\ell}^T\omega|| + t\\%    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-%    &\phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\}
-%\end{split}
-%\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
-
-% ==============================================================================
-% Section: Robustly Mixed Unitary Processes
-% ==============================================================================
-\section{Robustly Mixed Unitary Processes}
+\subsection{Robustly Mixed Unitary Processes}
 \label{sec:robustly_mixed}
@@
 This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{vectorspace.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-These error Hamiltonians lie in a vector space.
-a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no balanced control solutions.
-b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
-c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
-d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order mixed unitary process.}
-  \label{fig:vectorspace}
-\end{figure}
 
@@
 \label{sec:numerical_results}
-\subsection{Random Gate Synthesis}
-\label{sec:random_gate_synthesis}
- In this article, we use optimal control to generate the one qubit families of controls for MUPs.
-One could use any of the many available quantum optimal control techniques \cite{Khaneja2005, Caneva2011, Machnes2018}, and for our numerics we chose to use the GRAPE algorithm.
-First described in \cite{Khaneja2005}, the GRAPE (GRadient Ascent Pulse Engineering) algorithm is a technique for finding piecewise constant control sequences that approximate a desired unitary, $U_T$, given a Hamiltonian with controlled and uncontrolled terms.
-Defining the uncontrolled Hamiltonian as $H_0$, the control Hamiltonians as $H_{i\neq 0}$, and the \textit{control matrix} $c_{ij}$ as containing the control amplitude associated with the $i^{th}$ time step and the $j^{th}$ Hamiltonian, we can write an the unitary for any timestep of evolution as:
-\begin{equation}\label{eq:3}
-  U_i = \exp\{-i\Delta t(H_0 + \sum_{j=1}^{n}c_{ij}H_{j}\}
-\end{equation}
-To measure the simularity of our approxiate unitary $U=\prod_iU_{i=1}^n$ to our target unitary $U_T$, we can define a cost function $J(U) = Tr\{U_T^{\dagger}U\}$.
-
-To optimize this cost function we can perform the following standard update loop for some threshold value $\varepsilon > 0$ and step size $\delta > 0$:
-\begin{algorithm}[H]
-\floatname{algorithm}
-  \caption{\textsc{\textbf{Gradient Ascent}}}
-  \begin{algorithmic}
-    \While{$J(U) < (1-\varepsilon$)}
-    \State $c_{ij} \rightarrow c_{ij} + \delta\frac{\partial J(U)}{\partial c_{ij}}$
-    \For{$1 \leq i \leq n$}
-    \State $U_i \rightarrow \exp\{-i\Delta t(H_0 + \sum_{i=0}^{n}c_{ij}H_j)\}$
-    \EndFor
-    \State $U \rightarrow \prod_{i=1}^nU_i$
-    \EndWhile
-  \end{algorithmic}
-\end{algorithm}
-
-In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters through each timestep of the  via the chain rule.
-However, in \cite{Khaneja2005} Khaneja et al.
-derive an update formula that is correct to first order, and efficient to compute.
-In particular one can show that:
-\begin{equation}\label{eq:update}
-  \begin{split}
-\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
-\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
-  \end{split}
-\end{equation}
-
-Because we our trying to generate high-order MUPs, we want to generate controls that perform well even in the presence of drift. To do this, we modified the gradient in GRAPE to instead be:
-\begin{align}\label{eq:quadrature}
-\frac{\partial \tilde J(U)}{\partial u_{ij}} =
-\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta}))}{\partial u_{ij}} d\vec{\delta}
-\end{align}
-with $p(\vec{\delta})$ Gaussian distributed, as has been done in previous works \cite{Goerz2014} to ensure that the optimal control results are robust over a wide range of errors.
-To make this averaging tractable, we approximate this integral using Gaussian quadrature, approximating the cost function as a low order polynomial\cite{abramowiz1972handbook} (in particular degree 5).
-Note that despite updating the gradient, we did not change the cost function.
-The termination condition for the gradient ascent loop is still just that the controls perform well in the absence of drift.
-This is not a fundamental requirement of the routine, but rather was done to make finding solutions with $J(U) < 1 - \epsilon$  less computationally taxing.
-
-As discussed in Section \ref{sec:robustly_mixed}, for these controls to form an $\ell$MUP, we need $0\in $ Conv$[D_j^i]$.
-This can be accomplished by modifying the oracle in Campbell's algorithm\cite{Campbell2017} to produce robust controls.
-In this case, by updating the GRAPE cost function to include derivative information, one could produce controls with derivatives of order $\epsilon$.
-In our case, by using the Gaussian weighted cost function, we ensure that the controls generated should have vanishing first derivative.
-
-\subsection{One Qubit Performance Analysis}
 \label{one_qubit_performance}
@@
 We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less coherent error channel.
+Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{SQRTY.png}
+  \includegraphics[width=\textwidth]{SQRTY_no_member.png}
   \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
@@
   \centering
-  \includegraphics[width=\textwidth]{2QRBC.png}
+  \includegraphics[width=\textwidth]{2QRBC_no_member.png}
   \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.

### 2019-01-06 decorrelation/mixed_unitaries.tex
improvements after our phone call!

@@
 Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
 While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
-The diamond distance can be used to bound the TVD of a quantum circuit, but it is in general sensitive at first order torepeated application of gate with coherent errors.
+The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of gate with coherent errors.
 For long circuits, this can add up extremely quickly.
-Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over several distinct implementations of the target quantum gates.
-The resulting effective quantum process has a diamond distancea that grow only quadratically in the over/under rotation angle of the component gates.
+Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
+The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
 
-In this article we discuss various applications of mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
-We present an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
-We further present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Quantum Computing.
+%Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
+
+In this article we discuss various applications of these mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
+We demonstrate that, depending on the objective, different numerical optimzations may be prefered.
+We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
 Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
-We demonstrate that, depending on the objective, different numerical optimzations may be prefered.
+We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
 
@@
 If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
-If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry $\error_{ii}$ corresponding to the probability that the associated Pauli error:
+If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate.
+That is to say that $\error_{ii}$ gives the probability that the following map is applied:
 \begin{equation}
@@
 \end{equation}
- occurs in each application of the gate.
-
  If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
@@
 
-For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general is:
+For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general has elements:
 \begin{align}
@@
 		=& \tr{\sum_i p_i (\sigma_j^{\dagger} (\cos\theta_i + i \sin\theta_i H_i) \sigma_k		(\cos\theta_i - i \sin\theta_i H_i))} \\
-		=&\tr (\sum_i p_i (\sigma_j\sigma_k\cos\theta_i^2 + \sigma_jH_i\sigma_k H_i\sin\theta_i^2 \\ 
+		=& \tr (\sum_i p_i (\sigma_j\sigma_k\cos\theta_i^2 + \sigma_jH_i\sigma_k H_i\sin\theta_i^2 \\ 
 		&+ iH_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j H_i\sin\theta_i\cos\theta_i))
 \end{align}
-In this case, the first term corresponds to the identity.
-$\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+The first term corresponds to the identity, and $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
 The result would be a purely stochastic channel.
@@
 
-In fact, the problem of minimizing $\sin\theta\cos\theta$ can be seen equivalently as in Figure \ref{fig:vectorspace}.
-The problem can reduced to trying to construct a family of vectors, whose convex hull contains the origin.
+The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(H_i\sigma_k - \sigma_jH_i)$ whose convex hull contains the origin.
+This can be seen in Figure \ref{fig:vectorspace} a) and b).
 
+In addition to the type of errors, we care about the size of an error.
 The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
@@
 \end{equation}
-The diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
-It's interesting, however, to consider how these metrics assess the quality of stochastic quantum processes.
+Which metric is relevant depends on the application, and can yield very different numbers.
+For instance, the diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
+Similarly, these two metric perform very differently on stochastic quantum processes, that can be achieved by probabilistically mixing unitary operators.
 
@@
 The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-It is clear from Equation \ref{eq: fid} that the AGI is linear, and therefore we see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
+From this definition, we can compute the AGI of a MUP, by first computing the AGI of an convex combination of channels:
+\begin{align}
+\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) &= \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
+&= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} 
+\end{align}
+where we have used the linearity of the trace.
+%\begin{align}
+%\mathcal{F}(\error_{\rm M}) &= \mathcal{F}(\sum_j \omega_j \error_j)\\
+%&= \frac{\tr (\sum_j \omega_j \error_j) + d}{d^2 + d}\\
+%&= \frac{\sum_j(\tr (\omega_j \error_j)) + d}{d^2 + d}\\
+%&= \frac{\sum_j(\tr (\omega_j (\error_j + d))}{d^2 + d}\\
+%&= \sum_j\frac{(\tr (\omega_j (\error_j + d))}{d^2 + d}\\ 
+%\end{align}
+
+We therefore see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
 The diamond norm, however, is non-linear, and can in general be smaller for a MUP than any of the processes being mixed.
 
-Campbell\cite{Campbell2017} considered the very important problem of minimizing the diamond norm of the resulting error channel.
+Campbell\cite{Campbell2017} considered this important problem of minimizing the diamond norm of the resulting error channel.
 Given a collection of component channels with error at most $\epsilon$, they show that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
@@
 However, it is not the only optimization target that can be chosen.
-If the ultimate goal is to produce a channel whose effect can be efficiently simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
-Such a channel could be produced by instead minimizing the off-diagonal elements in (\ref{eq:process_matrix}).
+If the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
+Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
+Indeed, this is the approach we consider in Section \ref{sec:experimental_results}.
+More generally, the are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.
 
 % ==============================================================================
-% Section: Example Mixed Unitary Processes
+% Section: Constructing Useful Unitary Processes
 % ==============================================================================
@@
 \label{sec:mixed_unitary_processes}
-\subsection{Mixed Unitary Processes}
+\subsection{Mixed Unitary Processes with Small Diamond Norm}
+\label{sec:small_diamond_norm}
 There are often many possibly ways of implementing any given target quantum gate.
@@
 \end{equation}
-In \cite{Campbell2017}, Campbell constructs an algorithm that, using an abstract oracle to produce particular unitary controls, finds a MUP with this property.
+In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property.
 Alternatively, one can use convex optimization to solve this problem.
@@
 \end{equation}
-Then, if our weighting vector for our MUP is $\omega$, we rewrite this sum as a matrix product, two-norm will be zero if and only if the sum is zero.
-That is we can instead consider solving the following convex optimization problem:
+If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
+That is, we can instead consider solving the following convex optimization problem:
 
@@
 \end{equation}
-
-\subsection{Norm Regularization}
-While this particular convex optimization problem can be solved through a system of linear equations, casting it as a convex optimization problem allows us to regularize the cost function, and introduce additional constraints.
-In particular, this minimization problem, while sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, does not preferentially select the controls with the least error.
-That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} satisfy Equation \ref{eq:minimization}.
-To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
-
-\begin{equation}\label{eq:minimization_l2}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}:  }||H^T\omega||_2 + \eta\sum\omega_j||H_j||_2\\
-  \end{split}
-\end{equation}
-with $\eta \geq 0$.
-
-%\begin{equation}\label{eq:minimization_l2}
-%  \begin{split}
-%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
-%  \end{split}
-%\end{equation}
-\subsection{Sparsity Constraints}
-To ensure the routine remains practical, we would also like to regularize our objective function to enforce sparsity.
-In this case, lasso regularization \cite{tibshirani1996regression} is insufficient as we already constrain the one norm of the vector we optimize over to be one.
-However, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
-
-\begin{equation}\label{eq:minimization_regularization}
-\begin{split}
-\underset{n\in[N]}{\textbf{minimize}}\{
-    &\underset{\omega_j\geq0, |\omega|_1=1, t\geq0}{\textbf{minimize}: } ||H^T\omega|| + t\\
-    &\textbf{subject to: } \omega_n > \frac{\lambda}{t}\}
-\end{split}
-\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
-
+where the minimization is over all valid probability distributions.
 \subsection{Robustly Mixed Unitary Processes}
@@
 Thus, we would like to design MUPs that are \textit{robust} to this drift.
-A mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
+To enforce robustness, we can consider higher derivatives of the Hamiltonians in \ref{eq:campbell-condition}.
+Instead of just requiring that the $0^{th}$ derivative averages to zero, we should impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
+\begin{equation}
+D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
+\end{equation}
+Then we say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
 \begin{equation}\label{eq:MUP}
 \begin{gathered}
-\sum_k\omega_k(\sum_{n=0}^j D^n_k)^j = 0\\
-D^n_k = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}...\partial\delta{i_n}}H_k(t,\vec{\delta})|_{\delta=\vec{0}}
+\sum_j\omega_j(\sum_{n=0}^k D^n_j)^k = 0\\
 \end{gathered}
 \end{equation}
-These conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, write the error on each control in the MUP as 
+In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}.
+More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
+To see this, we can rewrite the error on each control in the MUP as:
 \begin{equation}\label{eq:taylor}
 \begin{gathered}
-\actual_j(\vec{\delta}) = exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + ...)\target
+\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
 \end{gathered}
 \end{equation}
-where $H(\delta)$ generates $\error$, as in Equation \ref{error_def}.
-By Taylor expanding Equation \ref{eq:taylor} in $\delta$, one finds that the the first $\ell$ derivatives of an $\ell MUP$ will be zero.
-
-Furthermore, if we assume that the derivatives are all of norm $\epsilon$, we can relax Equation \ref{eq:MUP}, to be
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell MUP$ will be zero.
+Furthermore, if we are only interested in being first order insensitve to drift and can select controls such that $|D_j^n|\approx\epsilon$, we see that Equation \ref{eq:MUP} can be approximated as:
 \begin{equation}\label{eq:MUP-relaxed}
 \begin{gathered}
-\sum_k\omega_kD^n_k = 0\\
+\sum_k\omega_jD^n_j = 0\\
 \end{gathered}
@@
 This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
-Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{\tilde{H}_i(t, \vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
 This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
 
-To generate robustly mixed unitary processes, we can solve the following convex optimization problem, generalizing Equation \ref{eq:minimization}:
+To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to \ref{eq:vectorized_hamiltonians}:
+\begin{equation}
+{D^{\ell}}^T =  \left(\begin{array}{cccc}
+		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
+		\vdots\ & \ddots &    \\
+		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
+	\end{array} 	
+	\right)
+\end{equation}
+
+Using this, we can then solve the following convex optimization problem, generalizing Equation \ref{eq:minimization}:
 
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||\\
-    &\textbf{subject to: } \forall i<\ell, \sum \omega_jD_j^i=0\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{D^{\ell}}^T\omega||\\
+    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
   \end{split}
 \end{equation}
-with $D_k^n$ defined in Equation \ref{eq:MUP}. Equations \ref{eq:minimization_l2} and\ref{eq:minimization_regularization} extend in a straightforward way:
+with $D_k^n$ defined in Equation \ref{eq:MUP}.
+
+\subsection{Hamiltonian Norm Regularization}
+While these particular convex optimization problem can be solved through a system of linear equations, casting it as a convex optimization problem allows us to regularize the cost function, and introduce additional constraints.
+In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:small_diamond_norm} satisfy Equation \ref{eq:minimization}.
+To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
 
@@
 
+\begin{equation}\label{eq:minimization_l2}
+\begin{split}
+&\underset{n\in[N]}{\textbf{minimize}}\{\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{D^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
+&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
+&\}
+\end{split}
+\end{equation}
+with $\eta \geq 0$. By making $\eta$ larger, we can require that the solver decreases the diamond norm of the constituent channel, while using only the best controls.
+
+%\begin{equation}\label{eq:minimization_l2}
+%  \begin{split}
+%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
+%  \end{split}
+%\end{equation}
+\subsection{Sparsity Constraints}
+As a practical consideration, we would also like to regularize our objective function to enforce sparsity.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
+As an example of where this would be necessary is Figure\ref{fig:vectorspace}.
+In Subfigure b, it's clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
+However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set.
+Thus we would like the solver to be frugal in which controls it selects.
+In many machine learning situation, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity, however here it is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+
 \begin{equation}\label{eq:minimization_regularization}
@@
 &\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||D_{\ell}^T\omega||+ \eta\sum\omega_j||H_j||_2 + t\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{D^{\ell}}^T\omega|| + t\\
 &\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall i<\ell, \sum \omega_jD_j^i=0\\
-\}
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
+&\}
 \end{split}
-\end{equation}
+\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
 

### 2019-01-07 decorrelation/mixed_unitaries.tex
a few more small changes
extra ^T
cleaning up equations
Trying to extend the mixing lemma

@@
 \newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
-
+\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
 \newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
@@
 \newcommand{\error}{\ensuremath{{\mathcal{E}}}}
+\def\id{\mbox{\small 1} \!\! \mbox{1}}
 
@@
 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\columnwidth]{simple_example.pdf}
+  \caption{An example of a mixed unitary process.
+Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
+Each time the gate is used, one of these implementations is chosen at random.
+The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
+  \label{fig:simple_example}
+\end{figure}
 % ==============================================================================
@@
 If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate.
-That is to say that $\error_{ii}$ gives the probability that the following map is applied:
+That is, $\error_{ii}$ gives the probability that the following map is applied:
 \begin{equation}
-\vec\rho \rightarrow \tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho}
+\vec\rho_k\rightarrow\sum_j\tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho_k}
 \end{equation}
@@
 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
-		=& \tr{\sum_i p_i (\sigma_j^{\dagger} (\cos\theta_i + i \sin\theta_i H_i) \sigma_k		(\cos\theta_i - i \sin\theta_i H_i))} \\
-		=& \tr (\sum_i p_i (\sigma_j\sigma_k\cos\theta_i^2 + \sigma_jH_i\sigma_k H_i\sin\theta_i^2 \\ 
-		&+ iH_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j H_i\sin\theta_i\cos\theta_i))
+		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
+		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
 \end{align}
@@
 a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no balanced control solutions.
+The origin is not contained in their convex hull, so there are no 0MUPs.
 b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions.
+Because there are more than $n+1$ implementations, there exist an infinite number of 0MUPs.
 c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error.
+As this parameter drifts, a 0MUP may drift, leading to a first-order error.
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order mixed unitary process.}
+If the origin lies in their convex hull, then it may be possible to construct a 1MUP.}
   \label{fig:vectorspace}
@@
 
-The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(H_i\sigma_k - \sigma_jH_i)$ whose convex hull contains the origin.
+The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)$ whose convex hull contains the origin.
 This can be seen in Figure \ref{fig:vectorspace} a) and b).
@@
 \begin{align}
-\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) &= \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
-&= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} 
+\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) = \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
+= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} \\
+= \alpha\mathcal{F}(\error_1) + (1-\alpha)\mathcal{F}(\error_2)
 \end{align}
@@
 
-Campbell\cite{Campbell2017} considered this important problem of minimizing the diamond norm of the resulting error channel.
-Given a collection of component channels with error at most $\epsilon$, they show that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
+Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel.
+Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
 The diamond norm is a particularly appealing target because the it provides useful error metrics on quantum circuits.
@@
 \label{sec:mixed_unitary_processes}
-\subsection{Mixed Unitary Processes with Small Diamond Norm}
+\subsection{Diamond Norm Minimization}
 \label{sec:small_diamond_norm}
@@
 \end{center}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a mixed unitary process.
-Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
-Each time the gate is used, one of these implementations is chosen at random.
-The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
-  \label{fig:simple_example}
-\end{figure}
 
@@
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell MUP$ will be zero.
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero.
 Furthermore, if we are only interested in being first order insensitve to drift and can select controls such that $|D_j^n|\approx\epsilon$, we see that Equation \ref{eq:MUP} can be approximated as:
@@
 This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
-Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
-This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.
+A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
+Namely, Campbell shows that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP.
+This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.
 
@@
 \begin{equation}
-{D^{\ell}}^T =  \left(\begin{array}{cccc}
+{D^{\ell}} =  \left(\begin{array}{cccc}
 		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
@@
 Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
-As an example of where this would be necessary is Figure\ref{fig:vectorspace}.
+As an example of where this would be necessary is Figure \ref{fig:vectorspace}.
 In Subfigure b, it's clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
+In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
+However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+  \label{fig:YMUP}
+\end{figure}
+
 First, naively generating a 0MUP results in nontrivial support on all the members of the control family.
@@
 In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls.
-An example of such a control is given in Figure \ref{fig:bangbang}.
 To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{bangbang.png}
-  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
-  \label{fig:bangbang}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{bangbang.png}
+%  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
+%  \label{fig:bangbang}
+%\end{figure}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+Shown with lower alpha values are example constituent controls.
+The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
+For all detuning values the 1MUP performs as well or better than the 0MUP.
+When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
+  \label{fig:2MUP}
+\end{figure}
 % ==============================================================================
@@
 \label{sec:appendix}
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=\textwidth]{SQRTY_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
-In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
-  \label{fig:YMUP}
-\end{figure*}
+\subsection{Robust Mixing Lemma}
+We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
 
-\begin{figure*}[h]
-  \centering
-  \includegraphics[width=\textwidth]{2QRBC_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
-Shown with lower alpha values are example constituent controls.
-The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
-For all detuning values the 1MUP performs as well or better than the 0MUP.
-When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
-Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
-  \label{fig:2MUP}
-\end{figure*}
+\begin{align}
+&= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+&= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+&\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
+\end{align}
+
+We begin by generalizing Lemma 2 from \cite{Campbell2017}. From A3 in \cite{Campbell2017}, we know that $||e^{iM}| - (\id + iM)|| \leq \frac{1}{2}||M||^2$.
+
+Thus we can Taylor expand any mixture of unitaries, as:
+\begin{equation}
+\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!}))
+\end{equation}
+By assumption, the derivatives of the first order term sum to zero, and so we see by A3 that
+\begin{equation}
+||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j\frac{c^2}{2} \leq \frac{c^2}{2}
+\end{equation}
+
+Additionally, 
+\begin{align}
+||\deriv e^{iH_j}|| &= ||\deriv(iH_j)e^{iH_j}|| \\
+&\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)H_j|| +  ||\deriv(iH_j)\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n|| \\
+&\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)||\cdot||H_j|| +  ||\deriv(iH_j)||\cdot||\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n||\\
+&\leq c + c^2 + \frac{1}{2}c^3
+\end{align}
+And so we see that Lemma 2 generalizes.
+%Where we have used H\"older's inequality.
+
+Next we generalize the Mixing Lemma from \cite{Campbell2017}:\ldots
 

### 2019-01-07 decorrelation/mixed_unitaries.tex
finished what should be a draft of a proof of campbell's result to first order

@@
 \subsection{Robust Mixing Lemma}
-We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
-
-\begin{align}
-&= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-&= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-&\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
-\end{align}
-
 We begin by generalizing Lemma 2 from \cite{Campbell2017}. From A3 in \cite{Campbell2017}, we know that $||e^{iM}| - (\id + iM)|| \leq \frac{1}{2}||M||^2$.
@@
 \end{align}
-And so we see that Lemma 2 generalizes.
+And so we see that Lemma 2 generalizes. In all of the above $||\cdot||$ is the Schatten 0-norm, which we will use to upper bound the 1-norm (and hence diamond norm) in the following.
 %Where we have used H\"older's inequality.
 
-Next we generalize the Mixing Lemma from \cite{Campbell2017}:\ldots
+Next we generalize the Mixing Lemma from \cite{Campbell2017}. We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
 
+\begin{align}
+&= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+&= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+&\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
+\end{align}
+And so we see it is sufficient to upperbound:
+\begin{equation}
+|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1
+\end{equation}
+From Equation 18 in \cite{Campbell2017}:
+\begin{align}
+&(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
+&\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
+\end{align}
+Thus, by H\"older's inequality we find:
+\begin{align}
+&||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq||\sum_j \omega_j\deriv\tilde{\delta}_j|| + ||\sum_j\omega_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\omega_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\omega_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
+\end{align}
+By assumption, all of these terms are neglible, and therefore we find:
+\begin{align}
+||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq 2a^2 + 2b^2
+\end{align}
 \end{document}
+And so we see that the mixing lemma extends to first order.
+In a similar way, it can be extended to arbitary order, and thus if we can find constructions that satisfy the generalized Lemma 2, we can use the Robust Mixing Lemma to conclude that there exists a weighting with linearly supressed diamond norm.

### 2019-01-07 decorrelation/mixed_unitaries.tex
cleaning up a bit more

@@
 \subsection{Robust Mixing Lemma}
-We begin by generalizing Lemma 2 from \cite{Campbell2017}. From A3 in \cite{Campbell2017}, we know that $||e^{iM}| - (\id + iM)|| \leq \frac{1}{2}||M||^2$.
-
-Thus we can Taylor expand any mixture of unitaries, as:
+We begin by generalizing Lemma 2 from \cite{Campbell2017}. If all of our error Hamiltonians $\{H_j\}$ have bounded error, that is:
 \begin{equation}
-\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!}))
+||H_j||\leq c
 \end{equation}
-By assumption, the derivatives of the first order term sum to zero, and so we see by A3 that
+Then we may consider the derivative of any mixture of unitaries as:
+%\begin{equation}
+%\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji%\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
+%\end{equation}
 \begin{equation}
-||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j\frac{c^2}{2} \leq \frac{c^2}{2}
+\deriv\sum_j \omega_je^{iH_j} = \sum_j\omega_ji\deriv (H_j)e^{iH_j}
 \end{equation}
-
+By assumption, the derivatives of the first order term sum to zero, and so we see by A3 in \cite{Campbell2017} that
+\begin{equation}
+||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\omega_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
+\end{equation}
+Where we have used the fact that $||AB|| \leq ||A||||B||$ with $||\cdot||$ being the $\infty$-norm.
 Additionally, 
@@
 &\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)||\cdot||H_j|| +  ||\deriv(iH_j)||\cdot||\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n||\\
-&\leq c + c^2 + \frac{1}{2}c^3
+&\leq c + c^2 + \frac{c^3}{2}
 \end{align}
-And so we see that Lemma 2 generalizes. In all of the above $||\cdot||$ is the Schatten 0-norm, which we will use to upper bound the 1-norm (and hence diamond norm) in the following.
-%Where we have used H\"older's inequality.
+And so we see that Lemma 2 generalizes. We will use the above to upper bound the 1-norm (and hence diamond norm) in the following.
 
@@
 \end{align}
-\end{document}
 And so we see that the mixing lemma extends to first order.
 In a similar way, it can be extended to arbitary order, and thus if we can find constructions that satisfy the generalized Lemma 2, we can use the Robust Mixing Lemma to conclude that there exists a weighting with linearly supressed diamond norm.
+\end{document}

### 2019-01-10 decorrelation/mixed_unitaries.tex
updates

@@
 Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
-Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip.
+Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
 These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.
@@
 While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
-The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of gate with coherent errors.
+The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
 For long circuits, this can add up extremely quickly.
@@
 
-%Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
-
-In this article we discuss various applications of these mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the target gates.
-We demonstrate that, depending on the objective, different numerical optimzations may be prefered.
-We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
-Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
-We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
-
-% For instance, the repeated measurements that occur in quantum error correction are suspected to reduce the potential impact of coherent buildup of error.
-Modern devices, however, do not have sufficient numbers of qubits and their errors are above the threshold at which QEC becomes a viable option.
-
-\begin{figure}[h]
+\begin{figure}[t]
   \centering
@@
 \end{figure}
+
+%Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
+
+In this article we discuss various applications of these mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the gate implementations.
+We demonstrate that, depending on the objective, different numerical optimizations may be preferred.
+We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
+Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
+We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+
 % ==============================================================================
@@
 If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate.
-That is, $\error_{ii}$ gives the probability that the following map is applied:
+Any such Pauli error is expressible as a unitary matrix $U$ that acts on the density matrix by conjugation, and has an action on the vectorized density matrix given by:
 \begin{equation}
-\vec\rho_k\rightarrow\sum_j\tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho_k}
-\end{equation}
+\vec{\rho}\rightarrow \rho_i\vec{\Sigma}_{ijk}U^{\dagger}_{kl}\vec{\Sigma}_{lmn}U_{mj}\end{equation}
  If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
@@
 
-For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general has elements:
+In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
 \begin{align}
@@
 \end{align}
-The first term corresponds to the identity, and $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
 The result would be a purely stochastic channel.
@@
 
-The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)$ whose convex hull contains the origin.
-This can be seen in Figure \ref{fig:vectorspace} a) and b).
+The problem of minimizing the last term:
+\begin{equation}
+\sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
+\end{equation}
+ can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).
 
@@
 These may be represented in terms of the error maps as
-\begin{equation}
-	\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1
-\end{equation}
-\begin{equation}\label{eq: fid}
-	\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d}
-\end{equation}
+\begin{align}
+	&\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1\\
+	&\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d} 
+\end{align}
+
 Which metric is relevant depends on the application, and can yield very different numbers.
 For instance, the diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
-Similarly, these two metric perform very differently on stochastic quantum processes, that can be achieved by probabilistically mixing unitary operators.
+These two metrics also vary significantly in performance on mixed processes.
 
@@
 The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-From this definition, we can compute the AGI of a MUP, by first computing the AGI of an convex combination of channels:
-\begin{align}
-\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) = \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
-= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} \\
-= \alpha\mathcal{F}(\error_1) + (1-\alpha)\mathcal{F}(\error_2)
-\end{align}
-where we have used the linearity of the trace.
-%\begin{align}
-%\mathcal{F}(\error_{\rm M}) &= \mathcal{F}(\sum_j \omega_j \error_j)\\
-%&= \frac{\tr (\sum_j \omega_j \error_j) + d}{d^2 + d}\\
-%&= \frac{\sum_j(\tr (\omega_j \error_j)) + d}{d^2 + d}\\
-%&= \frac{\sum_j(\tr (\omega_j (\error_j + d))}{d^2 + d}\\
-%&= \sum_j\frac{(\tr (\omega_j (\error_j + d))}{d^2 + d}\\ 
-%\end{align}
-
-We therefore see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear, and can in general be smaller for a MUP than any of the processes being mixed.
+From this definition, we can use linearity to compute the AGI of a MUP.
+We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.
 
@@
 Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
-The diamond norm is a particularly appealing target because the it provides useful error metrics on quantum circuits.
+The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits.
 However, it is not the only optimization target that can be chosen.
@@
 Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
-Indeed, this is the approach we consider in Section \ref{sec:experimental_results}.
-More generally, the are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.
+Indeed, this is the approach we consider in our experimental implementation in Section \ref{sec:experimental_results}.
+More generally, as we will discuss, there are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.
 
@@
 \label{sec:mixed_unitary_processes}
-\subsection{Diamond Norm Minimization}
-\label{sec:small_diamond_norm}
-There are often many possibly ways of implementing any given target quantum gate.
+\subsection{A Simple Example}
+\label{simple_example}
+There are often many possible ways of implementing any given target quantum gate.
 Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.
@@
 
-In this case, the MUP that minimizes the diamond norm is given by:
-\begin{equation}
-\frac{1}{2}U_{+\epsilon}^*\otimes U_{+\epsilon} + \frac{1}{2}U_{-\epsilon}^*\otimes U_{-\epsilon}
+In this case, the MUP that minimizes the diamond norm has matrix elements given by:
+\begin{equation}\label{eq:balanced}
+\frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
 \end{equation}
-More generally, the problem remains: given a collection of channels, how can one efficiently compute a weighting that minimizes a particular metric?
+This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a nonzero linear dependence on $\epsilon$.
+On the otherhand, any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
+Additionally, it is clear that it is favorable in both cases to draw from the channels with smaller error, rather than those with larger error, to minimize the multiplicative coefficient on the air.
+In \cite{Campbell2017} all channels are assumed to have performance less than some threshold, however in realistic scenarios some controls will have better performance than others, and it is important to select from those controls when able to.
 
+Another interesting property of the MUP given in \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+If the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
+Thus the multiplicative prefactor on the diamond norm will vary in time, but the supression of the first order insensitivity to the static detuning $\epsilon$ will be supressed, as we will discuss later.
+Given these consideration from this simple example, the problem remains: given a collection of controls, how can one efficiently compute a weighting that minimizes a particular metric?
+\subsection{Diamond Norm Minimization}
+\label{sec:small_diamond_norm}
 As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
@@
 \begin{equation}\label{eq:vectorized_hamiltonians}
-	H = \left(\begin{array}{cccc}
+	\bold{H} = \left(\begin{array}{cccc}
 		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
@@
 If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
-That is, we can instead consider solving the following convex optimization problem:
+Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one.
+Such a problem forms what is known as a convex optimization problem, and can be written with the following shorthand:
 
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||H^T\omega||_2\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{H}^T\omega||_2\\
   \end{split}
 \end{equation}
-where the minimization is over all valid probability distributions.
+
+where we write the contraints on the variable to be optimized over below the objective, and we write the cost function on the right.
+Linearly constrained minimizations with quadratic cost functions like this have been shown to be efficiently solvable by methods like the Elipsoid Method, however these have very poor average case performance.
+Indeed, there are many existing convex solver software packages that solve these problems efficiently in practice, and formal proofs showing convergence in $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$ time, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
 \subsection{Robustly Mixed Unitary Processes}
@@
 \end{equation}
-Then we say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
+If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
+We say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
 \begin{equation}\label{eq:MUP}
 \begin{gathered}
-\sum_j\omega_j(\sum_{n=0}^k D^n_j)^k = 0\\
+\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
 \end{gathered}
@@
 We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP.
-This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.
+Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.
 
@@
 \begin{equation}
-{D^{\ell}} =  \left(\begin{array}{cccc}
+{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
 		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{D^{\ell}}^T\omega||\\
-    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}^T\omega||\\
+    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=\vec{0}\\
   \end{split}
 \end{equation}
-with $D_k^n$ defined in Equation \ref{eq:MUP}.
+with $D_n^j$ defined in Equation \ref{eq:taylor}.
+Note that these algorithms are independent of the number of rows, which in our case is the number of drifting parameters.
+However, the size of the matrix that must be computed grow as $Nd^{\ell}$, and the runtime grows as $N^4$, again with $d$ being the number of drifting parameters, and $N$ being the number of controls.
 
@@
 That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:small_diamond_norm} satisfy Equation \ref{eq:minimization}.
-To encourage the inclusion of controls with smaller error, we may impose an $\ell_2$ penalty to our cost function by rewriting it as:
+To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
+In our case, we chose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
 
@@
 &\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{D^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
 &\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
@@
 \end{equation}
-with $\eta \geq 0$. By making $\eta$ larger, we can require that the solver decreases the diamond norm of the constituent channel, while using only the best controls.
+with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
 
@@
 &\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{D^{\ell}}^T\omega|| + t\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
 &\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\

### 2019-01-10 decorrelation/mixed_unitaries.tex
more changes

@@
 \subsection{A Simple Example}
-\label{simple_example}
+\label{sec:simple_example}
+Before discussing how to produce MUPs with desirable qualities, we will give a simple example demonstrating the merits of different approaches to producing MUPs.
 There are often many possible ways of implementing any given target quantum gate.
@@
 \begin{equation}\label{eq:balanced}
-\frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
+\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
 \end{equation}
-This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a nonzero linear dependence on $\epsilon$.
+This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will a linear dependence on $\epsilon$.
 On the otherhand, any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
-Additionally, it is clear that it is favorable in both cases to draw from the channels with smaller error, rather than those with larger error, to minimize the multiplicative coefficient on the air.
-In \cite{Campbell2017} all channels are assumed to have performance less than some threshold, however in realistic scenarios some controls will have better performance than others, and it is important to select from those controls when able to.
 
-Another interesting property of the MUP given in \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
-If the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
-Thus the multiplicative prefactor on the diamond norm will vary in time, but the supression of the first order insensitivity to the static detuning $\epsilon$ will be supressed, as we will discuss later.
-Given these consideration from this simple example, the problem remains: given a collection of controls, how can one efficiently compute a weighting that minimizes a particular metric?
+In both cases it is clear that we should select the gates with smaller error, i.e.
+$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
+Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
+\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
+We will discuss numerical approaches to solving this Section \ref{sec:norm}.
+
+Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
+Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
+In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.
 \subsection{Diamond Norm Minimization}
@@
 In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property.
-Alternatively, one can use convex optimization to solve this problem.
+Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations.
+In these situations, one can equivantly use convex optimization to solve this problem.
 Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e.
@@
 where we write the contraints on the variable to be optimized over below the objective, and we write the cost function on the right.
-Linearly constrained minimizations with quadratic cost functions like this have been shown to be efficiently solvable by methods like the Elipsoid Method, however these have very poor average case performance.
-Indeed, there are many existing convex solver software packages that solve these problems efficiently in practice, and formal proofs showing convergence in $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$ time, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
+Linearly constrained minimization problems with quadratic cost functions like this have been proveb to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance.
+However, there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
 \subsection{Robustly Mixed Unitary Processes}
@@
 Thus, we would like to design MUPs that are \textit{robust} to this drift.
-To enforce robustness, we can consider higher derivatives of the Hamiltonians in \ref{eq:campbell-condition}.
-Instead of just requiring that the $0^{th}$ derivative averages to zero, we should impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
+To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}.
+Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
 \begin{equation}
@@
 If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
+We say that a mixed unitary process is robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
 \begin{equation}\label{eq:MUP}
@@
 By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can select controls such that $|D_j^n|\approx\epsilon$, we see that Equation \ref{eq:MUP} can be approximated as:
+Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MUP} as:
 \begin{equation}\label{eq:MUP-relaxed}
 \begin{gathered}
-\sum_k\omega_jD^n_j = 0\\
+\sum\omega_jD^n_j = 0\\
 \end{gathered}
@@
 A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
-Namely, Campbell shows that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
 We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP.
@@
 
-To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to \ref{eq:vectorized_hamiltonians}:
+To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
 \begin{equation}
@@
 with $D_n^j$ defined in Equation \ref{eq:taylor}.
-Note that these algorithms are independent of the number of rows, which in our case is the number of drifting parameters.
-However, the size of the matrix that must be computed grow as $Nd^{\ell}$, and the runtime grows as $N^4$, again with $d$ being the number of drifting parameters, and $N$ being the number of controls.
+The time to solve these convex optimization problems is independent of the number of rows, which in our case is the number of drifting parameters.
+However, the size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the runtime of solving the optimization problem grows as $N^4$, with $d$ being the number of drifting parameters, and $N$ being the number of controls.
 
 \subsection{Hamiltonian Norm Regularization}
-While these particular convex optimization problem can be solved through a system of linear equations, casting it as a convex optimization problem allows us to regularize the cost function, and introduce additional constraints.
+\label{sec:norm}
+While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
 In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:small_diamond_norm} satisfy Equation \ref{eq:minimization}.
+That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
 To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
-In our case, we chose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
+In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
 
@@
 \end{equation}
-with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
+with $\eta \geq 0$.
+By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
+The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
 
-%\begin{equation}\label{eq:minimization_l2}
-%  \begin{split}
-%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
-%  \end{split}
-%\end{equation}
 \subsection{Sparsity Constraints}
@@
 Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
-As an example of where this would be necessary is Figure \ref{fig:vectorspace}.
-In Subfigure b, it's clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set.
-Thus we would like the solver to be frugal in which controls it selects.
-In many machine learning situation, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity, however here it is insufficient as we already constrain the one norm of the vector we optimize over to be one.
+As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}.
+In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
+Thus we would prefer that our solution, if we are forming a $0$MUP, ignores $H_4$.
+However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
+Thus we would like to be frugal in which controls we select.
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one.
 Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
@@
 \end{split}
-\end{equation} where $\lambda$ is a hyperparameter to be optimized over.
+\end{equation} with $\lambda\geq0$.
+As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be.
+For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
 
@@
 \end{equation}
-We use the GRAPE algorithm as discussed in Section \ref{sec:random_gate_synthesis} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls, with a standard deviation of $\sigma=.001$ for the distribution in Equation \ref{eq:quadrature}.
+We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
+In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$.
 We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.

### 2019-01-11 decorrelation/mixed_unitaries.tex
moving sections around

@@
 However, it is not the only optimization target that can be chosen.
-If the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic.
-Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
-Indeed, this is the approach we consider in our experimental implementation in Section \ref{sec:experimental_results}.
-More generally, as we will discuss, there are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.
 
@@
 \label{sec:mixed_unitary_processes}
-\subsection{A Simple Example}
+\subsection{Simple Example}
 \label{sec:simple_example}
-Before discussing how to produce MUPs with desirable qualities, we will give a simple example demonstrating the merits of different approaches to producing MUPs.
 There are often many possible ways of implementing any given target quantum gate.
-Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.
-As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
+Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
 The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$.
@@
 \begin{center}
-
 \begin{tabular}{cccc}
@@
 \end{tabular}
-
 \end{center}
 
-In this case, the MUP that minimizes the diamond norm has matrix elements given by:
+In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
+Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
+More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
+We implemented such a routine on a superconducting qubit.
+% ==============================================================================
+% Section: Experimental Results
+% ==============================================================================
+
+\subsection{Experimental Implementation}
+\label{sec:experimental_results}
+Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit.
+In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
+To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+
+As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
+To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
+In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
+The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
+Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{rb_data.pdf}
+  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
+  \label{fig:rb}
+\end{figure}
+
+Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error.
+To see that this is the case, we cite the results in \cite{Ball2016}.
+For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
+On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
+We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
+Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
+
+\subsection{Diamond Norm Minimization}
+\label{sec:small_diamond_norm}
+If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm.
+As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
 \begin{equation}\label{eq:balanced}
@@
 \end{equation}
-This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will a linear dependence on $\epsilon$.
-On the otherhand, any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
-
-In both cases it is clear that we should select the gates with smaller error, i.e.
-$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
-Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
-\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
-We will discuss numerical approaches to solving this Section \ref{sec:norm}.
-
-Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
-In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
-Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
-In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.
-\subsection{Diamond Norm Minimization}
-\label{sec:small_diamond_norm}
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
+This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$.
+Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
+While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application.
+However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one.
-Such a problem forms what is known as a convex optimization problem, and can be written with the following shorthand:
+This forms a convex optimization problem, and can be written as:
 
@@
 
-where we write the contraints on the variable to be optimized over below the objective, and we write the cost function on the right.
-Linearly constrained minimization problems with quadratic cost functions like this have been proveb to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance.
+Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance.
 However, there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
+
+%In both cases it is clear that we should select the gates with smaller error, i.e.
+$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
+Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
+\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
+We will discuss numerical approaches to solving this Section \ref{sec:norm}.
+
+%Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
+Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
+In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.
+
 \subsection{Robustly Mixed Unitary Processes}
@@
 
+% ==============================================================================
+% Section: Numerical Results
+% ==============================================================================
+\subsection{Numerical Implementation}
+\label{sec:numerical_results}
+\label{one_qubit_performance}
+In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
+\begin{equation}\label{eq:1Qham}
+  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
+\end{equation}
+We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
+In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
+Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}.
+These results demonstrate several properties that make MUPs both useful and tractable.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
+In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
+However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+  \label{fig:YMUP}
+\end{figure}
+
+In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
+\begin{equation} \label{eq:2Qham}
+\begin{split}
+H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
+&+ \frac{1}{10}(XX + YY)
+\end{split}
+\end{equation}
+
+In this example it was infeasible to use GRAPE to return non-trivial solutions.
+Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
+In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls.
+To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
+
+In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
+There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
+Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+For all values of the drifting parameters we see that the 1MUP performs as well or better than 0MUP.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
+  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+Shown with lower alpha values are example constituent controls.
+The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
+For all detuning values the 1MUP performs as well or better than the 0MUP.
+When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
+  \label{fig:2MUP}
+\end{figure}
+
 \subsection{Hamiltonian Norm Regularization}
@@
 The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
+Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family.
+However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls.
+This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
 
@@
 For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-
-% ==============================================================================
-% Section: Numerical Results
-% ==============================================================================
-\section{Numerical Results}
-\label{sec:numerical_results}
-\label{one_qubit_performance}
-In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
-\begin{equation}\label{eq:1Qham}
-  H(\delta, \epsilon, t) = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
-\end{equation}
-We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
-In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
-Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}.
-These results demonstrate several properties that make MUPs both useful and tractable.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
-In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
-  \label{fig:YMUP}
-\end{figure}
-
-First, naively generating a 0MUP results in nontrivial support on all the members of the control family.
-However, by rewriting the minimization to impose the sparsity constraint discussed in Section \ref{sec:robustly_mixed}, we can generate a 0MUP that uses just five of the controls.
-This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
-In both cases we impose the same $\ell_2$ penalty as described in Section \ref{sec:robustly_mixed}, so that the algorithm preferentially selects controls with smaller errors.
+In both the 0MUP and the 1MUP case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constrain made the 0MUP perform better at the origin by nearly an order of magnitude, and moved the 1MUP from being out-performed by the 0MUP for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
 Imposing this constraint allows us to trade off flatness at the origin for performance.
-\subsection{Two Qubit Performance Analysis}
-\label{two_qubit_performance}
-In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
-\begin{equation} \label{eq:2Qham}
-\begin{split}
-H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
-&+ \frac{1}{10}(XX + YY)
-\end{split}
-\end{equation}
-
-In this example it was infeasible to use GRAPE to return non-trivial solutions.
-Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
-In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls.
-To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
-
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=\columnwidth]{bangbang.png}
-%  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
-%  \label{fig:bangbang}
-%\end{figure}
-
-In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
-There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
-For all values of the drifting parameters we see that the 1MUP performs as well or better than 0MUP.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
-Shown with lower alpha values are example constituent controls.
-The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
-For all detuning values the 1MUP performs as well or better than the 0MUP.
-When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
-Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
-  \label{fig:2MUP}
-\end{figure}
-% ==============================================================================
-% Section: Experimental Results
-% ==============================================================================
-
-\section{Experimental Results}
-\label{sec:experimental_results}
-Here we present experimental results from implementing our routine on a fixed-frequency superconducting transmon qubit.
-In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{Randomized benchmarking experiments ran using different pulse definitions.
-The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
-  \label{fig:rb}
-\end{figure}
-
-As discussed in Section \ref{sec:robustly_mixed}, we chose here to minimize the off diagonal elements of the process matrix.
-To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
-We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
-In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
-The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
-
-Additionally, by minimizing the off-diagonal elements of the process matrix, rather than balancing the Hamiltonian errors, we expect to produce a process with minimal coherent error in the absence of drift.
-To see that this is the case, we cite the results in \cite{Ball2016}.
-For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
-On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
 
@@
 By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
-
 % ==============================================================================
@@
 % ==============================================================================
+
 \section{Acknowledgements}

### 2019-02-22 decorrelation/mixed_unitaries.tex
Rigedits

@@
 Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices.
-While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone \cite{1203.5813} has yet to be definitively reached.
+While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached.
 The limiting factor, of course, is errors in the quantum gate operations.
@@
 Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
-Errors of this type are correlated in time and add up coherently.
-They are are  computationally expensive to model and it is difficult to place tight analytic bounds on circuit performance.
+Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
+They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance.
 Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
 Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
-These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.
+These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate [Ken Brown, Steve Flammia].
 
-Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict.
+Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance [].
+\note{Discuss subadditivity of diamond norm here...
+The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
+While these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
 The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
 For long circuits, this can add up extremely quickly.
+}. 
+Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
 Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
-The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
 
@@
 \begin{equation}
-  \vec \rho = \tr(\rho \vec \Sigma),
+  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
 \end{equation}
-where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
+where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators.
+For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.
+The action of a gate is then given by the usual matrix multiplication:
 \begin{equation}\label{error_def}
@@
 
-In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
+\note{this should go somewhere:}
+There are often many possible ways of implementing any given target quantum gate.
+Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011}
+
+In addition to the type of errors, we care about the size of an error.
+The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
+Two of the most common metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
+These may be represented in terms of the error maps as
 \begin{align}
-	\mathcal{M}_{jk} 
-		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
-		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
-		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
-		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
+	&\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1\\
+	&\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d} 
 \end{align}
-The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+
+Which metric is relevant depends on the application, and can yield very different numbers.
+For instance, the diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
+These two metrics also vary significantly in performance on mixed processes.
+
+\note{fix this} A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
+The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
+From this definition, we can use linearity to compute the AGI of a MUP.
+We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.
+
+Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel.
+Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
+The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits.
+However, it is not the only optimization target that can be chosen.
+
+\subsection{A simple example}
+\label{sec:simple_example}
+As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
+The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$.
+Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.
+
+In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
+Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
+More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
+We implemented such a routine on a superconducting qubit.
+
+The error operator corresponding to a rotation error by angle $\epsilon$ is then:
+\begin{equation}
+\error(\epsilon) =
+	\left(\begin{array}{ccccc}
+		1 & 0 & 0 & 0 \\ 
+		0 & \cos\epsilon & \sin\epsilon  & 0  \\
+		0 & -\sin\epsilon & \cos\epsilon & 0  \\
+		0 & 0 & 0 & 1
+	\end{array} 	
+	\right)
+\end{equation}
+\note{Don't be dumb with right hand rules}
+The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$.
+If we were construct two channels, one with error $\error(\epsilon)$ and one with error $\error(-\epsilon)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\epsilon) + \error(\epsilon)\right)$.
+The effective channel then has a matrix representation:
+\begin{equation}
+	\error(\epsilon) =
+	\left(\begin{array}{ccccc}
+		1 & 0 & 0 & 0 \\ 
+		0 & \cos\epsilon & 0  & 0  \\
+		0 & 0 & \cos\epsilon & 0  \\
+		0 & 0 & 0 & 1
+	\end{array} 	
+	\right) \simeq \mathcal{I} - 
+	\left(\begin{array}{ccccc}
+		0 & 0 & 0 & 0 \\ 
+		0 & \epsilon^2/2 & 0  & 0  \\
+		0 & 0 & \epsilon^2/2 & 0  \\
+		0 & 0 & 0 & 0
+	\end{array} 	
+	\right)
+\end{equation}
+And with same average process fidelity, $\epsilon^2$, but now a suppressed diamond norm $\epsilon^2$. Now write this in terms of the error generators $\error(\epsilon) = \exp(\epsilon G)$ where
+\begin{equation}
+	G =
+	\left(\begin{array}{ccccc}
+		0 & 0 & 0 & 0 \\ 
+		0 & 0 & 1  & 0  \\
+		0 & -1 & 0 & 0  \\
+		0 & 0 & 0 & 0
+	\end{array} 	
+	\right)
+\end{equation}
+The effective generator vanishes at first order.
+
+\begin{equation}
+	\error(\epsilon) = \mathcal{I} + \epsilon G + \frac{1}{2}\epsilon^2 G^2 + \mathcal{O}(\epsilon^3)
+\end{equation}
+\begin{align}
+	\error_{\text{eff}} 
+		% &= \sum_i \omega_i \error_i \\
+		% &= \sum_i \omega_i \left(\mathcal{I} + \epsilon_i G_i + \frac{1}{2}\epsilon_i^2 G_i^2 + \cdots \right) \\
+		&= \mathcal{I} + \sum_i \omega_i \epsilon_i G_i+ \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + + \mathcal{O}(\epsilon^3)
+\end{align}
+\begin{equation}
+	\error_{\text{eff}} = \mathcal{I} + \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + \mathcal{O}(\epsilon^3)
+\end{equation}
+
+\begin{center}
+\begin{tabular}{cccc}
+	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
+\hline
+	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
+	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
+	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
+	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
+\end{tabular}
+\end{center}
+
+Alternatively, \note{Draw box around the (2,4),(2,3),(3,4) elements of the G matrix}.
+We can then eliminate off diagonal entries, resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable.
+\note{more here about alternative method.
+Also discuss Fig 2.}.
+
+\note{END}
+
+% In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
+% \begin{align}
+% 	\mathcal{M}_{jk} 
+% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
+% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
+% 		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
+% 		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
+% \end{align}
+% The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
 The result would be a purely stochastic channel.
@@
 
-The problem of minimizing the last term:
-\begin{equation}
-\sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
-\end{equation}
- can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).
-
-In addition to the type of errors, we care about the size of an error.
-The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
-Two of the most common metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
-These may be represented in terms of the error maps as
-\begin{align}
-	&\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1\\
-	&\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d} 
-\end{align}
-
-Which metric is relevant depends on the application, and can yield very different numbers.
-For instance, the diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
-These two metrics also vary significantly in performance on mixed processes.
-
-A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
-The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-From this definition, we can use linearity to compute the AGI of a MUP.
-We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.
-
-Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel.
-Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
-The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits.
-However, it is not the only optimization target that can be chosen.
+% The problem of minimizing the last term:
+% \begin{equation}
+% \sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
+% \end{equation}
+%  can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).
 
@@
 \label{sec:mixed_unitary_processes}
-\subsection{Simple Example}
-\label{sec:simple_example}
-There are often many possible ways of implementing any given target quantum gate.
-Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
-The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$.
-Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.
+\note{write an introduction to this section here} 
+In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors.
+These vectors might represent the off-diagonal elements of the error maps, or they could be the error generator.
+As we'll see in section ...
+we could also include the derivatives with respect to various parameters.
+With appropriate weighting, we could minimize any number of effects.
+Which optimization we choose will depend on the approach.
+\note{Then go into examples below.
+}
 
-\begin{center}
-\begin{tabular}{cccc}
-	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
-\hline
-	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
-	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
-	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
-	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
-\end{tabular}
-\end{center}
-
-In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
-Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
-More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
-We implemented such a routine on a superconducting qubit.
 % ==============================================================================
-% Section: Experimental Results
+% Section: Generators
 % ==============================================================================
 
-\subsection{Experimental Implementation}
-\label{sec:experimental_results}
-Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit.
-In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
-
-As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
-To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
-We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
-In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
-In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
-The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{Randomized benchmarking experiments ran using different pulse definitions.
-The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the MUP.}
-  \label{fig:rb}
-\end{figure}
-
-Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error.
-To see that this is the case, we cite the results in \cite{Ball2016}.
-For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
-On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
-
-\subsection{Diamond Norm Minimization}
-\label{sec:small_diamond_norm}
+\subsection{First-order generators} % (fold)
+\label{sub:first_order_generators}
+\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
 If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm.
@@
 
-\subsection{Robustly Mixed Unitary Processes}
-\label{sec:robustly_mixed}
+% subsection first_order_generators (end)
 
+% ==============================================================================
+% Section: Off-diagonals
+% ==============================================================================
+
+\subsection{Off-diagonals} % (fold)
+\label{sub:off_diagonals}
+
+% subsection off_diagonals (end)
+
+% ==============================================================================
+% Section: Robustness
+% ==============================================================================
+
+\subsection{Adding robustness} % (fold)
+\label{sub:adding_robustness}
+\note{this section is a little bit heavy on the notation - is there anything we can do to ease that?
+Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
 While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
@@
 
+% subsection adding_robustness (end)
+
+% ==============================================================================
+% Section: Norm regularization
+% ==============================================================================
+
+\subsection{Hamiltonian Norm Regularization}
+\label{sec:norm}
+While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
+In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
+To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
+In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
+
+\newcommand{\bunderbrace}[2]{%
+  \begin{array}[t]{@{}c@{}}
+  #1\\
+  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
+  \end{array}
+}
+
+\begin{equation}\label{eq:minimization_l2}
+\begin{split}
+&\underset{n\in[N]}{\textbf{minimize}}\{\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
+&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
+&\}
+\end{split}
+\end{equation}
+with $\eta \geq 0$.
+By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
+The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
+Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family.
+However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls.
+This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
+
+% ==============================================================================
+% Section: Sparsity
+% ==============================================================================
+
+\subsection{Sparsity Constraints}
+As a practical consideration, we would also like to regularize our objective function to enforce sparsity.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
+As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}.
+In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
+Thus we would prefer that our solution, if we are forming a $0$MUP, ignores $H_4$.
+However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
+Thus we would like to be frugal in which controls we select.
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one.
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+
+\begin{equation}\label{eq:minimization_regularization}
+\begin{split}
+&\underset{n\in[N]}{\textbf{minimize}}\{\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
+&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
+&\}
+\end{split}
+\end{equation} with $\lambda\geq0$.
+As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be.
+For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
+In both the 0MUP and the 1MUP case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constrain made the 0MUP perform better at the origin by nearly an order of magnitude, and moved the 1MUP from being out-performed by the 0MUP for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
+Imposing this constraint allows us to trade off flatness at the origin for performance.
+
+\section{Results} % (fold)
+\label{sec:results}
+
+% ==============================================================================
+% Section: Experimental Results
+% ==============================================================================
+
+\subsection{Experimental} % (fold)
+\label{sub:experimental}
+Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit.
+In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
+To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+
+As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
+To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
+In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
+The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
+Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{rb_data.pdf}
+  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+The first four boxes result from using each of four different implementations of the ${\pi/2}$ rotations.
+The coherent noise present in these implementations leads to large variance of the survival probability over sequences.
+The fifth (dark blue) box illustrates the survival probability using a highly-tuned gate implementation.
+It displays improved average survival probability as well as reduced variance.
+The final box (dark red) illustrates the distribution over survival probabilities for a randomized MUP composed of Pulse1 through Pulse4.
+It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
+The reduced variance of the MUP is a tell-tale sign of reduced coherent error in the effective channel.
+}
+  \label{fig:rb}
+\end{figure}
+
+Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error.
+To see that this is the case, we cite the results in \cite{Ball2016}.
+For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
+On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
+We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
+Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
+% subsection experimental (end)
+
 % ==============================================================================
@@
 \subsection{Numerical Implementation}
-\label{sec:numerical_results}
-\label{one_qubit_performance}
 In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
@@
 \end{figure}
-
-\subsection{Hamiltonian Norm Regularization}
-\label{sec:norm}
-While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
-In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
-To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
-In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
-
-\newcommand{\bunderbrace}[2]{%
-  \begin{array}[t]{@{}c@{}}
-  #1\\
-  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
-  \end{array}
-}
-
-\begin{equation}\label{eq:minimization_l2}
-\begin{split}
-&\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
-&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
-&\}
-\end{split}
-\end{equation}
-with $\eta \geq 0$.
-By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
-The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
-Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family.
-However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls.
-This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
-
-\subsection{Sparsity Constraints}
-As a practical consideration, we would also like to regularize our objective function to enforce sparsity.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
-As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}.
-In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that our solution, if we are forming a $0$MUP, ignores $H_4$.
-However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
-Thus we would like to be frugal in which controls we select.
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
-
-\begin{equation}\label{eq:minimization_regularization}
-\begin{split}
-&\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
-&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
-&\}
-\end{split}
-\end{equation} with $\lambda\geq0$.
-As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be.
-For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-In both the 0MUP and the 1MUP case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constrain made the 0MUP perform better at the origin by nearly an order of magnitude, and moved the 1MUP from being out-performed by the 0MUP for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
-Imposing this constraint allows us to trade off flatness at the origin for performance.
 

### 2019-02-26 decorrelation/mixed_unitaries.tex
filling in some of the sections that needed filling in

@@
 \begin{document}
-\title{Advantages of mixed unitary operators for quantum information processing}
+\title{Advantages of mixed quantum channels for information processing}
 
@@
 The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
-Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices.
+Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices.
 While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached.
@@
 
-Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance [].
-\note{Discuss subadditivity of diamond norm here...
-The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
-While these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
+Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance, $||\cdot||_\diamond$.
+This particular metric, defined in Section \ref{sec:representing_quantum_gates}, has the appealing property of being subadditive, namely for a channels $\mathcal{F}_1$, $\mathcal{F}_2$ we have:
+\begin{equation}
+||\mathcal{F}_1\circ\mathcal{F}_2||_\diamond \leq ||\mathcal{F}_1||_\diamond + ||\mathcal{F}_2||_\diamond
+\end{equation}
 The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
-For long circuits, this can add up extremely quickly.
-}. 
-Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
+For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
+Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
 Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
+In this case, the resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
 
@@
   \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a mixed unitary process.
+  \caption{An example of a mixed quantum channel.
 Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
@@
 % ==============================================================================
-\section{Mathematical preliminaries}
+\section{Mixed quantum channels}
 \label{sec:representing_quantum_gates}
@@
 
-\note{this should go somewhere:}
-There are often many possible ways of implementing any given target quantum gate.
-Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011}
-
 In addition to the type of errors, we care about the size of an error.
@@
 
-\note{fix this} A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
+A \textit{mixed quantum channel} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
 The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-From this definition, we can use linearity to compute the AGI of a MUP.
-We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.
+From this definition, we can use linearity to compute the AGI of a MQC.
+We see that the AGI of any MQC will be the convex sum of the consituent fidelities, with the same weighting.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.
 
-Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel.
+When performing a quantum gate, there are often many possible ways of it might be implemented.
+Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel.
 Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
@@
 \end{equation}
-\note{Don't be dumb with right hand rules}
+
 The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$.
@@
 		0 & 0 & 0 & 0 \\ 
-		0 & 0 & 1  & 0  \\
-		0 & -1 & 0 & 0  \\
+		0 & 0 & -1  & 0  \\
+		0 & 1 & 0 & 0  \\
 		0 & 0 & 0 & 0
@@
 \end{equation}
+
 The effective generator vanishes at first order.
@@
 
-Alternatively, \note{Draw box around the (2,4),(2,3),(3,4) elements of the G matrix}.
-We can then eliminate off diagonal entries, resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable.
-\note{more here about alternative method.
-Also discuss Fig 2.}.
+Alternatively, we might consider eliminating off-diagonal entries of G:
+\begin{equation}
+	\left(\begin{array}{@{}ccccc@{}}
+		0 & 0 & 0 & 0 \\ 
+  		\cline{3-4}
+    	0 & 0 & \multicolumn{1}{|c}{-1} & \multicolumn{1}{c|}{0} \\
+    	\cline{3-3}		
+		0 & 1 & 0 & \multicolumn{1}{|c|}{0}\\
+		\cline{4-4}	
+		0 & 0 & 0 & 0
+	\end{array} 	
+	\right)
+\end{equation}
+ resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable problem.
+In the case of a single qubit, it is clear that our generator is expressible as $\hat{n}\cdot\vec{\Sigma}$, where $\vec{\Sigma}$ is again the vector of Pauli operators.
+The condition that the off-diagonal terms vanish is then again the same condition that the origin lies in the convex hull of the vectors $\vec{n}_i$ for each $G_i$.
+ \note{more here about alternative method. Also discuss Fig 2.}.
 
@@
 a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no 0MUPs.
+The origin is not contained in their convex hull, so there are no 0MQCs.
 b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of 0MUPs.
+Because there are more than $n+1$ implementations, there exist an infinite number of 0MQCs.
 c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a 0MUP may drift, leading to a first-order error.
+As this parameter drifts, a 0MQC may drift, leading to a first-order error.
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a 1MUP.}
+If the origin lies in their convex hull, then it may be possible to construct a 1MQC.}
   \label{fig:vectorspace}
@@
 \note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
-If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm.
-As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
+If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is instead minimizing the diamond norm.
+As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm has matrix elements given by:
 \begin{equation}\label{eq:balanced}
@@
 While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application.
-However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
+However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{H_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 \end{equation}
-In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property.
-Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations.
+In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MQC with this property.
+Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MQC with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations.
 In these situations, one can equivantly use convex optimization to solve this problem.
@@
 \end{equation}
-If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
+If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
 Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one.
@@
 
-%Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+%Another interesting property of the MQC given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
 In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
@@
 In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MQCs.
 
@@
 Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
-While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
-Because of this drift, the quality of the MUP will degrade.
-Thus, we would like to design MUPs that are \textit{robust} to this drift.
+While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
+Because of this drift, the quality of the MQC will degrade.
+Thus, we would like to design MQCs that are \textit{robust} to this drift.
 To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}.
@@
 If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that a mixed unitary process is robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
-\begin{equation}\label{eq:MUP}
+We say that a mixed quantum channel is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
+\begin{equation}\label{eq:MQC}
 \begin{gathered}
@@
 \end{equation}
-In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}.
-More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
-To see this, we can rewrite the error on each control in the MUP as:
+In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}.
+More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
+To see this, we can rewrite the error on each control in the MQC as:
 \begin{equation}\label{eq:taylor}
@@
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MUP} as:
-\begin{equation}\label{eq:MUP-relaxed}
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
+Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
+\begin{equation}\label{eq:MQC-relaxed}
 \begin{gathered}
@@
 Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
-We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP.
-Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.
+We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC.
+Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.
 
-To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
+To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
 \begin{equation}
@@
 The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
-Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family.
-However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls.
-This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.
+Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family.
+However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MQC uses just five of the controls.
+This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.
 
@@
 As a practical consideration, we would also like to regularize our objective function to enforce sparsity.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls.
 As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}.
 In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that our solution, if we are forming a $0$MUP, ignores $H_4$.
-However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
+Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$.
+However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
 Thus we would like to be frugal in which controls we select.
@@
 For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-In both the 0MUP and the 1MUP case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constrain made the 0MUP perform better at the origin by nearly an order of magnitude, and moved the 1MUP from being out-performed by the 0MUP for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
+In both the 0MQC and the 1MQC case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constrain made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
 Imposing this constraint allows us to trade off flatness at the origin for performance.
@@
 In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a MUP on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement a MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
 As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
-To benchmark the quality of the MUP, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+To benchmark the quality of the MQC, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
 We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
@@
 The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MUP, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
+Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MQC, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
 \begin{figure}[t]
@@
 It displays improved average survival probability as well as reduced variance.
-The final box (dark red) illustrates the distribution over survival probabilities for a randomized MUP composed of Pulse1 through Pulse4.
+The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQC composed of Pulse1 through Pulse4.
 It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
-The reduced variance of the MUP is a tell-tale sign of reduced coherent error in the effective channel.
+The reduced variance of the MQC is a tell-tale sign of reduced coherent error in the effective channel.
 }
@@
 We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MUP better than the constituent gates, it also has a signicantly less-coherent error channel.
+Thus, our experiment demonstrates that not only is the performance of the MQC better than the constituent gates, it also has a signicantly less-coherent error channel.
 % subsection experimental (end)
@@
 \subsection{Numerical Implementation}
-In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MUPs. We consider the following model for a single tunable qubit: 
+In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MQCs. We consider the following model for a single tunable qubit: 
 \begin{equation}\label{eq:1Qham}
@@
 We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
-Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MUPs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMUP}.
-These results demonstrate several properties that make MUPs both useful and tractable.
+Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MQCs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQC}.
+These results demonstrate several properties that make MQCs both useful and tractable.
 
@@
   \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+  \caption{Numerical results comparing a 0MQC to a 1MQC for a single tunable qubit, for $RY(\frac{\pi}{2})$.
 The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
-In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
-  \label{fig:YMUP}
+In this case the 0MQC outperforms both the 1MQC by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
+However, varying over $\delta$ we see that the 1MQC outperforms the 0MQC by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+  \label{fig:YMQC}
 \end{figure}
@@
 
-In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MUP}.
+In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MQC}.
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using a MUP improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
-For all values of the drifting parameters we see that the 1MUP performs as well or better than 0MUP.
+Nonetheless, using a MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+For all values of the drifting parameters we see that the 1MQC performs as well or better than 0MQC.
 
@@
   \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
-  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction.
+  \caption{Numerical results comparing a 0MQC to a 1MQC for a pair of tunable qubits, with a resonant exchange interaction.
 Shown with lower alpha values are example constituent controls.
-The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin.
-For all detuning values the 1MUP performs as well or better than the 0MUP.
-When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm.
-Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
-  \label{fig:2MUP}
+The 0MQC and 1MQC can be seen to outperform these controls by half of an order of magnitude at the origin.
+For all detuning values the 1MQC performs as well or better than the 0MQC.
+When there is $.2\%$ drift in the qubit frequency, the 1MQC outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQC outperforms the the constituent controls by over half an order of magnitude.}
+  \label{fig:2MQC}
 \end{figure}
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using MUPs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+We have shown numerically that using MQCs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.

### 2019-03-04 decorrelation/mixed_unitaries.tex
Minor updates

@@
 While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached.
-The limiting factor, of course, is errors in the quantum gate operations.
+A critical limiting factor, of course, is errors in the quantum gate operations.
 
-The impact of an error in a quantum gate depends strongly on both the magnitude and the nature of the errors.
+The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
 Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
 Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
-They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance.
-Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment.
-Systems with stochastic errors can be  modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
+They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance [cite].
+Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment.
+Systems with stochastic errors can usually be modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
 These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate [Ken Brown, Steve Flammia].
 
-Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance, $||\cdot||_\diamond$.
+Quantitative bounds on the performance of a quantum circuit composed of faulty gates can be constructed using the diamond distance, $||\cdot||_\diamond$.
 This particular metric, defined in Section \ref{sec:representing_quantum_gates}, has the appealing property of being subadditive, namely for a channels $\mathcal{F}_1$, $\mathcal{F}_2$ we have:
@@
 Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.
-But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.
-When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
+But if the gates are fairly stable with time and context\cite{1810.05651}, then we can model their action with completely positive, trace-preserving (CPTP) maps.
+These maps have a number of useful representations, including as Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
+But for the purposes of this article, \emph{process matrices} will be most convenient.
+The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the denity matrix.
+\note{Write some more...}
+
+it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
 \begin{equation}
@@
 For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.
-The action of a gate is then given by the usual matrix multiplication:
+We can then represent the action of a CPTP map using a \emph{process matrix}, which acts on a vectorized quantum state by the usual matrix multiplication:
 \begin{equation}\label{error_def}
-  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
+  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
 \end{equation}
-Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:
-
+Here $\actual$ is the actual gate as implemented, $\target$ is the target operation, and $\error$ is the effective error channel:
 \begin{equation}\label{eq:process_matrix}

### 2019-03-04 decorrelation/mixed_unitaries.tex
Edits from discussion

@@
 \newcommand{\error}{\ensuremath{{\mathcal{E}}}}
+\newcommand{\generator}{\ensuremath{{\mathsf{G}}}}
 \def\id{\mbox{\small 1} \!\! \mbox{1}}
@@
 
+\note{don't define diamond norm here}
+
 Quantitative bounds on the performance of a quantum circuit composed of faulty gates can be constructed using the diamond distance, $||\cdot||_\diamond$.
@@
 \label{sec:representing_quantum_gates}
+\begin{enumerate}
+	\item Specify the process matrix representation of a quantum channel in terms of the generalized Bloch vector
+	\item 
+\end{enumerate}
 Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits.
@@
 But for the purposes of this article, \emph{process matrices} will be most convenient.
-The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the denity matrix.
+The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the system density matrix.
 \note{Write some more...}
-
-it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
+\begin{equation}\label{error_def}
+  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
+\end{equation}
+We vectorize the density matrix as
 \begin{equation}
@@
 We can then represent the action of a CPTP map using a \emph{process matrix}, which acts on a vectorized quantum state by the usual matrix multiplication:
-\begin{equation}\label{error_def}
-  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
-\end{equation}
+
+An important consequence of the linearity of this representation is that classical randomness can be easily encoded in the density matrix.
+Suppose that each time a gate is implemented, a different version of the gate is applied at random.
+
 Here $\actual$ is the actual gate as implemented, $\target$ is the target operation, and $\error$ is the effective error channel:
@@
 
-Alternatively, we might consider eliminating off-diagonal entries of G:
+Alternatively, we might consider eliminating off-diagonal entries of $\error(\epsilon)$ \note{fix this}:
 \begin{equation}
@@
 \label{sec:mixed_unitary_processes}
-\note{write an introduction to this section here} 
+\note{write an introduction to this section here, change notation to be consistent with other sections} 
 In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors.
@@
 % ==============================================================================
-
-\subsection{First-order generators} % (fold)
+\subsection{Optimization Targets}
+\subsubsection{First-order generators} % (fold)
 \label{sub:first_order_generators}
@@
 
-\subsection{Off-diagonals} % (fold)
+\subsubsection{Off-diagonals} % (fold)
 \label{sub:off_diagonals}
-
+\note{write this section to basically discuss the original optimization problem (from years ago)}
 % subsection off_diagonals (end)
@@
 % ==============================================================================
-
-\subsection{Adding robustness} % (fold)
+\subsection{Additional Constraints}
+\subsubsection{Adding robustness} % (fold)
 \label{sub:adding_robustness}
-\note{this section is a little bit heavy on the notation - is there anything we can do to ease that?
-Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
+\note{ Try to make this more readable }
 While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
@@
 
-\subsection{Hamiltonian Norm Regularization}
+\subsubsection{Hamiltonian Norm Regularization}
 \label{sec:norm}
@@
 
-\subsection{Sparsity Constraints}
+\subsubsection{Sparsity Constraints}
 As a practical consideration, we would also like to regularize our objective function to enforce sparsity.

### 2019-03-06 decorrelation/mixed_unitaries.tex
some small updates

@@
 % ==============================================================================
-% Section: Constructing Useful Unitary Processes
+% Section: Constructing Useful Mixed Quantum Channels
 % ==============================================================================
-\section{Constructing Useful Unitary Processes}
+\section{Constructing Useful Mixed Quantum Channels}
 \label{sec:mixed_unitary_processes}
-\note{write an introduction to this section here, change notation to be consistent with other sections} 
-In general, we want to construct a problem so that 0 is in the convex hull of some set of vectors.
-These vectors might represent the off-diagonal elements of the error maps, or they could be the error generator.
-As we'll see in section ...
-we could also include the derivatives with respect to various parameters.
-With appropriate weighting, we could minimize any number of effects.
-Which optimization we choose will depend on the approach.
-\note{Then go into examples below.
-}
+Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
+In each of the optimization targets we considered, the problem reduces to finding a collection of vectors whose convex hull contains the origin.
+These vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
+As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift.
+By considering the appropriate collection of vectors and weightings, we can minimize any number of effects.
+Which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 \label{sub:first_order_generators}
-\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
-If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is instead minimizing the diamond norm.
-As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm has matrix elements given by:
+If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is to minimize the diamond norm.
+The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
+However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order.
+As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm to first-order in $\epsilon$ is:
 \begin{equation}\label{eq:balanced}
@@
 While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application.
-However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{H_j\}$ to first order is:
+However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
-\sum \omega_j H_j = 0
+\sum \omega_j G_j = 0
 \end{equation}
-In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MQC with this property.
-Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MQC with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations.
+In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property.
+Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
 In these situations, one can equivantly use convex optimization to solve this problem.
-Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e.
+Consider the matrix whose columns are the vectorized Hamiltonians at our disposal, i.e.
 for $m$, $n\times n$ Hamiltonians:
 \begin{equation}\label{eq:vectorized_hamiltonians}
-	\bold{H} = \left(\begin{array}{cccc}
-		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
+	\bold{G} = \left(\begin{array}{cccc}
+		G_{1_{11}} & G_{2_{11}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		H_{m_{11}} &  &  H_{m_{nn}} \\ 
+		G_{1_{nn}} &  &  G_{m_{nn}} \\ 
 	\end{array} 	
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{H}^T\omega||_2\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{G}\omega||_2\\
   \end{split}
@@
 
-Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\needcite, however these have very poor average case performance.
-However, there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
+Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
 
@@
 \label{sub:off_diagonals}
-\note{write this section to basically discuss the original optimization problem (from years ago)}
+Instead of targeting the diamond norm and vectorizing the error generators, we can instead consider error channels $\error_i$ such that $\error_i\actual_i=\target$, where $\target$ is again the target gate.
+To approximate a depolarizing channel we may define a different minimization problem to  minimize the off-diagonal terms:
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
+    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
+    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
+  \end{split}
+\end{equation}
+
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
+Therefore we can view our approach as a regularization of this method, where we have imposed the condition that our final channel must arise from a BCS.
+In doing so, we move from computing the diamond norm to needing to computing a sum.
+In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates.
 % subsection off_diagonals (end)
@@
 Thus, we would like to design MQCs that are \textit{robust} to this drift.
-To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}.
-Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
+To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
+Instead of only requiring that the $0^{th}$-order derivatives average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift:
 \begin{equation}
@@
 \subsection{Numerical Implementation}
+\label{sec:numerical_results}
 In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MQCs. We consider the following model for a single tunable qubit: 

### 2019-03-06 decorrelation/mixed_unitaries.tex
one more thing

@@
 	\bold{G} = \left(\begin{array}{cccc}
-		G_{1_{11}} & G_{2_{11}} & \ldots   \\ 
+		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		G_{1_{nn}} &  &  G_{m_{nn}} \\ 
+		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
 	\end{array} 	
@@
 Instead of targeting the diamond norm and vectorizing the error generators, we can instead consider error channels $\error_i$ such that $\error_i\actual_i=\target$, where $\target$ is again the target gate.
-To approximate a depolarizing channel we may define a different minimization problem to  minimize the off-diagonal terms:
-\begin{equation}\label{eq:minimization}
+To approximate a depolarizing channel we may define a different minimization problem to  minimize the off-diagonal terms.
+Consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
+
+\begin{equation}\label{eq:vectorized_off_diagonal}
+	\bold{R} = \left(\begin{array}{cccc}
+		R_{1_{1,1}} & R_{2_{1,1}} & \ldots   \\ 
+		\vdots\ & \ddots &    \\
+		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
+	\end{array} 	
+	\right)
+\end{equation}
+then again we consider the same minimziation problem, where we replace $\bold{G}$ with $\bold{R}$:
+
+\begin{equation}\label{eq:minimization_diagonal}
   \begin{split}
-    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
-    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
-    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{R}\omega||_2\\
   \end{split}
@@
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, and while this gives a good theoretical framework, it requires the use of a convex solver, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
-Therefore we can view our approach as a regularization of this method, where we have imposed the condition that our final channel must arise from a BCS.
-In doing so, we move from computing the diamond norm to needing to computing a sum.
-In the next section we give a simple example, followed by numerical results for one qubit and two qubits gates.
+While previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, this requires many evaluations of the diamond norm, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
+Our approach, on the other hand, guarantees that the resulting MQC is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
+
+Depending on which properties are desired of a MQC, many different optimization targets can be chosen.
+From the examples given above, it is clear that if one desires to produce a channel that maximizes worst-case performance, considering the first-order generators is an appropriate target.
+If instead the goal is produce a MQC whose error channel is more tractable to simulate, minimzing the off-diagonal elements may be more appropriate.
 % subsection off_diagonals (end)
@@
 \label{sub:adding_robustness}
-\note{ Try to make this more readable }
 While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
 Because of this drift, the quality of the MQC will degrade.
-Thus, we would like to design MQCs that are \textit{robust} to this drift.
+Thus, we would like to design MQCs that are robust to this drift.
 To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
-Instead of only requiring that the $0^{th}$-order derivatives average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift:
+Instead of only requiring that the error generators average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+If our control Hamiltonian is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
 \begin{equation}
@@
 {\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
-		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
+		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
+		D^\ell_{1_{n,n}} &  &  D^\ell_{m_{n,n}} \\ 
 	\end{array} 	
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}^T\omega||\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||\\
     &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=\vec{0}\\
@@
 &\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||+ \eta\sum\omega_j||D^0_j||_2\\
 &\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
@@
 &\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}^T\omega|| + t\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega|| + t\\
 &\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\

### 2019-03-07 decorrelation/mixed_unitaries.tex
some changes to section 3

@@
 Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel.
-Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
+Given a collection of component channels with error at most $\epsilon$, he showed that Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
 The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits.
@@
 Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
-In each of the optimization targets we considered, the problem reduces to finding a collection of vectors whose convex hull contains the origin.
-These vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
+In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin.
+In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
 As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift.
-By considering the appropriate collection of vectors and weightings, we can minimize any number of effects.
-Which routine we choose will depend on the quantities we are trying to minimize.
+By considering the appropriate collection of vectors and weightings, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 \label{sub:first_order_generators}
-If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is to minimize the diamond norm.
+If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm.
 The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
-However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order.
-As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm to first-order in $\epsilon$ is:
-\begin{equation}\label{eq:balanced}
-\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
-\end{equation}
-This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$.
-Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
-While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application.
-However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
+However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property.
-Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
-In these situations, one can equivantly use convex optimization to solve this problem.
-Consider the matrix whose columns are the vectorized Hamiltonians at our disposal, i.e.
-for $m$, $n\times n$ Hamiltonians:
-\begin{equation}\label{eq:vectorized_hamiltonians}
+Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
+In these situations, one can use convex optimization to solve this problem.
+Consider the matrix whose columns are the vectorized error generators at our disposal, i.e.
+for $m$, $n\times n$ generators:
+\begin{equation}\label{eq:vectorized_generators}
 	\bold{G} = \left(\begin{array}{cccc}
@@
 If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
-Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one.
+Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
 This forms a convex optimization problem, and can be written as:
@@
 
-Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice, with some formal proofs showing runtimes as good as $\mathcal{O}(\log{\frac{1}{\epsilon}}L^2n^4)$, where $\epsilon$ is the accuracy in the solution, $L$ is the number of bits in the input, and $n^4$ is the number of variables.
+Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice.
 
@@
 \label{sub:off_diagonals}
-Instead of targeting the diamond norm and vectorizing the error generators, we can instead consider error channels $\error_i$ such that $\error_i\actual_i=\target$, where $\target$ is again the target gate.
-To approximate a depolarizing channel we may define a different minimization problem to  minimize the off-diagonal terms.
-Consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
+Of course, there are other properties of a channel that one might consider optimizing.
+Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is more amenable to classical simulation.
+Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
+We can write this error channel as a process matrix, vectorize the $R$ submatrices and consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
 
@@
 \end{equation}
-then again we consider the same minimziation problem, where we replace $\bold{G}$ with $\bold{R}$:
+then again we consider the same minimization problem, where we replace $\bold{G}$ with $\bold{R}$:
 
@@
 
-While previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, this requires many evaluations of the diamond norm, and in particular does not have the restriction that the optimal channel be decomposable into a given family of controls.
+Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, however this requires multiple evaluations of the diamond norm, and in particular does not have the restriction that the resulting channel be decomposable into a given family of controls.
 Our approach, on the other hand, guarantees that the resulting MQC is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
-
-Depending on which properties are desired of a MQC, many different optimization targets can be chosen.
-From the examples given above, it is clear that if one desires to produce a channel that maximizes worst-case performance, considering the first-order generators is an appropriate target.
-If instead the goal is produce a MQC whose error channel is more tractable to simulate, minimzing the off-diagonal elements may be more appropriate.
 % subsection off_diagonals (end)
@@
 Instead of only requiring that the error generators average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
-If our control Hamiltonian is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
+If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
 \begin{equation}
-D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
+D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}G_j(\vec{\delta})|_{\delta=\vec{0}}
 \end{equation}
@@
 \begin{gathered}
-\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
+\actual_j(\vec{\delta}) = \exp(-i(G_j(\vec{0}) + \frac{\partial}{\partial\delta_i}G_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} G_j(d\delta_i d\delta_k) + \ldots))\target
 \end{gathered}
@@
 A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
-Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
+Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
 We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC.
@@
 
-To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
+To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
 \begin{equation}
@@
 The time to solve these convex optimization problems is independent of the number of rows, which in our case is the number of drifting parameters.
-However, the size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the runtime of solving the optimization problem grows as $N^4$, with $d$ being the number of drifting parameters, and $N$ being the number of controls.
+However, the size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the runtime of solving the optimization problem grows as $N^4$, with $d$ being the number of drifting parameters, and $N$ being the number of controls.\needcite
 
@@
 Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family.
-However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MQC uses just five of the controls.
-This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.
+However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQC uses just five of the controls.
 
@@
 Imposing this constraint allows us to trade off flatness at the origin for performance.
-
+This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.
 \section{Results} % (fold)

### 2019-03-10 decorrelation/mixed_unitaries.tex
Updates to section 2 -  done for the day

--- 2019-03-06 decorrelation/mixed_unitaries.tex
@@
 \newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
-\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
-\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
-\newcommand{\error}{\ensuremath{{\mathcal{E}}}}
+
+\newcommand{\actual}{\ensuremath{\tilde{\mathsf{G}}}}
+\newcommand{\target}{\ensuremath{{\mathsf{G}}}}
+\newcommand{\error}{\ensuremath{{\mathsf{E}}}}
 \newcommand{\generator}{\ensuremath{{\mathsf{G}}}}
+\newcommand{\vectorize}[1]{\ensuremath{\mathsf{vec}\left(#1\right)}}
 \def\id{\mbox{\small 1} \!\! \mbox{1}}
@@
 \begin{document}
-\title{Advantages of mixed quantum channels for information processing}
+\title{Advantages of mixed quantum gates for information processing}
 
@@
 \label{sec:introduction}
-
+\note{discuss variance narrowing and cite Biercuk}
 The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
@@
   \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a mixed quantum channel.
+  \caption{An example of a mixed quantum gate.
 Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
@@
 
+\note{Discuss the advantages of convex/quadratic programs. Discuss randomized compiling.}
+
 % ==============================================================================
@@
 % ==============================================================================
-\section{Mixed quantum channels}
+\section{Mixed quantum gates}
 \label{sec:representing_quantum_gates}
-\begin{enumerate}
-	\item Specify the process matrix representation of a quantum channel in terms of the generalized Bloch vector
-	\item 
-\end{enumerate}
-Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits.
-Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.
-But if the gates are fairly stable with time and context\cite{1810.05651}, then we can model their action with completely positive, trace-preserving (CPTP) maps.
-These maps have a number of useful representations, including as Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
-But for the purposes of this article, \emph{process matrices} will be most convenient.
-The process matrix representation of a quantum gate acts through the usual matrix multiplication on a vectorized representation of the system density matrix.
-\note{Write some more...}
-\begin{equation}\label{error_def}
-  \vec\rho \rightarrow \actual\vec\rho = \error \target \vec\rho.
+
+\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device.
+Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.
+But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended.
+If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
+This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
+
+% \begin{equation}
+% 	\tr\left(\mathsf{G}(\rho) \cdot\Sigma_i\right)/2^n = 
+% 	 \sum_{j} \mathcal{G}_{ij} \tr\left(\rho \cdot\Sigma_j\right)/2^n
+% 	% (\mathcal{G})_{ij} = 
+% \end{equation}
+% if $\rho=\Sigma_j$, then the only term that survives is
+
+\subsection{Representing CPTP maps}
+\noindent CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
+But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
+A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
+\begin{align}
+	\vectorize{\mathsf{\tilde G}(\rho)}
+		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
+		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
+\end{align}
+We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators.  In this basis,
+\begin{equation}
+  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
 \end{equation}
-We vectorize the density matrix as
+and
 \begin{equation}
-  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
+	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
 \end{equation}
-where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators.
-For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.
-We can then represent the action of a CPTP map using a \emph{process matrix}, which acts on a vectorized quantum state by the usual matrix multiplication:
-
-An important consequence of the linearity of this representation is that classical randomness can be easily encoded in the density matrix.
-Suppose that each time a gate is implemented, a different version of the gate is applied at random.
-
-Here $\actual$ is the actual gate as implemented, $\target$ is the target operation, and $\error$ is the effective error channel:
+Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} []. Error maps take an especially nice form in this representation:
 \begin{equation}\label{eq:process_matrix}
-\error =
+\mathcal{E} =
 	\left(\begin{array}{c|cccc}
@@
 \end{equation}
-The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.
-The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping.
-If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
-If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate.
-Any such Pauli error is expressible as a unitary matrix $U$ that acts on the density matrix by conjugation, and has an action on the vectorized density matrix given by:
-\begin{equation}
-\vec{\rho}\rightarrow \rho_i\vec{\Sigma}_{ijk}U^{\dagger}_{kl}\vec{\Sigma}_{lmn}U_{mj}\end{equation}
- If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
+The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping.
+If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
+Importantly, if $R$ is diagonal, then the error  is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
+% If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
 For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.
 
-In addition to the type of errors, we care about the size of an error.
-The \emph{size} of an error in quantum gates may  be quantified in a number of ways.
-Two of the most common metrics are the average gate fidelity, $\mathcal{F}$, and the diamond norm, $\vert\vert\cdot\vert\vert_\diamond$.
-These may be represented in terms of the error maps as
+\subsection{Defining Mixed Quantum Gates}
+\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
+% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
+Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
+This procedure is operationally indistinguishable from a situation in which we always apply the effective operation,
 \begin{align}
-	&\vert\vert I - \error \vert\vert_\diamond = \sup_\rho \vert \vert (I\otimes I)(\rho) - (\error \otimes I)(\rho) \vert\vert_1\\
-	&\mathcal{F}(\error) = \frac{\tr{\error} + d}{d^2 + d} 
+	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i,
 \end{align}
+which we call a \emph{mixed quantum gate} or MQG. Error metrics can then be computed in terms of the effective error map, 
+\begin{equation}
+	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
+\end{equation}
+Two important error metrics are the average gate infidelity, $\epsilon_\mathcal{F}$, and the diamond distance, $\epsilon_\diamond$ \cite{}. These may be represented in terms of the error maps as
+\begin{align}
+	&\epsilon_\diamond \left(\mathsf{E}\right)
+		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
+										  - (\error \otimes \mathsf{I}_d)(\rho) \vert\vert_1,\\
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\error} + d}{d^2 + d},
+\end{align}
+where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
+If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity.
+One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question.
+the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
 
-Which metric is relevant depends on the application, and can yield very different numbers.
-For instance, the diamond norm is generally linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
 These two metrics also vary significantly in performance on mixed processes.
 
-A \textit{mixed quantum channel} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
+From this definition, we can use linearity to compute the AGI of a MQC.
+We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.
+
+% A \textit{mixed quantum gate} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
 The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-From this definition, we can use linearity to compute the AGI of a MQC.
-We see that the AGI of any MQC will be the convex sum of the consituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.
 
@@
 % ==============================================================================
-% Section: Constructing Useful Mixed Quantum Channels
+% Section: Constructing Useful mixed quantum gates
 % ==============================================================================
-\section{Constructing Useful Mixed Quantum Channels}
+\section{Constructing Useful mixed quantum gates}
 \label{sec:mixed_unitary_processes}
-Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
+Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum gates.
 In each of the optimization targets we considered, the problem reduces to finding a collection of vectors whose convex hull contains the origin.
@@
 \label{sub:first_order_generators}
+\note{There are simple examples where you can make the error perfectly stochastic, but you may make the average gate fidelity very bad to do that.}
 If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is to minimize the diamond norm.
@@
 \label{sub:off_diagonals}
+\note{Discuss why this can make simulation easier. }
 Instead of targeting the diamond norm and vectorizing the error generators, we can instead consider error channels $\error_i$ such that $\error_i\actual_i=\target$, where $\target$ is again the target gate.
@@
 \label{sub:adding_robustness}
-While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
+While mixed quantum gates offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
 Because of this drift, the quality of the MQC will degrade.
@@
 If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that a mixed quantum channel is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
+We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
 \begin{equation}\label{eq:MQC}
@@
 
-To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
+To generate robustly mixed quantum gates, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
 \begin{equation}

### 2019-03-10 decorrelation/mixed_unitaries.tex

@@
 \label{sec:mixed_unitary_processes}
-Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum gates.
-In each of the optimization targets we considered, the problem reduces to finding a collection of vectors whose convex hull contains the origin.
-These vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
+Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
+In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin.
+In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
 As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift.
-By considering the appropriate collection of vectors and weightings, we can minimize any number of effects.
-Which routine we choose will depend on the quantities we are trying to minimize.
+By considering the appropriate collection of vectors and weightings, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 \label{sub:first_order_generators}
-\note{There are simple examples where you can make the error perfectly stochastic, but you may make the average gate fidelity very bad to do that.}
-If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is to minimize the diamond norm.
+
+If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm.
 The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
-However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order.
-As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm to first-order in $\epsilon$ is:
-\begin{equation}\label{eq:balanced}
-\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
-\end{equation}
-This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$.
-Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$.
-While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application.
-However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
+However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 \label{sub:off_diagonals}
-\note{Discuss why this can make simulation easier. }
-Instead of targeting the diamond norm and vectorizing the error generators, we can instead consider error channels $\error_i$ such that $\error_i\actual_i=\target$, where $\target$ is again the target gate.
-To approximate a depolarizing channel we may define a different minimization problem to  minimize the off-diagonal terms.
-Consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
+Of course, there are other properties of a channel that one might consider optimizing.
+Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is more amenable to classical simulation.
+Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
+We can write this error channel as a process matrix, vectorize the $R$ submatrices and consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
 
@@
 \label{sub:adding_robustness}
-While mixed quantum gates offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
+While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
 Because of this drift, the quality of the MQC will degrade.
@@
 
-To generate robustly mixed quantum gates, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
+To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
 \begin{equation}

### 2019-03-18 decorrelation/mixed_unitaries.tex
small changes

@@
 
-From this definition, we can use linearity to compute the AGI of a MQC.
+From this definition, we can use linearity to compute the AGI of an MQC.
 We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for an MQC than any of the processes being mixed.
 
@@
 \label{sec:mixed_unitary_processes}
-Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
-In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin.
+Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like a general methodology for producing \textit{useful} mixed quantum channels.
+In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
 In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
-As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift.
-By considering the appropriate collection of vectors and weightings, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
+As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
+In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQC with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property.
-Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
+Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
 In these situations, one can use convex optimization to solve this problem.
-Consider the matrix whose columns are the vectorized error generators at our disposal, i.e.
-for $m$, $n\times n$ generators:
+Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
+We can then consider the matrix whose columns are the vectorized generators of the error channels for each control, i.e.
+$G_i$ such that $e^{G_i}=\error_i$.
+Then we will have $m$, $n\times n$ generators:
 \begin{equation}\label{eq:vectorized_generators}
@@
 Of course, there are other properties of a channel that one might consider optimizing.
-Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is more amenable to classical simulation.
-Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
-We can write this error channel as a process matrix, vectorize the $R$ submatrices and consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
+Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
+We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
 
@@
 	\bold{R} = \left(\begin{array}{cccc}
-		R_{1_{1,1}} & R_{2_{1,1}} & \ldots   \\ 
+		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
@@
 To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
-Instead of only requiring that the error generators average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+Instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
 If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
@@
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
+Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQC} as:
 \begin{equation}\label{eq:MQC-relaxed}
 \begin{gathered}
-\sum\omega_jD^n_j = 0\\
+\sum\omega_jD^n_j + \mathcal{O}(\epsilon^2) = 0\\
 \end{gathered}
@@
 This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
-A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
+%A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
 Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
@@
  Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.
-
-To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
+To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
 \begin{equation}
@@
 While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
-In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+In particular, while this minimization problem is sufficient for supressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
 That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
@@
 with $\eta \geq 0$.
-By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
+By making $\eta$ larger, we can ensure that we are selecting the controls that will give us a smaller prefactor.
 The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
@@
 In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement a MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement an MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
@@
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using a MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+Nonetheless, using an MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
 For all values of the drifting parameters we see that the 1MQC performs as well or better than 0MQC.

### 2019-03-18 decorrelation/mixed_unitaries.tex
a little more

@@
 with $\eta \geq 0$.
-By making $\eta$ larger, we can ensure that we are selecting the controls that will give us a smaller prefactor.
+By varying $\eta$, we encourage the optimizer to include better controls in addition to minimizing the diamon norm.
 The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
-Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family.
+
+%Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family.
 However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQC uses just five of the controls.
-
 % ==============================================================================
@@
 \subsubsection{Sparsity Constraints}
+
 As a practical consideration, we would also like to regularize our objective function to enforce sparsity.

### 2019-03-18 decorrelation/mixed_unitaries.tex
last bit of tidying section 3 up

@@
 
-As a practical consideration, we would also like to regularize our objective function to enforce sparsity.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls.
-As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}.
+As a practical consideration, we would also like to regularize our objective function to penalize for non-sparse weightings.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs only require a small number of controls.
+As an example, consider Figure \ref{fig:vectorspace}.
 In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$.
-However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'.
+Thus we would prefer that a $0$MQC, ignore $H_4$.
+However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
 Thus we would like to be frugal in which controls we select.
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one.
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain the one norm of $\omega$ to be one.
 Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
@@
 For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-In both the 0MQC and the 1MQC case in our numerical implementation we imposed the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constrain made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
-Imposing this constraint allows us to trade off flatness at the origin for performance.
+In both the 0MQC and the 1MQC case in our numerical implementation in Section \ref{sub:experimental} we impose the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constraint made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
+Imposing this constraint allows us to trade off flatness at the origin for performance at the origin.
 This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.

### 2019-03-18 decorrelation/mixed_unitaries.tex
Figure and section 2

--- 2019-03-18 decorrelation/mixed_unitaries.tex
@@
 \graphicspath{{./figures/}}
-\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
+\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue}
 \newcommand{\tr}{{\rm Tr\thinspace}}
@@
 
+\subsection{Representing errors in quantum gates}
 \noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device.
@@
 % if $\rho=\Sigma_j$, then the only term that survives is 
-
-\subsection{Representing CPTP maps}
-\noindent CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
+ CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
 But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
@@
 \end{align}
-We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators.  In this basis,
+We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
+In this basis,
 \begin{equation}
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} []. Error maps take an especially nice form in this representation:
+Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} []. Error maps take an especially nice form in this representation:
 \begin{equation}\label{eq:process_matrix}
@@
 \end{equation}
-The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping.
+The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping [].
 If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
 Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
-% If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$).
-For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.
+\footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
+For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.}
 
@@
 % , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
-Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
+Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde G}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
 This procedure is operationally indistinguishable from a situation in which we always apply the effective operation,
@@
 										  - (\error \otimes \mathsf{I}_d)(\rho) \vert\vert_1,\\
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\error} + d}{d^2 + d},
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\mathcal{E}} + d}{d^2 + d},
 \end{align}
 where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
-If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity.
+If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity [Wallman - Error rates in quantum circuits].
+The diamond distance is subaddative [Watroos TQI book] under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the diamond distance of a circuit is less than or equal to the sum of the diamond distances for the component gates.
+
+Because $\epsilon_{\mathcal{F}}$ is linear in the error map, we have:
+\begin{equation}
+	\epsilon_{\mathcal{F}}\!\left(\mathsf{E}_{\rm eff}\right) = \sum_i w_i \,\epsilon_{\mathcal{F}}(\mathsf{E}_i).
+\end{equation}
+So there can be little hope of reducing the AGI by combining various implementations.
+However, the diamond distance is a nonlinear function of error map.
+The Ky Fan singular value inequality [K.
+Fan, Maximum properties and inequalities for the eigenvalues of completely continuous operators, Proc.
+Nat.
+Acad.
+Sci.
+U.S.A.
+37 (1951), 760–766] implies that:
+\begin{equation}
+	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
+\end{equation}
+
 One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question.
@@
 
-From this definition, we can use linearity to compute the AGI of an MQC.
+From this definition, we can use linearity to compute the AGI of a MQC.
 We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for an MQC than any of the processes being mixed.
+The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.
 
@@
 \label{sec:mixed_unitary_processes}
-Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like a general methodology for producing \textit{useful} mixed quantum channels.
-In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
+Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like to find a general methodology for producing \textit{useful} mixed quantum channels.
+In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin.
 In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
-As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
-In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
+As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivates of the error generators, if we want to consider the sensitivity of the controls to drift.
+By considering the appropriate collection of vectors and weightings, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQC with error generators $\{G_j\}$ to first order is:
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property.
-Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
+Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce weighting a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
 In these situations, one can use convex optimization to solve this problem.
-Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
-We can then consider the matrix whose columns are the vectorized generators of the error channels for each control, i.e.
-$G_i$ such that $e^{G_i}=\error_i$.
-Then we will have $m$, $n\times n$ generators:
+Consider the matrix whose columns are the vectorized error generators at our disposal, i.e.
+for $m$, $n\times n$ generators:
 \begin{equation}\label{eq:vectorized_generators}
@@
 Of course, there are other properties of a channel that one might consider optimizing.
-Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
-We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
+Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is more amenable to classical simulation.
+Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
+We can write this error channel as a process matrix, vectorize the $R$ submatrices and consider the matrix of off-diagonal terms in Equation \ref{eq:process_matrix}:
 
@@
 	\bold{R} = \left(\begin{array}{cccc}
-		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
+		R_{1_{1,1}} & R_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
@@
 To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
-Instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+Instead of only requiring that the error generators average to zero, we will impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
 If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
@@
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQC} as:
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
+Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
 \begin{equation}\label{eq:MQC-relaxed}
 \begin{gathered}
-\sum\omega_jD^n_j + \mathcal{O}(\epsilon^2) = 0\\
+\sum\omega_jD^n_j = 0\\
 \end{gathered}
@@
 This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
-%A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
+A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
 Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
@@
 Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.
-To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
+
+To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
 \begin{equation}
@@
 While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
-In particular, while this minimization problem is sufficient for supressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+In particular, while this minimization problem is sufficient for quadratically decreasing the diamond norm relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
 That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
@@
 with $\eta \geq 0$.
-By making $\eta$ larger, we can ensure that we are selecting the controls that will give us a smaller prefactor.
+By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor.
 The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
@@
 In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement a MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
@@
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using an MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+Nonetheless, using a MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
 For all values of the drifting parameters we see that the 1MQC performs as well or better than 0MQC.

### 2019-03-19 decorrelation/mixed_unitaries.tex
removing reference to run time of any particular quadratic optimization problem

--- 2019-03-18 decorrelation/mixed_unitaries.tex
@@
 with $D_n^j$ defined in Equation \ref{eq:taylor}.
-The time to solve these convex optimization problems is independent of the number of rows, which in our case is the number of drifting parameters.
-However, the size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the runtime of solving the optimization problem grows as $N^4$, with $d$ being the number of drifting parameters, and $N$ being the number of controls.\needcite
+The size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the time required to solve the optimization problem will depend on the particular optimizer and algorithm used.
 

### 2019-03-20 decorrelation/mixed_unitaries.tex
added in some references, now I need to sleep

@@
 Systems with stochastic errors can usually be modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
-These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate [Ken Brown, Steve Flammia].
+These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.
 
@@
 \subsection{Representing CPTP maps}
-\noindent CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
-But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
+\noindent CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
+But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
 A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} []. Error maps take an especially nice form in this representation:
+Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} \cite{Chow2012}. Error maps take an especially nice form in this representation:
 \begin{equation}\label{eq:process_matrix}

### 2019-03-25 decorrelation/mixed_unitaries.tex
Edits to draft

--- 2019-03-18 decorrelation/mixed_unitaries.tex
@@
 \graphicspath{{./figures/}}
-\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue}
+\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
 \newcommand{\tr}{{\rm Tr\thinspace}}
@@
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended.
-If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
+If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$, on density matrices.
 This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
@@
  CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
-But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
+But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ by the corresponding calligraphic character, $\mathcal{G}$.
 A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
@@
 If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
-Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
-\footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
+Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.\footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
 For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.}
+
+In what follows it will be useful to define the \emph{error generator}, $\mathcal{L}$, associated with a faulty gate: 
+\begin{align}
+	\label{eq:generator}
+	\mathcal{E} 
+		&= \exp\left(\mathcal{L}\right) \\
+		&\approx \mathcal{I}_d + \mathcal{L}.
+\end{align}
 
@@
 \end{equation}
-Two important error metrics are the average gate infidelity, $\epsilon_\mathcal{F}$, and the diamond distance, $\epsilon_\diamond$ \cite{}. These may be represented in terms of the error maps as
+Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
 \begin{align}
+	\label{eq:def_agi}
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d}\\
+	\label{eq:def_diamond}
 	&\epsilon_\diamond \left(\mathsf{E}\right)
 		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
-										  - (\error \otimes \mathsf{I}_d)(\rho) \vert\vert_1,\\
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{\tr{\mathcal{E}} + d}{d^2 + d},
+										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
 \end{align}
 where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
+In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated process matrix, $\mathcal{E}$.
 If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity [Wallman - Error rates in quantum circuits].
@@
 However, the diamond distance is a nonlinear function of error map.
-The Ky Fan singular value inequality [K.
-Fan, Maximum properties and inequalities for the eigenvalues of completely continuous operators, Proc.
-Nat.
-Acad.
-Sci.
-U.S.A.
-37 (1951), 760–766] implies that:
+As we show in the appendix (\ref{sub:diamond_distance_inequality}):
 \begin{equation}
+	\label{eq:diamond_ineq}
 	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
 \end{equation}
+So by mixing various implementations, each with a different error channel, the resulting channel can have a diamond distance error less than any of the component implementations.
 
-One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question.
+% One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question.
 the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
 
-These two metrics also vary significantly in performance on mixed processes.
+% These two metrics also vary significantly in performance on mixed processes.
 
-From this definition, we can use linearity to compute the AGI of an MQC.
+% From this definition, we can use linearity to compute the AGI of an MQC.
 We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting.
@@
 
-When performing a quantum gate, there are often many possible ways of it might be implemented.
+% When performing a quantum gate, there are often many possible ways of it might be implemented.
 Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel.
@@
 \label{sec:simple_example}
-As a simple example, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis.
-The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$.
-Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.
+\noindent As a simple example, consider a single-qubit and four different implementations of a $\mathsf{PHASE}$ gate: $\{3\pi,\pi,-\pi,3\pi\}$ rotations about the $\sigma_z$-axis.
+If the control amplitude is too high, then the error maps associated with these four implementations are themselves unitary rotations about the $\sigma_z$-axis with rotation angles $\{3\eta, \eta, -\eta, -3\eta\}$, repectively (and $\eta \ll \pi$).
 
@@
 
-The error operator corresponding to a rotation error by angle $\epsilon$ is then:
+The error operator corresponding to a rotation error by angle $\eta$ is then:
 \begin{equation}
-\error(\epsilon) =
+\error(\eta) =
 	\left(\begin{array}{ccccc}
 		1 & 0 & 0 & 0 \\ 
-		0 & \cos\epsilon & \sin\epsilon  & 0  \\
-		0 & -\sin\epsilon & \cos\epsilon & 0  \\
+		0 & \cos\eta & \sin\eta  & 0  \\
+		0 & -\sin\eta & \cos\eta & 0  \\
 		0 & 0 & 0 & 1
@@
 
-The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$.
-If we were construct two channels, one with error $\error(\epsilon)$ and one with error $\error(-\epsilon)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\epsilon) + \error(\epsilon)\right)$.
+The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\eta)}_\diamond \simeq \eta$, while the fidelity of the channel is $\mathcal{F}(\error(\eta)) = \eta^2$.
+If we were construct two channels, one with error $\error(\eta)$ and one with error $\error(-\eta)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\eta) + \error(\eta)\right)$.
 The effective channel then has a matrix representation:
 \begin{equation}
-	\error(\epsilon) =
+	\error(\eta) =
 	\left(\begin{array}{ccccc}
 		1 & 0 & 0 & 0 \\ 
-		0 & \cos\epsilon & 0  & 0  \\
-		0 & 0 & \cos\epsilon & 0  \\
+		0 & \cos\eta & 0  & 0  \\
+		0 & 0 & \cos\eta & 0  \\
 		0 & 0 & 0 & 1
@@
 		0 & 0 & 0 & 0 \\ 
-		0 & \epsilon^2/2 & 0  & 0  \\
-		0 & 0 & \epsilon^2/2 & 0  \\
+		0 & \eta^2/2 & 0  & 0  \\
+		0 & 0 & \eta^2/2 & 0  \\
 		0 & 0 & 0 & 0
@@
 \end{equation}
-And with same average process fidelity, $\epsilon^2$, but now a suppressed diamond norm $\epsilon^2$. Now write this in terms of the error generators $\error(\epsilon) = \exp(\epsilon G)$ where
+And with same average process fidelity, $\eta^2$, but now a suppressed diamond norm $\eta^2$. Now write this in terms of the error generators $\error(\eta) = \exp(\eta G)$ where
 \begin{equation}
@@
 \begin{equation}
-	\error(\epsilon) = \mathcal{I} + \epsilon G + \frac{1}{2}\epsilon^2 G^2 + \mathcal{O}(\epsilon^3)
+	\error(\eta) = \mathcal{I} + \eta G + \frac{1}{2}\eta^2 G^2 + \mathcal{O}(\eta^3)
 \end{equation}
@@
 		% &= \sum_i \omega_i \error_i \\
-		% &= \sum_i \omega_i \left(\mathcal{I} + \epsilon_i G_i + \frac{1}{2}\epsilon_i^2 G_i^2 + \cdots \right) \\
-		&= \mathcal{I} + \sum_i \omega_i \epsilon_i G_i+ \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + + \mathcal{O}(\epsilon^3)
+		% &= \sum_i \omega_i \left(\mathcal{I} + \eta_i G_i + \frac{1}{2}\eta_i^2 G_i^2 + \cdots \right) \\
+		&= \mathcal{I} + \sum_i \omega_i \eta_i G_i+ \sum_i \omega_i \frac{1}{2}\eta^2_i G_i^2 + + \mathcal{O}(\eta^3)
 \end{align}
 \begin{equation}
-	\error_{\text{eff}} = \mathcal{I} + \sum_i \omega_i \frac{1}{2}\epsilon^2_i G_i^2 + \mathcal{O}(\epsilon^3)
+	\error_{\text{eff}} = \mathcal{I} + \sum_i \omega_i \frac{1}{2}\eta^2_i G_i^2 + \mathcal{O}(\eta^3)
 \end{equation}
@@
 \hline
-	$U_{+2\epsilon}$ & $2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$\\
-	$U_{+\epsilon}$ & $\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
-	$U_{-\epsilon}$ & $-\epsilon \sigma_x$ & $\epsilon^2$ & $\epsilon$ \\
-	$U_{-2\epsilon}$ & $-2\epsilon \sigma_x$ & $4\epsilon^2$ & $2\epsilon$ 
+	$U_{+2\eta}$ & $2\eta \sigma_z$ & $4\eta^2$ & $2\eta$\\
+	$U_{+\eta}$ & $\eta \sigma_z$ & $\eta^2$ & $\eta$ \\
+	$U_{-\eta}$ & $-\eta \sigma_z$ & $\eta^2$ & $\eta$ \\
+	$U_{-2\eta}$ & $-2\eta \sigma_z$ & $4\eta^2$ & $2\eta$ 
 \end{tabular}
@@
 
-Alternatively, we might consider eliminating off-diagonal entries of $\error(\epsilon)$ \note{fix this}:
+Alternatively, we might consider eliminating off-diagonal entries of $\error(\eta)$ \note{fix this}:
 \begin{equation}
@@
 \note{more here about alternative method. Also discuss Fig 2.}.
-
-\note{END}
 
@@
 \newpage
-\onecolumngrid
+% \onecolumngrid
 % ==============================================================================
@@
 \label{sec:appendix}
-\subsection{Robust Mixing Lemma}
-We begin by generalizing Lemma 2 from \cite{Campbell2017}. If all of our error Hamiltonians $\{H_j\}$ have bounded error, that is:
+
+% ==============================================================================
+% Section: Diamond Distance Inequality
+% ==============================================================================
+\subsection{Diamond distance inequality}
+\label{sub:diamond_distance_inequality}
+Here we prove the claim of \eqref{eq:diamond_ineq} that:
 \begin{equation}
-||H_j||\leq c
+	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
 \end{equation}
-Then we may consider the derivative of any mixture of unitaries as:
-%\begin{equation}
-%\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji%\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
-%\end{equation}
-\begin{equation}
-\deriv\sum_j \omega_je^{iH_j} = \sum_j\omega_ji\deriv (H_j)e^{iH_j}
-\end{equation}
-By assumption, the derivatives of the first order term sum to zero, and so we see by A3 in \cite{Campbell2017} that
-\begin{equation}
-||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\omega_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
-\end{equation}
-Where we have used the fact that $||AB|| \leq ||A||||B||$ with $||\cdot||$ being the $\infty$-norm.
-Additionally, 
+The effective error channel for a mixed quantum gate is $\mathsf{E}_{\rm{eff}} = \sum_i w_i\,\mathsf{E}_i$, where $\mathsf{E}_i$ are the error channels for the component gates.
+The diamond distance to the identity of the effective error channel is:
 \begin{align}
-||\deriv e^{iH_j}|| &= ||\deriv(iH_j)e^{iH_j}|| \\
-&\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)H_j|| +  ||\deriv(iH_j)\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n|| \\
-&\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)||\cdot||H_j|| +  ||\deriv(iH_j)||\cdot||\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n||\\
-&\leq c + c^2 + \frac{c^3}{2}
+	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
+		&= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
+										  - (\mathsf{E}_{\rm eff} \otimes \mathsf{I}_d)(\rho) \vert\vert_1\\
+		&= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
+										  - (\sum_i w_i\,\mathsf{E}_i \otimes \mathsf{I}_d)(\rho) \vert\vert_1 \\
+		&= \frac{1}{2} \sup_\rho \vert \vert \sum_i w_i\,((\mathsf{I}_d
+										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho) \vert\vert_1
 \end{align}
-And so we see that Lemma 2 generalizes. We will use the above to upper bound the 1-norm (and hence diamond norm) in the following.
+The space of density matrices is compact, so the supremum is achievable. Call a state that achieves the supremum $\rho^*$. Then 
+\begin{align}
+	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
+		&= \frac{1}{2} \vert \vert \sum_i w_i\,((\mathsf{I}_d
+										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*) \vert\vert_1 \\
+		&= \frac{1}{2} \vert \vert \sum_i w_i\, \rho^*_i \vert\vert_1,
+\end{align}
+where we have defined $\rho^*_i = ((\mathsf{I}_d - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*)$.
+The nuclear norm above is equal to the sum of the singular values of $\sum_i w_i \rho_i$.
+Using the Ky Fan singular value inequality [K.
+Fan, Maximum properties and inequalities for the eigenvalues of completely continuous operators, Proc.
+Nat.
+Acad.
+Sci.
+U.S.A.
+37 (1951), 760–766] , we have
+\begin{align}
+	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
+		&\le \frac{1}{2} \sum_i w_i \vert \vert \rho^*_i \vert\vert_1 \\
+		&\le \sum_i w_i\, \epsilon_\diamond(\mathsf{E}_i)
+\end{align}
+The second inequality above follows because $\rho^*$ defines an explicit lower bound for the diamond distance for each of the component error maps.
 
-Next we generalize the Mixing Lemma from \cite{Campbell2017}. We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
+% % subsection diamond_distance_inequality
 
-\begin{align}
-&= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-&= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-&\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
-\end{align}
-And so we see it is sufficient to upperbound:
-\begin{equation}
-|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1
-\end{equation}
-From Equation 18 in \cite{Campbell2017}:
-\begin{align}
-&(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
-&\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
-\end{align}
-Thus, by H\"older's inequality we find:
-\begin{align}
-&||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq||\sum_j \omega_j\deriv\tilde{\delta}_j|| + ||\sum_j\omega_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\omega_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\omega_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
-\end{align}
-By assumption, all of these terms are neglible, and therefore we find:
-\begin{align}
-||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq 2a^2 + 2b^2
-\end{align}
-And so we see that the mixing lemma extends to first order.
+% \subsection{Robust Mixing Lemma}
+% \label{sub:rml}
+% We begin by generalizing Lemma 2 from \cite{Campbell2017}. If all of our error Hamiltonians $\{H_j\}$ have bounded error, that is:
+% \begin{equation}
+% ||H_j||\leq c
+% \end{equation}
+% Then we may consider the derivative of any mixture of unitaries as:
+% %\begin{equation}
+% %\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji%\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
+% %\end{equation}
+% \begin{equation}
+% \deriv\sum_j \omega_je^{iH_j} = \sum_j\omega_ji\deriv (H_j)e^{iH_j}
+% \end{equation}
+% By assumption, the derivatives of the first order term sum to zero, and so we see by A3 in \cite{Campbell2017} that
+% \begin{equation}
+% ||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\omega_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
+% \end{equation}
+% Where we have used the fact that $||AB|| \leq ||A||||B||$ with $||\cdot||$ being the $\infty$-norm.
+% Additionally, 
+% \begin{align}
+% ||\deriv e^{iH_j}|| &= ||\deriv(iH_j)e^{iH_j}|| \\
+% &\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)H_j|| +  ||\deriv(iH_j)\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n|| \\
+% &\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)||\cdot||H_j|| +  ||\deriv(iH_j)||\cdot||\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n||\\
+% &\leq c + c^2 + \frac{c^3}{2}
+% \end{align}
+% And so we see that Lemma 2 generalizes. We will use the above to upper bound the 1-norm (and hence diamond norm) in the following.
+
+% Next we generalize the Mixing Lemma from \cite{Campbell2017}. We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
+
+% \begin{align}
+% &= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+% &= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
+% &\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
+% \end{align}
+% And so we see it is sufficient to upperbound:
+% \begin{equation}
+% |\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1
+% \end{equation}
+% From Equation 18 in \cite{Campbell2017}:
+% \begin{align}
+% &(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
+% &\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
+% \end{align}
+% Thus, by H\"older's inequality we find:
+% \begin{align}
+% &||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq||\sum_j \omega_j\deriv\tilde{\delta}_j|| + ||\sum_j\omega_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\omega_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\omega_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
+% \end{align}
+% By assumption, all of these terms are neglible, and therefore we find:
+% \begin{align}
+% ||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq 2a^2 + 2b^2
+% \end{align}
+% And so we see that the mixing lemma extends to first order.
 In a similar way, it can be extended to arbitary order, and thus if we can find constructions that satisfy the generalized Lemma 2, we can use the Robust Mixing Lemma to conclude that there exists a weighting with linearly supressed diamond norm.
+
 \end{document}

### 2019-03-25 decorrelation/mixed_unitaries.tex

@@
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended.
-If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$, on density matrices.
+If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
 This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
 
-% \begin{equation}
-% 	\tr\left(\mathsf{G}(\rho) \cdot\Sigma_i\right)/2^n = 
-% 	 \sum_{j} \mathcal{G}_{ij} \tr\left(\rho \cdot\Sigma_j\right)/2^n
-% 	% (\mathcal{G})_{ij} = 
-% \end{equation}
-% if $\rho=\Sigma_j$, then the only term that survives is 
- CPTP maps possesses a number of useful representations, including Kraus operators[], Choi matrices[], and Jamiolkowsi states[].
-But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient [], and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ by the corresponding calligraphic character, $\mathcal{G}$.
+\subsection{Representing CPTP maps}
+\noindent CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
+But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
 A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
@@
 \end{align}
-We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
-In this basis,
+We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators.  In this basis,
 \begin{equation}
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} []. Error maps take an especially nice form in this representation:
+Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} \cite{Chow2012}. Error maps take an especially nice form in this representation:
 \begin{equation}\label{eq:process_matrix}
@@
 % , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
-Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde G}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
+Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
 This procedure is operationally indistinguishable from a situation in which we always apply the effective operation,

### 2019-03-25 decorrelation/mixed_unitaries.tex
Cleaning up the git repo

@@
 
-\note{don't define diamond norm here}
+% \note{don't define diamond norm here}
 
@@
 In this case, the resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
+
+\note{Discuss randomized compiling}
 
@@
 % ==============================================================================
-\section{Mixed quantum gates}
+\section{Representing Errors }
 \label{sec:representing_quantum_gates}
 
-\subsection{Representing errors in quantum gates}
+\subsection{Representing Errors in Quantum Gates}
 \noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device.
@@
 
-\subsection{Representing CPTP maps}
-\noindent CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
+CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
 But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
+For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix.
 A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as a \emph{Pauli transfer matrix} \cite{Chow2012}. Error maps take an especially nice form in this representation:
+Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}, and error maps take an especially nice form in this basis:
 \begin{equation}\label{eq:process_matrix}
@@
 	\mathcal{E} 
-		&= \exp\left(\mathcal{L}\right) \\
-		&\approx \mathcal{I}_d + \mathcal{L}.
+		&= \exp\left(\mathcal{L}\right) \approx \mathcal{I}_d + \mathcal{L}.
 \end{align}
+If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms.
 
-\subsection{Defining Mixed Quantum Gates}
+\subsection{Mixed Quantum Gates}
 \noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
@@
 										  - (\mathsf{E}_{\rm eff} \otimes \mathsf{I}_d)(\rho) \vert\vert_1\\
-		&= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
-										  - (\sum_i w_i\,\mathsf{E}_i \otimes \mathsf{I}_d)(\rho) \vert\vert_1 \\
+		% &= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
+										  % - (\sum_i w_i\,\mathsf{E}_i \otimes \mathsf{I}_d)(\rho) \vert\vert_1 \\
 		&= \frac{1}{2} \sup_\rho \vert \vert \sum_i w_i\,((\mathsf{I}_d
@@
 \end{align}
-The space of density matrices is compact, so the supremum is achievable. Call a state that achieves the supremum $\rho^*$. Then 
+For qubits, the space of density matrices is compact, so the supremum is achievable. Call a state that achieves the supremum $\rho^*$. Then 
 \begin{align}

### 2019-05-21 decorrelation/mixed_unitaries.tex
Updates to text before IIIA

@@
 \usepackage{calc}
+\usepackage{tabularx}
+\newcolumntype{Y}{>{\centering\arraybackslash}X}
 \graphicspath{{./figures/}}
@@
 \begin{document}
-\title{Advantages of mixed quantum gates for information processing}
+\title{Robustly decorrelating errors with mixed quantum gates}
 
@@
 \author{Kevin C. Young}
-\affiliation{Sandia National Laboratories, Livermore, CA}
+\affiliation{Quantum Performance Laboratory, Sandia National Laboratories, Livermore, CA}
 
@@
 \begin{abstract}
-Coherent errors in quantum operations are ubiquitous.
+\noindent Coherent errors in quantum operations are ubiquitous.
 Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate.
-As Hastings and Campbell have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error.
-Our results extend those of Hastings and Campbell to include robustness to drifting external control parameters.
-We implement these constructions using a superconducting qubit and will discuss randomized benchmarking results consistent with a marked reduction in coherent error.
+As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error.
+Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem.
+We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates.
+Finally, we implement these mixed quantum gate on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
+{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
+{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
 \end{abstract}
@@
 \label{sec:introduction}
-\note{discuss variance narrowing and cite Biercuk}
-The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
+\noindent The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
 Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices.
@@
 A critical limiting factor, of course, is errors in the quantum gate operations.
+\note{I think we can just strike this whole paragraph.
+I hate these introductions.}
 
 The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
-Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
 Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
-They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance [cite].
+They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}.
 Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment.
-Systems with stochastic errors can usually be modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
+Systems with stochastic errors can usually be accurately modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
 These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.
-
-% \note{don't define diamond norm here}
-
-Quantitative bounds on the performance of a quantum circuit composed of faulty gates can be constructed using the diamond distance, $||\cdot||_\diamond$.
-This particular metric, defined in Section \ref{sec:representing_quantum_gates}, has the appealing property of being subadditive, namely for a channels $\mathcal{F}_1$, $\mathcal{F}_2$ we have:
-\begin{equation}
-||\mathcal{F}_1\circ\mathcal{F}_2||_\diamond \leq ||\mathcal{F}_1||_\diamond + ||\mathcal{F}_2||_\diamond
-\end{equation}
-The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
-For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
-Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
-In this case, the resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.
-
-\note{Discuss randomized compiling}
 
@@
 
+Recent works by Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
+They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the native gates are perfect.
+Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error.
+So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \note{cite Debbie Leung}, which has significiantly less coherent error than any single compilation on its own.
+A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.
+We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts.
+\note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion?
+We should also discuss randomized compiling there.
+}
+
+In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations.
+We demonstrate that, depending on the objective, different numerical optimization targets may be preferred.
+We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
+Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error \cite{Ball2016}.
+We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+The resulting convex optimizations can be performed quickly and efficiently.
+\note{This paragraph is pretty good, but should be cleaned up a bit.}
+
+% Reducing the coherence of a the quantum gate error
+
+% 
+%
+
+% It has long been recognized, however, that one may inject additional decorrelating randomness
+
+% By injecting additional decorrelating randomness into the system,
+
+% By introducing additional decorrelating randomness, a number of techniques are able to convert coherent  errors into stochastic errors.
+
+% By introducing intentional additional randomness to the 
+% The gate-to-gate correlations that occur in the presence of coherent noise
+
+% \note{don't define diamond norm here}
+% The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
+For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
+Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
+
 %Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
-
-In this article we discuss various applications of these mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the gate implementations.
-We demonstrate that, depending on the objective, different numerical optimizations may be preferred.
-We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
-Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error.
-We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
-
-\note{Discuss the advantages of convex/quadratic programs. Discuss randomized compiling.}
 
@@
 Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.
-But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended.
-If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
+But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, the qubits experience errors.
+If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
 This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
@@
 For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix.
-A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
+A key feature of process matrices is that they are composable and act through the usual matrix multiplication on the vectorized quantum state:
 \begin{align}
@@
 \end{align}
-We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
+We shall work in the basis of Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
 In this basis,
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}, and error maps take an especially nice form in this basis:
+Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
 \begin{equation}\label{eq:process_matrix}
@@
 \end{equation}
-The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping [].
+The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}.
 If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
-Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.\footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
-For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.}
+Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
+If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
+For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.
 
@@
 	\mathcal{E} 
-		&= \exp\left(\mathcal{L}\right) \approx \mathcal{I}_d + \mathcal{L}.
+		&= \exp\left(\mathcal{L}\right) \\
+		&= \mathcal{I}_d + \mathcal{L} + \frac{1}{2}\mathcal{L}^2 + \order{\mathcal{L}^3}.
 \end{align}
-If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms.
+If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms, and the Taylor expansion above may reliably be truncated at first or second order.
 
@@
 Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
-This procedure is operationally indistinguishable from a situation in which we always apply the effective operation,
+This procedure is operationally indistinguishable from always applying the effective operation,
 \begin{align}
-	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i,
+	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i.
 \end{align}
-which we call a \emph{mixed quantum gate} or MQG. Error metrics can then be computed in terms of the effective error map, 
+We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for MQGs can be computed in terms of their effective error map, 
 \begin{equation}
+	\label{eq:effective_error}
 	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
@@
 	\label{eq:def_agi}
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d}\\
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
 	\label{eq:def_diamond}
@@
 where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
-In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated process matrix, $\mathcal{E}$.
-If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity [Wallman - Error rates in quantum circuits].
-The diamond distance is subaddative [Watroos TQI book] under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the diamond distance of a circuit is less than or equal to the sum of the diamond distances for the component gates.
+In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
+If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \note{[Wallman - Error rates in quantum circuits]}.
+The diamond distance is subaddative \note{[Watroos TQI book]} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \note{[Aharanov, Kitaev, Nisan, 1998]}.
 
@@
 \end{equation}
-So there can be little hope of reducing the AGI by combining various implementations.
+That is, the AGI of the mixed quantum gate is simply the weighted average of the component AGIs, so there is no hope of reducing the AGI by combining various implementations.
 However, the diamond distance is a nonlinear function of error map.
@@
 
-% One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question.
-the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.
-
-% These two metrics also vary significantly in performance on mixed processes.
-
-% From this definition, we can use linearity to compute the AGI of an MQC.
-We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting.
-The diamond norm, however, is non-linear function of the channel, and can in general be smaller for an MQC than any of the processes being mixed.
-
-% A \textit{mixed quantum gate} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.
-The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.
-
-% When performing a quantum gate, there are often many possible ways of it might be implemented.
-Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel.
-Given a collection of component channels with error at most $\epsilon$, he showed that Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed.
-The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits.
-However, it is not the only optimization target that can be chosen.
-
-\subsection{A simple example}
-\label{sec:simple_example}
-\noindent As a simple example, consider a single-qubit and four different implementations of a $\mathsf{PHASE}$ gate: $\{3\pi,\pi,-\pi,3\pi\}$ rotations about the $\sigma_z$-axis.
-If the control amplitude is too high, then the error maps associated with these four implementations are themselves unitary rotations about the $\sigma_z$-axis with rotation angles $\{3\eta, \eta, -\eta, -3\eta\}$, repectively (and $\eta \ll \pi$).
-
-In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
-Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
-More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
-We implemented such a routine on a superconducting qubit.
-
-The error operator corresponding to a rotation error by angle $\eta$ is then:
-\begin{equation}
-\error(\eta) =
-	\left(\begin{array}{ccccc}
-		1 & 0 & 0 & 0 \\ 
-		0 & \cos\eta & \sin\eta  & 0  \\
-		0 & -\sin\eta & \cos\eta & 0  \\
-		0 & 0 & 0 & 1
-	\end{array} 	
-	\right)
-\end{equation}
-
-The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\eta)}_\diamond \simeq \eta$, while the fidelity of the channel is $\mathcal{F}(\error(\eta)) = \eta^2$.
-If we were construct two channels, one with error $\error(\eta)$ and one with error $\error(-\eta)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\eta) + \error(\eta)\right)$.
-The effective channel then has a matrix representation:
-\begin{equation}
-	\error(\eta) =
-	\left(\begin{array}{ccccc}
-		1 & 0 & 0 & 0 \\ 
-		0 & \cos\eta & 0  & 0  \\
-		0 & 0 & \cos\eta & 0  \\
-		0 & 0 & 0 & 1
-	\end{array} 	
-	\right) \simeq \mathcal{I} - 
-	\left(\begin{array}{ccccc}
-		0 & 0 & 0 & 0 \\ 
-		0 & \eta^2/2 & 0  & 0  \\
-		0 & 0 & \eta^2/2 & 0  \\
-		0 & 0 & 0 & 0
-	\end{array} 	
-	\right)
-\end{equation}
-And with same average process fidelity, $\eta^2$, but now a suppressed diamond norm $\eta^2$. Now write this in terms of the error generators $\error(\eta) = \exp(\eta G)$ where
-\begin{equation}
-	G =
-	\left(\begin{array}{ccccc}
-		0 & 0 & 0 & 0 \\ 
-		0 & 0 & -1  & 0  \\
-		0 & 1 & 0 & 0  \\
-		0 & 0 & 0 & 0
-	\end{array} 	
-	\right)
-\end{equation}
-
-The effective generator vanishes at first order.
-
-\begin{equation}
-	\error(\eta) = \mathcal{I} + \eta G + \frac{1}{2}\eta^2 G^2 + \mathcal{O}(\eta^3)
-\end{equation}
+Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.
+Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target.
+Explicitly, the weight are chosen such that the error generator is canceled to first order.
+Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
 \begin{align}
-	\error_{\text{eff}} 
-		% &= \sum_i \omega_i \error_i \\
-		% &= \sum_i \omega_i \left(\mathcal{I} + \eta_i G_i + \frac{1}{2}\eta_i^2 G_i^2 + \cdots \right) \\
-		&= \mathcal{I} + \sum_i \omega_i \eta_i G_i+ \sum_i \omega_i \frac{1}{2}\eta^2_i G_i^2 + + \mathcal{O}(\eta^3)
+	\label{eq:generators_and_effective_error}
+	\mathcal{E}_{\rm eff} \simeq \left(\mathcal{I}_d + \sum_i w_i \mathcal{L}_i + \frac{1}{2} \sum_i w_i \mathcal{L}_i^2\right)
 \end{align}
-\begin{equation}
-	\error_{\text{eff}} = \mathcal{I} + \sum_i \omega_i \frac{1}{2}\eta^2_i G_i^2 + \mathcal{O}(\eta^3)
-\end{equation}
-
-\begin{center}
-\begin{tabular}{cccc}
-	Gate & $H_{\rm{eff}}$ & AGI & $\vert\vert\cdot\vert\vert_\diamond$ \\
-\hline
-	$U_{+2\eta}$ & $2\eta \sigma_z$ & $4\eta^2$ & $2\eta$\\
-	$U_{+\eta}$ & $\eta \sigma_z$ & $\eta^2$ & $\eta$ \\
-	$U_{-\eta}$ & $-\eta \sigma_z$ & $\eta^2$ & $\eta$ \\
-	$U_{-2\eta}$ & $-2\eta \sigma_z$ & $4\eta^2$ & $2\eta$ 
-\end{tabular}
-\end{center}
-
-Alternatively, we might consider eliminating off-diagonal entries of $\error(\eta)$ \note{fix this}:
-\begin{equation}
-	\left(\begin{array}{@{}ccccc@{}}
-		0 & 0 & 0 & 0 \\ 
-  		\cline{3-4}
-    	0 & 0 & \multicolumn{1}{|c}{-1} & \multicolumn{1}{c|}{0} \\
-    	\cline{3-3}		
-		0 & 1 & 0 & \multicolumn{1}{|c|}{0}\\
-		\cline{4-4}	
-		0 & 0 & 0 & 0
-	\end{array} 	
-	\right)
-\end{equation}
-resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable problem.
-In the case of a single qubit, it is clear that our generator is expressible as $\hat{n}\cdot\vec{\Sigma}$, where $\vec{\Sigma}$ is again the vector of Pauli operators.
-The condition that the off-diagonal terms vanish is then again the same condition that the origin lies in the convex hull of the vectors $\vec{n}_i$ for each $G_i$.
-\note{more here about alternative method. Also discuss Fig 2.}.
-
-% In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
-% \begin{align}
-% 	\mathcal{M}_{jk} 
-% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
-% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
-% 		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
-% 		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
-% \end{align}
-% The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
-The result would be a purely stochastic channel.
+If, as Campbell required, the origin is in the convex hull of the generators (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $w_i^*$, such that $\sum_i w^*=1$ and:
+\begin{align}
+	\label{eq:cancel}
+	&\sum_i w_i^* \mathcal{L} = 0
+	% \mathrm{with}\;&\sum_i w_i = 1
+\end{align}
+If the error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
+Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians.
+Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull.
+If, however, the error map contains stochastic components, then the condition of Eq.~\ref{eq:cancel} might be impossible to satisfy.
+Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull.
+This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators.
+In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.
 
@@
 
+While Campbell's approach can provide a guaranteed suppression of the error rate, it does not necessarily lead to a purely stochastic channel.
+Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel.
+In order to definitively eliminate these coherent errors, we seek weights, $w_i$, that annihilate the off-diagonal entries of the unital submatrix of the effective error map, resulting in an effective error:
+% \begin{equation}
+% 	\mathcal{E}_{eff} = 
+% 	\left(\begin{array}{@{}ccccc@{}}
+% 		\cdot & \cdot & \cdot & \cdot \\ 
+%   		\cline{1-1}\cline{3-4}
+%     	\multicolumn{1}{|c}{0} & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c}{0} & \multicolumn{1}{c|}{0} \\
+%     	\cline{2-2}\cline{3-3}		
+% 		\multicolumn{1}{|c}{0} & 0 & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c|}{0}\\
+% 		\cline{3-3}\cline{4-4}	
+% 		\multicolumn{1}{|c}{0} & 0 & 0 & \multicolumn{1}{|c}{\cdot}\\
+% 		\cline{1-3}
+% 	\end{array} 	
+% 	\right).
+% \end{equation}
+
+\begin{equation}
+	\mathcal{E}_{\rm{eff}} = 
+	\left(\begin{array}{@{}ccccc@{}}
+		1 & 0 & 0 & 0 \\ 
+    	0 &  p_x & 0 & 0 \\
+		0 & 0 &  p_y & 0\\
+		0 & 0 & 0 &  p_z\\
+	\end{array} 	
+	\right).
+\end{equation}
+The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability.
+We can formulate this problem in analogously to the generator approach.
+The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.
+
+In the remainder of this paper, we will formalize this process, presenting explicit convex optimizations to both generate a family of unitary controls and construct the optimal weighting vector.
+We will discuss how one might include additional desiderata, including a reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the mixed gate.
+
+% \subsection{A simple example}
+% \label{sec:simple_example}
+% \noindent As a simple example of a mixed quantum gate, consider a single-qubit and two distinct implementations of a dynamically decoupled identity gate.
+Suppose that some control parameter, $\eta$, is prone to drift, causing each of these implementations to suffer a distinct, spurious phase error.
+These errors are equivalent to a small rotations about the $\sigma_z$ axis with angles $\theta = \{-\eta, 2\eta\}$.
+% % The resulting diamond distance errors and average gate fidelities of these four implementations are summarized in the following table:
+% % \begin{center}
+% % \begin{tabular}{|c|c|c|}
+% % 	\hline
+% % 	Rotation & Average gate  & Diamond  \\
+% % 	angle &  infidelity & distance \\
+% % 	$\theta$ & $\epsilon_{\mathcal{F}}$ & $\epsilon_{\diamond}$ \\
+% % 	\hline\hline
+% % 	${+2\eta}$ 	& $4\eta^2$  & $2\eta$\\
+% % 	${+\eta}$ 	& $\;\eta^2$ & $\eta$ \\
+% % 	${-\eta}$ 	& $\;\eta^2$ & $\eta$ \\
+% % 	${-2\eta}$ 	& $4\eta^2$  & $2\eta$ \\
+% % 	\hline
+% % \end{tabular}
+% % \end{center}
+% % In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
+Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
+More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
+% The error operators are then all of the form:
+% \begin{equation}
+% \mathcal{E}(\theta) = \exp(\theta \mathcal{L}_z) =
+% 	\left(\begin{array}{ccccc}
+% 		1 & 0 & 0 & 0 \\ 
+% 		0 & \cos\theta & \sin\theta  & 0  \\
+% 		0 & -\sin\theta & \cos\theta & 0  \\
+% 		0 & 0 & 0 & 1
+% 	\end{array} 	
+% 	\right) 
+% \end{equation}
+% Where the z-axis generator, $\mathcal{L}_z$ is:
+% \begin{equation}
+% 	\mathcal{L}_z =
+% 	\left(\begin{array}{ccccc}
+% 		0 & 0 & 0 & 0 \\ 
+% 		0 & 0 & -1  & 0  \\
+% 		0 & 1 & 0 & 0  \\
+% 		0 & 0 & 0 & 0
+% 	\end{array} 	
+% 	\right).
+% \end{equation}
+% The diamond distance associated with such an error is $\epsilon_\diamond(\mathcal{E}(\theta)) \simeq \theta$, while the fidelity is $\epsilon_\mathcal{F}(\error(\theta)) \simeq \theta^2$.
+Because 0 lies in the covex hull of the Following the Campbell procedure, we would assign weights $w = $
+
+% If we were construct two channels, one with error $\error(\eta)$ and one with error $\error(-\eta)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\eta) + \error(\eta)\right)$.
+The effective channel then has a matrix representation:
+% \begin{equation}
+% 	\error(\eta) =
+% 	\left(\begin{array}{ccccc}
+% 		1 & 0 & 0 & 0 \\ 
+% 		0 & \cos\eta & 0  & 0  \\
+% 		0 & 0 & \cos\eta & 0  \\
+% 		0 & 0 & 0 & 1
+% 	\end{array} 	
+% 	\right) \simeq \mathcal{I} - 
+% 	\left(\begin{array}{ccccc}
+% 		0 & 0 & 0 & 0 \\ 
+% 		0 & \eta^2/2 & 0  & 0  \\
+% 		0 & 0 & \eta^2/2 & 0  \\
+% 		0 & 0 & 0 & 0
+% 	\end{array} 	
+% 	\right)
+% \end{equation}
+% And with same average process fidelity, $\eta^2$, but now a suppressed diamond norm $\eta^2$. Now write this in terms of the error generators $\error(\eta) = \exp(\eta G)$ where
+% \begin{equation}
+% 	G =
+% 	\left(\begin{array}{ccccc}
+% 		0 & 0 & 0 & 0 \\ 
+% 		0 & 0 & -1  & 0  \\
+% 		0 & 1 & 0 & 0  \\
+% 		0 & 0 & 0 & 0
+% 	\end{array} 	
+% 	\right)
+% \end{equation}
+
+% The effective generator vanishes at first order.
+
+% In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
+% \begin{align}
+% 	\mathcal{M}_{jk} 
+% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
+% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
+% 		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
+% 		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
+% \end{align}
+% The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
+The result would be a purely stochastic channel.
+
 % The problem of minimizing the last term:
@@
 % ==============================================================================
-\section{Constructing Useful mixed quantum gates}
+\section{Constructing mixed quantum gates}
 \label{sec:mixed_unitary_processes}
-Motivated by the simple example provided in Section \ref{sec:simple_example}, we would like a general methodology for producing \textit{useful} mixed quantum channels.
-In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
+\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above.
+As mentioned, our method requires two steps.
+The first is a control synthesis step, in which we construct an ensemble of gate implementations.
+Campbell and Hastings draw their ensembles from various different gate compilations, but for this work, we use quantum optimal control theory to produce these ensembles.
+By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates.
+We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
+We note that advanced quantum control protocols may provide a more principled approach to control synthesis.
+DMORPH [Rabiz and Dominey], for example, allows one to explore families of controls on fidelity level sets.
+
+The remainder of this section will focus on the second step, constructing the optimal weight vector to reduce the coherence of the effective error channel.
+We will begin by discussing two classes of optimization targets, i) cancelation of the first-order generator, and ii) elimination of the off-diagonal elements of the error channel.
+We then discuss a set of additions to the numerical optimization that can improve the performance by i) adding robustness to drift,  ii) targeting low-error rate solutions, and iii) reducing the number of native unitaries that comprise the effective channel.
+
+% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
 In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
@@
 Our approach, on the other hand, guarantees that the resulting MQC is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
+\note{what does this mean?}
 % subsection off_diagonals (end)
@@
 \begin{split}
-&\underset{n\in[N]}{\textbf{minimize}}\{\\
+&\underset{n\in[N]}{\textbf{minimize}}\\
 &\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega|| + t\\
 &\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0\\
-&\}
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0
 \end{split}
@@
 Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
-\bibliography{decorrelation.bib}
+\bibliography{mixed_unitaries.bib}
 

### 2019-05-22 decorrelation/mixed_unitaries.tex
bibliography, cleaning up, and the like

@@
 We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates.
-Finally, we implement these mixed quantum gate on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
+Finally, we implement these mixed quantum gates on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
 {[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
@@
 \label{sec:introduction}
-\noindent The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs).
-Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices.
-While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached.
-A critical limiting factor, of course, is errors in the quantum gate operations.
-\note{I think we can just strike this whole paragraph.
-I hate these introductions.}
-
-The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
+\noindent The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
 Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
@@
 Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error.
-So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \note{cite Debbie Leung}, which has significiantly less coherent error than any single compilation on its own.
+So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which has significantly less coherent error than any single compilation on its own.
 A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.
-We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts.
-\note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion?
-We should also discuss randomized compiling there.
-}
 
 In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations.
-We demonstrate that, depending on the objective, different numerical optimization targets may be preferred.
+We demonstrate that, depending on what properties of the resulting channel are desired, different numerical optimization targets may be preferred.
 We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
@@
 We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
-The resulting convex optimizations can be performed quickly and efficiently.
-\note{This paragraph is pretty good, but should be cleaned up a bit.}
 
@@
 
-CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
+CPTP maps possess a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
 But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
@@
 \end{equation}
-Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
+Process matrices written in the Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
 \begin{equation}\label{eq:process_matrix}
@@
 The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}.
-If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
+If the error map is unitary, then the error is called \textit{coherent} , and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
 Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
@@
 \subsection{Mixed Quantum Gates}
-\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
+\noindent Now suppose that we have access to an ensemble of different implementations of the target gate, $\{\mathsf{\tilde G}_i\}$.
 % , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
-Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
+Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde{G}}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
 This procedure is operationally indistinguishable from always applying the effective operation,
@@
 	\label{eq:def_agi}
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathsf{E}}}{d^2 + d},\\
 	\label{eq:def_diamond}
@@
 where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
-In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
-If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \note{[Wallman - Error rates in quantum circuits]}.
-The diamond distance is subaddative \note{[Watroos TQI book]} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \note{[Aharanov, Kitaev, Nisan, 1998]}.
+In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$, in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
+If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}.
+The diamond distance is subaddative \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \cite{aharonov1998quantum}.
 
@@
 Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target.
-Explicitly, the weight are chosen such that the error generator is canceled to first order.
+Explicitly, the weights are chosen such that the error generator is canceled to first order.
 Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
@@
 \end{align}
-If the error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
+If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
 Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians.
@@
 a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no 0MQCs.
+The origin is not contained in their convex hull, so there are no 0MQGs.
 b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of 0MQCs.
+Because there are more than $n+1$ implementations, there exist an infinite number of 0MQGs.
 c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a 0MQC may drift, leading to a first-order error.
+As this parameter drifts, a 0MQG may drift, leading to a first-order error.
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a 1MQC.}
+If the origin lies in their convex hull, then it may be possible to construct a 1MQG.}
   \label{fig:vectorspace}
@@
 The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability.
-We can formulate this problem in analogously to the generator approach.
+We can formulate this problem analogously to the generator approach.
 The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.
@@
 The first is a control synthesis step, in which we construct an ensemble of gate implementations.
-Campbell and Hastings draw their ensembles from various different gate compilations, but for this work, we use quantum optimal control theory to produce these ensembles.
+Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use quantum optimal control theory to produce these ensembles.
 By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates.
@@
 We note that advanced quantum control protocols may provide a more principled approach to control synthesis.
-DMORPH [Rabiz and Dominey], for example, allows one to explore families of controls on fidelity level sets.
+DMORPH \cite{dominy2008exploring}, for example, allows one to explore families of controls on fidelity level sets.
 
@@
 As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
-In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQC for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
+In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 
-If our primary goal is for our MQC to have increased worst-case performance, then a useful target for constructing MQCs is to minimize the diamond norm.
+If our primary goal is for our MQG to have increased worst-case performance, then a useful target for constructing MQGs is to minimize the diamond norm.
 The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
 However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQC with error generators $\{G_j\}$ to first order is:
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{G_j\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 \end{equation}
-In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQC with this property.
+In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQG with this property.
 Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
 In these situations, one can use convex optimization to solve this problem.
-Given a collection of controls in our MQC, each will have an associated error channel $\error_i$ given by $\error_i\actual_i=\target$.
-We can then consider the matrix whose columns are the vectorized generators of the error channels for each control, i.e.
-$G_i$ such that $e^{G_i}=\error_i$.
-Then we will have $m$, $n\times n$ generators:
+Given a collection of controls in our MQG, we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
 \begin{equation}\label{eq:vectorized_generators}
-	\bold{G} = \left(\begin{array}{cccc}
-		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
+	\bold{H} = \left(\begin{array}{cccc}
+		H_{1_{1,1}} & H_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
+		H_{1_{n,n}} &  &  H_{m_{n,n}} \\ 
 	\end{array} 	
@@
 \end{equation}
-If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
+If our weighting vector for our MQG is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
 Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{G}\omega||_2\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{H}\omega||_2\\
   \end{split}
@@
 
-%Another interesting property of the MQC given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
 In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
@@
 In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MQCs.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
 
@@
 Of course, there are other properties of a channel that one might consider optimizing.
-Instead of minimizing the diamond norm, we might want our resulting MQC to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
+Instead of minimizing the diamond norm, we might want our resulting MQG to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
 We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
@@
 \end{equation}
-then again we consider the same minimization problem, where we replace $\bold{G}$ with $\bold{R}$:
+then again we consider the same minimization problem, where we replace $\bold{H}$ with $\bold{R}$:
 
@@
 Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, however this requires multiple evaluations of the diamond norm, and in particular does not have the restriction that the resulting channel be decomposable into a given family of controls.
-Our approach, on the other hand, guarantees that the resulting MQC is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
+Our approach, on the other hand, guarantees that the resulting MQG is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
 \note{what does this mean?}
@@
 While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
-Because of this drift, the quality of the MQC will degrade.
-Thus, we would like to design MQCs that are robust to this drift.
+Because of this drift, the quality of the MQG will degrade.
+Thus, we would like to design MQGs that are robust to this drift.
 To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
@@
 If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
-\begin{equation}\label{eq:MQC}
+We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
+\begin{equation}\label{eq:MQG}
 \begin{gathered}
@@
 \end{equation}
-In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}.
-More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
-To see this, we can rewrite the error on each control in the MQC as:
+In particular, we see that a 0MQG satisfies Equation \ref{eq:campbell-condition}.
+More generally, these conditions imply that an $\ell$MQG is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
+To see this, we can rewrite the error on each control in the MQG as:
 \begin{equation}\label{eq:taylor}
@@
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQC will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQC} as:
-\begin{equation}\label{eq:MQC-relaxed}
+By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
+Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQG} as:
+\begin{equation}\label{eq:MQG-relaxed}
 \begin{gathered}
@@
 Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
-We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC.
- Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.
+We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
+ Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQG.
 To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
@@
 
-%Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family.
-However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQC uses just five of the controls.
+%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
+However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
 % ==============================================================================
@@
 As a practical consideration, we would also like to regularize our objective function to penalize for non-sparse weightings.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs only require a small number of controls.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MQGs only require a small number of controls.
 As an example, consider Figure \ref{fig:vectorspace}.
 In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that a $0$MQC, ignore $H_4$.
-However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
+Thus we would prefer that a $0$MQG, ignore $H_4$.
+However, if we additionally want our controls to form a 1MQG, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
 Thus we would like to be frugal in which controls we select.
@@
 For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-In both the 0MQC and the 1MQC case in our numerical implementation in Section \ref{sub:experimental} we impose the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constraint made the 0MQC perform better at the origin by nearly an order of magnitude, and moved the 1MQC from being out-performed by the 0MQC for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
+In both the 0MQG and the 1MQG case in our numerical implementation in Section \ref{sub:experimental} we impose the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
 Imposing this constraint allows us to trade off flatness at the origin for performance at the origin.
-This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.
+This shows that through adding constraints to our optimization routine, we can make the MQG practically useful.
 \section{Results} % (fold)
@@
 In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an MQC on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement an MQG on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
 As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
-To benchmark the quality of the MQC, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
+To benchmark the quality of the MQG, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
 We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
@@
 The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MQC, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
+Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MQG, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
 \begin{figure}[t]
@@
 It displays improved average survival probability as well as reduced variance.
-The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQC composed of Pulse1 through Pulse4.
+The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQG composed of Pulse1 through Pulse4.
 It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
-The reduced variance of the MQC is a tell-tale sign of reduced coherent error in the effective channel.
+The reduced variance of the MQG is a tell-tale sign of reduced coherent error in the effective channel.
 }
@@
 We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MQC better than the constituent gates, it also has a signicantly less-coherent error channel.
+Thus, our experiment demonstrates that not only is the performance of the MQG better than the constituent gates, it also has a signicantly less-coherent error channel.
 % subsection experimental (end)
@@
 \label{sec:numerical_results}
-In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MQCs. We consider the following model for a single tunable qubit: 
+In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs. We consider the following model for a single tunable qubit: 
 \begin{equation}\label{eq:1Qham}
@@
 We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
-Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MQCs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQC}.
-These results demonstrate several properties that make MQCs both useful and tractable.
+Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MQGs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
+These results demonstrate several properties that make MQGs both useful and tractable.
 
@@
   \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{Numerical results comparing a 0MQC to a 1MQC for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+  \caption{Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
 The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
-In this case the 0MQC outperforms both the 1MQC by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MQC outperforms the 0MQC by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
-  \label{fig:YMQC}
+In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
+However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+  \label{fig:YMQG}
 \end{figure}
@@
 
-In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MQC}.
+In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MQG}.
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using an MQC improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
-For all values of the drifting parameters we see that the 1MQC performs as well or better than 0MQC.
+Nonetheless, using an MQG improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+For all values of the drifting parameters we see that the 1MQG performs as well or better than 0MQG.
 
@@
   \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
-  \caption{Numerical results comparing a 0MQC to a 1MQC for a pair of tunable qubits, with a resonant exchange interaction.
+  \caption{Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.
 Shown with lower alpha values are example constituent controls.
-The 0MQC and 1MQC can be seen to outperform these controls by half of an order of magnitude at the origin.
-For all detuning values the 1MQC performs as well or better than the 0MQC.
-When there is $.2\%$ drift in the qubit frequency, the 1MQC outperforms members of the control famlies by almost an order of magnitude in diamond norm.
-Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQC outperforms the the constituent controls by over half an order of magnitude.}
-  \label{fig:2MQC}
+The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin.
+For all detuning values the 1MQG performs as well or better than the 0MQG.
+When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
+  \label{fig:2MQG}
 \end{figure}
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using MQCs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+We have shown numerically that using MQGs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
+
+We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts.
+\note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion?
+We should also discuss randomized compiling there.
+}
 

### 2019-06-17 decorrelation/mixed_unitaries.tex
various and manifold changes

@@
 \noindent The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
-Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP.
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor or QIP.
 Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
@@
 
-The remainder of this section will focus on the second step, constructing the optimal weight vector to reduce the coherence of the effective error channel.
+The remainder of this section will focus on the second step constructing the optimal weight vector to reduce the coherence of the effective error channel.
 We will begin by discussing two classes of optimization targets, i) cancelation of the first-order generator, and ii) elimination of the off-diagonal elements of the error channel.
@@
 
-If our primary goal is for our MQG to have increased worst-case performance, then a useful target for constructing MQGs is to minimize the diamond norm.
+If our primary goal is for our MQG to have better worst-case performance, then a useful optimization target is minimizing the diamond norm.
 The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
@@
 \end{equation}
-In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, generates controls and weightings to find an MQG with this property.
-Alternatively one might ask the question: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
+In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle to approximate arbitary unitary operations, generates controls and weightings to find an MQG with this property.
+Alternatively one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
 In these situations, one can use convex optimization to solve this problem.
-Given a collection of controls in our MQG, we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
+Given an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
 \begin{equation}\label{eq:vectorized_generators}
-	\bold{H} = \left(\begin{array}{cccc}
-		H_{1_{1,1}} & H_{2_{1,1}} & \ldots   \\ 
+	\bold{G} = \left(\begin{array}{cccc}
+		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		H_{1_{n,n}} &  &  H_{m_{n,n}} \\ 
+		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
 	\end{array} 	
@@
 \end{equation}
-If our weighting vector for our MQG is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero.
-Additionally, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
-This forms a convex optimization problem, and can be written as:
+Then to satisfy Equation \ref{eq:campbell-condition}, we can write the sum as a matrix product and solve the following optimization problem, where the two-norm will be zero if and only if the sum is zero:
 
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{H}\omega||_2\\
+    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{G}\omega||_2\\
   \end{split}
@@
 
-Linearly constrained minimization problems with quadratic cost functions like this have been proven to be efficiently solvable by methods like the Elipsoid Method\cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice.
+As noted, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
+Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by methods like the Elipsoid Method \cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice.
 
@@
 \label{sub:off_diagonals}
-Of course, there are other properties of a channel that one might consider optimizing.
-Instead of minimizing the diamond norm, we might want our resulting MQG to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
-We can write this error channel as a process matrix, vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
+There are other properties of a channel that one might consider optimizing instead of minimizing the diamond norm.
+For instance, we might want our MQG to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
+We can vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
 
@@
 \end{equation}
-then again we consider the same minimization problem, where we replace $\bold{H}$ with $\bold{R}$:
+and then again consider the minimization problem in Equation \ref{eq:minimization}, where we replace $\bold{G}$ with $\bold{R}$:
 
@@
 
-Previous authors have considered minimizing the diamond distance to the nearest Pauli or Clifford Channel \cite{Magesan2013}, however this requires multiple evaluations of the diamond norm, and in particular does not have the restriction that the resulting channel be decomposable into a given family of controls.
-Our approach, on the other hand, guarantees that the resulting MQG is able to be implemented with the available controls, and is an easy-to-solve quadratic program.
-\note{what does this mean?}
+The resulting MQG will be, to first order, the closest Pauli Channel that can be produced by mixing over the available gate implementations.
+Previous authors have considered finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013}, but this does not have the restriction that the resulting channel be decomposable into a given family of controls.
+
 % subsection off_diagonals (end)
@@
 Thus, we would like to design MQGs that are robust to this drift.
-To enforce robustness, we can consider higher derivatives of the generators in Equation \ref{eq:campbell-condition}.
-Instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
-If our control generator is parameterized by a vector $\vec{\delta}$, then the quantity we will be interested in is:
+To enforce robustness, we can consider the generators in Equation \ref{eq:campbell-condition} to be functions of a control vector $\vec{\delta}$, and instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+Specifically, we are interested in the $n^{th}$ order derivatives:
 \begin{equation}
-D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}G_j(\vec{\delta})|_{\delta=\vec{0}}
+D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}\mathcal{L}_j(\vec{\delta})|_{\delta=\vec{0}}
 \end{equation}
@@
 More generally, these conditions imply that an $\ell$MQG is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
-To see this, we can rewrite the error on each control in the MQG as:
+To see this, we can rewrite the implementations of the target gate as:
 \begin{equation}\label{eq:taylor}
 \begin{gathered}
-\actual_j(\vec{\delta}) = \exp(-i(G_j(\vec{0}) + \frac{\partial}{\partial\delta_i}G_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} G_j(d\delta_i d\delta_k) + \ldots))\target
+\actual_j(d\vec{\delta}) = \exp(-i(\mathcal{L}(\vec{0}) + \frac{\partial}{\partial\delta_i}\mathcal{L}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \mathcal{L}(d\delta_i d\delta_k) + \ldots))\target
 \end{gathered}
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQG} as:
+By Taylor expanding Equation \ref{eq:taylor} in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
+Furthermore, if we are only interested in being first order insensitive to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQG} as:
 \begin{equation}\label{eq:MQG-relaxed}
@@
 \end{equation}
-This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$.
+This condition guarantees that errors will be surpressed quadratically for all derivatives up to order $\ell$.
 %A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
@@
 We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
- Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQG.
-To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
+As discussed in \cite{Campbell2017}, the geometric picture for the first-order suppression of the diamond norm is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
+Figure \ref{fig:vectorspace} generalizes this picture to $\ell$MQGs and gives intuition for the conditions required to produce them.
+To produce $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
 \begin{equation}
@@
 with $D_n^j$ defined in Equation \ref{eq:taylor}.
-The size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the time required to solve the optimization problem will depend on the particular optimizer and algorithm used.
 
@@
 \label{sec:norm}
-While up until this point, these particular convex optimization problem could be solved using a system of linear equations, casting them as convex optimization problems allows us to penalize the cost function to encourage different behavior in the solution.
-In particular, while this minimization problem is sufficient for supressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-That is to say, both \{$U_{+2\epsilon}$, $U_{-2\epsilon}$\} and \{$U_{\epsilon}$, $U_{-\epsilon}$\} from Section \ref{sec:simple_example} satisfy Equation \ref{eq:minimization}.
+Up until this point the convex optimization problems discussed have known analytic solutions, however casting them as convex optimization problems allows us to add penalty terms to the cost function to promote different properties of our MQG.
+In particular, while this minimization problem is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+As an example, any MQG that mixes equally over equal and opposite errors will satisfy Equation \ref{eq:minimization}, but depending on the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent error.
 To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
-In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm, and thus we modify our cost function to be:
+In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
 
@@
 with $\eta \geq 0$.
-By varying $\eta$, we encourage the optimizer to include better controls in addition to minimizing the diamon norm.
-The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$.
+By increasing $\eta$, we encourage the optimizer to include better controls while minimizing the diamond norm.
+The value of $\eta$ that is best for any particular problem instance depends on the values in $\bold{D}^\ell$.
 
@@
 As an example, consider Figure \ref{fig:vectorspace}.
-In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that a $0$MQG, ignore $H_4$.
-However, if we additionally want our controls to form a 1MQG, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
-Thus we would like to be frugal in which controls we select.
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain the one norm of $\omega$ to be one.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+In b), it is clear that $H_4$ is unnecessary to contain the origin in the convex hull of the error generators.
+Thus we would prefer that a $0$MQG exclude $H_4$.
+However, if we additionally want our controls to form a 1MQG, we see from d) that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
+
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\omega$ to be a valid probability distribution.
+The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
 

### 2019-06-18 decorrelation/mixed_unitaries.tex
Addded ASCR statement

--- 2019-05-21 decorrelation/mixed_unitaries.tex
@@
 \newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
-\newcommand{\note}[1]{{\color{red}[#1]}}
+% \newcommand{\note}[1]{{\color{red}[#1]}}
+\newcommand{\note}[1]{}
 \newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
@@
 \label{sec:acknowledgements}
+This material was funded in part by the U.S.
+Department of Energy, Office of Science, Office of Advanced Scientific Computing Research Quantum Testbed Program.
 Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S.

### 2019-06-25 decorrelation/mixed_unitaries.tex
more changes

--- 2019-06-17 decorrelation/mixed_unitaries.tex
@@
 \noindent The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
-Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor or QIP.
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor (QIP).
 Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
 They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}.
-Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment.
+Contrast this against random, or \emph{stochastic}, errors which often result from high-frequency noise in the controls or the environment.
 Systems with stochastic errors can usually be accurately modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips.
@@
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, the qubits experience errors.
-If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
+If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
 This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
@@
 \end{equation}
-The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}.
+The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \cite{preskill1997lecture}.
 If the error map is unitary, then the error is called \textit{coherent} , and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
@@
 \end{equation}
-Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
+Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{watrous2018theory}, defined as:
 \begin{align}
 	\label{eq:def_agi}
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathsf{E}}}{d^2 + d},\\
+	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
 	\label{eq:def_diamond}
@@
 where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
-In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$, in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
+In \ref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$, in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
 If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}.
@@
 \end{equation}
-That is, the AGI of the mixed quantum gate is simply the weighted average of the component AGIs, so there is no hope of reducing the AGI by combining various implementations.
+That is, the AGI of the MQG is simply the weighted average of the component AGIs, so there is no hope of reducing the AGI by combining various implementations.
 However, the diamond distance is a nonlinear function of error map.
@@
 Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.
-Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target.
+Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a MQG with quadratically suppressed diamond distance to the target.
 Explicitly, the weights are chosen such that the error generator is canceled to first order.
-Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
+Using (\ref{eq:effective_error} )and (\ref{eq:generator}), the effective error map for a MQG in terms of the component error generators is:
 \begin{align}
@@
 If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
-Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians.
+Campbell considered error channels that were strictly unitary, so the error generators in \ref{eq:cancel} were Hamiltonians.
 Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull.
-If, however, the error map contains stochastic components, then the condition of Eq.~\ref{eq:cancel} might be impossible to satisfy.
+If, however, the error map contains stochastic components, then the condition of \ref{eq:cancel} might be impossible to satisfy.
 Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull.
-This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators.
+This can be rectified by restricting the sum in \ref{eq:cancel} to only the Hamiltonian component of the generators.
 In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.
@@
 The origin is not contained in their convex hull, so there are no 0MQGs.
-b) The origin is contained in the covex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations, there exist an infinite number of 0MQGs.
+b) The origin is contained in the convex hull after adding an additional control solution.
+Because there are more than $n+1$ implementations (n=3), there exist an infinite number of 0MQGs.
 c) The error Hamiltonians shown with their derivative with respect to a control parameter.
@@
 We can formulate this problem analogously to the generator approach.
-The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.
+The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.
 
@@
 
-The remainder of this section will focus on the second step constructing the optimal weight vector to reduce the coherence of the effective error channel.
+The remainder of this section will focus on the second step of constructing the optimal weight vector to reduce the coherence of the effective error channel.
 We will begin by discussing two classes of optimization targets, i) cancelation of the first-order generator, and ii) elimination of the off-diagonal elements of the error channel.
@@
 If our primary goal is for our MQG to have better worst-case performance, then a useful optimization target is minimizing the diamond norm.
-The diamond norm is a non-linear function that in general requires a convex optimizer to compute.
-However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
+The diamond norm is a non-linear function that in general requires a convex optimizer to compute\cite{watrous2018theory}.
+However, if our errors are small enough we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
 As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{G_j\}$ to first order is:
@@
 In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle to approximate arbitary unitary operations, generates controls and weightings to find an MQG with this property.
-Alternatively one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we randomly generate a collection of gate implementations.
-In these situations, one can use convex optimization to solve this problem.
-Given an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
+Alternatively one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
+Given such an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
 \begin{equation}\label{eq:vectorized_generators}
@@
 \end{equation}
-Then to satisfy Equation \ref{eq:campbell-condition}, we can write the sum as a matrix product and solve the following optimization problem, where the two-norm will be zero if and only if the sum is zero:
+To satisfy (\ref{eq:campbell-condition}), we can write the sum as a matrix product and solve the following optimization problem, which will be zero if and only if the sum is zero:
 
@@
 
-As noted, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
-Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by methods like the Elipsoid Method \cite{wright1999numerical, khachiyan}, and there are many existing convex solver software packages that solve these problems efficiently in practice.
+As denoted, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
+Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by methods like the Elipsoid Method \cite{wright1999numerical, khachiyan}.
+More importantly, there are many existing convex solver software packages that solve these problems efficiently in practice.
 
@@
 \label{sub:off_diagonals}
-There are other properties of a channel that one might consider optimizing instead of minimizing the diamond norm.
-For instance, we might want our MQG to have an error channel that is well-approximated by a Pauli-Stochastic channel, so that the error on our channel is amenable to classical simulation.
-We can vectorize the $R$ submatrices in Equation \ref{eq:process_matrix}, and consider the matrix of off-diagonal terms:
+There are other properties of a channel that one might consider optimizing.
+For instance, if an MQG has an error channel that is well-approximated by a Pauli-Stochastic channel, then it may be amenable to classical simulation.
+We can modify our optimization problem accordingly.
+By vectorizing the $R$ submatrices in (\ref{eq:process_matrix}), and considering the matrix of off-diagonal terms, we can :
 
@@
 \end{equation}
-and then again consider the minimization problem in Equation \ref{eq:minimization}, where we replace $\bold{G}$ with $\bold{R}$:
+and then again consider the minimization problem in (\ref{eq:minimization}), where we replace $\bold{G}$ with $\bold{R}$:
 
@@
 Thus, we would like to design MQGs that are robust to this drift.
-To enforce robustness, we can consider the generators in Equation \ref{eq:campbell-condition} to be functions of a control vector $\vec{\delta}$, and instead of only requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and instead of requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
 Specifically, we are interested in the $n^{th}$ order derivatives:
 \begin{equation}
-D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}\mathcal{L}_j(\vec{\delta})|_{\delta=\vec{0}}
+\label{eq:derivative}
+D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}\mathcal{L}_j(\vec{\delta})|_{\vec{\delta}=\vec{0}}
 \end{equation}
@@
 \end{equation}
-In particular, we see that a 0MQG satisfies Equation \ref{eq:campbell-condition}.
-More generally, these conditions imply that an $\ell$MQG is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$.
+In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}).
+More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$.
 To see this, we can rewrite the implementations of the target gate as:
@@
 \begin{gathered}
-\actual_j(d\vec{\delta}) = \exp(-i(\mathcal{L}(\vec{0}) + \frac{\partial}{\partial\delta_i}\mathcal{L}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \mathcal{L}(d\delta_i d\delta_k) + \ldots))\target
+\tilde{\mathcal{G}_j}(d\vec{\delta}) = \exp(-i(\mathcal{L}(\vec{0}) + \frac{\partial}{\partial\delta_i}\mathcal{L}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \mathcal{L}(d\delta_i d\delta_k) + \ldots))\mathcal{G}
 \end{gathered}
 \end{equation}
-By Taylor expanding Equation \ref{eq:taylor} in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore, if we are only interested in being first order insensitive to drift and can find controls such that $|D_j^n|\leq\epsilon$, we can approximate Equation \ref{eq:MQG} as:
+By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
+Furthermore if we can find controls such that $|D_j^n|\leq\epsilon$, we can approximate (\ref{eq:MQG}) as:
 \begin{equation}\label{eq:MQG-relaxed}
@@
 \end{equation}
-This condition guarantees that errors will be surpressed quadratically for all derivatives up to order $\ell$.
+This condition guarantees that errors will be suppressed to second order for all derivatives up to order $\ell$.
 %A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
@@
 We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
-As discussed in \cite{Campbell2017}, the geometric picture for the first-order suppression of the diamond norm is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
-Figure \ref{fig:vectorspace} generalizes this picture to $\ell$MQGs and gives intuition for the conditions required to produce them.
-To produce $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_generators}:
+As discussed in \cite{Campbell2017}, the geometric picture for 0MQGs is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
+Figure \ref{fig:vectorspace} generalizes this picture to 1MQGs and gives intuition for the conditions required to produce them.
+To produce $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
 \begin{equation}
@@
 
-Using this, we can then solve the following convex optimization problem, generalizing Equation \ref{eq:minimization}:
+Using this, we can then solve the following convex optimization problem, generalizing (\ref{eq:minimization}):
 
@@
 \end{equation}
-with $D_n^j$ defined in Equation \ref{eq:taylor}.
+with $D_n^j$ defined in (\ref{eq:derivative}).
 
@@
 \label{sec:norm}
-Up until this point the convex optimization problems discussed have known analytic solutions, however casting them as convex optimization problems allows us to add penalty terms to the cost function to promote different properties of our MQG.
-In particular, while this minimization problem is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-As an example, any MQG that mixes equally over equal and opposite errors will satisfy Equation \ref{eq:minimization}, but depending on the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent error.
-To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
+Up until this point the convex optimization problems discussed can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
+In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but depending on the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent error.\note{Just give an explicit example.} To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
 In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
@@
 \begin{split}
-&\underset{n\in[N]}{\textbf{minimize}}\{\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||+ \eta\sum\omega_j||D^0_j||_2\\
+& \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||+ \eta\sum\omega_j||D^0_j||_2\\
 &\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
-&\}
 \end{split}
@@
 with $\eta \geq 0$.
-By increasing $\eta$, we encourage the optimizer to include better controls while minimizing the diamond norm.
-The value of $\eta$ that is best for any particular problem instance depends on the values in $\bold{D}^\ell$.
+By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
+The value of $\eta$ that is best for any particular problem instance will depend on the values in $\bold{D}^\ell$.
 
@@
 
-As a practical consideration, we would also like to regularize our objective function to penalize for non-sparse weightings.
+As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
 Control electronics often have a limited amount of waveform memory, and thus it is important that MQGs only require a small number of controls.
@@
 In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\omega$ to be a valid probability distribution.
-The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
+The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
 
@@
 \end{split}
-\end{equation} with $\lambda\geq0$.
-As with $\eta$ in the last subsection, the optimal value of this parameter is problem specific, depending on $\bold{D}^\ell$, and how sparse the solution needs to be.
-For $\lambda$ small, the problem reduces to the original problem, and for $\lambda$ large we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
-In both the 0MQG and the 1MQG case in our numerical implementation in Section \ref{sub:experimental} we impose the same $\ell_2$ penalty, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
-Imposing this constraint allows us to trade off flatness at the origin for performance at the origin.
-This shows that through adding constraints to our optimization routine, we can make the MQG practically useful.
+\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\bold{D}^\ell$ and how sparse the solution needs to be.
+
+For small $\lambda$, the sparsity penalty is negligible, and for large $\lambda$ we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
+In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
+
 \section{Results} % (fold)
@@
 \label{sub:experimental}
-Here we present experimental results from implementing this routine on a fixed-frequency superconducting transmon qubit.
-In particular, we used qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an MQG on this qubit, four incorrectly calibrated Gaussian pulses were produced by scaling the pulseshape amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+Here we present experimental results from implementing this routine on a fixed-frequency, superconducting transmon qubit.
+In particular, we use qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
+To implement an MQG on this qubit, four miscalibrated Gaussian pulses were produced by scaling the amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
-As discussed in the previous section, we chose here to minimize the off diagonal elements of the process matrix.
+As discussed in Section \ref{sub:off_diagonals}, we chose to minimize the off diagonal elements of the process matrix.
 To benchmark the quality of the MQG, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
-We used $1000$ shots per experiment, $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
-In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$) and RY($\frac{\pi}{2})$) pulses.
+We used $1000$ shots per experiment and $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
+In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$ and RY($\frac{\pi}{2})$.
 In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
@@
 
-Additionally, by minimizing the off-diagonal elements of the process matrix, we expect to produce a process with minimal coherent error.
+More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with supressed coherent error.
 To see that this is the case, we cite the results in \cite{Ball2016}.
@@
 In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated, as is the case in systems that implement RZ rotations with phase shifts of the control signal.
-Solving the optimization problem defined in Section \ref{sec:robustly_mixed} yields similar MQGs for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
-These results demonstrate several properties that make MQGs both useful and tractable.
+We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfectly correlated.
+Additionally, we impose the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
+Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
+Imposing this constraint allows us to trade off flatness at the origin for performance at the origin.
+This shows that through adding constraints to our optimization routine, we can make the MQG practically useful.
+The MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
 
@@
 For all detuning values the 1MQG performs as well or better than the 0MQG.
-When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control famlies by almost an order of magnitude in diamond norm.
+When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm.
 Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
@@
 We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts.
-\note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion?
-We should also discuss randomized compiling there.
-}
+In \cite{Viola2005, Santos2006} the usage of randomness is discussed in the context of dynamical decoupling.
+In particular, it's shown that both stochastic and hybrid approaches can result in better or more feasible coherent controls.
+Additionally Pauli Frame Randomization\cite{Wallman2016} has been demonstrated \cite{1803.01818} to reduce coherent errors by introducing randomness in a pre-compilation step.
+The techniques discussed in this paper are different from both of these approaches in that they explicitly produce incoherent errors through mixing, and that the randomness is hardware efficient for any desired gate.
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a precompilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 
@@
 for more than a few qubits.
-
-In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nealder-Mead to perform the minimization.
-While performing a complete optimization in this way would require full process tomography, one could intead optimize via partial tomography.
+In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nelder-Mead to perform the minimization.
+While performing a complete optimization in this way would require full process tomography, one could instead optimize via partial tomography.
 By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
@@
 The nuclear norm above is equal to the sum of the singular values of $\sum_i w_i \rho_i$.
-Using the Ky Fan singular value inequality [K.
-Fan, Maximum properties and inequalities for the eigenvalues of completely continuous operators, Proc.
-Nat.
-Acad.
-Sci.
-U.S.A.
-37 (1951), 760–766] , we have
+Using the Ky Fan singular value inequality \cite{fan1951maximum} , we have
 \begin{align}

### 2019-06-27 decorrelation/mixed_unitaries.tex
last changes from most recent read thru

@@
 
-More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with supressed coherent error.
-To see that this is the case, we cite the results in \cite{Ball2016}.
-For non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
+More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with suppressed coherent error.
+To see that this is the case, we can observe the drastic reduction in the variance at each point for the MQG relative to the miscalibrated pulses.
+A discussed in \cite{Ball2016}, for non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
 On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
 We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus, our experiment demonstrates that not only is the performance of the MQG better than the constituent gates, it also has a signicantly less-coherent error channel.
+Thus our experiment demonstrates that the MQG has a significantly less-coherent error channel.
 % subsection experimental (end)
@@
 \label{sec:numerical_results}
-In the following numerical results, we explore using the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs. We consider the following model for a single tunable qubit: 
+In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs. We consider the following model for a single tunable qubit: 
 \begin{equation}\label{eq:1Qham}
@@
 \end{equation}
+where $\epsilon$ is a random variable used to model fluctuations in the qubit frequency, and $\delta$ is a random variable used to model fluctuations in the control field.
 We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
-In our implementation, we modify the gradient so that we find controls that perform well in a Gaussian weighted neighborhood, with a standard deviation of $\sigma=.001$.
-We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfectly correlated.
-Additionally, we impose the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
+
+In our implementation, we considered the performance function presented in \cite{Khaneja2005}, and averaged over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that perform well in a neighborhood.
+The standard deviations considered for all random variables in our numerical experiments were fixed to $\sigma=.001$.
+Finally, we assume that the errors on $\sigma_x$ and $\sigma_y$ are perfectly correlated, as in our experimental implementation.
+
+Using controls generated in this way, the MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
+By imposing the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
 Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
@@
 This shows that through adding constraints to our optimization routine, we can make the MQG practically useful.
-The MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
 
@@
 \begin{split}
-H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
+H(\vec{\delta}, \vec{\epsilon}, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^j(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
 &+ \frac{1}{10}(XX + YY)
@@
 In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls.
-To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
+To give the control family a variety of RF errors, we also added uniformly distributed amplitude errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.
 
@@
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using an MQG improves performance by half of an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
+Nonetheless, using an MQG improves performance by half an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
 For all values of the drifting parameters we see that the 1MQG performs as well or better than 0MQG.
@@
 \section{Conclusion and Future Work}
-We have shown numerically that using MQGs can reduce coherent error on a quantum channel by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
+We have shown numerically that using MQGs can reduce coherent error by more than an order of magnitude in diamond norm, over a wide range of quasi-static values of noise.
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
 
-We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts.
-In \cite{Viola2005, Santos2006} the usage of randomness is discussed in the context of dynamical decoupling.
-In particular, it's shown that both stochastic and hybrid approaches can result in better or more feasible coherent controls.
-Additionally Pauli Frame Randomization\cite{Wallman2016} has been demonstrated \cite{1803.01818} to reduce coherent errors by introducing randomness in a pre-compilation step.
+Randomized protocols have a long history of outperforming their deterministic counterparts.
+In \cite{Viola2005, Santos2006} the use of randomness is discussed in the context of dynamical decoupling.
+In particular, it is shown that both stochastic and hybrid approaches can result in better or more tractable coherent controls.
+Additionally Pauli Frame Randomization\cite{Wallman2016} has been shown \cite{1803.01818} to reduce coherent errors by introducing randomness in a pre-compilation step.
 The techniques discussed in this paper are different from both of these approaches in that they explicitly produce incoherent errors through mixing, and that the randomness is hardware efficient for any desired gate.

### 2019-08-02 decorrelation/mixed_unitaries.tex
changing my email to my gmail
more house keeping

@@
 \author{Anthony M. Polloreno}
-\email[Email: ]{anthony@rigetti.com}
+\email[Email: ]{ampolloreno@gmail.com}
 \affiliation{Rigetti Computing, Berkeley, CA}
@@
 Explicitly, the weights are chosen such that the error generator is canceled to first order.
-Using (\ref{eq:effective_error} )and (\ref{eq:generator}), the effective error map for a MQG in terms of the component error generators is:
+Using (\ref{eq:effective_error}) and (\ref{eq:generator}), the effective error map for a MQG in terms of the component error generators is:
 \begin{align}
@@
 	\label{eq:cancel}
-	&\sum_i w_i^* \mathcal{L} = 0
+	&||\sum_i w_i^* \mathcal{L}_i||= 0
 	% \mathrm{with}\;&\sum_i w_i = 1
 \end{align}
+where $||\cdot||$ is meant to mean the Frobenius norm.
+
 If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
@@
 The diamond norm is a non-linear function that in general requires a convex optimizer to compute\cite{watrous2018theory}.
-However, if our errors are small enough we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{G_j\}$ to first order is:
+However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
-\sum \omega_j G_j = 0
+||\sum \omega_i \mathcal{L}_i ||= 0
 \end{equation}
-In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle to approximate arbitary unitary operations, generates controls and weightings to find an MQG with this property.
-Alternatively one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
+In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle to approximate arbitrary unitary operations, generates controls and weightings to find an MQG with this property.
+Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
 Given such an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
 \begin{equation}\label{eq:vectorized_generators}
-	\bold{G} = \left(\begin{array}{cccc}
-		G_{1_{1,1}} & G_{2_{1,1}} & \ldots   \\ 
+	\bold{L} = \left(\begin{array}{cccc}
+		\mathcal{L}_{1_{1,1}} & \mathcal{L}_{2_{1,1}} & \ldots   \\ 
 		\vdots\ & \ddots &    \\
-		G_{1_{n,n}} &  &  G_{m_{n,n}} \\ 
+		\mathcal{L}_{1_{n,n}} &  &  \mathcal{L}_{m_{n,n}} \\ 
 	\end{array} 	
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{G}\omega||_2\\
+    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{L}\omega||_1\\
   \end{split}
 \end{equation}
+where $||\cdot||_1$ is the $\ell_1$ norm.
 
-As denoted, this optimization needs to be constrained so that $\omega \geq 0$ and $|\omega|_1 = 1$.
+As denoted, this optimization needs to be constrained so that $\omega$ is a proper probability distribution.
 Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by methods like the Elipsoid Method \cite{wright1999numerical, khachiyan}.
@@
 We can modify our optimization problem accordingly.
-By vectorizing the $R$ submatrices in (\ref{eq:process_matrix}), and considering the matrix of off-diagonal terms, we can :
+By vectorizing the $R$ submatrices in (\ref{eq:process_matrix}), and considering the matrix of off-diagonal terms, we can again consider the minimization problem in (\ref{eq:minimization}), where we replace $\bold{L}$ with $\bold{R}$:
 
@@
 \end{equation}
-and then again consider the minimization problem in (\ref{eq:minimization}), where we replace $\bold{G}$ with $\bold{R}$:
 
-\begin{equation}\label{eq:minimization_diagonal}
-  \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{R}\omega||_2\\
-  \end{split}
-\end{equation}
-
-The resulting MQG will be, to first order, the closest Pauli Channel that can be produced by mixing over the available gate implementations.
+In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel.
 Previous authors have considered finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013}, but this does not have the restriction that the resulting channel be decomposable into a given family of controls.
@@
 \label{eq:derivative}
-D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}\mathcal{L}_j(\vec{\delta})|_{\vec{\delta}=\vec{0}}
+D^n_i = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
 \end{equation}
-If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that a mixed quantum gate is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
+If the dimension of $\vec{\delta}$ is $d$, the indices $j_0, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
+We say that an MQG is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
 \begin{equation}\label{eq:MQG}
 \begin{gathered}
-\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
+||\sum_i\omega_i(\sum_{n=0}^k D^n_i)^n|| = 0\\
 \end{gathered}
@@
 \begin{gathered}
-\tilde{\mathcal{G}_j}(d\vec{\delta}) = \exp(-i(\mathcal{L}(\vec{0}) + \frac{\partial}{\partial\delta_i}\mathcal{L}_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} \mathcal{L}(d\delta_i d\delta_k) + \ldots))\mathcal{G}
+\tilde{\mathcal{G}_i}(d\vec{\delta}) = \exp(-i(\mathcal{L}_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\mathcal{L}_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \mathcal{L}_i(\vec{0})d\delta_j d\delta_k + \ldots))\mathcal{G}
 \end{gathered}
@@
 By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore if we can find controls such that $|D_j^n|\leq\epsilon$, we can approximate (\ref{eq:MQG}) as:
+Furthermore if we can find controls such that $||D_i^n||\leq\epsilon$, we can approximate (\ref{eq:MQG}) as:
 \begin{equation}\label{eq:MQG-relaxed}
 \begin{gathered}
-\sum\omega_jD^n_j + \mathcal{O}(\epsilon^2) = 0\\
+||\sum\omega_iD^n_i||+ \mathcal{O}(\epsilon^2) = 0\\
 \end{gathered}
 \end{equation}
-This condition guarantees that errors will be suppressed to second order for all derivatives up to order $\ell$.
+This condition guarantees that errors will be suppressed to second order in $\epsilon$ for all derivatives up to order $\ell$.
 %A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
@@
 Figure \ref{fig:vectorspace} generalizes this picture to 1MQGs and gives intuition for the conditions required to produce them.
-To produce $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
+To generate $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
 \begin{equation}
@@
   \begin{split}
-    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||\\
-    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=\vec{0}\\
+    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||_1\\
+    &\textbf{subject to: } \forall n<\ell, ||\sum \omega_iD_i^n||=0\\
   \end{split}
 \end{equation}
-with $D_n^j$ defined in (\ref{eq:derivative}).
+with $D_n^i$ defined in (\ref{eq:derivative}).
 
@@
 \label{sec:norm}
-Up until this point the convex optimization problems discussed can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
+The convex optimization problems discussed up until this point can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
 In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
@@
 \begin{split}
-& \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||+ \eta\sum\omega_j||D^0_j||_2\\
-&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
+& \ \bunderbrace{\textbf{minimize}: }{\omega_i\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||_1+ \eta\sum\omega_i||D^0_i||_2\\
+&\ \ \textbf{subject to: } \forall n<\ell, ||\sum \omega_iD_i^n||=0\\
 \end{split}
@@
 &\underset{n\in[N]}{\textbf{minimize}}\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega|| + t\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\omega_i\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega||_1 + t\\
 &\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, \sum \omega_jD_j^n=0
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \omega_iD_i^n||=0
 \end{split}
@@
 \begin{equation}
-	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
+	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum w_i \, \epsilon_\diamond(\mathsf{E}_i).
 \end{equation}
-The effective error channel for a mixed quantum gate is $\mathsf{E}_{\rm{eff}} = \sum_i w_i\,\mathsf{E}_i$, where $\mathsf{E}_i$ are the error channels for the component gates.
+The effective error channel for a mixed quantum gate is $\mathsf{E}_{\rm{eff}} = \sum w_i\,\mathsf{E}_i$, where $\mathsf{E}_i$ are the error channels for the component gates.
 The diamond distance to the identity of the effective error channel is:
@@
 										  % - (\sum_i w_i\,\mathsf{E}_i \otimes \mathsf{I}_d)(\rho) \vert\vert_1 \\
-		&= \frac{1}{2} \sup_\rho \vert \vert \sum_i w_i\,((\mathsf{I}_d
+		&= \frac{1}{2} \sup_\rho \vert \vert \sum w_i\,((\mathsf{I}_d
 										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho) \vert\vert_1
@@
 	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
-		&= \frac{1}{2} \vert \vert \sum_i w_i\,((\mathsf{I}_d
+		&= \frac{1}{2} \vert \vert \sum w_i\,((\mathsf{I}_d
 										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*) \vert\vert_1 \\
-		&= \frac{1}{2} \vert \vert \sum_i w_i\, \rho^*_i \vert\vert_1,
+		&= \frac{1}{2} \vert \vert \sum w_i\, \rho^*_i \vert\vert_1,
 \end{align}
 where we have defined $\rho^*_i = ((\mathsf{I}_d - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*)$.
-The nuclear norm above is equal to the sum of the singular values of $\sum_i w_i \rho_i$.
+The nuclear norm above is equal to the sum of the singular values of $\sum w_i \rho_i$.
 Using the Ky Fan singular value inequality \cite{fan1951maximum} , we have

### 2019-08-02 decorrelation/mixed_unitaries.tex
more house cleaning

@@
 In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but depending on the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent error.\note{Just give an explicit example.} To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
+As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent errors.
+To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
 In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:

### 2019-08-05 decorrelation/mixed_unitaries.tex
just need to read thru the experimental section one more time
Notes and updates

@@
 \graphicspath{{./figures/}}
-\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
+\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Robustly decorrelating errors with mixed quantum gates, citecolor=blue, linkcolor=blue}
 \newcommand{\tr}{{\rm Tr\thinspace}}
@@
 \newcommand{\note}[1]{}
-\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
-\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
+\newcommand{\kcy}[1]{{\color{red}[#1]\textsubscript{\rm{KCY}}}}
+\newcommand{\amp}[1]{{\color{red}[#1]\textsubscript{\rm{AMP}}}}
 \newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
@@
 Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate.
-As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error.
+As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, by replacing the deterministic implementation of a quantum gate with a randomized ensemble of implementations, on can dramatically suppress coherent errors.
 Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem.
@@
 Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error.
-So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which has significantly less coherent error than any single compilation on its own.
-A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.
+So by selecting from these various compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which can have significantly less coherent error than any single compilation on its own.
+A very simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}.
 
@@
 We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
-Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error \cite{Ball2016}.
-We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, consistent with a reduction in the coherence of the error \cite{Ball2016}.
+We further apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
 
@@
 Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.
-But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, the qubits experience errors.
-If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$.
+But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, there are errors in the gate.
+If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$ acting on the Hilbert space of the target qubits.
 This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
@@
 \begin{equation}
-  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
+  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right),
 \end{equation}
@@
 \begin{equation}
-	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
+	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right).
 \end{equation}
-Process matrices written in the Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
+Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
 \begin{equation}\label{eq:process_matrix}
@@
 The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \cite{preskill1997lecture}.
-If the error map is unitary, then the error is called \textit{coherent} , and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector.
+If the error map is unitary, then the error is called \textit{coherent} and the unital submatrix $R$ is a rotation matrix.
 Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
-If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$).
-For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.
 
@@
 \end{equation}
-Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{watrous2018theory}, defined as:
+Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target (or simply, the \emph{diamond distance}), $\epsilon_\diamond$ \cite{watrous2018theory}, defined as:
 \begin{align}
@@
 \end{equation}
-That is, the AGI of the MQG is simply the weighted average of the component AGIs, so there is no hope of reducing the AGI by combining various implementations.
+That is, the AGI of the MQG is simply the weighted average of the component AGIs, so there is no hope of reducing it by combining various implementations.
 However, the diamond distance is a nonlinear function of error map.
@@
 \end{align}
-where $||\cdot||$ is meant to mean the Frobenius norm.
+where $||\cdot||$ is the Frobenius norm. \kcy{why the norm, why not just $\sum_i w_i L_i = 0$}.
 
 If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
-Campbell considered error channels that were strictly unitary, so the error generators in \ref{eq:cancel} were Hamiltonians.
+Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\eqref{eq:cancel} were Hamiltonians.
 Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull.
-If, however, the error map contains stochastic components, then the condition of \ref{eq:cancel} might be impossible to satisfy.
+If, however, the error map contains stochastic components, then the condition of Eq.~\eqref{eq:cancel} might be impossible to satisfy.
 Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull.
-This can be rectified by restricting the sum in \ref{eq:cancel} to only the Hamiltonian component of the generators.
+This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators.
 In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.
@@
   \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-These error Hamiltonians lie in a vector space.
+These error Hamiltonians lie in a vector space, which we illustrate as two-dimensional here.
 a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no 0MQGs.
-b) The origin is contained in the convex hull after adding an additional control solution.
-Because there are more than $n+1$ implementations (n=3), there exist an infinite number of 0MQGs.
+The origin is not contained in their convex hull, so there are no MQGs.
+b) After including an additional control solution, the convex hull grows to contain the origin, and so an MQG exists.
 c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a 0MQG may drift, leading to a first-order error.
+As this parameter drifts, a MQG may drift, leading to a first-order error.
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a 1MQG.}
+If the origin lies in their convex hull, then it may be possible to construct a MQG.
+\kcy{Split this figure into two.}}
   \label{fig:vectorspace}
@@
 We note that advanced quantum control protocols may provide a more principled approach to control synthesis.
-DMORPH \cite{dominy2008exploring}, for example, allows one to explore families of controls on fidelity level sets.
+DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations against secondary criteria, such as robustness or duration.
 
@@
 We will begin by discussing two classes of optimization targets, i) cancelation of the first-order generator, and ii) elimination of the off-diagonal elements of the error channel.
-We then discuss a set of additions to the numerical optimization that can improve the performance by i) adding robustness to drift,  ii) targeting low-error rate solutions, and iii) reducing the number of native unitaries that comprise the effective channel.
+We then discuss a set of additions to the numerical optimization that can improve the performance by i) incorporating robustness to drift,  ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
 
@@
 
-If our primary goal is for our MQG to have better worst-case performance, then a useful optimization target is minimizing the diamond norm.
-The diamond norm is a non-linear function that in general requires a convex optimizer to compute\cite{watrous2018theory}.
-However, if our errors are small enough, we can consider the linearized problem, and minimize the diamond norm to first-order in the error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
+Dnorm min:
+\begin{equation}\label{eq:ddmin}
+  \begin{split}
+    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } \hspace{.5cm} \epsilon_\diamond\left(\sum_i\mathsf{E}_i \omega_i\right)
+  \end{split}
+\end{equation}
+
+One reason to construct an MQG is to improve the worst-case performance of a quantum gate.
+The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target.
+The diamond distance, however, is a non-linear function that in general requires a convex optimization to compute\cite{watrous2018theory}.
+This can dramatically slow down iterative optimizers, and so minimizing the diamond distance is a computationally expensive optimization target.
+However, if the errors are small enough, we can consider a linearized problem, minimizing the diamond distance to first-order in the effective error generator.
+As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond distance of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
 \begin{equation}\label{eq:campbell-condition}
@@
 \end{equation}
-In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle to approximate arbitrary unitary operations, generates controls and weightings to find an MQG with this property.
+\kcy{again with the norm}
+In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle that produces approximate unitary operations, will generate controls and weightings to find an MQG with this property.
 Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
@@
 As denoted, this optimization needs to be constrained so that $\omega$ is a proper probability distribution.
-Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by methods like the Elipsoid Method \cite{wright1999numerical, khachiyan}.
+Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by, e.g.
+the ellipsoid method \cite{wright1999numerical, khachiyan}.
 More importantly, there are many existing convex solver software packages that solve these problems efficiently in practice.
@@
 
-\subsubsection{Off-diagonals} % (fold)
+\subsubsection{Approximate Pauli Channel} % (fold)
 \label{sub:off_diagonals}
@@
 Previous authors have considered finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013}, but this does not have the restriction that the resulting channel be decomposable into a given family of controls.
+\kcy{Citations to simulation of Pauli noise channels.
+Discussion of people looking for Pauli channels that approximate their noise.
+}
 
@@
 \end{split}
-\end{equation} with $\lambda\geq0$. As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\bold{D}^\ell$ and how sparse the solution needs to be.
-
-For small $\lambda$, the sparsity penalty is negligible, and for large $\lambda$ we see that if $\omega$ is not sparse then $t$ must be very large, which increases the cost of that particular solution.
+\end{equation} with $\lambda\geq0$.
+As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\bold{D}^\ell$ and how sparse the solution needs to be.
 In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.

### 2019-08-05 decorrelation/mixed_unitaries.tex
bye bye norms

@@
 	\label{eq:cancel}
-	&||\sum_i w_i^* \mathcal{L}_i||= 0
+	&\sum_i w_i^* \mathcal{L}_i= 0
 	% \mathrm{with}\;&\sum_i w_i = 1
 \end{align}
-where $||\cdot||$ is the Frobenius norm. \kcy{why the norm, why not just $\sum_i w_i L_i = 0$}.
 
@@
 \begin{equation}\label{eq:campbell-condition}
-||\sum \omega_i \mathcal{L}_i ||= 0
+\sum \omega_i \mathcal{L}_i = 0
 \end{equation}
@@
 \begin{gathered}
-||\sum_i\omega_i(\sum_{n=0}^k D^n_i)^n|| = 0\\
+\sum_i\omega_i(\sum_{n=0}^k D^n_i)^n = 0\\
 \end{gathered}
@@
 By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore if we can find controls such that $||D_i^n||\leq\epsilon$, we can approximate (\ref{eq:MQG}) as:
+Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is approximately satisfied in the sense that:
 \begin{equation}\label{eq:MQG-relaxed}
 \begin{gathered}
-||\sum\omega_iD^n_i||+ \mathcal{O}(\epsilon^2) = 0\\
+||\sum\omega_iD^n_i||+ \mathcal{O}(\alpha^2) = 0\\
 \end{gathered}
 \end{equation}
-This condition guarantees that errors will be suppressed to second order in $\epsilon$ for all derivatives up to order $\ell$.
+where $||\cdot||$ is the Frobenius norm.
+This condition guarantees, as before, that errors will be suppressed to second order in $\alpha$, but now for all derivatives up to order $\ell$.
 %A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.

### 2019-08-05 decorrelation/mixed_unitaries.tex
removing now old note

@@
 We note that advanced quantum control protocols may provide a more principled approach to control synthesis.
-DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations against secondary criteria, such as robustness or duration.
+DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations  fst secondary criteria, such as robustness or duration.
 
@@
 \end{equation}
-\kcy{again with the norm}
 In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle that produces approximate unitary operations, will generate controls and weightings to find an MQG with this property.

### 2019-08-06 code/2d_mpi_plot.py
Added code to analyze the data, also some plots

@@ -1,0 +1,94 @@
+# Standard imports
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+# Set the environment variables
+import os 
+os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+
+# Initialize the parallel processing
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+# Additional imports
+from time import time
+import pygsti 
+if rank == 0:
+    import matplotlib 
+    matplotlib.use('Agg')
+    from matplotlib import pyplot as plt
+
+def print(*args, **kwargs):
+    if rank == 0:
+        return __builtin__.print(*args, **kwargs)
+
+# Import the data
+import dill
+filenames = {0: '0_pickled_controls106.pkl', 1: '1_pickled_controls106.pkl'}
+with open(filenames[1], 'rb') as f:
+    data = dill.load(f)
+
+# Divide list into n approximately equally sized chunks
+def split(n, a):
+    k, m = divmod(len(a), n)
+    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
+
+
+# Get the unitary associated with a given index
+def get_unitary(c_ind, epsilon1, epsilon2, delta1, delta2):
+    u = np.eye(4, dtype='complex')
+    
+    a = epsilon1 * data.ambient_hamiltonian[0]
+    b = epsilon2 * data.ambient_hamiltonian[1]
+    c = data.ambient_hamiltonian[2] 
+    h0 = a+b+c
+    
+    for t_ind in range(500):
+        d = (1+delta2) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
+        e = (1+delta2) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1] 
+        f = (1+delta1) * data.controlset[c_ind][t_ind][2] * data.control_hamiltonians[2] 
+        g = (1+delta1) * data.controlset[c_ind][t_ind][3] * data.control_hamiltonians[3] 
+        ham = h0 + d + e + f + g
+        u = np.dot(slin.expm(-1.j*ham*data.dt), u)    
+    return u    
+
+# for testing:
[…]

### 2019-08-21 code/2q_dnorm.py
Diamond norms for components

@@ -6,6 +6,7 @@ os.environ['NUMEXPR_NUM_THREADS'] = '1'
 os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
 
 from pauli_channel_approximation import PCA
+from time import time
 
 from mpi4py import MPI
 comm = MPI.COMM_WORLD
@@ -113,11 +114,16 @@ if rank == 0:
         ep0 = dill.load(f)
     with open('./figures/epsilon.dat', 'rb') as f:
         ep1 = dill.load(f)
+else:
+    data0 = None
+    data1 = None
+    ep0 = None
+    ep1 = None
 
 
 def split(n, a):
     k, m = divmod(len(a), n)
-    return _np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
+    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
 
 
 data0 = comm.bcast(data0, root=0)
@@ -125,26 +131,34 @@ data1 = comm.bcast(data1, root=0)
 ep0 = comm.bcast(ep0, root=0)
 ep1 = comm.bcast(ep1, root=0)
 
-my_points = split(size, np.arange(data0.num_controls))
 
+
+my_points = split(size, np.arange(data0.num_controls))[rank]
 my_values = []
 
-for point in my_points:
+t0 = time()
+num_points = len(my_points)
+for p_ind, point in enumerate(my_points):
+    t1 = time()
     ed = []
     for val in ep0['vals']:
-        # u = get_unitary(data1, ind,val,val,0,0)
-        # pu = change_basis(np.kron(u.conj(), u), 'col', 'pp')
-        # ed += [pygsti.tools.optools.diamonddist(piSWAP, pu, 'pp')/2]
-        ed += [0]
+        u = get_unitary(data1, point, val,val,0,0)
+        pu = change_basis(np.kron(u.conj(), u), 'col', 'pp')
+        ed += [pygsti.tools.optools.diamonddist(piSWAP, pu, 'pp')/2]
+        # ed += [0]
     my_values += [ed]
+    delta_t = np.round(time() - t1)
+    delta_T = np.round(time() - t0)
+    print(f"Node {rank} finished index {point} in {delta_t} seconds. Remaining: {delta_T*num_points/(p_ind+1)}")
 
 all_values = comm.gather(my_values, root = 0)
 
 
 if rank == 0:
+    print(np.array(all_values).shape)
[…]

### 2019-08-21 decorrelation/mixed_unitaries.tex

@@
   \begin{split}
-    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{L}\omega||_1\\
+    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{L}\omega||_2\\
   \end{split}
 \end{equation}
-where $||\cdot||_1$ is the $\ell_1$ norm.
+where $||\cdot||_2$ is the $\ell_2$ norm.
 
@@
 Specifically, we are interested in the $n^{th}$ order derivatives:
+\kcy{move this later}
 \begin{equation}
@@
 To see this, we can rewrite the implementations of the target gate as:
+\kcy{move this earlier}
 \begin{equation}\label{eq:taylor}
@@
 \label{sec:norm}
-The convex optimization problems discussed up until this point can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
+The convex optimization problems discussed up until this point can be solved analytically, \kcy{nope!} however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
 In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
@@
 In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\omega$ to be a valid probability distribution.
-The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
+\kcy{more here} The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
 
@@
 \label{sub:experimental}
+\kcy{more introduction} 
 Here we present experimental results from implementing this routine on a fixed-frequency, superconducting transmon qubit.
 In particular, we use qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an MQG on this qubit, four miscalibrated Gaussian pulses were produced by scaling the amplitude for a calibrated 10 sample 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+To implement an MQG on this qubit, four intentionally miscalibrated Gaussian pulses were produced by scaling the amplitude of a calibrated, 10-sample, 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
@@
 
+\kcy{Kill all non-markovians}
 More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with suppressed coherent error.
@@
 \label{sec:numerical_results}
+\kcy{more introduction - what is going on. We are constructing solutions that are themseleves naturally robust, then combining them to make a MQG that is... something better? }
 In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs. We consider the following model for a single tunable qubit: 
@@
 \end{equation}
+\kcy{dimensionless}
 where $\epsilon$ is a random variable used to model fluctuations in the qubit frequency, and $\delta$ is a random variable used to model fluctuations in the control field.
@@
 Using controls generated in this way, the MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
-By imposing the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
+\kcy{not a sentence -->} By imposing the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
 Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
@@
   \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+  \caption{\kcy{Axis label is screwed up} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
 The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
@@
   \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
-  \caption{Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.
+  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.
 Shown with lower alpha values are example constituent controls.

### 2019-08-22 code/2q_dnorm.py
2q diamond norms calculated

@@ -144,12 +144,12 @@ for p_ind, point in enumerate(my_points):
     for val in ep0['vals']:
         u = get_unitary(data1, point, val,val,0,0)
         pu = change_basis(np.kron(u.conj(), u), 'col', 'pp')
-        ed += [pygsti.tools.optools.diamonddist(piSWAP, pu, 'pp')/2]
+        ed += [pygsti.tools.optools.diamonddist(piSWAP, pu, 'pp')/2.]
         # ed += [0]
     my_values += [ed]
     delta_t = np.round(time() - t1)
     delta_T = np.round(time() - t0)
-    print(f"Node {rank} finished index {point} in {delta_t} seconds. Remaining: {delta_T*num_points/(p_ind+1)}")
+    print(f"Node {rank} finished {p_ind+1} of {num_points} in {delta_T} seconds. Remaining: {delta_T*(num_points-p_ind-1)/(p_ind+1)}. Min dnorm: {np.min(ed)}.")
 
 all_values = comm.gather(my_values, root = 0)
 

### 2019-08-25 decorrelation/mixed_unitaries.tex
Text edits.

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
+  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
+a) The error Hamiltonians shown with their derivative with respect to a control parameter.
+As this parameter drifts, a MQG may drift, leading to a first-order error.
+b) The derivatives also lie in a vector space.
+If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.}
+  \label{fig:vectorspace}
+\end{figure}
+
 % subsection adding_robustness (end)
@@
 
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
   \centering
-  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
+  \includegraphics[width=\columnwidth]{2q_robustness.png}
   \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.

### 2019-08-25 decorrelation/mixed_unitaries.tex
Moved 2Q figure file

@@
 d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a MQG.
-\kcy{Split this figure into two.}}
+If the origin lies in their convex hull, then it may be possible to construct a MQG.}
   \label{fig:vectorspace}
@@
 Specifically, we are interested in the $n^{th}$ order derivatives:
-\kcy{move this later}
+\kcy{This shoudl probably use the comma derivative notation that we use in the figures. Should the figures change from H to something else?}
+\begin{equation}
+\label{eq:derivative}
+D^n_i = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
+\end{equation}
 \begin{equation}
@@
 b) The derivatives also lie in a vector space.
-If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.}
+If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.
+\kcy{This should appear in the main text somewhere.
+When we add the derivatives we make our space larger, but we still want the origin to be in the higher-dimensional convex hull.}}
   \label{fig:vectorspace}
@@
   \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{\kcy{Axis label is screwed up} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
+  \caption{\kcy{Axis label is screwed up.
+Should we replot these as in the 2Q example?} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
 The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
 In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
+However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.
+}
   \label{fig:YMQG}
@@
   \centering
-  \includegraphics[width=\columnwidth]{2q_robustness.png}
+  \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
   \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.
@@
 By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
+
 % ==============================================================================

### 2019-08-26 code/1q_dnorm.py
an attempt at copying the code for 2q stuff for 1q stuff. Looks approximately correct.

@@ -1,0 +1,167 @@
+import os
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+os.environ['NUMEXPR_NUM_THREADS'] = '1'
+os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
+
+from pauli_channel_approximation import PCA
+from time import time
+import scipy
+
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+import os; os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+import pygsti
+
+import pygsti
+import numpy as np
+import itertools
+from functools import reduce
+
+multi_kron = lambda *a: reduce(np.kron, a)
+
+def change_basis(process, from_basis, to_basis):
+    """
+    PyGSTi 'std' basis is *row stacked* rather than column stacked, so need to defined a 'col' basis.
+    """
+    allowed_bases = ['col', 'std', 'gm', 'pp', 'qsim']
+    if not ((from_basis in allowed_bases) or (to_basis in allowed_bases)):
+        raise ValueError("Allowed bases are 'col', 'std', 'gm', 'pp', 'qsim' ")
+
+    n_qubits = int(np.log(len(process)) / np.log(4))
+    if from_basis == 'col' or to_basis == 'col':
+
+        if len(process) != 4**n_qubits:
+            raise ValueError('The dimension of the process matrix must be a power of 4.')
+        def matrix_unit(n,i,j):
+            unit = np.zeros([n,n], dtype='complex')
+            unit[i,j] = 1.
+            return unit
+        col_stacked_matrix_units = [matrix_unit(2**n_qubits, i, j) for j in range(2**n_qubits) for i in range(2**n_qubits)]
+
+        from pygsti.objects import ExplicitBasis
+        col = ExplicitBasis(col_stacked_matrix_units, ["myElement%d" % i for i in range(4**n_qubits)],
+                                     name='col', longname='Column=-Stacked')
+        if from_basis == 'col':
+            from_basis = col
[…]

### 2019-08-26 code/2d_mpi_plot_1q.py

@@ -1,0 +1,171 @@
+# Standard imports
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+# Set the environment variables
+import os
+
+os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+
+# Initialize the parallel processing
+from mpi4py import MPI
+
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+# Additional imports
+from time import time
+import pygsti
+
+if rank == 0:
+    import matplotlib
+
+    matplotlib.use('Agg')
+    from matplotlib import pyplot as plt
+
+
+def print(*args, root=0, **kwargs):
+    if rank == root:
+        import builtins
+        return builtins.print(*args, **kwargs)
+
+
+# Import the data
+import dill
+
+filenames = {0: '0_pickled_controls5.pkl', 1: '1_pickled_controls5.pkl'}
+with open(filenames[1], 'rb') as f:
+    data = dill.load(f)
+
+
+# Divide list into n approximately equally sized chunks
+def split(n, a):
+    k, m = divmod(len(a), n)
+    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
+
+
+# Get the unitary associated with a given index
+def get_unitary(c_ind, epsilon1, delta1):
+    u = np.eye(2, dtype='complex')
+    a = epsilon1 * data.ambient_hamiltonian[0]
+    h0 = a
+    for t_ind in range(25):
+        f = (1 + delta1) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
+        g = (1 + delta1) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1]
+        ham = h0 + f + g
+        u = np.dot(slin.expm(-1.j * ham * data.dt), u)
+    return u
+
+
+# for testing:
+my_inds = split(size, np.arange(len(data.controlset)))[rank]
+
+
+# my_inds = np.array(split(size, np.arange(size)))[rank]
+
+
+# Get the process matrix for a given setting of the error parameters
[…]

### 2019-08-26 code/1q_dnorm.py
1q plots and data

@@ -102,9 +102,9 @@ if rank == 0:
     with open('1_pickled_controls5.pkl', 'rb') as f:
         data1 = dill.load(f)
 
-    with open('./figures/0_epsilon_1q.dat', 'rb') as f:
+    with open('./figures/0_delta_1q.dat', 'rb') as f:
         ep0 = dill.load(f)
-    with open('./figures/1_epsilon_1q.dat', 'rb') as f:
+    with open('./figures/1_delta_1q.dat', 'rb') as f:
         ep1 = dill.load(f)
 else:
     data0 = None
@@ -124,8 +124,7 @@ ep0 = comm.bcast(ep0, root=0)
 ep1 = comm.bcast(ep1, root=0)
 
 
-
-my_points = split(size, np.arange(data0.num_controls))[rank]
+my_points = split(size, np.arange(len(data0.controlset)))[rank]
 my_values = []
 
 t0 = time()
@@ -134,7 +133,7 @@ for p_ind, point in enumerate(my_points):
     t1 = time()
     ed = []
     for val in ep0['vals']:
-        u = get_unitary(data1, point, val, 0)
+        u = get_unitary(data1, point, 0, val)
         pu = change_basis(np.kron(u.conj(), u), 'col', 'pp')
         ed += [pygsti.tools.optools.diamonddist(psqrt_x, pu, 'pp')/2.]
         # ed += [0]
@@ -149,9 +148,9 @@ all_values = comm.gather(my_values, root = 0)
 if rank == 0:
     print(np.array(all_values).shape)
     all_values = [inner for outer in all_values for inner in outer]
-    data = {ind: all_values[ind] for ind in range(data0.num_controls)}
+    data = {ind: all_values[ind] for ind in range(len(data0.controlset))}
     data['epsilons'] = ep0['vals']
-    with open('1q_dnorms.dat', 'wb') as f:
+    with open('1q_dnorms_delta.dat', 'wb') as f:
         dill.dump(data, f)
 
 

### 2019-08-26 code/2d_mpi_plot_1q.py

@@ -102,12 +102,12 @@ def flatten(the_list):
 if __name__ == '__main__':
 
     diamond_distances = []
-    vals = np.linspace(-.02,.02,1001)
+    vals = np.linspace(-.002,.002,1001)
     target_process = pygsti.tools.optools.unitary_to_pauligate(data.target_operator)
     t0 = time()
     for v_ind, val in enumerate(vals):
         t1 = time()
-        process = get_process(val, 0)
+        process = get_process(0, val)
         if rank == 0:
             error = pygsti.tools.optools.diamonddist(target_process, process, 'pp')/2
             t_total = np.round(time()-t0,3)
@@ -118,15 +118,15 @@ if __name__ == '__main__':
 
     if rank == 0:
         save_data = {'vals': vals, 'diamond_distances': diamond_distances}
-        with open('./figures/1_epsilon_1q.dat', 'wb') as f:
+        with open('./figures/1_delta_1q.dat', 'wb') as f:
             dill.dump(save_data, f)
         plt.plot(vals, diamond_distances)
-        plt.xlabel('Epsilon')
+        plt.xlabel('Delta')
         plt.ylabel('Diamond Distance')
         plt.savefig('./figures/1_epsilon_correlated_dense_1q.pdf')
 
     t1 = time()
-    ddists = get_process(.01, 0, False, True)
+    ddists = get_process(0,.01, False, True)
     print(ddists)
     if rank == 0:
         print(ddists)
@@ -136,12 +136,12 @@ if __name__ == '__main__':
         print(np.round(time() - t1, 1))
 
     target_process = pygsti.tools.optools.unitary_to_pauligate(data.target_operator)
-    vals = np.linspace(-0.02, 0.02, 79)
+    vals = np.linspace(-0.002, 0.002, 79)
     my_vals = split(size, vals)[rank]
     for index in [399, 39, 234, 252, 824]:
         my_ddists = []
         for val in my_vals:
-            process = pygsti.tools.optools.unitary_to_pauligate(get_unitary(index,val,val,0,0))
+            process = pygsti.tools.optools.unitary_to_pauligate(get_unitary(index,0, val))
             ddist = pygsti.tools.optools.diamonddist(process, target_process, 'pp')/2.
             my_ddists += [ddist]
         ddists = comm.gather(my_ddists, root = 0)

### 2019-08-27 decorrelation/mixed_unitaries.tex
updating the text to address notes from Kevin, and including the redone 1q plot

@@
 In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel.
-Previous authors have considered finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013}, but this does not have the restriction that the resulting channel be decomposable into a given family of controls.
-\kcy{Citations to simulation of Pauli noise channels.
-Discussion of people looking for Pauli channels that approximate their noise.
-}
+If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods.
+Better yet, if the circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
 
@@
 Thus, we would like to design MQGs that are robust to this drift.
-To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and instead of requiring that the error generators average to zero, we can impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and if the fluctuations are small enough, it is convenient to write the gate as a Taylor expansion in this small parameter:
+\begin{equation}\label{eq:taylor}
+\begin{gathered}
+\tilde{\mathcal{G}_i}(d\vec{\delta}) = \exp(-i(\mathcal{L}_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\mathcal{L}_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \mathcal{L}_i(\vec{0})d\delta_j d\delta_k + \ldots))\mathcal{G}
+\end{gathered}
+\end{equation}
+
+Now, instead of requiring that only the error generators average to zero, we can additionally impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
 Specifically, we are interested in the $n^{th}$ order derivatives:
-\kcy{This shoudl probably use the comma derivative notation that we use in the figures. Should the figures change from H to something else?}
+\kcy{Should the figures change from H to something else?}
+\amp{Right.
+It seems to me they should be written as something like $D^1_{i,k}$.
+Then in the equation below I can use the comma notation, but for the $i^{th}$ derivative it's going to be some gross multi-index...
+I think your point is that the comma is standard notation (although I've never used it before.)}
 \begin{equation}
 \label{eq:derivative}
-D^n_i = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
+D^n_{i, (j_1, \ldots, j_n)} = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
 \end{equation}
-\begin{equation}
-\label{eq:derivative}
-D^n_i = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
-\end{equation}
-If the dimension of $\vec{\delta}$ is $d$, the indices $j_0, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
+If the dimension of $\vec{\delta}$ is $d$, the indices $j_1, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
 We say that an MQG is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
@@
 \end{equation}
-In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}).
-More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$.
-To see this, we can rewrite the implementations of the target gate as:
-\kcy{move this earlier}
-\begin{equation}\label{eq:taylor}
-\begin{gathered}
-\tilde{\mathcal{G}_i}(d\vec{\delta}) = \exp(-i(\mathcal{L}_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\mathcal{L}_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \mathcal{L}_i(\vec{0})d\delta_j d\delta_k + \ldots))\mathcal{G}
-\end{gathered}
-\end{equation}
+In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}). More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$. 
 By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is approximately satisfied in the sense that:
+Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is a pproximately satisfied in the sense that:
 \begin{equation}\label{eq:MQG-relaxed}
@@
 b) The derivatives also lie in a vector space.
-If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.
+If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$\amp{I'm not sure what you mean by the $_k$ subscript, nor why the tensor product is there.
+Also I think your indices are backwards?} then it may be possible to construct a robust 1-MQG.
 \kcy{This should appear in the main text somewhere.
@@
 \label{sec:norm}
-The convex optimization problems discussed up until this point can be solved analytically, \kcy{nope!} however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG.
+While quadratic programs with equality constraints have analytic solutions, the program we are considering has both constraints on the norm of the weight vector, and inequality constraints.
+Additionally, casting this problem as a convex optimization problem allows us to add penalty terms to the cost function to promote different properties of the MQG.
 In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
@@
 \subsubsection{Sparsity Constraints}
-
+\label{sec:sparsity}
 As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
@@
 In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\omega$ to be a valid probability distribution.
-\kcy{more here} The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
+Lasso regularization works by penalizing solutions with large $\ell_1$ norm, however if $\omega$ represents probabilities, it will always have an $\ell_1$ norm of one.
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
 
@@
 \label{sub:experimental}
-\kcy{more introduction} 
-Here we present experimental results from implementing this routine on a fixed-frequency, superconducting transmon qubit.
-In particular, we use qubit 8 on the Rigetti 19Q-Acorn chip, whose characterization can be found in \cite{1712.05771}.
-To implement an MQG on this qubit, four intentionally miscalibrated Gaussian pulses were produced by scaling the amplitude of a calibrated, 10-sample, 50ns $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+In modern quantum computing platforms, diagnosing and correcting coherent errors remains a challenge.
+Methodologies like RPE and DRAG are sufficient for routinely achieving high single qubit fidelities in superconducting qubit architectures, however as coherence times increase, the community will continue to be interested in removing coherent errors to achieve higher fidelities.
+As a proof of principle, we implemented an MQG with a superconducting transmon qubit on the Rigetti 19Q-Acorn chip, whose performance we describe below.
+While this device consisted of 20 qubits with fixed couplings, here we will give results for a single qubit MQG on qubit 8.
+For more details about this particular device, characterization can be found in \cite{1712.05771}.
+
+To implement an MQG on this qubit, we first calibrated a 10-sample, 50ns Gaussian pulse by coherently amplifying and correcting over- and under-rotation errors through repeated application.
+After the gate was sufficiently calibrated, four intentionally miscalibrated Gaussian pulses were produced by scaling the amplitude of the calibrated $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 
@@
 
-\kcy{Kill all non-markovians}
 More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with suppressed coherent error.
 To see that this is the case, we can observe the drastic reduction in the variance at each point for the MQG relative to the miscalibrated pulses.
-A discussed in \cite{Ball2016}, for non-Markovian error models, noise will manifest as gamma distributed points for each sequence length.
-On the other hand, Markovian noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
+A discussed in \cite{Ball2016}, for coherent error models, noise will manifest as gamma distributed points for each sequence length.
+On the other hand, incoherent noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
 We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
@@
 \label{sec:numerical_results}
-\kcy{more introduction - what is going on. We are constructing solutions that are themseleves naturally robust, then combining them to make a MQG that is... something better? }
-In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs. We consider the following model for a single tunable qubit: 
+In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs, and then analyze their performance for a range of Hamiltonian parameters.
+More specifically, we will construct a family of controls with some degree of inherent robustness to drift, and leverage the numerical techniques introduced to assign each control a probability.
+When drawn from with these probabilities, the controls will form an MQG with enhanced robustness to drift on the control parameters.
+We consider the following dimensionless model for a single tunable qubit:
 \begin{equation}\label{eq:1Qham}
@@
 \end{equation}
-\kcy{dimensionless}
-where $\epsilon$ is a random variable used to model fluctuations in the qubit frequency, and $\delta$ is a random variable used to model fluctuations in the control field.
-We use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
+where $\epsilon$ corresponds to fluctuations in qubit frequency and $\delta$ corresponds to fluctuations in the control field.
 
-In our implementation, we considered the performance function presented in \cite{Khaneja2005}, and averaged over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that perform well in a neighborhood.
-The standard deviations considered for all random variables in our numerical experiments were fixed to $\sigma=.001$.
+To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
+However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
+In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
+The standard deviations considered for all parameters in our numerical experiments were fixed to $\sigma=.001$.
 Finally, we assume that the errors on $\sigma_x$ and $\sigma_y$ are perfectly correlated, as in our experimental implementation.
 
-Using controls generated in this way, the MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RY(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
-\kcy{not a sentence -->} By imposing the $\ell_2$ penalty from Section \ref{sec:norm}, so that the algorithm preferentially selects controls with smaller errors.
-Adding this constraint made the 0MQG perform better at the origin by nearly an order of magnitude, and moved the 1MQG from being out-performed by the 0MQG for all detunings, to out performing by nearly an order of magnitude when there is $.1\%$ drift in the controls.
-Imposing this constraint allows us to trade off flatness at the origin for performance at the origin.
+Using controls generated in this way, the MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RX(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
+By imposing the penalty from Section \ref{sec:norm}, we sought to ensure that the algorithm preferentially selected controls with smaller errors.
+Adding this constraint increased the performance of the 0MQG by nearly an order of magnitude at the origin, and produced a 1MQG whose performance is an order of magnitude better than the 0MQG away from the origin.
+Imposing this constraint allows us to trade off flatness for performance.
 This shows that through adding constraints to our optimization routine, we can make the MQG practically useful.
@@
   \centering
-  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
-  \caption{\kcy{Axis label is screwed up.
-Should we replot these as in the 2Q example?} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$.
-The results are qualitatively similar to those for $RX(\frac{\pi}{2})$.
+  \includegraphics[width=\columnwidth]{figures/1q_robustness_delta.pdf}
+  \caption{\amp{needs to be on previous page?}Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RX(\frac{\pi}{2})$.
+The results are qualitatively similar to those for $RY(\frac{\pi}{2})$.
 In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.
-}
+However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude.}
   \label{fig:YMQG}
@@
 
-In this example it was infeasible to use GRAPE to return non-trivial solutions.
+\amp{This section is still tough to read, but I'm not sure of a better way to handle it.
+The constituent controls are clearly contrived, so I think it best to be explicit about how they were constructed.}In this example it was infeasible to use GRAPE to return non-trivial solutions.
 Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.

### 2019-08-27 decorrelation/mixed_unitaries.tex
one more small change

@@
 If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods.
-Better yet, if the circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
+Better yet, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
 

### 2019-08-27 decorrelation/mixed_unitaries.tex
n -> d^2

@@
 
-Dnorm min:
+One reason to construct an MQG is to improve the worst-case performance of a quantum gate.
+The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target:
 \begin{equation}\label{eq:ddmin}
@@
 \end{equation}
-
-One reason to construct an MQG is to improve the worst-case performance of a quantum gate.
-The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target.
 The diamond distance, however, is a non-linear function that in general requires a convex optimization to compute\cite{watrous2018theory}.
@@
 Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
-Given such an MQC we can consider the $n^2\times m$ matrix whose columns are the vectorized error generators:
+Given such an MQC with $m$ members, we can consider the $d^4\times m$ matrix whose columns are the vectorized error generators:
 \begin{equation}\label{eq:vectorized_generators}
@@
 		\vdots\ & \ddots &    \\
-		\mathcal{L}_{1_{n,n}} &  &  \mathcal{L}_{m_{n,n}} \\ 
+		\mathcal{L}_{1_{d^2,d^2}} &  &  \mathcal{L}_{m_{d^2,d^2}} \\ 
 	\end{array} 	
@@
 		\vdots\ & \ddots &    \\
-		D^\ell_{1_{n,n}} &  &  D^\ell_{m_{n,n}} \\ 
+		D^\ell_{1_{d^2,d^2}} &  &  D^\ell_{m_{d^2,d^2}} \\ 
 	\end{array} 	
@@
 \begin{split}
-&\underset{n\in[N]}{\textbf{minimize}}\\
+&\underset{m\in[N]}{\textbf{minimize}}\\
 &\ \ \bunderbrace{\textbf{minimize}: }{\omega_i\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega||_1 + t\\
-&\ \ \textbf{subject to: } \omega_n > \frac{\lambda}{t}\\
+&\ \ \textbf{subject to: } \omega_m > \frac{\lambda}{t}\\
 &\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \omega_iD_i^n||=0

### 2019-09-10 decorrelation/mixed_unitaries.tex
Major reshuffling and rewriting started
I’m still working - don’t edit this

@@
 \newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
-\newcommand{\ident}{{\mathbb1}}
+% \newcommand{\identmat}{{\mathbb1}}
 \newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
@@
 \newcommand{\actual}{\ensuremath{\tilde{\mathsf{G}}}}
+\newcommand{\actmat}{\ensuremath{\tilde{\mathcal{G}}}}
 \newcommand{\target}{\ensuremath{{\mathsf{G}}}}
+\newcommand{\tarmat}{\ensuremath{{\mathcal{G}}}}
 \newcommand{\error}{\ensuremath{{\mathsf{E}}}}
-\newcommand{\generator}{\ensuremath{{\mathsf{G}}}}
+\newcommand{\errmat}{\ensuremath{{\mathcal{E}}}}
+\newcommand{\genmat}{\ensuremath{{\mathcal{L}}}}
 \newcommand{\vectorize}[1]{\ensuremath{\mathsf{vec}\left(#1\right)}}
+\newcommand{\AGI}{\ensuremath{\epsilon_\mathcal{F}}}
+\newcommand{\dnorm}{\ensuremath{\epsilon_\diamond}}
+\newcommand{\identmat}{\ensuremath{\mathcal{I}}}
+\newcommand{\ident}{\ensuremath{\mathsf{I}}}
+\newcommand{\weight}{\ensuremath{w}}
+
 \def\id{\mbox{\small 1} \!\! \mbox{1}}
@@
   \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{An example of a mixed quantum gate.
-Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$).
-Each time the gate is used, one of these implementations is chosen at random.
-The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
+  \caption{A simple example of a mixed quantum gate.
+Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite coherent errors (if one implementation over-rotates by a small angle $\theta$, then the other \emph{under}-rotates by $\theta$).
+Each time the gate is used, one of these two implementations is chosen at random.
+The resulting effective quantum gate is equivalent to a perfect implementation of the gate followed by dephasing with associated probability $\order{\theta^2}$.}
   \label{fig:simple_example}
@@
 
-Recent works by Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
-They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the native gates are perfect.
-Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error.
+Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
+They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
+Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary errors.
 So by selecting from these various compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which can have significantly less coherent error than any single compilation on its own.
@@
 
-In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations.
+In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates and show that the advantages of their approach can be made robust to drift in the gate implementations.
 We demonstrate that, depending on what properties of the resulting channel are desired, different numerical optimization targets may be preferred.
 We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
-Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, consistent with a reduction in the coherence of the error \cite{Ball2016}.
-We further apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.
+Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, consistent with a significant reduction in the coherence of the error \cite{Ball2016}.
+We further apply our methods in simulation, constructing single- and two-qubit mixed unitary controls that are robust to drift and uncertainty in the control parameters.
 
@@
 % ==============================================================================
-\section{Representing Errors }
-\label{sec:representing_quantum_gates}
+\section{Preliminaries}
+\label{sec:preliminaries}
 
 \subsection{Representing Errors in Quantum Gates}
-\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device.
+\label{sec:rep_errors}
+\noindent Suppose that one wishes to apply a unitary gate, $\target$, on some quantum device.
 Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, there are errors in the gate.
-If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$ acting on the Hilbert space of the target qubits.
-This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.
+If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\actual$ acting on the Hilbert space of the target qubits.
+This map can always be written as $\actual = \error\circ\target$, where $\error = \actual\circ\target^{-1}$ is the \emph{error map}, which is itself CPTP because $\target$ is unitary.
 
 CPTP maps possess a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}.
-But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$.
+But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\target$ with its corresponding calligraphic character, $\tarmat$.
 For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix.
@@
 \begin{align}
-	\vectorize{\mathsf{\tilde G}(\rho)}
-		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
-		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
+	\vectorize{\actual(\rho)}
+		&= \actmat\cdot\vectorize{\rho} \\
+		&= \errmat\cdot\tarmat\cdot\vectorize{\rho}
 \end{align}
-We shall work in the basis of Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
+The $\mathsf{vec}$ operation is typically performed using a basis of matrix units, for which $\vectorize{\rho}$ would be the column vector obtained by stacking the columns of $\rho$.
+In this work, however, we shall use a basis of Pauli matrices, defining $P = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).
 In this basis,
 \begin{equation}
-  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right),
+  \vectorize{\rho}_i = \expect{P_i} = \tr\!\left(P_i\; \rho \right),
 \end{equation}
@@
 \begin{equation}
-	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right).
+	(\actmat)_{ij} = \tr\!\left(P_i \;\actual\!\left(P_j\right) \right).
 \end{equation}
-Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
+Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented in this basis take the particularly nice form,
 \begin{equation}\label{eq:process_matrix}
-\mathcal{E} =
+\errmat =
 	\left(\begin{array}{c|cccc}
@@
 
-In what follows it will be useful to define the \emph{error generator}, $\mathcal{L}$, associated with a faulty gate: 
+In what follows it will be useful to define the \emph{error generator}, $\genmat$, associated with a faulty gate: 
 \begin{align}
 	\label{eq:generator}
-	\mathcal{E} 
-		&= \exp\left(\mathcal{L}\right) \\
-		&= \mathcal{I}_d + \mathcal{L} + \frac{1}{2}\mathcal{L}^2 + \order{\mathcal{L}^3}.
+	\errmat 
+		&= \exp\left(\genmat\right) \\
+		&= \identmat_d + \genmat + \frac{1}{2}\genmat^2 + \order{\genmat^3}.
 \end{align}
-If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms, and the Taylor expansion above may reliably be truncated at first or second order.
+If an implemented gate is relatively close to its target, then the error generator will be small under any of the usual matrix norms, and the Taylor expansion above may reliably be truncated at first or second order.
 
 \subsection{Mixed Quantum Gates}
-\noindent Now suppose that we have access to an ensemble of different implementations of the target gate, $\{\mathsf{\tilde G}_i\}$.
-% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
-Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{\tilde{G}}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$).
-This procedure is operationally indistinguishable from always applying the effective operation,
+\label{sec:mqg}
+\noindent Suppose that we have access to an ensemble of distinct implementations, 
+$\{\actual_i\}$, of a target gate, $\target$.
+Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\actual_i$ is $\weight_i$ (and we ensure that $\sum_i \weight_i=1$).
+This procedure is operationally indistinguishable from always applying the effective channel,
 \begin{align}
-	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i.
+	\actual_{\rm eff} &= \sum_i \weight_i \actual_i = \left(\sum_i \weight_i \error_i \right) \circ\target
 \end{align}
-We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for MQGs can be computed in terms of their effective error map, 
+We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for these MQGs can be computed in terms of their effective error map, 
 \begin{equation}
 	\label{eq:effective_error}
-	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
+	\error_{\rm eff} = \sum_i \weight_i \error_i.
 \end{equation}
-Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target (or simply, the \emph{diamond distance}), $\epsilon_\diamond$ \cite{watrous2018theory}, defined as:
+Two important error metrics are the average gate infidelity (AGI), $\AGI$, and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
 \begin{align}
 	\label{eq:def_agi}
-	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
+	&\AGI(\error) = \frac{d^2 - \tr{\errmat}}{d^2 + d},\\
 	\label{eq:def_diamond}
-	&\epsilon_\diamond \left(\mathsf{E}\right)
-		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
-										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
+	&\dnorm \left(\error\right)
+		= \frac{1}{2} \sup_\rho \vert \vert (\ident_d\otimes \ident_d)(\rho) 
+										  - (\error \otimes \ident_d)(\rho) \vert\vert_1,
 \end{align}
-where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.
-In \ref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$, in terms of its associated Pauli transfer matrix, $\mathcal{E}$.
-If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}.
-The diamond distance is subaddative \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \cite{aharonov1998quantum}.
+where $d=2^n$ and $\ident_d$ is the $d$-dimensional identity operator.
+In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\error$, in terms of its associated Pauli transfer matrix, $\errmat$.
+If the error channel is purely stochastic, then $\dnorm(\error) = \AGI(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}.
+The diamond distance is subaddative \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for gates that compose the circuit \cite{aharonov1998quantum}.
 
-Because $\epsilon_{\mathcal{F}}$ is linear in the error map, we have:
+Because $\AGI$ is linear in the error map, we have:
 \begin{equation}
-	\epsilon_{\mathcal{F}}\!\left(\mathsf{E}_{\rm eff}\right) = \sum_i w_i \,\epsilon_{\mathcal{F}}(\mathsf{E}_i).
+	\AGI\!\left(\error_{\rm eff}\right) = \sum_i \weight_i \,\AGI(\error_i).
 \end{equation}
-That is, the AGI of the MQG is simply the weighted average of the component AGIs, so there is no hope of reducing it by combining various implementations.
+That is, the AGI of the effective error channel is simply the weighted average of the component AGIs, so MQGs provide little benefit for reducing the AGI.
 However, the diamond distance is a nonlinear function of error map.
-As we show in the appendix (\ref{sub:diamond_distance_inequality}):
+As we show in the appendix (\ref{sub:diamond_distance_inequality}),
 \begin{equation}
 	\label{eq:diamond_ineq}
-	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
+	\dnorm\!\left(\error_{\rm eff}\right) \le \sum_i \weight_i \, \dnorm(\error_i).
 \end{equation}
-So by mixing various implementations, each with a different error channel, the resulting channel can have a diamond distance error less than any of the component implementations.
+So by mixing various implementations, each with a different error channel, the resulting channel can have a diamond distance error that is less than the diamond distance error of any of the component implementations.
 
-Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.
+Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered these mixed channels using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.
 Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a MQG with quadratically suppressed diamond distance to the target.
 Explicitly, the weights are chosen such that the error generator is canceled to first order.
-Using (\ref{eq:effective_error}) and (\ref{eq:generator}), the effective error map for a MQG in terms of the component error generators is:
+Using (\ref{eq:effective_error}) and (\ref{eq:generator}), the effective error map for a MQG in terms of the component error generators is,
 \begin{align}
 	\label{eq:generators_and_effective_error}
-	\mathcal{E}_{\rm eff} \simeq \left(\mathcal{I}_d + \sum_i w_i \mathcal{L}_i + \frac{1}{2} \sum_i w_i \mathcal{L}_i^2\right)
+	% \errmat_{\rm eff} \simeq \left(\identmat_d + \sum_i \weight_i \genmat_i + \frac{1}{2} \sum_i \weight_i \genmat_i^2\right)
+	\errmat_{\rm eff} \simeq \sum_i \weight_i \left(\identmat_d + \genmat_i + \frac{1}{2}  \genmat_i^2\right)
 \end{align}
-If, as Campbell required, the origin is in the convex hull of the generators (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $w_i^*$, such that $\sum_i w^*=1$ and:
+These error generators lie in a vector space.
+If, as Campbell required, the origin lies in their convex hull (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $\weight_i^*$, such that $\sum_i \weight^*=1$ and,
 \begin{align}
 	\label{eq:cancel}
-	&\sum_i w_i^* \mathcal{L}_i= 0
-	% \mathrm{with}\;&\sum_i w_i = 1
+	&\sum_i \weight_i^* \genmat_i= 0
+	% \mathrm{with}\;&\sum_i \weight_i = 1
 \end{align}
+When this condition is satisfied, we call the resulting operation a \emph{generator-exact} MQG.
 
-If the error rates, as measured by the diamond distance, of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$.
+If the diamond distance error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the diamond distance error rate of the MQG is bounded by $\alpha^2$.
 Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\eqref{eq:cancel} were Hamiltonians.
@@
 If, however, the error map contains stochastic components, then the condition of Eq.~\eqref{eq:cancel} might be impossible to satisfy.
-Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull.
+Such errors always have strictly positive probabilities, so the origin can \emph{never} lie in their convex hull.
 This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators.
-In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.
+In the rest of this paper, we will be considering gates subject only to unitary errors, so we will neglect this complication going forward.
+\note{Use the notation "first-order exact MQG" when "Pauli-exact MQG" to the  }
 
@@
   \includegraphics[width=\columnwidth]{vectorspace.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-These error Hamiltonians lie in a vector space, which we illustrate as two-dimensional here.
-a) Four effective Hamiltonians.
-The origin is not contained in their convex hull, so there are no MQGs.
-b) After including an additional control solution, the convex hull grows to contain the origin, and so an MQG exists.
-c) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a MQG may drift, leading to a first-order error.
-d) The derivatives also lie in a vector space.
-If the origin lies in their convex hull, then it may be possible to construct a MQG.}
+  \caption{A target unitary gate can be implemented a number of ways, each associated with a different error generator, $\genmat_i$.
+These generators lie in a vector space, which we illustrate as two-dimensional here.
+a) Four error generators.
+The origin is not contained in their convex hull, so there are no exact MQGs.
+b) After including an additional control solution, the convex hull grows to contain the origin, and so an exact MQG exists.
+}
   \label{fig:vectorspace}
@@
 
-While Campbell's approach can provide a guaranteed suppression of the error rate, it does not necessarily lead to a purely stochastic channel.
+While generator-exact MQGs provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be a purely stochastic.
 Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel.
-In order to definitively eliminate these coherent errors, we seek weights, $w_i$, that annihilate the off-diagonal entries of the unital submatrix of the effective error map, resulting in an effective error:
+In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the unital submatrix of the effective error map.
+The resulting diagonal error map is Pauli stochastic.
+For a single qubit gate, it takes the form,
 % \begin{equation}
-% 	\mathcal{E}_{eff} = 
+% 	\errmat_{eff} = 
 % 	\left(\begin{array}{@{}ccccc@{}}
@@
 % \end{equation}
-
 \begin{equation}
-	\mathcal{E}_{\rm{eff}} = 
+	\errmat_{\rm{eff}} = \sum_i \weight_i^P \errmat_i = 
 	\left(\begin{array}{@{}ccccc@{}}
@@
 	\end{array} 	
-	\right).
+	\right),
 \end{equation}
-The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability.
-We can formulate this problem analogously to the generator approach.
-The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.
+where $p_x, p_y$ and $p_z$ are the rates of Pauli $X$, $Y$, and $Z$ errors, respectively.
+We refer to such channels as \emph{Pauli-exact} MQGs, and the same geometric argument we used in constructing generator-exact MQGs is again applicable here.
+The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$.
 
-In the remainder of this paper, we will formalize this process, presenting explicit convex optimizations to both generate a family of unitary controls and construct the optimal weighting vector.
-We will discuss how one might include additional desiderata, including a reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the mixed gate.
+In the remainder of this paper, we will formalize this process, presenting efficient convex programs to both generate a family of unitary controls and compute the weights required to yeild either type of MQG.
+We discuss how one might include additional desiderata, including reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the MQG.
 
@@
 % % 	angle &  infidelity & distance \\
-% % 	$\theta$ & $\epsilon_{\mathcal{F}}$ & $\epsilon_{\diamond}$ \\
+% % 	$\theta$ & $\AGI$ & $\epsilon_{\diamond}$ \\
 % % 	\hline\hline
@@
 % \begin{equation}
-% \mathcal{E}(\theta) = \exp(\theta \mathcal{L}_z) =
+% \errmat(\theta) = \exp(\theta \genmat_z) =
 % 	\left(\begin{array}{ccccc}
@@
 % \end{equation}
-% Where the z-axis generator, $\mathcal{L}_z$ is:
+% Where the z-axis generator, $\genmat_z$ is:
 % \begin{equation}
-% 	\mathcal{L}_z =
+% 	\genmat_z =
 % 	\left(\begin{array}{ccccc}
@@
 % \end{equation}
-% The diamond distance associated with such an error is $\epsilon_\diamond(\mathcal{E}(\theta)) \simeq \theta$, while the fidelity is $\epsilon_\mathcal{F}(\error(\theta)) \simeq \theta^2$.
+% The diamond distance associated with such an error is $\dnorm(\errmat(\theta)) \simeq \theta$, while the fidelity is $\AGI(\error(\theta)) \simeq \theta^2$.
 Because 0 lies in the covex hull of the Following the Campbell procedure, we would assign weights $w = $
@@
 % 	\end{array} 	
-% 	\right) \simeq \mathcal{I} - 
+% 	\right) \simeq \identmat - 
 % 	\left(\begin{array}{ccccc}
@@
 %  can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).
-
-% ==============================================================================
-% Section: Constructing Useful mixed quantum gates
-% ==============================================================================
-\section{Constructing mixed quantum gates}
-\label{sec:mixed_unitary_processes}
-\noindent In this section, we present a methodology for producing useful mixed quantum channels, formalizing the intuitive approach discussed above.
-As mentioned, our method requires two steps.
-The first is a control synthesis step, in which we construct an ensemble of gate implementations.
-Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use quantum optimal control theory to produce these ensembles.
-By running simple gradient descent algorithms, such as GRAPE \cite{Khaneja2005}, with different random initial seeds, one can quickly construct large ensembles of approximate quantum gates.
-We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
-We note that advanced quantum control protocols may provide a more principled approach to control synthesis.
-DMORPH \cite{dominy2008exploring}, for example, provides a means of exploring continuous families of controls on fidelity level sets, thereby enabling further optimizations  fst secondary criteria, such as robustness or duration.
-
-The remainder of this section will focus on the second step of constructing the optimal weight vector to reduce the coherence of the effective error channel.
-We will begin by discussing two classes of optimization targets, i) cancelation of the first-order generator, and ii) elimination of the off-diagonal elements of the error channel.
-We then discuss a set of additions to the numerical optimization that can improve the performance by i) incorporating robustness to drift,  ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
-
-% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
-In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
-As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
-In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
-
-% ==============================================================================
-% Section: Generators
-% ==============================================================================
-\subsection{Optimization Targets}
-\subsubsection{First-order generators} % (fold)
-\label{sub:first_order_generators}
-
-One reason to construct an MQG is to improve the worst-case performance of a quantum gate.
-The worst-case performance is bounded by the diamond distance to the target, which would constitute a natural optimization target:
-\begin{equation}\label{eq:ddmin}
-  \begin{split}
-    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } \hspace{.5cm} \epsilon_\diamond\left(\sum_i\mathsf{E}_i \omega_i\right)
-  \end{split}
-\end{equation}
-The diamond distance, however, is a non-linear function that in general requires a convex optimization to compute\cite{watrous2018theory}.
-This can dramatically slow down iterative optimizers, and so minimizing the diamond distance is a computationally expensive optimization target.
-However, if the errors are small enough, we can consider a linearized problem, minimizing the diamond distance to first-order in the effective error generator.
-As discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond distance of an MQG with error generators $\{\mathcal{L}_i\}$ to first order is:
-\begin{equation}\label{eq:campbell-condition}
-\sum \omega_i \mathcal{L}_i = 0
-\end{equation}
-In \cite{Campbell2017} Campbell presents an algorithm that, given an oracle that produces approximate unitary operations, will generate controls and weightings to find an MQG with this property.
-Alternatively, one might consider the following problem: \textit{Given a fixed collection of controls, how can I produce a weighting with minimal diamond norm?} Such a situation might arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we are given a collection of precomputed gate implementations.
-Given such an MQC with $m$ members, we can consider the $d^4\times m$ matrix whose columns are the vectorized error generators:
-\begin{equation}\label{eq:vectorized_generators}
-	\bold{L} = \left(\begin{array}{cccc}
-		\mathcal{L}_{1_{1,1}} & \mathcal{L}_{2_{1,1}} & \ldots   \\ 
-		\vdots\ & \ddots &    \\
-		\mathcal{L}_{1_{d^2,d^2}} &  &  \mathcal{L}_{m_{d^2,d^2}} \\ 
-	\end{array} 	
-	\right)
-\end{equation}
-To satisfy (\ref{eq:campbell-condition}), we can write the sum as a matrix product and solve the following optimization problem, which will be zero if and only if the sum is zero:
-
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||\bold{L}\omega||_2\\
-  \end{split}
-\end{equation}
-where $||\cdot||_2$ is the $\ell_2$ norm.
-
-As denoted, this optimization needs to be constrained so that $\omega$ is a proper probability distribution.
-Nevertheless, this forms a convex optimization problem, and such linearly constrained minimization problems with quadratic cost functions have been proven to be efficiently solvable by, e.g.
-the ellipsoid method \cite{wright1999numerical, khachiyan}.
-More importantly, there are many existing convex solver software packages that solve these problems efficiently in practice.
-
-%In both cases it is clear that we should select the gates with smaller error, i.e.
-$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
-Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
-\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
-We will discuss numerical approaches to solving this Section \ref{sec:norm}.
-
-%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
-In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
-Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
-In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
-
-% subsection first_order_generators (end)
-
-% ==============================================================================
-% Section: Off-diagonals
-% ==============================================================================
-
-\subsubsection{Approximate Pauli Channel} % (fold)
-\label{sub:off_diagonals}
-There are other properties of a channel that one might consider optimizing.
-For instance, if an MQG has an error channel that is well-approximated by a Pauli-Stochastic channel, then it may be amenable to classical simulation.
-We can modify our optimization problem accordingly.
-By vectorizing the $R$ submatrices in (\ref{eq:process_matrix}), and considering the matrix of off-diagonal terms, we can again consider the minimization problem in (\ref{eq:minimization}), where we replace $\bold{L}$ with $\bold{R}$:
-
-\begin{equation}\label{eq:vectorized_off_diagonal}
-	\bold{R} = \left(\begin{array}{cccc}
-		R_{1_{2,1}} & R_{2_{2,1}} & \ldots   \\ 
-		\vdots\ & \ddots &    \\
-		R_{1_{n-1,n-1}} &  &  R_{m_{n-1,n-1}} \\ 
-	\end{array} 	
-	\right)
-\end{equation}
-
-In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel.
-If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods.
-Better yet, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
-
-% subsection off_diagonals (end)
-
-% ==============================================================================
-% Section: Robustness
-% ==============================================================================
-\subsection{Additional Constraints}
-\subsubsection{Adding robustness} % (fold)
-\label{sub:adding_robustness}
-While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance.
-Because of this drift, the quality of the MQG will degrade.
-Thus, we would like to design MQGs that are robust to this drift.
-To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and if the fluctuations are small enough, it is convenient to write the gate as a Taylor expansion in this small parameter:
-\begin{equation}\label{eq:taylor}
-\begin{gathered}
-\tilde{\mathcal{G}_i}(d\vec{\delta}) = \exp(-i(\mathcal{L}_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\mathcal{L}_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \mathcal{L}_i(\vec{0})d\delta_j d\delta_k + \ldots))\mathcal{G}
-\end{gathered}
-\end{equation}
-
-Now, instead of requiring that only the error generators average to zero, we can additionally impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
-Specifically, we are interested in the $n^{th}$ order derivatives:
-\kcy{Should the figures change from H to something else?}
-\amp{Right.
-It seems to me they should be written as something like $D^1_{i,k}$.
-Then in the equation below I can use the comma notation, but for the $i^{th}$ derivative it's going to be some gross multi-index...
-I think your point is that the comma is standard notation (although I've never used it before.)}
-\begin{equation}
-\label{eq:derivative}
-D^n_{i, (j_1, \ldots, j_n)} = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\mathcal{L}_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
-\end{equation}
-If the dimension of $\vec{\delta}$ is $d$, the indices $j_1, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that an MQG is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
-\begin{equation}\label{eq:MQG}
-\begin{gathered}
-\sum_i\omega_i(\sum_{n=0}^k D^n_i)^n = 0\\
-\end{gathered}
-\end{equation}
-In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}). More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$. 
-By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is a pproximately satisfied in the sense that:
-\begin{equation}\label{eq:MQG-relaxed}
-\begin{gathered}
-||\sum\omega_iD^n_i||+ \mathcal{O}(\alpha^2) = 0\\
-\end{gathered}
-\end{equation}
-where $||\cdot||$ is the Frobenius norm.
-This condition guarantees, as before, that errors will be suppressed to second order in $\alpha$, but now for all derivatives up to order $\ell$.
-%A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
-Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm.
-We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
-As discussed in \cite{Campbell2017}, the geometric picture for 0MQGs is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
-Figure \ref{fig:vectorspace} generalizes this picture to 1MQGs and gives intuition for the conditions required to produce them.
-To generate $\ell$MQGs, we first define the vectorized derivative matrix ${\bold{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
-\begin{equation}
-{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
-		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
-		\vdots\ & \ddots &    \\
-		D^\ell_{1_{d^2,d^2}} &  &  D^\ell_{m_{d^2,d^2}} \\ 
-	\end{array} 	
-	\right)
-\end{equation}
-
-Using this, we can then solve the following convex optimization problem, generalizing (\ref{eq:minimization}):
-
-\begin{equation}\label{eq:robust_minimization}
-  \begin{split}
-    &\underset{\omega_i\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||_1\\
-    &\textbf{subject to: } \forall n<\ell, ||\sum \omega_iD_i^n||=0\\
-  \end{split}
-\end{equation}
-with $D_n^i$ defined in (\ref{eq:derivative}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-a) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a MQG may drift, leading to a first-order error.
-b) The derivatives also lie in a vector space.
-If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$\amp{I'm not sure what you mean by the $_k$ subscript, nor why the tensor product is there.
-Also I think your indices are backwards?} then it may be possible to construct a robust 1-MQG.
-\kcy{This should appear in the main text somewhere.
-When we add the derivatives we make our space larger, but we still want the origin to be in the higher-dimensional convex hull.}}
-  \label{fig:vectorspace}
-\end{figure}
-
-% subsection adding_robustness (end)
-
-% ==============================================================================
-% Section: Norm regularization
-% ==============================================================================
-
-\subsubsection{Hamiltonian Norm Regularization}
-\label{sec:norm}
-While quadratic programs with equality constraints have analytic solutions, the program we are considering has both constraints on the norm of the weight vector, and inequality constraints.
-Additionally, casting this problem as a convex optimization problem allows us to add penalty terms to the cost function to promote different properties of the MQG.
-In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent errors.
-To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
-In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
-
-\newcommand{\bunderbrace}[2]{%
-  \begin{array}[t]{@{}c@{}}
-  #1\\
-  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
-  \end{array}
-}
-
-\begin{equation}\label{eq:minimization_l2}
-\begin{split}
-& \ \bunderbrace{\textbf{minimize}: }{\omega_i\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}\omega||_1+ \eta\sum\omega_i||D^0_i||_2\\
-&\ \ \textbf{subject to: } \forall n<\ell, ||\sum \omega_iD_i^n||=0\\
-\end{split}
-\end{equation}
-with $\eta \geq 0$.
-By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
-The value of $\eta$ that is best for any particular problem instance will depend on the values in $\bold{D}^\ell$.
-
-%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
-However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
-% ==============================================================================
-% Section: Sparsity
-% ==============================================================================
-
-\subsubsection{Sparsity Constraints}
-\label{sec:sparsity}
-As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MQGs only require a small number of controls.
-As an example, consider Figure \ref{fig:vectorspace}.
-In b), it is clear that $H_4$ is unnecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that a $0$MQG exclude $H_4$.
-However, if we additionally want our controls to form a 1MQG, we see from d) that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
-
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\omega$ to be a valid probability distribution.
-Lasso regularization works by penalizing solutions with large $\ell_1$ norm, however if $\omega$ represents probabilities, it will always have an $\ell_1$ norm of one.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
-
-\begin{equation}\label{eq:minimization_regularization}
-\begin{split}
-&\underset{m\in[N]}{\textbf{minimize}}\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\omega_i\geq0, |\omega|_1=1,\\ t\geq0} ||{\bold{D}^{\ell}}\omega||_1 + t\\
-&\ \ \textbf{subject to: } \omega_m > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \omega_iD_i^n||=0
-\end{split}
-\end{equation} with $\lambda\geq0$.
-As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\bold{D}^\ell$ and how sparse the solution needs to be.
-In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
 
@@
 Finally, we assume that the errors on $\sigma_x$ and $\sigma_y$ are perfectly correlated, as in our experimental implementation.
+We note that advanced quantum control protocols may provide an even more principled approach to control synthesis.
+DMORPH \cite{dominy2008exploring}, for example, explores continuous families of controls on fidelity level sets, thereby enabling further optimizations against secondary criteria, such as the duration of the control pulse or robustness to drift.
 
@@
 % ==============================================================================
+% Section: Constructing Useful mixed quantum gates
+% ==============================================================================
+\section{Constructing mixed quantum gates}
+\label{sec:mixed_unitary_processes}
+\noindent In this section, we present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above.
+As mentioned, our method requires two steps.
+The first is a control synthesis step, in which we construct an ensemble of gate implementations.
+Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use utilize quantum optimal control theory.
+Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target.
+By seeding such algorithms with many initial guesses, one can quickly construct a large ensemble of approximate quantum gates, each with a different error.
+We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
+
+The remainder of this section will assume such a capability for generating a large ensemble of gate implementations, and will focus instead on the second step: constructing a distribution over that ensemble that reduces the coherence of the effective error channel.
+We will begin by discussing the two broad optimization targets introduced above: i) generator-exact MQGs and ii) Pauli-exact MQGs.
+We then propose a set of secondary targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
+
+% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
+In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
+As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
+In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
+
+% ==============================================================================
+% Section: Generators
+% ==============================================================================
+\subsection{Convex Programs for Mixed Quantum Gates}
+\subsubsection{Generator-exact MQGs} % (fold)
+\label{sub:first_order_generators}
+\noindent A compelling reason to construct an MQG is to improve the worst-case performance of a quantum gate.
+The diamond distance bounds this worst-case performance, and so one might assume minimizing it would be a natural optimization target:
+\begin{equation}\label{eq:ddmin}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm} \dnorm\left(\sum_i\error_i \weight_i\right)
+  \end{split}
+\end{equation}
+The diamond distance, however, is a non-linear function that in general requires its own convex optimization to compute\cite{watrous2018theory}.
+This can dramatically slow down iterative optimizers, and so directly minimizing the diamond distance is a computationally burdensome optimization target.
+However, for quantum computing purposes the error rates are typically quite small, so we can consider a linearized problem, minimizing the diamond distance at first-order in the effective error generator.
+As discussed around Eq.~\eqref{eq:cancel}, if the origin lies in in the convex hull of the generators, $\mathbf{0} \in \mathsf{conv}(\{\genmat_i\})$, then we can construct a generator-exact MQG.
+In \cite{Campbell2017} Campbell presents an iterative algorithm that, given an oracle that produces approximate unitary operations, will continually generate controls until the geometric constraint is satisfied and then identify the optimal weighting.
+We consider instead a situation in which one has access only to $m$ distinct, precomputed gate implementations and we wish to to identify the  MQG with minimum error.
+An efficiently computable heuristic is to minimize the Frobenius norm of the first-order effective error generator:
+\begin{equation}\label{eq:frobmin}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm}  \left\vert\left\vert\sum_i \weight_i \genmat_i \right\vert\right\vert_F
+  \end{split}
+\end{equation}
+This optimization problem is equivalent to:
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2\\
+  \end{split}
+\end{equation}
+Where $\mathbf{L}=\left( \mathsf{col}(\genmat_1) \; \mathsf{col}(\genmat_2) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked error generators and $||\cdot||_2$ is the $\ell_2$ norm.
+
+The constraints on these optimizations are required to ensure that the weights, $\weight_i$, form a proper probability distribution.
+Nevertheless, linearly constrained minimization problems with quadratic cost functions are convex and have been proven to be efficiently solvable by, e.g.
+the ellipsoid method \cite{wright1999numerical, khachiyan}.
+Many existing convex solver software packages are available that can solve these problems efficiently in practice.
+\kcy{Need some citations here.}
+
+%In both cases it is clear that we should select the gates with smaller error, i.e.
+$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
+Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
+\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
+We will discuss numerical approaches to solving this Section \ref{sec:norm}.
+
+%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
+Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
+In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
+
+% subsection first_order_generators (end)
+
+% ==============================================================================
+% Section: Off-diagonals
+% ==============================================================================
+
+\subsubsection{Pauli-exact MQGs} % (fold)
+\label{sub:off_diagonals}
+As quantum devices grow in size, it is increasingly expensive to simulate their dynamics.
+Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
+As discussed above, Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
+\note{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
+
+As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$.
+We wish to construct an MQG whose effective error is Pauli-stochastic and is therefore diagonal.
+This can be done with the following simple minimization:
+\begin{equation}\label{eq:minimization2}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_1=1}{\textbf{minimize}: } ||\sum_i\weight_i \errmat_i - \mathsf{diag}(\sum_i \weight_i \errmat_i)||_2\\
+  \end{split}
+\end{equation}
+Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero.
+This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of $\errmat_i$.
+\footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to
+\begin{equation}\label{eq:minimization3}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{E}\cdot\vec\weight||_2
+  \end{split}
+\end{equation}
+The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both.
+
+\kcy{do something with the paragraph}
+In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel.
+If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods.
+Better yet, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
+
+% subsection off_diagonals (end)
+
+% ==============================================================================
+% Section: Robustness
+% ==============================================================================
+\subsection{Additional Constraints}
+\noindent 
+Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly.
+It is often the case that one will have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
+This often leads to the the minimization problems discussed in the previous section being massively under-constrained, yielding many possible exact solutions.
+Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area.
+In this section we present explicit convex programs for such secondary objectives, including adding robustness to drift or model uncertainty, reducing the effective gate error, and minimizing the number of constituent gates utilized by the MQG.
+
+\subsubsection{Robustness to drift and model uncertainty} % (fold)
+\label{sub:adding_robustness}
+\noindent 
+While mixed quantum gates offer significant performance improvements, their construction assumes a good knowledge of the errors experienced by the constituent gates.
+But often the gates are not perfectly well characterized.
+This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \kcy{cite Tim's drift manuscript}.
+In either case, the performance of the MQG will be negatively impacted.
+We can model the effect of this uncertainty by writing the gate
+
+If the uncertainty in our estimate of the gate errors is small, then we can write a gate's error generator as a Taylor expansion in the model uncertainty
+\begin{equation}
+	\genmat_i(\vec \delta) = \genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\vec 0) + \order{\delta^2}
+\end{equation} 
+In the above expression we have used the comma derivative, 
+\begin{equation}
+	\genmat_{i,k}(\vec \delta_0) = \frac{\partial}{\partial \delta_k} \genmat_i(\vec\delta) \vert_{\vec \delta=\delta_0}.
+\end{equation}
+
+most control electronics experience drift over time scales relevant to QIP performance.
+Because of this drift, the quality of the MQG will degrade.
+Thus, we would like to design MQGs that are robust to this drift.
+To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and if the fluctuations are small enough, it is convenient to write the gate as a Taylor expansion in this small parameter:
+\begin{equation}\label{eq:taylor}
+\begin{gathered}
+\tilde{\tarmat_i}(d\vec{\delta}) = \exp(-i(\genmat_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\genmat_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \genmat_i(\vec{0})d\delta_j d\delta_k + \ldots))\tarmat
+\end{gathered}
+\end{equation}
+
+Now, instead of requiring that only the error generators average to zero, we can additionally impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
+Specifically, we are interested in the $n^{th}$ order derivatives:
+\kcy{Should the figures change from H to something else?}
+\amp{Right.
+It seems to me they should be written as something like $D^1_{i,k}$.
+Then in the equation below I can use the comma notation, but for the $i^{th}$ derivative it's going to be some gross multi-index...
+I think your point is that the comma is standard notation (although I've never used it before.)}
+\begin{equation}
+\label{eq:derivative}
+D^n_{i, (j_1, \ldots, j_n)} = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\genmat_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
+\end{equation}
+If the dimension of $\vec{\delta}$ is $d$, the indices $j_1, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
+We say that an MQG is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
+\begin{equation}\label{eq:MQG}
+\begin{gathered}
+\sum_i\weight_i(\sum_{n=0}^k D^n_i)^n = 0\\
+\end{gathered}
+\end{equation}
+In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}). More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$. 
+By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
+Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is a pproximately satisfied in the sense that:
+\begin{equation}\label{eq:MQG-relaxed}
+\begin{gathered}
+||\sum\weight_iD^n_i||+ \order{\alpha^2} = 0\\
+\end{gathered}
+\end{equation}
+where $||\cdot||$ is the Frobenius norm.
+This condition guarantees, as before, that errors will be suppressed to second order in $\alpha$, but now for all derivatives up to order $\ell$.
+%A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
+Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\weight}$ exists that quadratically decreases the diamond norm.
+We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\weight}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
+As discussed in \cite{Campbell2017}, the geometric picture for 0MQGs is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
+Figure \ref{fig:vectorspace} generalizes this picture to 1MQGs and gives intuition for the conditions required to produce them.
+To generate $\ell$MQGs, we first define the vectorized derivative matrix ${\mathbf{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
+\begin{equation}
+{\mathbf{D}^{\ell}} =  \left(\begin{array}{cccc}
+		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
+		\vdots\ & \ddots &    \\
+		D^\ell_{1_{d^2,d^2}} &  &  D^\ell_{m_{d^2,d^2}} \\ 
+	\end{array} 	
+	\right)
+\end{equation}
+
+Using this, we can then solve the following convex optimization problem, generalizing (\ref{eq:minimization}):
+
+\begin{equation}\label{eq:robust_minimization}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||{\mathbf{D}^{\ell}}\weight||_1\\
+    &\textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
+  \end{split}
+\end{equation}
+with $D_n^i$ defined in (\ref{eq:derivative}).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
+  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
+a) The error Hamiltonians shown with their derivative with respect to a control parameter.
+As this parameter drifts, a MQG may drift, leading to a first-order error.
+b) The derivatives also lie in a vector space.
+If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \oplus H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$\amp{I'm not sure what you mean by the $_k$ subscript, nor why the tensor product is there.
+Also I think your indices are backwards?} then it may be possible to construct a robust 1-MQG.
+\kcy{This should appear in the main text somewhere.
+When we add the derivatives we make our space larger, but we still want the origin to be in the higher-dimensional convex hull.}}
+  \label{fig:vectorspace}
+\end{figure}
+
+% subsection adding_robustness (end)
+
+% ==============================================================================
+% Section: Norm regularization
+% ==============================================================================
+
+\subsubsection{Hamiltonian Norm Regularization}
+\label{sec:norm}
+While quadratic programs with equality constraints have analytic solutions, the program we are considering has both constraints on the norm of the weight vector, and inequality constraints.
+Additionally, casting this problem as a convex optimization problem allows us to add penalty terms to the cost function to promote different properties of the MQG.
+In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
+As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent errors.
+To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
+In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
+
+\newcommand{\bunderbrace}[2]{%
+  \begin{array}[t]{@{}c@{}}
+  #1\\
+  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
+  \end{array}
+}
+
+\begin{equation}\label{eq:minimization_l2}
+\begin{split}
+& \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1} ||{\mathbf{D}^{\ell}}\weight||_1+ \eta\sum\weight_i||D^0_i||_2\\
+&\ \ \textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
+\end{split}
+\end{equation}
+with $\eta \geq 0$.
+By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
+The value of $\eta$ that is best for any particular problem instance will depend on the values in $\mathbf{D}^\ell$.
+
+%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
+However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
+% ==============================================================================
+% Section: Sparsity
+% ==============================================================================
+
+\subsubsection{Sparsity Constraints}
+\label{sec:sparsity}
+As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
+Control electronics often have a limited amount of waveform memory, and thus it is important that MQGs only require a small number of controls.
+As an example, consider Figure \ref{fig:vectorspace}.
+In b), it is clear that $H_4$ is unnecessary to contain the origin in the convex hull of the error generators.
+Thus we would prefer that a $0$MQG exclude $H_4$.
+However, if we additionally want our controls to form a 1MQG, we see from d) that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
+
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\weight$ to be a valid probability distribution.
+Lasso regularization works by penalizing solutions with large $\ell_1$ norm, however if $\weight$ represents probabilities, it will always have an $\ell_1$ norm of one.
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
+
+\begin{equation}\label{eq:minimization_regularization}
+\begin{split}
+&\underset{m\in[N]}{\textbf{minimize}}\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1,\\ t\geq0} ||{\mathbf{D}^{\ell}}\weight||_1 + t\\
+&\ \ \textbf{subject to: } \weight_m > \frac{\lambda}{t}\\
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \weight_iD_i^n||=0
+\end{split}
+\end{equation} with $\lambda\geq0$.
+As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\mathbf{D}^\ell$ and how sparse the solution needs to be.
+In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
+
+% ==============================================================================
 % Section: Acknowledgements
@@
 This material was funded in part by the U.S.
-Department of Energy, Office of Science, Office of Advanced Scientific Computing Research Quantum Testbed Program.
+Department of Energy, Office of Science, Office of Advanced Scientific Computing Research Quantum Testbed Program, as well as by Sandia National Laboratories' Laboratory Directed Research and Development program.
 Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S.
@@
 
-\newpage
+% b
 % \onecolumngrid
@@
 % ==============================================================================
-\subsection{Diamond distance inequality}
+\subsection{Proof of diamond distance inequality}
 \label{sub:diamond_distance_inequality}
@@
 \begin{equation}
-	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum w_i \, \epsilon_\diamond(\mathsf{E}_i).
+	\dnorm\!\left(\error_{\rm eff}\right) \le \sum \weight_i \, \dnorm(\error_i).
 \end{equation}
-The effective error channel for a mixed quantum gate is $\mathsf{E}_{\rm{eff}} = \sum w_i\,\mathsf{E}_i$, where $\mathsf{E}_i$ are the error channels for the component gates.
+The effective error channel for a mixed quantum gate is $\error_{\rm{eff}} = \sum \weight_i\,\error_i$, where $\error_i$ are the error channels for the component gates.
 The diamond distance to the identity of the effective error channel is:
 \begin{align}
-	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
-		&= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
-										  - (\mathsf{E}_{\rm eff} \otimes \mathsf{I}_d)(\rho) \vert\vert_1\\
-		% &= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
-										  % - (\sum_i w_i\,\mathsf{E}_i \otimes \mathsf{I}_d)(\rho) \vert\vert_1 \\
-		&= \frac{1}{2} \sup_\rho \vert \vert \sum w_i\,((\mathsf{I}_d
-										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho) \vert\vert_1
+	\dnorm \left(\error_{\rm eff}\right)
+		&= \frac{1}{2} \sup_\rho \vert \vert (\ident_d\otimes \ident_d)(\rho) 
+										  - (\error_{\rm eff} \otimes \ident_d)(\rho) \vert\vert_1\\
+		% &= \frac{1}{2} \sup_\rho \vert \vert (\ident_d\otimes \ident_d)(\rho) 
+										  % - (\sum_i \weight_i\,\error_i \otimes \ident_d)(\rho) \vert\vert_1 \\
+		&= \frac{1}{2} \sup_\rho \vert \vert \sum \weight_i\,((\ident_d
+										  - \error_i) \otimes \ident_d)(\rho) \vert\vert_1
 \end{align}
@@
 \begin{align}
-	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
-		&= \frac{1}{2} \vert \vert \sum w_i\,((\mathsf{I}_d
-										  - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*) \vert\vert_1 \\
-		&= \frac{1}{2} \vert \vert \sum w_i\, \rho^*_i \vert\vert_1,
+	\dnorm \left(\error_{\rm eff}\right)
+		&= \frac{1}{2} \vert \vert \sum \weight_i\,((\ident_d
+										  - \error_i) \otimes \ident_d)(\rho^*) \vert\vert_1 \\
+		&= \frac{1}{2} \vert \vert \sum \weight_i\, \rho^*_i \vert\vert_1,
 \end{align}
-where we have defined $\rho^*_i = ((\mathsf{I}_d - \mathsf{E}_i) \otimes \mathsf{I}_d)(\rho^*)$.
-The nuclear norm above is equal to the sum of the singular values of $\sum w_i \rho_i$.
+where we have defined $\rho^*_i = ((\ident_d - \error_i) \otimes \ident_d)(\rho^*)$.
+The nuclear norm above is equal to the sum of the singular values of $\sum \weight_i \rho_i$.
 Using the Ky Fan singular value inequality \cite{fan1951maximum} , we have
 \begin{align}
-	\epsilon_\diamond \left(\mathsf{E}_{\rm eff}\right)
-		&\le \frac{1}{2} \sum_i w_i \vert \vert \rho^*_i \vert\vert_1 \\
-		&\le \sum_i w_i\, \epsilon_\diamond(\mathsf{E}_i)
+	\dnorm \left(\error_{\rm eff}\right)
+		&\le \frac{1}{2} \sum_i \weight_i \vert \vert \rho^*_i \vert\vert_1 \\
+		&\le \sum_i \weight_i\, \dnorm(\error_i)
 \end{align}
@@
 % %\begin{equation}
-% %\deriv\sum_j \omega_je^{iH_j} = \deriv(\id + (\sum_ji%\omega_jH_j) + \sum \omega_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
+% %\deriv\sum_j \weight_je^{iH_j} = \deriv(\id + (\sum_ji%\weight_jH_j) + \sum \weight_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
 % %\end{equation}
 % \begin{equation}
-% \deriv\sum_j \omega_je^{iH_j} = \sum_j\omega_ji\deriv (H_j)e^{iH_j}
+% \deriv\sum_j \weight_je^{iH_j} = \sum_j\weight_ji\deriv (H_j)e^{iH_j}
 % \end{equation}
@@
 % \begin{equation}
-% ||\deriv\sum_j\omega_je^{iH_j}|| \leq \sum_j\omega_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\omega_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
+% ||\deriv\sum_j\weight_je^{iH_j}|| \leq \sum_j\weight_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\weight_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
 % \end{equation}
@@
 % \begin{align}
-% &= \deriv\sup|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-% &= \sup\deriv|\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I}|_1 \\
-% &\leq \sup|\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1 \\
+% &= \deriv\sup|\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat|_1 \\
+% &= \sup\deriv|\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat|_1 \\
+% &\leq \sup|\deriv(\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat)|_1 \\
 % \end{align}
@@
 % \begin{equation}
-% |\deriv(\mathcal{I}\otimes\mathcal{I}-\error(\vec{\delta})\otimes\mathcal{I})|_1
+% |\deriv(\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat)|_1
 % \end{equation}
@@
 % \begin{align}
-% &(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
-% &\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X) = \sum_j \omega_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
+% &(\mathcal{V}\circ\errmat - \id)(X) = \sum_j \weight_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
+% &\deriv(\mathcal{V}\circ\errmat - \id)(X) = \sum_j \weight_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
 % \end{align}
@@
 % \begin{align}
-% &||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq||\sum_j \omega_j\deriv\tilde{\delta}_j|| + ||\sum_j\omega_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\omega_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\omega_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
+% &||\deriv(\mathcal{V}\circ\errmat - \id)(X)||_1\leq||\sum_j \weight_j\deriv\tilde{\delta}_j|| + ||\sum_j\weight_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\weight_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\weight_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
 % \end{align}
@@
 % \begin{align}
-% ||\deriv(\mathcal{V}\circ\mathcal{E} - \id)(X)||_1\leq 2a^2 + 2b^2
+% ||\deriv(\mathcal{V}\circ\errmat - \id)(X)||_1\leq 2a^2 + 2b^2
 % \end{align}

### 2019-09-10 decorrelation/mixed_unitaries.tex
bus updates

@@
 % The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
-For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
+For long circuits, this can add up extremely quickly, and Additionalf`while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
 Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
@@
 In either case, the performance of the MQG will be negatively impacted.
-We can model the effect of this uncertainty by writing the gate
-
-If the uncertainty in our estimate of the gate errors is small, then we can write a gate's error generator as a Taylor expansion in the model uncertainty
+We can describe the effect of this uncertainty by first writing the gate explicitly as a function of the vector of model parameters, $\vec\lambda$, and their nominal values, $\vec\lambda_0$.
+These model parameters could include magnetic field strengths, laser or microwave intensities, coupling strengths, etc.
+If the parameters are close to their nominal values, then we can write a gate's error generator as a Taylor expansion in the model uncertainty, $\vec\delta = \vec\lambda-\vec\lambda_0$:
 \begin{equation}
-	\genmat_i(\vec \delta) = \genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\vec 0) + \order{\delta^2}
+	\genmat_i(\vec \delta) = \genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\vec 0) + \order{\delta^2}.
 \end{equation} 
@@
 
-most control electronics experience drift over time scales relevant to QIP performance.
-Because of this drift, the quality of the MQG will degrade.
-Thus, we would like to design MQGs that are robust to this drift.
-To enforce robustness, we can consider the generators in (\ref{eq:campbell-condition}) to be functions of a control vector $\vec{\delta}$, and if the fluctuations are small enough, it is convenient to write the gate as a Taylor expansion in this small parameter:
-\begin{equation}\label{eq:taylor}
-\begin{gathered}
-\tilde{\tarmat_i}(d\vec{\delta}) = \exp(-i(\genmat_i(\vec{0}) + \frac{\partial}{\partial\delta_j}\genmat_i(\vec{0})d\delta_j\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_j\partial\delta_k} \genmat_i(\vec{0})d\delta_j d\delta_k + \ldots))\tarmat
-\end{gathered}
+Now, rather than finding weight vectors such that only the effective generator vanishes, we can additionally impose a secondary constraint on the derivatives.  Following Eq.~\eqref{eq:minimization}, 
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2 + \sum_k||\mathbf{L}_{,k}\cdot\vec\weight||_2\\
+  \end{split}
 \end{equation}
+Where $\mathbf{L}_{,k}=\left( \mathsf{col}(\genmat_{1,k}) \; \mathsf{col}(\genmat_{2,k}) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked derivatives of the error generators with respect to the deviation $\delta_k$.
 
-Now, instead of requiring that only the error generators average to zero, we can additionally impose a similar condition on the higher-order derivatives with respect to parameters that may drift.
-Specifically, we are interested in the $n^{th}$ order derivatives:
-\kcy{Should the figures change from H to something else?}
-\amp{Right.
-It seems to me they should be written as something like $D^1_{i,k}$.
-Then in the equation below I can use the comma notation, but for the $i^{th}$ derivative it's going to be some gross multi-index...
-I think your point is that the comma is standard notation (although I've never used it before.)}
+We can additionally generalize the geometric criterion for ensuring that the minimum value of this objective is 0.
+As before, we would like the origin to lie in the convex hull of the generators, but this time we have to augment the generators with their derivatives.
+That is,
+we require that
+\begin{equation}
+\mathbf{0} \in \mathsf{conv}\left( \left\{
+\genmat_i \oplus \genmat_{i,1} \oplus \genmat_{i,2} \cdots
+\right\}	 \right).
+\end{equation}
+This is illustrated in Fig.~\ref{fig:vectorspace2}.
+
+We call a gate constructed in this way a \emph{robust} generator-exact MQG.
+Similar constructs can be used to construct robust Pauli-exact MQGs by taking derivatives of the off-diagonal elements of the error maps with respect to the model deviations.
+
+\kcy{ignore from here to end of section***********}
+
 \begin{equation}

### 2019-09-12 decorrelation/mixed_unitaries.tex
Finished up to section IVB

@@
 \newcommand{\ident}{\ensuremath{\mathsf{I}}}
+\newcommand{\0}{\ensuremath{\mathbf{0}}}
 \newcommand{\weight}{\ensuremath{w}}
 
-\def\id{\mbox{\small 1} \!\! \mbox{1}}
+\newcommand{\bunderbrace}[2]{
+  \begin{array}[t]{@{}c@{}}
+  	#1\\
+  	\parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
+  \end{array}}
 
@@
 \label{sec:introduction}
-\noindent The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error.
+\noindent The ultimate impact of a gate error on the performance of a quantum circuit depends strongly on both the magnitude and the nature of the error.
 Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor (QIP).
-Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit.
-They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}.
+Errors of this type are correlated in time and may add up constructively or destructively, depending on details of the circuit in which they appear.
+This can make it difficult to construct tight analytic bounds on circuit performance \cite{Beale2018}, and numerical studies are often limited by the high computational cost of modeling coherent errors.
 Contrast this against random, or \emph{stochastic}, errors which often result from high-frequency noise in the controls or the environment.
@@
   \includegraphics[width=\columnwidth]{simple_example.pdf}
-  \caption{A simple example of a mixed quantum gate.
-Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite coherent errors (if one implementation over-rotates by a small angle $\theta$, then the other \emph{under}-rotates by $\theta$).
+  \caption{\textbf{Simple example of a mixed quantum gate:} Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite coherent errors (if one implementation over-rotates by a small angle $\theta$, then the other \emph{under}-rotates by $\theta$).
 Each time the gate is used, one of these two implementations is chosen at random.
@@
 
-Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.
-They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
-Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary errors.
+Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations.
+They focus on errors in gate compilation, such as arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
+Different approximate gate compilations of the same target unitary will almost certainly result in different unitary errors.
 So by selecting from these various compilations at random, the resulting quantum channel becomes a mixture of unitaries \cite{DBLP:journals/corr/cs-CC-0012017}, which can have significantly less coherent error than any single compilation on its own.
@@
 
-In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates and show that the advantages of their approach can be made robust to drift in the gate implementations.
-We demonstrate that, depending on what properties of the resulting channel are desired, different numerical optimization targets may be preferred.
-We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing.
-Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, consistent with a significant reduction in the coherence of the error \cite{Ball2016}.
-We further apply our methods in simulation, constructing single- and two-qubit mixed unitary controls that are robust to drift and uncertainty in the control parameters.
-
-% Reducing the coherence of a the quantum gate error
-
-% 
-%
-
-% It has long been recognized, however, that one may inject additional decorrelating randomness
-
-% By injecting additional decorrelating randomness into the system,
-
-% By introducing additional decorrelating randomness, a number of techniques are able to convert coherent  errors into stochastic errors.
-
-% By introducing intentional additional randomness to the 
-% The gate-to-gate correlations that occur in the presence of coherent noise
-
-% \note{don't define diamond norm here}
-% The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors.
-For long circuits, this can add up extremely quickly, and Additionalf`while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict.
-Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.
-
-%Drifting control parameters or environmental variables can easily have long correlation times that result in errors which are strongly coherent over the length of a quantum circuit.
+In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates and show that the advantages of their approach can be made robust to drift and model uncertainty.
+We provide an explicit series of convex programs able to efficiently compute MQGs with a variety of useful properties.
+We demonstrate our results on a superconducting testbed device at Rigetti Computing.
+In a simple experiment based on randomized benchmarking circuits, MQGs demonstrate a marked improvement in error rates and a reduced variance in circuit outcome probabilities, consistent with a significant reduction in the coherence of the error \cite{Ball2016}.
+We further apply our methods in simulation, constructing both single- and two-qubit mixed unitary controls that are robust to drift and uncertainty in the control parameters.
 
@@
 \label{sec:rep_errors}
-\noindent Suppose that one wishes to apply a unitary gate, $\target$, on some quantum device.
-Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.
+\noindent In order to implement a desired unitary gate, $\target$, on a quantum device, one generally applies a carefully tuned sequence of classical control fields.
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, there are errors in the gate.
-If the device is fairly stable with time and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\actual$ acting on the Hilbert space of the target qubits.
+If the device is fairly stable with time\kcy{cite drift paper} and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\actual$ acting on the Hilbert space of the target qubits.
 This map can always be written as $\actual = \error\circ\target$, where $\error = \actual\circ\target^{-1}$ is the \emph{error map}, which is itself CPTP because $\target$ is unitary.
@@
 Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
+\kcy{We might need more here defining coherent noise.
+There is a lot of literature on this, most of it inconsistent.
+Try Joel's Estimating the Coherence of Noise (terrible title) and Gottesman's paper on Maximally Sensitive States.}
 
@@
 \begin{align}
-	\label{eq:generator}
 	\errmat 
 		&= \exp\left(\genmat\right) \\
+	\label{eq:generator}
 		&= \identmat_d + \genmat + \frac{1}{2}\genmat^2 + \order{\genmat^3}.
@@
 \end{equation}
-Two important error metrics are the average gate infidelity (AGI), $\AGI$, and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
+Two important error metrics are the average gate infidelity (AGI), $\AGI$, \kcy{We need a citation for this, and check if it's right!
+Gives weird answer if E = I.
+I feel like it should be $(d + \tr(\errmat))/(d+d^2)$.
+Maybe cite Nielsen's paper, or Horodecki**3.} and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
 \begin{align}
@@
 \end{align}
-These error generators lie in a vector space.
+These error generators are linear operators and so are elements of a vector space.
 If, as Campbell required, the origin lies in their convex hull (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $\weight_i^*$, such that $\sum_i \weight^*=1$ and,
@@
 If the diamond distance error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the diamond distance error rate of the MQG is bounded by $\alpha^2$.
-Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\eqref{eq:cancel} were Hamiltonians.
+For gate compilation errors, the error channels are dominated by unitary approximation error, so the error generators are Hamiltonians.
 Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull.
@@
 Such errors always have strictly positive probabilities, so the origin can \emph{never} lie in their convex hull.
-This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators.
-In the rest of this paper, we will be considering gates subject only to unitary errors, so we will neglect this complication going forward.
-\note{Use the notation "first-order exact MQG" when "Pauli-exact MQG" to the  }
+This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators, or by replacing the exact condition with a minimization, as we discuss in Sec.~\ref{sec:mixed_unitary_processes}.
 
@@
   \includegraphics[width=\columnwidth]{vectorspace.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each associated with a different error generator, $\genmat_i$.
+  \caption{\textbf{Geometric condition for existence:} A target unitary gate can be implemented a number of ways, each associated with a different error generator, $\genmat_i$.
 These generators lie in a vector space, which we illustrate as two-dimensional here.
 a) Four error generators.
-The origin is not contained in their convex hull, so there are no exact MQGs.
-b) After including an additional control solution, the convex hull grows to contain the origin, and so an exact MQG exists.
+The origin is not contained in their convex hull, so there are no generator-exact MQGs.
+b) After including an additional control solution, the convex hull grows to contain the origin, and so a generator-exact MQG exists.
 }
@@
 
-While generator-exact MQGs provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be a purely stochastic.
+While generator-exact MQGs can provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be a purely stochastic.
 Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel.
-In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the unital submatrix of the effective error map.
-The resulting diagonal error map is Pauli stochastic.
+In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the effective error map.
+The resulting diagonal error map will be Pauli stochastic.
 For a single qubit gate, it takes the form,
@@
 The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$.
+If the error map contains non-unital components or correlated Pauli stochastic errors (such as $X+Y$), then this strict geometric condition will not hold and no Pauli-exact MQG will exist.
+However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.
 
-In the remainder of this paper, we will formalize this process, presenting efficient convex programs to both generate a family of unitary controls and compute the weights required to yeild either type of MQG.
+% In the remainder of this paper, we will formalize this process, laying out efficient convex programs to both generate a family of unitary controls \kcy{do we do this?} and compute the weights required to yield either type of MQG.
 We discuss how one might include additional desiderata, including reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the MQG.
 
-% \subsection{A simple example}
-% \label{sec:simple_example}
-% \noindent As a simple example of a mixed quantum gate, consider a single-qubit and two distinct implementations of a dynamically decoupled identity gate.
-Suppose that some control parameter, $\eta$, is prone to drift, causing each of these implementations to suffer a distinct, spurious phase error.
-These errors are equivalent to a small rotations about the $\sigma_z$ axis with angles $\theta = \{-\eta, 2\eta\}$.
-% % The resulting diamond distance errors and average gate fidelities of these four implementations are summarized in the following table:
-% % \begin{center}
-% % \begin{tabular}{|c|c|c|}
-% % 	\hline
-% % 	Rotation & Average gate  & Diamond  \\
-% % 	angle &  infidelity & distance \\
-% % 	$\theta$ & $\AGI$ & $\epsilon_{\diamond}$ \\
-% % 	\hline\hline
-% % 	${+2\eta}$ 	& $4\eta^2$  & $2\eta$\\
-% % 	${+\eta}$ 	& $\;\eta^2$ & $\eta$ \\
-% % 	${-\eta}$ 	& $\;\eta^2$ & $\eta$ \\
-% % 	${-2\eta}$ 	& $4\eta^2$  & $2\eta$ \\
-% % 	\hline
-% % \end{tabular}
-% % \end{center}
-% % In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic.
-Such a channel could be constructed, for instance, by drawing from this collection uniformly at random.
-More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}.
-% The error operators are then all of the form:
-% \begin{equation}
-% \errmat(\theta) = \exp(\theta \genmat_z) =
-% 	\left(\begin{array}{ccccc}
-% 		1 & 0 & 0 & 0 \\ 
-% 		0 & \cos\theta & \sin\theta  & 0  \\
-% 		0 & -\sin\theta & \cos\theta & 0  \\
-% 		0 & 0 & 0 & 1
-% 	\end{array} 	
-% 	\right) 
-% \end{equation}
-% Where the z-axis generator, $\genmat_z$ is:
-% \begin{equation}
-% 	\genmat_z =
-% 	\left(\begin{array}{ccccc}
-% 		0 & 0 & 0 & 0 \\ 
-% 		0 & 0 & -1  & 0  \\
-% 		0 & 1 & 0 & 0  \\
-% 		0 & 0 & 0 & 0
-% 	\end{array} 	
-% 	\right).
-% \end{equation}
-% The diamond distance associated with such an error is $\dnorm(\errmat(\theta)) \simeq \theta$, while the fidelity is $\AGI(\error(\theta)) \simeq \theta^2$.
-Because 0 lies in the covex hull of the Following the Campbell procedure, we would assign weights $w = $
+% ==============================================================================
+% Section: Constructing Useful mixed quantum gates
+% ==============================================================================
+\section{Constructing mixed quantum gates}
+\label{sec:mixed_unitary_processes}
+\noindent In this section, we present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above.
+As mentioned, our method requires two steps.
+The first is a control synthesis step, in which we construct an ensemble of gate implementations.
+Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use utilize quantum optimal control theory.
+Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target.
+By seeding such algorithms with many initial guesses, one can quickly construct a large ensemble of approximate quantum gates, each with a different error channel.
+We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
+\kcy{Why should the gates we generate have any error at all?
+They shouldn't if we know the model.
+Discuss this here.}
 
-% If we were construct two channels, one with error $\error(\eta)$ and one with error $\error(-\eta)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\eta) + \error(\eta)\right)$.
-The effective channel then has a matrix representation:
-% \begin{equation}
-% 	\error(\eta) =
-% 	\left(\begin{array}{ccccc}
-% 		1 & 0 & 0 & 0 \\ 
-% 		0 & \cos\eta & 0  & 0  \\
-% 		0 & 0 & \cos\eta & 0  \\
-% 		0 & 0 & 0 & 1
-% 	\end{array} 	
-% 	\right) \simeq \identmat - 
-% 	\left(\begin{array}{ccccc}
-% 		0 & 0 & 0 & 0 \\ 
-% 		0 & \eta^2/2 & 0  & 0  \\
-% 		0 & 0 & \eta^2/2 & 0  \\
-% 		0 & 0 & 0 & 0
-% 	\end{array} 	
-% 	\right)
-% \end{equation}
-% And with same average process fidelity, $\eta^2$, but now a suppressed diamond norm $\eta^2$. Now write this in terms of the error generators $\error(\eta) = \exp(\eta G)$ where
-% \begin{equation}
-% 	G =
-% 	\left(\begin{array}{ccccc}
-% 		0 & 0 & 0 & 0 \\ 
-% 		0 & 0 & -1  & 0  \\
-% 		0 & 1 & 0 & 0  \\
-% 		0 & 0 & 0 & 0
-% 	\end{array} 	
-% 	\right)
+The remainder of this section will assume such a capability for generating a large ensemble of gate implementations, and will focus instead on the second step: constructing a distribution over that ensemble that reduces the coherence of the effective error channel.
+We will begin by discussing the two broad optimization targets introduced above: i) generator-exact MQGs and ii) Pauli-exact MQGs.
+We then propose a set of secondary targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
+
+% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
+In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
+As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
+In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
+
+% ==============================================================================
+% Section: Generators
+% ==============================================================================
+\subsection{Convex Programs for Constructing Mixed Quantum Gates}
+\subsubsection{Generator-exact MQGs} % (fold)
+\label{sub:first_order_generators}
+\noindent A compelling reason to construct an MQG is to improve the worst-case performance of a quantum gate.
+The diamond distance bounds this worst-case performance, and so one might assume minimizing it would be a natural optimization target:
+\begin{equation}\label{eq:ddmin}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm} \dnorm\left(\sum_i\error_i \weight_i\right)
+  \end{split}
+\end{equation}
+The diamond distance, however, is a non-linear function that in general requires its own convex optimization to compute\cite{watrous2018theory}.
+This can dramatically slow down iterative optimizers, and so directly minimizing the diamond distance is a computationally burdensome optimization target.
+However, for quantum computing purposes the error rates are typically quite small, so we can consider a linearized problem, minimizing the diamond distance at first-order in the effective error generator.
+As discussed around Eq.~\eqref{eq:cancel}, if the origin lies in in the convex hull of the generators, $\0 \in \mathsf{conv}(\{\genmat_i\})$, then we can construct a generator-exact MQG.
+In \cite{Campbell2017} Campbell presents an iterative algorithm that, given an oracle able to produce approximate unitary operations, will continually generate controls until the geometric constraint is satisfied and then identify the optimal weighting.
+
+As discussed in the previous section, the geometric condition illustrated in Fig.~\ref{fig:vectorspace} may not be satisfied, due perhaps to stochastic errors in the generators or possible a situation in which one has access only to $m$ distinct, precomputed gate implementations.
+In this case, we may simply wish to to identify the MQG with minimum error.
+A heuristic that is efficiently computable is to minimize the Frobenius norm of the first-order effective error generator:
+\begin{equation}\label{eq:frobmin}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm}  \left\vert\left\vert\sum_i \weight_i \genmat_i \right\vert\right\vert_F
+  \end{split}
+\end{equation}
+This optimization problem is equivalent to:
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2\\
+  \end{split}
+\end{equation}
+Where $\mathbf{L}=\left( \mathsf{col}(\genmat_1) \; \mathsf{col}(\genmat_2) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked error generators and $||\cdot||_2$ is the $\ell_2$ norm.
+
+The constraints on these optimizations are required to ensure that the weights, $\weight_i$, form a proper probability distribution.
+Linearly constrained minimization problems with quadratic cost functions are convex and have been proven to be efficiently solvable by, e.g.
+the ellipsoid method \cite{wright1999numerical, khachiyan}.
+Many existing convex solver software packages are available that can solve these problems efficiently in practice.
+\kcy{Need some citations here.}
+
+%In both cases it is clear that we should select the gates with smaller error, i.e.
+$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
+Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
+\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
+We will discuss numerical approaches to solving this Section \ref{sec:norm}.
+
+%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
+In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
+Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
+In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
+Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
+
+% subsection first_order_generators (end)
+
+% ==============================================================================
+% Section: Off-diagonals
+% ==============================================================================
+
+\subsubsection{Pauli-exact MQGs} % (fold)
+\label{sub:off_diagonals}
+As quantum devices grow in size, it is increasingly expensive to simulate their dynamics.
+Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
+As discussed above, Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
+\kcy{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
+
+As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$.
+We wish to construct an MQG whose effective error is Pauli-stochastic and is therefore diagonal.
+This can be done with the following simple minimization:
+\begin{equation}\label{eq:minimization2}
+  \begin{split}
+    &\underset{\weight_i\geq0, \sum_i\weight_1=1}{\textbf{minimize}: } ||\sum_i\weight_i \errmat_i - \mathsf{diag}(\sum_i \weight_i \errmat_i)||_2\\
+  \end{split}
+\end{equation}
+Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero.
+This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$.
+\footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to
+\begin{equation}\label{eq:minimization3}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{E}\cdot\vec\weight||_2
+  \end{split}
+\end{equation}
+The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both.
+
+\kcy{do something with the paragraph}
+If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
+As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods.
+Furthermore, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} \kcy{Why this paper?} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014}.
+This protocol can implement gates with errors that are actually Pauli stochastic.
+\kcy{Discuss randomized compiling here and in the introduction.}
+
+% subsection off_diagonals (end)
+
+% ==============================================================================
+% Section: Robustness
+% ==============================================================================
+\subsection{Secondary Objectives}
+\noindent 
+Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly.
+It is often the case that one will have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
+This can lead to the the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions.
+Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area.
+In this section we present explicit convex programs for such secondary objectives, including adding robustness to drift or model uncertainty, reducing the effective gate error, and minimizing the number of constituent gates utilized by the MQG.
+We choose to take generator-exact MQGs as our starting point, though the following sections apply equally well to Pauli-exact MQGs with only trivial modifications.
+
+\subsubsection{Robustness to drift and model uncertainty} % (fold)
+\label{sub:adding_robustness}
+\noindent 
+While mixed quantum gates offer significant performance improvements, their construction assumes a good knowledge of the errors experienced by the constituent gates.
+But often the gates are not perfectly well characterized.
+This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \kcy{cite Tim's drift manuscript}.
+In either case, the performance of the MQG will be negatively impacted.
+We can describe the effect of this uncertainty by first writing the gate explicitly as a function of a vector of model parameters, $\vec\lambda$, and their nominal values, $\vec\lambda_0$.
+These model parameters could include magnetic field strengths, laser or microwave intensities, coupling strengths, etc.
+If the parameters are close to their nominal values, then we can write a gate's error generator as a Taylor expansion in the deviation vector, $\vec\delta = \vec\lambda-\vec\lambda_0$:
+\begin{equation}
+	\label{eq:sensitivity_expansion}
+	\genmat_i(\vec \delta) = \genmat_i(\0) + \sum_k \delta_k \,\genmat_{i,k}(\0) + \order{\delta^2}.
+\end{equation} 
+In the above expression we have used the comma derivative, 
+\begin{equation}
+	\genmat_{i,k}(\vec \delta_0) = \frac{\partial}{\partial \delta_k} \genmat_i(\vec\delta) \vert_{\vec \delta=\delta_0}.
+\end{equation}
+
+Combining Eq.~\eqref{eq:sensitivity_expansion} with Eq.~\eqref{eq:generator} and taking both Taylor expansions to first order, we have:
+\begin{align}
+\notag
+	\errmat_{\rm eff} =&
+		 \identmat_d + \sum_i \weight_i \left(\genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\0) \right) \\
+		 &+ \order{\genmat_i^2 + \genmat_i \delta + \delta^2}.
+\end{align}
+We would like to choose the weights $\vec\weight$ so that the effective error generator vanishes to first order.
+We can cast this problem as a convex optimization problem, much as we did in Sec.~\ref{sec:introduction} for synthesizing generator-exact MQGs.
+Following Eq.~\eqref{eq:minimization}, we have,
+\begin{equation}\label{eq:minimization}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2 + \sum_k||\mathbf{L}_{,k}\cdot\vec\weight||_2\\
+  \end{split}
+\end{equation}
+Where $\mathbf{L}_{,k}=\left( \mathsf{col}(\genmat_{1,k}(\0)) \; \mathsf{col}(\genmat_{2,k}(\0)) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked derivatives of the error generators with respect to the deviation $\delta_k$.
+
+We can additionally generalize the geometric criterion for guaranteeing the existence of generator-exact MQGs.
+To construct a robust, generator-exact MQG, there must exist a set of weights, $\{\weight_i\}$, so that $\sum_i \weight_i \genmat_i = \sum_i \weight_i \genmat_{i,k} = 0$.
+This is equivalent to demanding the origin lie in the convex hull of the generators augmented with their derivatives:
+\begin{equation}
+\0 \in \mathsf{conv}\left( \left\{
+\genmat_i \bigoplus_k \genmat_{i,k}
+\right\}_i	 \right).
+\end{equation}
+We illustrate this in Fig.~\ref{fig:vectorspace2}.
+
+We call a gate constructed in this way a \emph{robust} generator-exact MQG.
+These techniques can easily adapted to construct robust Pauli-exact MQGs, where vectors of the off-diagonal elements of the error maps take the role of the error generators used above.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{vectorspace3.png}
+  \caption{\textbf{Geometric condition for robustness:}   A target unitary gate can be implemented a number of ways, each with a different effective error generator, $\genmat_i$.
+a) The error generators are shown as elements of a vector space (solid, black arrows).
+Also shown are their derivatives $\genmat_{i,k}$ (dashed, grey arrows) with respect to a model parameter, $\delta_k$.
+As this parameter drifts, the generators may no longer cancel.
+b) To construct a robust, generator-exact MQG, there must exist a set of weights, $\{\weight_i\}$, so that $\sum_i \weight_i \genmat_i = \sum_i \weight_i \genmat_{i,k} = 0$.
+This is equivalent to demanding that the origin lie in the convex hull $\mathsf{conv}(\{\genmat_i \bigoplus_k \genmat_{i,k} \}_i)$.
+}
+  \label{fig:vectorspace2}
+\end{figure}
+
+% subsection adding_robustness (end)
+
+% ==============================================================================
+% Section: Norm regularization
+% ==============================================================================
+
+\subsubsection{Improving the average gate fidelity}
+\label{sec:norm}
+\noindent While the geometric constraint is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the best controls possible.
+As an example, consider four erroneous implementations of a Pauli $Z$ gate: $Z_{-2\theta}$, $Z_{-\theta}$, $Z_{\theta}$, and $Z_{2\theta}$, where the subscript indicates the magnitude of the $Z$-rotation error.
+An MQG consisting of equally weighted $Z_{-2\theta}$ and $Z_{2\theta}$ is generator-exact, as is $Z_{-\theta}$ and $Z_{\theta}$.
+But the error rate\footnote{The diamond distance is equal to the AGI here.} of the first is $~4\theta^2$, while the second achieves an error rate of $\theta^2$.
+
+To incentive the inclusion of controls with smaller error, we may instead minimize the average gate infidelity of the mixed quantum gate, subject to the condition that any solution we find be generator-exact:
+
+\begin{equation}\label{eq:agi_minimization_constrained}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } \sum_i \weight_i\; \AGI(\errmat_i)\\
+    & \textbf{subject to}: ||\mathbf{L}\cdot\vec\weight||_2 = 0 
+  \end{split}
+\end{equation}
+
+If we do not expect to have a space of generator-exact solutions available, then the constraint above will never be satisfied and the minimization will fail.
+This could occur if there are simply not enough controls to satisfy the generator-exact criterion, or if the error generators have stochastic components.
+In such a case, we can choose a weighting parameter, $\eta$, to explicitly balance the two competing objectives:
+
+\begin{equation}\label{eq:agi_minimization_weighted}
+  \begin{split}
+    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2  + \eta \sum_i \weight_i\; \AGI(\errmat_i)
+  \end{split}
+\end{equation}
+
+Both optimizations are convex and efficiently solvable.
+
+% then we can instead incentivize the construction of a lowest-error MQG by including an AGI penalty directly in the
+
+% \begin{equation}\label{eq:minimization}
+%   \begin{split}
+%     &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } \sum_i \weight_i\; \AGI(\errmat_i)\\
+%     & \textbf{subject to}: ||\mathbf{L}\cdot\vec\weight||_2 = 0 
+%   \end{split}
 % \end{equation}
 
-% The effective generator vanishes at first order.
+% \begin{equation}\label{eq:minimization_l2}
+% \begin{split}
+% & \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1} ||{\mathbf{D}^{\ell}}\weight||_1+ \eta\sum\weight_i||D^0_i||_2\\
+% &\ \ \textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
+% \end{split}
+% \end{equation}
+% with $\eta \geq 0$.
+By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
+The value of $\eta$ that is best for any particular problem instance will depend on the values in $\mathbf{D}^\ell$.
 
-% In general, if we have a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results from drawing from the controls probabilistically has elements given by:
-% \begin{align}
-% 	\mathcal{M}_{jk} 
-% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
-% 		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
-% 		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
-% 		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
-% \end{align}
-% The first term corresponds to the identity, and $\sin\theta_i^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta_i\cos\theta_i$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term.
-The result would be a purely stochastic channel.
+%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
+However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
+% ==============================================================================
+% Section: Sparsity
+% ==============================================================================
 
-% The problem of minimizing the last term:
-% \begin{equation}
-% \sum_i\sin\theta_i\cos\theta_i(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)
-% \end{equation}
-%  can equivalently be cast as trying to construct a family of vectors whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).
+\subsubsection{Sparsity Constraints}
+\label{sec:sparsity}
+As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
+Control electronics often have a limited amount of waveform memory, and thus it is important to be able to construct MQGs as few constituent gates as possible.
+In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions.
+Rather than penalizing the $\ell_0$ norm of the solution, which is not convex, lasso regularization penalizes the $\ell_1$, which is the convex relaxation of the $\ell_0$ norm.
+However this is insufficient for our purposes, as we require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
 
+\kcy{Make the rest of this section consistent with the current notation.}
+\begin{equation}\label{eq:minimization_regularization}
+\begin{split}
+&\underset{m\in[N]}{\textbf{minimize}}\\
+&\ \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1,\\ t\geq0} ||{\mathbf{D}^{\ell}}\weight||_1 + t\\
+&\ \ \textbf{subject to: } \weight_m > \frac{\lambda}{t}\\
+&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \weight_iD_i^n||=0
+\end{split}
+\end{equation} with $\lambda\geq0$.
+As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\mathbf{D}^\ell$ and how sparse the solution needs to be.
+In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
+
+% ==============================================================================
+% Section: Results
+% ==============================================================================
 \section{Results} % (fold)
@@
 
-\subsection{Experimental} % (fold)
+\subsection{Experimental implementation} % (fold)
 \label{sub:experimental}
-In modern quantum computing platforms, diagnosing and correcting coherent errors remains a challenge.
-Methodologies like RPE and DRAG are sufficient for routinely achieving high single qubit fidelities in superconducting qubit architectures, however as coherence times increase, the community will continue to be interested in removing coherent errors to achieve higher fidelities.
-As a proof of principle, we implemented an MQG with a superconducting transmon qubit on the Rigetti 19Q-Acorn chip, whose performance we describe below.
-While this device consisted of 20 qubits with fixed couplings, here we will give results for a single qubit MQG on qubit 8.
-For more details about this particular device, characterization can be found in \cite{1712.05771}.
+\noindent We implemented our methods using the 19Q-Acorn superconducting transmon processor at Rigetti Computing.
+Comprehensive device characterization for this processor can be found in \cite{1712.05771}.
+While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration.
+Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$pulse calibrated by iteratively amplifying and correcting over- and under-rotation errors via repeated application.
+Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived from this waveform by scaling the amplitude of the calibrated $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+The gates therefore experience unitary over/under rotations, which are coherent errors.
+These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities, \kcy{What are they?}, respectively.
 
-To implement an MQG on this qubit, we first calibrated a 10-sample, 50ns Gaussian pulse by coherently amplifying and correcting over- and under-rotation errors through repeated application.
-After the gate was sufficiently calibrated, four intentionally miscalibrated Gaussian pulses were produced by scaling the amplitude of the calibrated $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+We characterize the performance of the MQG using a series of randomized benchmarking (RB) experiments\cite{Magesan2011}: one for each of the miscalibrated pulses, one using the calibrated pulse, and using the MQG.
+In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were gates were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
+An RB experiment consisted of $10$ sequences sampled at each of lengths $\{2, 4, 8, 16, 32, 64\}$, and each sequence was repeated $1000$ times.
+We emphasize that, when benchmarking the MQG, each sequence repetition used a new, randomly sampled sequence of waveforms consistent with its definition.
+Results of the standard RB analysis are indicated in Table.~\eqref{tabl:rb}.
+The MQG is seen to perform nearly as well as the calibrated pulse, and better than any of the constituent pulses individually.
 
-As discussed in Section \ref{sub:off_diagonals}, we chose to minimize the off diagonal elements of the process matrix.
-To benchmark the quality of the MQG, we then performed six randomized benchmarking experiments\cite{Magesan2011}: one for each over-- and under--calibrated pulse, one for the calibrated pulse, and one for the mixed process.
-We used $1000$ shots per experiment and $10$ sequences per sequence length, for sequence lengths of $2, 4, 8, 16, 32$ and $64$.
-In each case, our Clifford operations were decomposed into RX($\frac{\pi}{2})$ and RY($\frac{\pi}{2})$.
-In our implementation, these gates are implemented using the same pulse envelope definitions and control electronics, phase shifted by $\frac{\pi}{2}$ radians, and are therefore subject to identical miscalibration errors.
-The results are shown in Figure \ref{fig:rb} for sequence lengths $L=64$.
-Fitting to the randomized benchmarking decay curves, we find one-qubit gate fidelities of $99.3\%$ for the calibrated pulse, $98.9\%$ for Pulse1, $99.1\%$ for Pulse2, $98.9\%$ for Pulse3, $98.5\%$ for Pulse4, and $99.2\%$ for the MQG, demonstrating that it performs almost as well as the calibrated pulse, and better than the constituent pulses.
+Figure \ref{fig:rb} illustrates the distribution of survival probabilities at sequence length $L=64$ for each of the experiments.
+
+\setlength{\tabcolsep}{0.5em} 
+{\renewcommand{\arraystretch}{1.2}
+\begin{table}[h]
+	\label{tabl:rb}
+	\centering
+	\begin{tabular}{|c|c|c|}
+		\hline
+		Pulse name & Calibration error & RB error rate\\
+		\hline
+		$\mathsf{Pulse1}$ 	& 6.4\% 	& 1.1\% \\
+		$\mathsf{Pulse2}$ 	& 3.9\% 	& 0.9\% \\
+		$\mathsf{Pulse3}$ 	& --\,6.3\% 	& 1.1\% \\
+		$\mathsf{Pulse4}$ 	& --\,8.8\% 	& 1.5\% \\
+		Calibrated 			& $\cdot$  	& 0.7\% \\
+		MQG 				& $\cdot$ 	& 0.8\% \\
+		\hline
+	\end{tabular}
+	\caption{\textbf{Randomized benchmarking results:} The MQG outperforms all of the individual miscalibrated gates of which it is composed, achieving an RB number nearly as low as the carefully calibrated pulse.
+}
+\end{table}
+
+By minimizing the off-diagonal elements of the process matrix, we expect the resulting MQG to display suppressed coherent error.
+To see that this is in fact the case, we can inspect the variance of the $RB$ survival probabilities for the MQG relative to the miscalibrated pulses.
+A discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution.
+Stochastic noise, such as depolarizing noise, will yeilds relatively narrow, Gaussian distributed success probabilities.
+In Fig.~\ref{fig:rb}, we plot the distribution of survival probabilities at sequence length $64$ for each of the benchmarked gate sets.
+We see that the intentionally miscalibrated controls in our RB experiment have long tails, consistent with coherent noise, while the calibrated and randomized implementations are both significantly less dispersed, consistent with stochastic errors.
+This experiment therefore provides compelling evidence that the MQG suffers considerably less coherent error than any of the miscalibrated gates from which it was constructed.
+
 \begin{figure}[t]
@@
   \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{Randomized benchmarking experiments ran using different pulse definitions.
+  \caption{\textbf{MQGs improve randomized benchmarking:}.
 The first four boxes result from using each of four different implementations of the ${\pi/2}$ rotations.
@@
 It displays improved average survival probability as well as reduced variance.
-The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQG composed of Pulse1 through Pulse4.
+The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQG composed of $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$.
 It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
@@
 
-More importantly, minimizing the off-diagonal elements of the process matrix, we expect to produce a process with suppressed coherent error.
-To see that this is the case, we can observe the drastic reduction in the variance at each point for the MQG relative to the miscalibrated pulses.
-A discussed in \cite{Ball2016}, for coherent error models, noise will manifest as gamma distributed points for each sequence length.
-On the other hand, incoherent noise, such as depolarizing noise, will result in Gaussian distributed fidelity estimates for each randomized benchmarking sequence length.
-We see that the coherently miscalibrated controls in our RB experiment have long tails, consistent with gamma distributed random variables, while the calibrated and randomized implementations both have much shorter tails, consistent with Gaussian distributed random variables.
-Thus our experiment demonstrates that the MQG has a significantly less-coherent error channel.
+We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed.
+In future work, we hope to apply this technique to two-qubit gates, which are harder to tune up in general and are more likely to possess lingering coherent errors \needcite.
+
 % subsection experimental (end)
@@
 \label{sec:numerical_results}
-In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs, and then analyze their performance for a range of Hamiltonian parameters.
+\noindent In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs, and then analyze their performance for a range of Hamiltonian parameters.
 More specifically, we will construct a family of controls with some degree of inherent robustness to drift, and leverage the numerical techniques introduced to assign each control a probability.
@@
   \includegraphics[width=\columnwidth]{figures/1q_robustness_delta.pdf}
-  \caption{\amp{needs to be on previous page?}Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RX(\frac{\pi}{2})$.
-The results are qualitatively similar to those for $RY(\frac{\pi}{2})$.
-In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin.
-However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude.}
+  \caption{\textbf{One-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
+The target is a RX($\pi/2$) gate on a single tunable \kcy{the model doesn't indicate that it is tunable - double check the x axis is correct} qubit.
+The generator-exact MQGs dramatically outperforms both the robust MQG and any of the bare unitaries at $\delta=0$.
+However, even a relatively small amplitude error leads to a regime in which the the robust MQG will yield the better gate.
+Similar results are obtained for drift in the qubit frequency.}
   \label{fig:YMQG}
@@
   \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
-  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction.
-Shown with lower alpha values are example constituent controls.
-The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin.
-For all detuning values the 1MQG performs as well or better than the 0MQG.
-When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm.
-Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
+  \caption{\textbf{Two-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).
+It is intended to models a pair of tunable qubits interacting via resonant exchange.
+Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings.
+The robust MQG performs always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings.
+Similar results are obtained for drift in the qubit control amplitude.}
   \label{fig:2MQG}
@@
 
-% ==============================================================================
-% Section: Constructing Useful mixed quantum gates
-% ==============================================================================
-\section{Constructing mixed quantum gates}
-\label{sec:mixed_unitary_processes}
-\noindent In this section, we present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above.
-As mentioned, our method requires two steps.
-The first is a control synthesis step, in which we construct an ensemble of gate implementations.
-Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use utilize quantum optimal control theory.
-Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target.
-By seeding such algorithms with many initial guesses, one can quickly construct a large ensemble of approximate quantum gates, each with a different error.
-We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
-
-The remainder of this section will assume such a capability for generating a large ensemble of gate implementations, and will focus instead on the second step: constructing a distribution over that ensemble that reduces the coherence of the effective error channel.
-We will begin by discussing the two broad optimization targets introduced above: i) generator-exact MQGs and ii) Pauli-exact MQGs.
-We then propose a set of secondary targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
-
-% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
-In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
-As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
-In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
-
-% ==============================================================================
-% Section: Generators
-% ==============================================================================
-\subsection{Convex Programs for Mixed Quantum Gates}
-\subsubsection{Generator-exact MQGs} % (fold)
-\label{sub:first_order_generators}
-\noindent A compelling reason to construct an MQG is to improve the worst-case performance of a quantum gate.
-The diamond distance bounds this worst-case performance, and so one might assume minimizing it would be a natural optimization target:
-\begin{equation}\label{eq:ddmin}
-  \begin{split}
-    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm} \dnorm\left(\sum_i\error_i \weight_i\right)
-  \end{split}
-\end{equation}
-The diamond distance, however, is a non-linear function that in general requires its own convex optimization to compute\cite{watrous2018theory}.
-This can dramatically slow down iterative optimizers, and so directly minimizing the diamond distance is a computationally burdensome optimization target.
-However, for quantum computing purposes the error rates are typically quite small, so we can consider a linearized problem, minimizing the diamond distance at first-order in the effective error generator.
-As discussed around Eq.~\eqref{eq:cancel}, if the origin lies in in the convex hull of the generators, $\mathbf{0} \in \mathsf{conv}(\{\genmat_i\})$, then we can construct a generator-exact MQG.
-In \cite{Campbell2017} Campbell presents an iterative algorithm that, given an oracle that produces approximate unitary operations, will continually generate controls until the geometric constraint is satisfied and then identify the optimal weighting.
-We consider instead a situation in which one has access only to $m$ distinct, precomputed gate implementations and we wish to to identify the  MQG with minimum error.
-An efficiently computable heuristic is to minimize the Frobenius norm of the first-order effective error generator:
-\begin{equation}\label{eq:frobmin}
-  \begin{split}
-    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm}  \left\vert\left\vert\sum_i \weight_i \genmat_i \right\vert\right\vert_F
-  \end{split}
-\end{equation}
-This optimization problem is equivalent to:
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2\\
-  \end{split}
-\end{equation}
-Where $\mathbf{L}=\left( \mathsf{col}(\genmat_1) \; \mathsf{col}(\genmat_2) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked error generators and $||\cdot||_2$ is the $\ell_2$ norm.
-
-The constraints on these optimizations are required to ensure that the weights, $\weight_i$, form a proper probability distribution.
-Nevertheless, linearly constrained minimization problems with quadratic cost functions are convex and have been proven to be efficiently solvable by, e.g.
-the ellipsoid method \cite{wright1999numerical, khachiyan}.
-Many existing convex solver software packages are available that can solve these problems efficiently in practice.
-\kcy{Need some citations here.}
-
-%In both cases it is clear that we should select the gates with smaller error, i.e.
-$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
-Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
-\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
-We will discuss numerical approaches to solving this Section \ref{sec:norm}.
-
-%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
-In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
-Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
-In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
-
-% subsection first_order_generators (end)
-
-% ==============================================================================
-% Section: Off-diagonals
-% ==============================================================================
-
-\subsubsection{Pauli-exact MQGs} % (fold)
-\label{sub:off_diagonals}
-As quantum devices grow in size, it is increasingly expensive to simulate their dynamics.
-Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
-As discussed above, Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
-\note{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
-
-As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$.
-We wish to construct an MQG whose effective error is Pauli-stochastic and is therefore diagonal.
-This can be done with the following simple minimization:
-\begin{equation}\label{eq:minimization2}
-  \begin{split}
-    &\underset{\weight_i\geq0, \sum_i\weight_1=1}{\textbf{minimize}: } ||\sum_i\weight_i \errmat_i - \mathsf{diag}(\sum_i \weight_i \errmat_i)||_2\\
-  \end{split}
-\end{equation}
-Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero.
-This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of $\errmat_i$.
-\footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to
-\begin{equation}\label{eq:minimization3}
-  \begin{split}
-    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{E}\cdot\vec\weight||_2
-  \end{split}
-\end{equation}
-The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both.
-
-\kcy{do something with the paragraph}
-In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel.
-If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods.
-Better yet, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
-
-% subsection off_diagonals (end)
-
-% ==============================================================================
-% Section: Robustness
-% ==============================================================================
-\subsection{Additional Constraints}
-\noindent 
-Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly.
-It is often the case that one will have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
-This often leads to the the minimization problems discussed in the previous section being massively under-constrained, yielding many possible exact solutions.
-Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area.
-In this section we present explicit convex programs for such secondary objectives, including adding robustness to drift or model uncertainty, reducing the effective gate error, and minimizing the number of constituent gates utilized by the MQG.
-
-\subsubsection{Robustness to drift and model uncertainty} % (fold)
-\label{sub:adding_robustness}
-\noindent 
-While mixed quantum gates offer significant performance improvements, their construction assumes a good knowledge of the errors experienced by the constituent gates.
-But often the gates are not perfectly well characterized.
-This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \kcy{cite Tim's drift manuscript}.
-In either case, the performance of the MQG will be negatively impacted.
-We can describe the effect of this uncertainty by first writing the gate explicitly as a function of the vector of model parameters, $\vec\lambda$, and their nominal values, $\vec\lambda_0$.
-These model parameters could include magnetic field strengths, laser or microwave intensities, coupling strengths, etc.
-If the parameters are close to their nominal values, then we can write a gate's error generator as a Taylor expansion in the model uncertainty, $\vec\delta = \vec\lambda-\vec\lambda_0$:
-\begin{equation}
-	\genmat_i(\vec \delta) = \genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\vec 0) + \order{\delta^2}.
-\end{equation} 
-In the above expression we have used the comma derivative, 
-\begin{equation}
-	\genmat_{i,k}(\vec \delta_0) = \frac{\partial}{\partial \delta_k} \genmat_i(\vec\delta) \vert_{\vec \delta=\delta_0}.
-\end{equation}
-
-Now, rather than finding weight vectors such that only the effective generator vanishes, we can additionally impose a secondary constraint on the derivatives.  Following Eq.~\eqref{eq:minimization}, 
-\begin{equation}\label{eq:minimization}
-  \begin{split}
-    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||\mathbf{L}\cdot\vec\weight||_2 + \sum_k||\mathbf{L}_{,k}\cdot\vec\weight||_2\\
-  \end{split}
-\end{equation}
-Where $\mathbf{L}_{,k}=\left( \mathsf{col}(\genmat_{1,k}) \; \mathsf{col}(\genmat_{2,k}) \; \cdots \;  \right)$ is the $d^2\times m$-dimensional matrix of column-stacked derivatives of the error generators with respect to the deviation $\delta_k$.
-
-We can additionally generalize the geometric criterion for ensuring that the minimum value of this objective is 0.
-As before, we would like the origin to lie in the convex hull of the generators, but this time we have to augment the generators with their derivatives.
-That is,
-we require that
-\begin{equation}
-\mathbf{0} \in \mathsf{conv}\left( \left\{
-\genmat_i \oplus \genmat_{i,1} \oplus \genmat_{i,2} \cdots
-\right\}	 \right).
-\end{equation}
-This is illustrated in Fig.~\ref{fig:vectorspace2}.
-
-We call a gate constructed in this way a \emph{robust} generator-exact MQG.
-Similar constructs can be used to construct robust Pauli-exact MQGs by taking derivatives of the off-diagonal elements of the error maps with respect to the model deviations.
-
-\kcy{ignore from here to end of section***********}
-
-\begin{equation}
-\label{eq:derivative}
-D^n_{i, (j_1, \ldots, j_n)} = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{j_1}\ldots\partial\delta_{j_n}}\genmat_i(\vec{\delta})|_{\vec{\delta}=\vec{0}}
-\end{equation}
-If the dimension of $\vec{\delta}$ is $d$, the indices $j_1, \ldots, j_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
-We say that an MQG is robust to order $\ell$ (an $\ell$MQG) if for all $1 \leq k \leq \ell$:
-\begin{equation}\label{eq:MQG}
-\begin{gathered}
-\sum_i\weight_i(\sum_{n=0}^k D^n_i)^n = 0\\
-\end{gathered}
-\end{equation}
-In particular, we see that a 0MQG satisfies (\ref{eq:campbell-condition}). More generally, these conditions imply that an $\ell$MQG is insensitive to $\ell^{th}$ order in drift in $\vec{\delta}$. 
-By Taylor expanding (\ref{eq:taylor}) in $d\vec{\delta}$, one can see that the the first $\ell$ derivatives of an $\ell$MQG will be zero.
-Furthermore if we can find controls such that $||D_i^n||\leq\alpha$, (\ref{eq:MQG}) is a pproximately satisfied in the sense that:
-\begin{equation}\label{eq:MQG-relaxed}
-\begin{gathered}
-||\sum\weight_iD^n_i||+ \order{\alpha^2} = 0\\
-\end{gathered}
-\end{equation}
-where $||\cdot||$ is the Frobenius norm.
-This condition guarantees, as before, that errors will be suppressed to second order in $\alpha$, but now for all derivatives up to order $\ell$.
-%A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}.
-Namely, Campbell showed that if $0\in $ Conv$[\{G_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\weight}$ exists that quadratically decreases the diamond norm.
-We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\weight}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQG.
-As discussed in \cite{Campbell2017}, the geometric picture for 0MQGs is to consider the error generators as vectors, and to ensure zero is contained in their convex hull.
-Figure \ref{fig:vectorspace} generalizes this picture to 1MQGs and gives intuition for the conditions required to produce them.
-To generate $\ell$MQGs, we first define the vectorized derivative matrix ${\mathbf{D}^{\ell}}$ in a similar way to (\ref{eq:vectorized_generators}):
-\begin{equation}
-{\mathbf{D}^{\ell}} =  \left(\begin{array}{cccc}
-		D^\ell_{1_{1,1}} & D^\ell_{2_{1,1}} & \ldots   \\ 
-		\vdots\ & \ddots &    \\
-		D^\ell_{1_{d^2,d^2}} &  &  D^\ell_{m_{d^2,d^2}} \\ 
-	\end{array} 	
-	\right)
-\end{equation}
-
-Using this, we can then solve the following convex optimization problem, generalizing (\ref{eq:minimization}):
-
-\begin{equation}\label{eq:robust_minimization}
-  \begin{split}
-    &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } ||{\mathbf{D}^{\ell}}\weight||_1\\
-    &\textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
-  \end{split}
-\end{equation}
-with $D_n^i$ defined in (\ref{eq:derivative}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
-  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error.
-a) The error Hamiltonians shown with their derivative with respect to a control parameter.
-As this parameter drifts, a MQG may drift, leading to a first-order error.
-b) The derivatives also lie in a vector space.
-If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \oplus H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$\amp{I'm not sure what you mean by the $_k$ subscript, nor why the tensor product is there.
-Also I think your indices are backwards?} then it may be possible to construct a robust 1-MQG.
-\kcy{This should appear in the main text somewhere.
-When we add the derivatives we make our space larger, but we still want the origin to be in the higher-dimensional convex hull.}}
-  \label{fig:vectorspace}
-\end{figure}
-
-% subsection adding_robustness (end)
-
-% ==============================================================================
-% Section: Norm regularization
-% ==============================================================================
-
-\subsubsection{Hamiltonian Norm Regularization}
-\label{sec:norm}
-While quadratic programs with equality constraints have analytic solutions, the program we are considering has both constraints on the norm of the weight vector, and inequality constraints.
-Additionally, casting this problem as a convex optimization problem allows us to add penalty terms to the cost function to promote different properties of the MQG.
-In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error.
-As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent errors.
-To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians.
-In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
-
-\newcommand{\bunderbrace}[2]{%
-  \begin{array}[t]{@{}c@{}}
-  #1\\
-  \parbox{\widthof{#1}}{$\scriptscriptstyle#2$}
-  \end{array}
-}
-
-\begin{equation}\label{eq:minimization_l2}
-\begin{split}
-& \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1} ||{\mathbf{D}^{\ell}}\weight||_1+ \eta\sum\weight_i||D^0_i||_2\\
-&\ \ \textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
-\end{split}
-\end{equation}
-with $\eta \geq 0$.
-By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
-The value of $\eta$ that is best for any particular problem instance will depend on the values in $\mathbf{D}^\ell$.
-
-%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
-However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
-% ==============================================================================
-% Section: Sparsity
-% ==============================================================================
-
-\subsubsection{Sparsity Constraints}
-\label{sec:sparsity}
-As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
-Control electronics often have a limited amount of waveform memory, and thus it is important that MQGs only require a small number of controls.
-As an example, consider Figure \ref{fig:vectorspace}.
-In b), it is clear that $H_4$ is unnecessary to contain the origin in the convex hull of the error generators.
-Thus we would prefer that a $0$MQG exclude $H_4$.
-However, if we additionally want our controls to form a 1MQG, we see from d) that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the other controls' derivatives.
-
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient for our purposes, as we already constrain $\weight$ to be a valid probability distribution.
-Lasso regularization works by penalizing solutions with large $\ell_1$ norm, however if $\weight$ represents probabilities, it will always have an $\ell_1$ norm of one.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
-
-\begin{equation}\label{eq:minimization_regularization}
-\begin{split}
-&\underset{m\in[N]}{\textbf{minimize}}\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1,\\ t\geq0} ||{\mathbf{D}^{\ell}}\weight||_1 + t\\
-&\ \ \textbf{subject to: } \weight_m > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \weight_iD_i^n||=0
-\end{split}
-\end{equation} with $\lambda\geq0$.
-As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\mathbf{D}^\ell$ and how sparse the solution needs to be.
-In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
+Crosstalk, two qubit gates, etc.
 
@@
 
-% b
-% \onecolumngrid
 % ==============================================================================
@@
 
-% % subsection diamond_distance_inequality
-
-% \subsection{Robust Mixing Lemma}
-% \label{sub:rml}
-% We begin by generalizing Lemma 2 from \cite{Campbell2017}. If all of our error Hamiltonians $\{H_j\}$ have bounded error, that is:
-% \begin{equation}
-% ||H_j||\leq c
-% \end{equation}
-% Then we may consider the derivative of any mixture of unitaries as:
-% %\begin{equation}
-% %\deriv\sum_j \weight_je^{iH_j} = \deriv(\id + (\sum_ji%\weight_jH_j) + \sum \weight_j\sum_{n=2}^{\infty}%\frac{(iH_j)^n}{n!}))
-% %\end{equation}
-% \begin{equation}
-% \deriv\sum_j \weight_je^{iH_j} = \sum_j\weight_ji\deriv (H_j)e^{iH_j}
-% \end{equation}
-% By assumption, the derivatives of the first order term sum to zero, and so we see by A3 in \cite{Campbell2017} that
-% \begin{equation}
-% ||\deriv\sum_j\weight_je^{iH_j}|| \leq \sum_j\weight_j||i\deriv (H_j)(iH_j + \sum_{n=2}^{\infty}\frac{(iH_j)^n}{n!})|| \leq \sum_j\weight_j(c^2 + \frac{c^2}{2}) \leq c^2 + \frac{c^3}{2}
-% \end{equation}
-% Where we have used the fact that $||AB|| \leq ||A||||B||$ with $||\cdot||$ being the $\infty$-norm.
-% Additionally, 
-% \begin{align}
-% ||\deriv e^{iH_j}|| &= ||\deriv(iH_j)e^{iH_j}|| \\
-% &\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)H_j|| +  ||\deriv(iH_j)\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n|| \\
-% &\leq ||\deriv(iH_j)|| + ||\deriv(iH_j)||\cdot||H_j|| +  ||\deriv(iH_j)||\cdot||\sum^{\infty}_{n=2}\frac{1}{(n)!}(iH_j)^n||\\
-% &\leq c + c^2 + \frac{c^3}{2}
-% \end{align}
-% And so we see that Lemma 2 generalizes. We will use the above to upper bound the 1-norm (and hence diamond norm) in the following.
-
-% Next we generalize the Mixing Lemma from \cite{Campbell2017}. We must assume that the 1-norm is uniformly differentiable. In that case, we see that:
-
-% \begin{align}
-% &= \deriv\sup|\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat|_1 \\
-% &= \sup\deriv|\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat|_1 \\
-% &\leq \sup|\deriv(\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat)|_1 \\
-% \end{align}
-% And so we see it is sufficient to upperbound:
-% \begin{equation}
-% |\deriv(\identmat\otimes\identmat-\error(\vec{\delta})\otimes\identmat)|_1
-% \end{equation}
-% From Equation 18 in \cite{Campbell2017}:
-% \begin{align}
-% &(\mathcal{V}\circ\errmat - \id)(X) = \sum_j \weight_j(\tilde{\delta}_jX + X\tilde{\delta}_j^{\dagger} + \tilde{\delta}_jX\delta_j^{\dagger})\\
-% &\deriv(\mathcal{V}\circ\errmat - \id)(X) = \sum_j \weight_j(\deriv\tilde{\delta}_jX + X\deriv\tilde{\delta}_j^{\dagger} + \deriv\tilde{\delta}_jX\delta_j^{\dagger} + \tilde{\delta}_jX\deriv\delta_j^{\dagger})\\
-% \end{align}
-% Thus, by H\"older's inequality we find:
-% \begin{align}
-% &||\deriv(\mathcal{V}\circ\errmat - \id)(X)||_1\leq||\sum_j \weight_j\deriv\tilde{\delta}_j|| + ||\sum_j\weight_j\deriv\tilde{\delta}_j^{\dagger}|| + \sum_j\weight_j|| \deriv\tilde{\delta}_j||\cdot||\delta_j^{\dagger}|| + \sum_j\weight_j||\tilde{\delta}_j||\cdot||\deriv\delta_j^{\dagger}||
-% \end{align}
-% By assumption, all of these terms are neglible, and therefore we find:
-% \begin{align}
-% ||\deriv(\mathcal{V}\circ\errmat - \id)(X)||_1\leq 2a^2 + 2b^2
-% \end{align}
-% And so we see that the mixing lemma extends to first order.
-In a similar way, it can be extended to arbitary order, and thus if we can find constructions that satisfy the generalized Lemma 2, we can use the Robust Mixing Lemma to conclude that there exists a weighting with linearly supressed diamond norm.
-
 \end{document}

### 2019-09-13 decorrelation/mixed_unitaries.tex
Just the last few minor changes

@@
 \usepackage{calc}
+\usepackage{siunitx}
 \usepackage{tabularx}
@@
 Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$pulse calibrated by iteratively amplifying and correcting over- and under-rotation errors via repeated application.
-Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived from this waveform by scaling the amplitude of the calibrated $RX(\frac{\pi}{2})$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
+Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived from this waveform by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 The gates therefore experience unitary over/under rotations, which are coherent errors.
@@
 {\renewcommand{\arraystretch}{1.2}
+% \newcolumntype{d}[1]{D{.}{.}{#1}}
 \begin{table}[h]
@@
 	\centering
-	\begin{tabular}{|c|c|c|}
+	\begin{tabular}{@{}ccc@{}}
 		\hline
@@
 
-Using controls generated in this way, the MQGs produced for $RX(\frac{\pi}{2})$ and $RY(\frac{\pi}{2})$ are qualitatively similar, with the results for $RX(\frac{\pi}{2})$ shown in Figure \ref{fig:YMQG}.
+Using controls generated in this way, the MQGs produced for $X_{\pi/2}$ and $Y_{\pi/2}$ are qualitatively similar, with the results for $X_{\pi/2}$ shown in Figure \ref{fig:YMQG}.
 By imposing the penalty from Section \ref{sec:norm}, we sought to ensure that the algorithm preferentially selected controls with smaller errors.
@@
   \caption{\textbf{One-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
-The target is a RX($\pi/2$) gate on a single tunable \kcy{the model doesn't indicate that it is tunable - double check the x axis is correct} qubit.
+The target is an $X_{\pi/2}$ gate on a single tunable \kcy{the model doesn't indicate that it is tunable - double check the x axis is correct} qubit.
 The generator-exact MQGs dramatically outperforms both the robust MQG and any of the bare unitaries at $\delta=0$.
@@
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation \kcy{this needs to be explained in the experimental section} step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 
-Another interesting area of research would be using model-free approaches.
-The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
+That these methods depnd on accurate system models is a clear shortcoming.
+The robust MQG The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
 in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.

### 2019-09-13 decorrelation/mixed_unitaries.tex
small typos

@@
 Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations.
-They focus on errors in gate compilation, such as arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
+They focus on errors in gate compilation, such as those that arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
 Different approximate gate compilations of the same target unitary will almost certainly result in different unitary errors.
@@
 Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero.
-This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$.
+This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$\amp{Why E?}, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$.
 \footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to
@@
 This protocol can implement gates with errors that are actually Pauli stochastic.
-\kcy{Discuss randomized compiling here and in the introduction.}
+\kcy{Discuss randomized compiling here and in the introduction.}\amp{still rough}
 
@@
 While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration.
-Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$pulse calibrated by iteratively amplifying and correcting over- and under-rotation errors via repeated application.
+Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated by iteratively amplifying and correcting over- and under-rotation errors via repeated application.
 Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived from this waveform by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
 The gates therefore experience unitary over/under rotations, which are coherent errors.
-These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities, \kcy{What are they?}, respectively.
+These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities, \kcy{What are they?}\amp{I'll have to go hunting, I didn't save these}, respectively.
 
 We characterize the performance of the MQG using a series of randomized benchmarking (RB) experiments\cite{Magesan2011}: one for each of the miscalibrated pulses, one using the calibrated pulse, and using the MQG.
-In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were gates were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
+In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
 An RB experiment consisted of $10$ sequences sampled at each of lengths $\{2, 4, 8, 16, 32, 64\}$, and each sequence was repeated $1000$ times.
@@
 To see that this is in fact the case, we can inspect the variance of the $RB$ survival probabilities for the MQG relative to the miscalibrated pulses.
-A discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution.
+As discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution.
 Stochastic noise, such as depolarizing noise, will yeilds relatively narrow, Gaussian distributed success probabilities.

### 2019-09-16 decorrelation/mixed_unitaries.tex
Minor changes to tex file

--- 2019-09-13 decorrelation/mixed_unitaries.tex
@@
 \begin{equation}
-	(\actmat)_{ij} = \tr\!\left(P_i \;\actual\!\left(P_j\right) \right).
+	(\actmat)_{ij} = \frac{1}{d}\tr\!\left(P_i \;\actual\!\left(P_j\right) \right).
 \end{equation}
@@
 \noindent 
-While mixed quantum gates offer significant performance improvements, their construction assumes a good knowledge of the errors experienced by the constituent gates.
-But often the gates are not perfectly well characterized.
+Mixed quantum gates can offer significant performance improvements over bare unitary gates, but their construction requires a good knowledge of the errors experienced by the constituent gates.
+Often, however, the gates are not perfectly well characterized.
 This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \kcy{cite Tim's drift manuscript}.
@@
 \notag
-	\errmat_{\rm eff} =&
-		 \identmat_d + \sum_i \weight_i \left(\genmat_i(0) + \sum_k \delta_k \,\genmat_{i,k}(\0) \right) \\
+	\errmat_{\rm eff} =
+		 \identmat_d &+ \sum_i \weight_i \left(\genmat_i(\0) + \sum_k \delta_k \,\genmat_{i,k}(\0) \right) \\
 		 &+ \order{\genmat_i^2 + \genmat_i \delta + \delta^2}.
@@
 \label{sec:sparsity}
+\noindent
 As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
@@
 
-\subsection{Experimental implementation} % (fold)
+\subsection{Experimental implementation } % (fold)
 \label{sub:experimental}

### 2019-09-19 decorrelation/mixed_unitaries.tex
Text and plot updates

@@
 \label{sec:mixed_unitary_processes}
-\noindent In this section, we present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above.
+\noindent We now present a methodology for constructing mixed quantum channels, formalizing the intuitive approach discussed above with a series of explicit convex programs.
 As mentioned, our method requires two steps.
@@
 We discuss this approach in some detail in Sec.~\ref{sec:numerical_results}.
-\kcy{Why should the gates we generate have any error at all?
-They shouldn't if we know the model.
-Discuss this here.}
 
@@
 This is equivalent to demanding that the origin lie in the convex hull $\mathsf{conv}(\{\genmat_i \bigoplus_k \genmat_{i,k} \}_i)$.
+The gradient arrows indicate that this space is higher-dimensional.
 }
@@
 In such a case, we can choose a weighting parameter, $\eta$, to explicitly balance the two competing objectives:
-
 \begin{equation}\label{eq:agi_minimization_weighted}
@@
 \end{equation}
-
 Both optimizations are convex and efficiently solvable.
@@
 \noindent We implemented our methods using the 19Q-Acorn superconducting transmon processor at Rigetti Computing.
-Comprehensive device characterization for this processor can be found in \cite{1712.05771}.
+Comprehensive characterization of this device can be found in \cite{1712.05771}.
 While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration.
-Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated by iteratively amplifying and correcting over- and under-rotation errors via repeated application.
-Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived from this waveform by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by $106.4\%$,  $103.9\%$, $93.7\%$ and $91.2\%$.
-The gates therefore experience unitary over/under rotations, which are coherent errors.
+Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated via Rabi oscillation.
+Four intentionally miscalibrated Gaussian pulses, labeled $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$, were derived by scaling the amplitude of the calibrated $X_{\pi/2}$ pulse by a factor $S \in \{1.064, 1.039,0.937, 0.912\}$, respectively.
+We model their effect on the qubit state as perfectly unitary rotations, $X_{A \pi/2} = \exp{(-i A \pi/2 \sigma_x)}$.
 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities, \kcy{What are they?}\amp{I'll have to go hunting, I didn't save these}, respectively.
@@
 In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
-An RB experiment consisted of $10$ sequences sampled at each of lengths $\{2, 4, 8, 16, 32, 64\}$, and each sequence was repeated $1000$ times.
+An RB experiment consisted of sampling and running $10$ random Clifford sequences at each of lengths $L\in\{2, 4, 8, 16, 32, 64\}$.
+Each sequence was repeated $1000$ times.
 We emphasize that, when benchmarking the MQG, each sequence repetition used a new, randomly sampled sequence of waveforms consistent with its definition.
-Results of the standard RB analysis are indicated in Table.~\eqref{tabl:rb}.
+Results of the standard RB analysis are discussed in Table.~\eqref{tabl:rb}.
 The MQG is seen to perform nearly as well as the calibrated pulse, and better than any of the constituent pulses individually.
-
-Figure \ref{fig:rb} illustrates the distribution of survival probabilities at sequence length $L=64$ for each of the experiments.
 
@@
 		\hline
-		Pulse name & Calibration error & RB error rate\\
+		Pulse name & Rotation error & RB error rate\\
 		\hline
@@
 As discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution.
-Stochastic noise, such as depolarizing noise, will yeilds relatively narrow, Gaussian distributed success probabilities.
-In Fig.~\ref{fig:rb}, we plot the distribution of survival probabilities at sequence length $64$ for each of the benchmarked gate sets.
+Stochastic noise, such as depolarizing noise, will yield comparatively narrow, Gaussian-distributed success probabilities.
+In Fig.~\ref{fig:rb}, we plot the experimentally observed distribution of survival probabilities at sequence length $64$ for each of the benchmarked gate sets.
 We see that the intentionally miscalibrated controls in our RB experiment have long tails, consistent with coherent noise, while the calibrated and randomized implementations are both significantly less dispersed, consistent with stochastic errors.
@@
   \includegraphics[width=\columnwidth]{rb_data.pdf}
-  \caption{\textbf{MQGs improve randomized benchmarking:}.
-The first four boxes result from using each of four different implementations of the ${\pi/2}$ rotations.
-The coherent noise present in these implementations leads to large variance of the survival probability over sequences.
+  \caption{\textbf{Evidence of reduced coherent error:}.
+Shown here is the distribution of randomized benchmarking survival probabilities at $L=64$ for each of six native gate implementations.
+The first four boxes (light blue) result four intentionally miscalibrated ${\pi/2}$ rotations.
+The coherent noise present in these implementations leads to large variance in the survival probability over sequences.
 The fifth (dark blue) box illustrates the survival probability using a highly-tuned gate implementation.
 It displays improved average survival probability as well as reduced variance.
-The final box (dark red) illustrates the distribution over survival probabilities for a randomized MQG composed of $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$.
+The final box (dark red) illustrates the distribution for a randomized MQG composed of $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$.
 It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
-The reduced variance of the MQG is a tell-tale sign of reduced coherent error in the effective channel.
+The reduced variance of the MQG is a tell-tale sign of reduced coherent error in the effective channel \kcy{cite Biercuk's paper}.
 }
@@
 We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed.
-In future work, we hope to apply this technique to two-qubit gates, which are harder to tune up in general and are more likely to possess lingering coherent errors \needcite.
+In future work, we hope to apply this technique to two-qubit gates, which are significantly more difficult to tune up in general and are more likely to possess lingering coherent errors.
+Tomography or modeling can then be used to construct the process matrix estimates required to build a mixed gate.
 
@@
 % ==============================================================================
-\subsection{Numerical Implementation}
+\subsection{Numerical implementations}
 \label{sec:numerical_results}
-\noindent In the following numerical results, we use the methods in Section \ref{sec:mixed_unitary_processes} to build MQGs, and then analyze their performance for a range of Hamiltonian parameters.
-More specifically, we will construct a family of controls with some degree of inherent robustness to drift, and leverage the numerical techniques introduced to assign each control a probability.
-When drawn from with these probabilities, the controls will form an MQG with enhanced robustness to drift on the control parameters.
+\noindent In the following numerical results, we use the various methods in Section \ref{sec:mixed_unitary_processes} to build a range of one- and two-qubit MQGs for model systems.
+We analyze the resulting mixed gates for a range of Hamiltonian parameters, demonstrating both a reduction in diamond distance and an improved robustness to model uncertainty.
+
+% ------------------------------------------------------------------------------
+% Subsection: Single-qubit example
+% ------------------------------------------------------------------------------
+\subsection{Single-qubit example} 
+\label{sub:one_qubit}
 We consider the following dimensionless model for a single tunable qubit: 
@@
 
+% ------------------------------------------------------------------------------
+% Subsection: Single-qubit example
+% ------------------------------------------------------------------------------
+\subsection{Two-qubit example} 
+\label{sub:two_qubit}
 In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:

### 2019-09-19 data/raw_data/diamond.py
Cleaning up data directory

@@ -1,101 +1,0 @@
-"""
-diamond.py
-
-Compute the diamond norm of a quantum process
-
-Kevin Young
-Sandia National Laboratories
-2 September 2015
-
-------------------------------------------------------
-
-Uses the primal SDP from arXiv:1207.5726v2, Sec 3.2
-
-Maximize 1/2 ( < J(phi), X > + < J(phi).dag, X.dag > )
-Subject to  [[ I otimes rho0, X],
-            [X.dag, I otimes rho1]] >> 0
-              rho0, rho1 are density matrices
-              X is linear operator
-
-Jamiolkowski representation of the process
-  J(phi) = sum_ij Phi(Eij) otimes Eij
-
-< A, B > = Tr(A.dag B)
-"""
-
-from scipy import transpose, array, zeros
-import scipy
-from itertools import chain, repeat
-import cvxpy as cvx
-import pickle
-import numpy as np
-
-def vec(matrix_in):
-    # Stack the columns of a matrix to return a vector
-    return [b for a in transpose(matrix_in) for b in a]
-
-def unvec(vector_in):
-    # Slice a vector into columns of a matrix
-    dim = int(scipy.sqrt(len(vector_in)))
-    return transpose(array(list(zip(*[chain(vector_in, repeat(None, dim-1))]*dim))))
-
-def jamiolkowski(process, representation = 'superoperator'):
-    # Return the Choi-Jamiolkowski representation of a quantum process
-    # Add methods as necessary to accept different representations
-    process = array(process)
-    if representation == 'unitary':
-        process = np.kron(process.conj(), process)
-        representation = 'superoperator'
-    if representation == 'superoperator':
-        # Superoperator is the linear operator acting on vec(rho)
-        dimension = int(scipy.sqrt(process.shape[0]))
-        jamiolkowski_matrix = zeros([dimension**2, dimension**2], dtype='complex')
-        for i in range(dimension**2):
-            Ei_vec= zeros(dimension**2)
-            Ei_vec[i] = 1
-            output = unvec(scipy.dot(process,Ei_vec))
-            jamiolkowski_matrix += scipy.kron(output, unvec(Ei_vec))
-        return jamiolkowski_matrix
-
-def diamond_norm( jamiolkowski_matrix ):
[…]

### 2019-09-19 data/raw_data/pauli_channel_approximation.py

@@ -1,646 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-plt.switch_backend('agg')
-from GRAPE import GRAPE, control_unitaries, adjoint, average_over_noise
-import numpy as np
-from scipy.optimize import minimize
-import scipy
-import dill
-import itertools
-from copy import deepcopy
-from functools import reduce
-import subprocess
-import os.path
-import multiprocessing
-from mpi4py import MPI
-import sys
-import time as timemod
-COMM = MPI.COMM_WORLD
-#Note ambient hamiltonian as been changed to a list of hamiltonians, but the name remains unchanged.
-
-I = np.eye(2)
-X = np.array([[0, 1], [1, 0]])
-Y = np.array([[0, -1.j], [1.j, 0]])
-Z = np.array([[1, 0], [0, -1]])
-PAULIS = [I, X, Y, Z]
-
-from itertools import product
-def generate_indices(num_points, order_desired):
-    num_indices = len(order_desired)
-    tuples = product(range(num_points), repeat=num_indices)
-    indices = [sum([num_points**(num_indices - 1 - order_desired[i]) * t[i] for i in range(num_indices)]) for t in tuples]
-    return indices
-
-def error_unitary(unitary, target):
-    """
-    Constructs the superoperator for the error unitary corresponding propagating forward by target,
-     and back by unitary.
-
-    :param np.array unitary: Control unitary realized in the computational basis.
-    :param np.array target: The desired unitary in the computational basis.
-    :return: The superoperator corresponding to the unitary postrotational error.
-    :rtype: numpy.array
-    """
-    error = adjoint(unitary).dot(target)
-    return np.kron(np.conj(error), error)
-
-
-def off_diagonal_projection(sop):
-    """
-    Computes a quantity proportional to the sum of the magnitudes of terms corresponding to non-stochastic evolution.
-
-    :param numpy.ndarry sop: Representation our operator as a superoperator, e.g. operating on vectorized density
-     matrices.
-    """
-    basis = PAULIS
-    for _ in range(int(np.log2(sop.shape[0]) / 2.0) - 1):
-        basis = [np.kron(base, pauli) for pauli in PAULIS for base in basis]
-    off_diagonal = 0
-    for i, base1 in enumerate(basis):
-        for j, base2 in enumerate(basis):
-            if i != j:
[…]

### 2019-09-19 code/GRAPE.py
removing more pickles, and moving code to the one qubit numerics

@@ -1,362 +1,0 @@
-import itertools
-import numpy as np
-import scipy
-import scipy.optimize as optimize
-from numpy.polynomial.hermite import hermgauss
-from functools import reduce
-from mpi4py import MPI
-
-COMM = MPI.COMM_WORLD
-
-
-def split(container, count):
-    """
-    Simple function splitting a container into equal length chunks.
-    Order is not preserved but this is potentially an advantage depending on
-    the use case.
-    """
-    return [list(container)[_i::count] for _i in range(count)]
-
-
-def adjoint(operator):
-    """
-    Computes the adjoint of a given matrix.
-
-    :param numpy.array operator: Array to compute the adjoint of.
-    :return: The adjoint of operator.
-    :rtype: numpy.array
-    """
-    return np.conj(operator).T
-
-
-def control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt):
-    """
-    Given an controllable and a non-controllable hamiltonian, with controls and the time step size,
-    computes the unitaries that give the time evolution. e.g.
-
-    control_unitaries(I, [X], [[0],[1],[0],[1]], np.pi)
-    [I, X, I, X]
-
-    :param numpy.array ambient_hamiltonian: A square 2D array, corresponding to the uncontrollable
-     part of the system hamiltonian.
-    :param list control_hamiltonians: A list of square 2D numpy.arrays, corresponding to the
-     controllable terms in the hamiltonian. This should be as long as the second dimension of
-     controls.
-    :param numpy.array controls: A 2D numpy.array, whose rows represent time steps, and whose
-     jth column corresponds to the control amplitude for the jth element of control_hamiltonians.
-    :param float dt: The time to evolve each row of controls for.
-    :return: The list of unitaries corresponding to the discretized evolution of the system.
-    :rtype: list
-    """
-    if len(controls.shape) == 1:
-        controls = controls.reshape(-1, len(control_hamiltonians))
-    unitaries = []
-    for row in controls:
-        step_hamiltonian = [control * control_hamiltonians[i] for i, control in enumerate(row)]
-        #print(step_hamiltonian)
-        evolution = scipy.linalg.expm(
-            -1.j * dt * (sum(ambient_hamiltonian) + np.sum(step_hamiltonian, axis=0)))
-        unitaries.append(evolution)
-    return unitaries
-
-
-def grape_perf(ambient_hamiltonian, control_hamiltonians, controls, dt, target_operator):
-    """
[…]

### 2019-09-19 data/one_qubit_numeric/GRAPE.py

@@ -1,0 +1,362 @@
+import itertools
+import numpy as np
+import scipy
+import scipy.optimize as optimize
+from numpy.polynomial.hermite import hermgauss
+from functools import reduce
+from mpi4py import MPI
+
+COMM = MPI.COMM_WORLD
+
+
+def split(container, count):
+    """
+    Simple function splitting a container into equal length chunks.
+    Order is not preserved but this is potentially an advantage depending on
+    the use case.
+    """
+    return [list(container)[_i::count] for _i in range(count)]
+
+
+def adjoint(operator):
+    """
+    Computes the adjoint of a given matrix.
+
+    :param numpy.array operator: Array to compute the adjoint of.
+    :return: The adjoint of operator.
+    :rtype: numpy.array
+    """
+    return np.conj(operator).T
+
+
+def control_unitaries(ambient_hamiltonian, control_hamiltonians, controls, dt):
+    """
+    Given an controllable and a non-controllable hamiltonian, with controls and the time step size,
+    computes the unitaries that give the time evolution. e.g.
+
+    control_unitaries(I, [X], [[0],[1],[0],[1]], np.pi)
+    [I, X, I, X]
+
+    :param numpy.array ambient_hamiltonian: A square 2D array, corresponding to the uncontrollable
+     part of the system hamiltonian.
+    :param list control_hamiltonians: A list of square 2D numpy.arrays, corresponding to the
+     controllable terms in the hamiltonian. This should be as long as the second dimension of
+     controls.
+    :param numpy.array controls: A 2D numpy.array, whose rows represent time steps, and whose
+     jth column corresponds to the control amplitude for the jth element of control_hamiltonians.
+    :param float dt: The time to evolve each row of controls for.
+    :return: The list of unitaries corresponding to the discretized evolution of the system.
+    :rtype: list
+    """
+    if len(controls.shape) == 1:
+        controls = controls.reshape(-1, len(control_hamiltonians))
+    unitaries = []
+    for row in controls:
+        step_hamiltonian = [control * control_hamiltonians[i] for i, control in enumerate(row)]
+        #print(step_hamiltonian)
+        evolution = scipy.linalg.expm(
+            -1.j * dt * (sum(ambient_hamiltonian) + np.sum(step_hamiltonian, axis=0)))
+        unitaries.append(evolution)
+    return unitaries
+
+
+def grape_perf(ambient_hamiltonian, control_hamiltonians, controls, dt, target_operator):
+    """
[…]

### 2019-09-19 data/one_qubit_numeric/convex.py

@@ -1,0 +1,174 @@
+from scipy.misc import derivative
+from itertools import product
+from functools import reduce
+from copy import deepcopy
+from GRAPE import control_unitaries
+from scipy.linalg import logm
+import cvxpy as cp
+import numpy as np
+from scipy.linalg import norm
+
+DEFAULT_TOL = 1e-8
+
+
+def error(combo, controls, target_operator, control_hamiltonians, ambient_hamiltonian0, dt):
+    """Return the Hamiltonian that when exponentiated gives the error unitary from the target."""
+    adjoint_target = np.conj(target_operator.T)
+    newcontrols = deepcopy(controls)
+    ambient_hamiltonian = [deepcopy(ah).astype("complex") for ah in ambient_hamiltonian0]
+    combo = list(combo)
+    if len(combo) == 2:
+        combo = combo + combo[-1:]
+        assert len(combo) == 3
+    else:
+        assert len(combo) == 5
+        combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo[4:]
+        assert len(combo) == 7
+    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
+    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
+    for cnum, value in enumerate(combo):
+        cnum -= len(ambient_hamiltonian0)
+        if cnum >= 0:
+            newcontrols[:, cnum] = newcontrols[:, cnum] * (1 + value)
+        if cnum < 0:
+            idx = len(ambient_hamiltonian) - abs(cnum)
+            if cnum == -1 and len(combo) != 3: # not the one qubit case, in particular the uncontrolled 2q hamiltonian
+                continue
+            ambient_hamiltonian[idx] *= float(value)
+    # just check the first one
+    assert np.isclose(ambient_hamiltonian[0], np.conj(ambient_hamiltonian[0].T)).all()
+    for h in control_hamiltonians:
+        assert np.isclose(h, np.conj(h.T)).all()
+    step_unitaries = control_unitaries(ambient_hamiltonian,
+                                       control_hamiltonians,
+                                       newcontrols,
+                                       dt)
+    for u in step_unitaries:
+        assert np.isclose(np.conj(u.T).dot(u), np.eye(int(np.sqrt(target_operator.size)))).all(), np.conj(u.T).dot(u)
[…]

### 2019-09-19 code/1q_dnorm.py
removing code directory

@@ -1,166 +1,0 @@
-import os
-os.environ['OPENBLAS_NUM_THREADS'] = '1'
-os.environ['GOTO_NUM_THREADS'] = '1'
-os.environ['OMP_NUM_THREADS'] = '1'
-os.environ['NUMEXPR_NUM_THREADS'] = '1'
-os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
-
-from pauli_channel_approximation import PCA
-from time import time
-import scipy
-
-from mpi4py import MPI
-comm = MPI.COMM_WORLD
-rank = comm.Get_rank()
-size = comm.Get_size()
-
-import numpy as np
-import scipy as sp
-import numpy.linalg as lin
-import scipy.linalg as slin
-
-import os; os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
-import pygsti
-
-import pygsti
-import numpy as np
-import itertools
-from functools import reduce
-
-multi_kron = lambda *a: reduce(np.kron, a)
-
-def change_basis(process, from_basis, to_basis):
-    """
-    PyGSTi 'std' basis is *row stacked* rather than column stacked, so need to defined a 'col' basis.
-    """
-    allowed_bases = ['col', 'std', 'gm', 'pp', 'qsim']
-    if not ((from_basis in allowed_bases) or (to_basis in allowed_bases)):
-        raise ValueError("Allowed bases are 'col', 'std', 'gm', 'pp', 'qsim' ")
-
-    n_qubits = int(np.log(len(process)) / np.log(4))
-    if from_basis == 'col' or to_basis == 'col':
-
-        if len(process) != 4**n_qubits:
-            raise ValueError('The dimension of the process matrix must be a power of 4.')
-        def matrix_unit(n,i,j):
-            unit = np.zeros([n,n], dtype='complex')
-            unit[i,j] = 1.
-            return unit
-        col_stacked_matrix_units = [matrix_unit(2**n_qubits, i, j) for j in range(2**n_qubits) for i in range(2**n_qubits)]
-
-        from pygsti.objects import ExplicitBasis
-        col = ExplicitBasis(col_stacked_matrix_units, ["myElement%d" % i for i in range(4**n_qubits)],
-                                     name='col', longname='Column=-Stacked')
-        if from_basis == 'col':
-            from_basis = col
-        if to_basis == 'col':
[…]

### 2019-09-19 code/2d_mpi_plot.py

@@ -1,162 +1,0 @@
-# Standard imports
-import numpy as np
-import scipy as sp
-import numpy.linalg as lin
-import scipy.linalg as slin
-
-# Set the environment variables
-import os 
-os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
-os.environ['OPENBLAS_NUM_THREADS'] = '1'
-os.environ['GOTO_NUM_THREADS'] = '1'
-os.environ['OMP_NUM_THREADS'] = '1'
-
-# Initialize the parallel processing
-from mpi4py import MPI
-comm = MPI.COMM_WORLD
-rank = comm.Get_rank()
-size = comm.Get_size()
-
-# Additional imports
-from time import time
-import pygsti 
-if rank == 0:
-    import matplotlib 
-    matplotlib.use('Agg')
-    from matplotlib import pyplot as plt
-
-def print(*args, root = 0, **kwargs):
-    if rank == root:
-        return __builtin__.print(*args, **kwargs)
-
-# Import the data
-import dill
-filenames = {0: '0_pickled_controls106.pkl', 1: '1_pickled_controls106.pkl'}
-with open(filenames[0], 'rb') as f:
-    data = dill.load(f)
-
-# Divide list into n approximately equally sized chunks
-def split(n, a):
-    k, m = divmod(len(a), n)
-    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
-
-
-# Get the unitary associated with a given index
-def get_unitary(c_ind, epsilon1, epsilon2, delta1, delta2):
-    u = np.eye(4, dtype='complex')
-    
-    a = epsilon1 * data.ambient_hamiltonian[0]
-    b = epsilon2 * data.ambient_hamiltonian[1]
-    c = data.ambient_hamiltonian[2] 
-    h0 = a+b+c
-    
-    for t_ind in range(500):
-        d = (1+delta2) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
-        e = (1+delta2) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1] 
-        f = (1+delta1) * data.controlset[c_ind][t_ind][2] * data.control_hamiltonians[2] 
-        g = (1+delta1) * data.controlset[c_ind][t_ind][3] * data.control_hamiltonians[3] 
-        ham = h0 + d + e + f + g
[…]

### 2019-09-19 code/2d_mpi_plot_1q.py

@@ -1,171 +1,0 @@
-# Standard imports
-import numpy as np
-import scipy as sp
-import numpy.linalg as lin
-import scipy.linalg as slin
-
-# Set the environment variables
-import os
-
-os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
-os.environ['OPENBLAS_NUM_THREADS'] = '1'
-os.environ['GOTO_NUM_THREADS'] = '1'
-os.environ['OMP_NUM_THREADS'] = '1'
-
-# Initialize the parallel processing
-from mpi4py import MPI
-
-comm = MPI.COMM_WORLD
-rank = comm.Get_rank()
-size = comm.Get_size()
-
-# Additional imports
-from time import time
-import pygsti
-
-if rank == 0:
-    import matplotlib
-
-    matplotlib.use('Agg')
-    from matplotlib import pyplot as plt
-
-
-def print(*args, root=0, **kwargs):
-    if rank == root:
-        import builtins
-        return builtins.print(*args, **kwargs)
-
-
-# Import the data
-import dill
-
-filenames = {0: '0_pickled_controls5.pkl', 1: '1_pickled_controls5.pkl'}
-with open(filenames[1], 'rb') as f:
-    data = dill.load(f)
-
-
-# Divide list into n approximately equally sized chunks
-def split(n, a):
-    k, m = divmod(len(a), n)
-    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
-
-
-# Get the unitary associated with a given index
-def get_unitary(c_ind, epsilon1, delta1):
-    u = np.eye(2, dtype='complex')
-    a = epsilon1 * data.ambient_hamiltonian[0]
-    h0 = a
-    for t_ind in range(25):
-        f = (1 + delta1) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
-        g = (1 + delta1) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1]
-        ham = h0 + f + g
-        u = np.dot(slin.expm(-1.j * ham * data.dt), u)
-    return u
-
-
-# for testing:
-my_inds = split(size, np.arange(len(data.controlset)))[rank]
-
-
-# my_inds = np.array(split(size, np.arange(size)))[rank]
-
-
-# Get the process matrix for a given setting of the error parameters
[…]

### 2019-09-19 code/2q_dnorm.py

@@ -1,170 +1,0 @@
-import os
-os.environ['OPENBLAS_NUM_THREADS'] = '1'
-os.environ['GOTO_NUM_THREADS'] = '1'
-os.environ['OMP_NUM_THREADS'] = '1'
-os.environ['NUMEXPR_NUM_THREADS'] = '1'
-os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
-
-from pauli_channel_approximation import PCA
-from time import time
-
-from mpi4py import MPI
-comm = MPI.COMM_WORLD
-rank = comm.Get_rank()
-size = comm.Get_size()
-
-import numpy as np
-import scipy as sp
-import numpy.linalg as lin
-import scipy.linalg as slin
-
-import os; os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
-import pygsti 
-
-import pygsti
-import numpy as np
-import itertools
-from functools import reduce
-
-multi_kron = lambda *a: reduce(np.kron, a)
-
-def change_basis(process, from_basis, to_basis):
-    """
-    PyGSTi 'std' basis is *row stacked* rather than column stacked, so need to defined a 'col' basis.
-    """
-    allowed_bases = ['col', 'std', 'gm', 'pp', 'qsim']
-    if not ((from_basis in allowed_bases) or (to_basis in allowed_bases)):
-        raise ValueError("Allowed bases are 'col', 'std', 'gm', 'pp', 'qsim' ")
-
-    n_qubits = int(np.log(len(process)) / np.log(4))
-    if from_basis == 'col' or to_basis == 'col':
-
-        if len(process) != 4**n_qubits:
-            raise ValueError('The dimension of the process matrix must be a power of 4.')
-        def matrix_unit(n,i,j):
-            unit = np.zeros([n,n], dtype='complex')
-            unit[i,j] = 1.
-            return unit
-        col_stacked_matrix_units = [matrix_unit(2**n_qubits, i, j) for j in range(2**n_qubits) for i in range(2**n_qubits)]
-
-        from pygsti.objects import ExplicitBasis
-        col = ExplicitBasis(col_stacked_matrix_units, ["myElement%d" % i for i in range(4**n_qubits)],
-                                     name='col', longname='Column=-Stacked')
-        if from_basis == 'col':
-            from_basis = col
-        if to_basis == 'col':
[…]

### 2019-09-19 code/diamond.py

@@ -1,102 +1,0 @@
-"""
-diamond.py
-
-Compute the diamond norm of a quantum process
-
-Kevin Young
-Sandia National Laboratories
-2 September 2015
-
-------------------------------------------------------
-
-Uses the primal SDP from arXiv:1207.5726v2, Sec 3.2
-
-Maximize 1/2 ( < J(phi), X > + < J(phi).dag, X.dag > )
-Subject to  [[ I otimes rho0, X],
-            [X.dag, I otimes rho1]] >> 0
-              rho0, rho1 are density matrices
-              X is linear operator
-
-Jamiolkowski representation of the process
-  J(phi) = sum_ij Phi(Eij) otimes Eij
-
-< A, B > = Tr(A.dag B)
-"""
-
-from scipy import transpose, array, zeros
-import scipy
-from itertools import chain, repeat
-import cvxpy as cvx
-import pickle
-import numpy as np
-
-def vec(matrix_in):
-    # Stack the columns of a matrix to return a vector
-    return [b for a in transpose(matrix_in) for b in a]
-
-def unvec(vector_in):
-    # Slice a vector into columns of a matrix
-    dim = int(scipy.sqrt(len(vector_in)))
-    return transpose(array(list(zip(*[chain(vector_in, repeat(None, dim-1))]*dim))))
-
-def jamiolkowski(process, representation = 'superoperator'):
-    # Return the Choi-Jamiolkowski representation of a quantum process
-    # Add methods as necessary to accept different representations
-    process = array(process)
-    if representation == 'unitary':
-        process = np.kron(process.conj(), process)
-        representation = 'superoperator'
-    if representation == 'superoperator':
-        # Superoperator is the linear operator acting on vec(rho)
-        dimension = int(scipy.sqrt(process.shape[0]))
-        jamiolkowski_matrix = zeros([dimension**2, dimension**2], dtype='complex')
-        for i in range(dimension**2):
-            Ei_vec= zeros(dimension**2)
-            Ei_vec[i] = 1
-            output = unvec(scipy.dot(process,Ei_vec))
-            jamiolkowski_matrix += scipy.kron(output, unvec(Ei_vec))
-        return jamiolkowski_matrix
-
-def diamond_norm( jamiolkowski_matrix ):
[…]

### 2019-09-19 code/pauli_channel_approximation.py

@@ -1,250 +1,0 @@
-import matplotlib
-matplotlib.use('Agg')
-from GRAPE import GRAPE, control_unitaries, adjoint
-import numpy as np
-import dill
-from functools import reduce
-import time as timemod
-from convex import (all_derivs, optimal_weights)
-from mpi4py import MPI
-import scipy
-import os
-from itertools import product
-
-COMM = MPI.COMM_WORLD
-
-I = np.eye(2)
-X = np.array([[0, 1], [1, 0]])
-Y = np.array([[0, -1.j], [1.j, 0]])
-Z = np.array([[1, 0], [0, -1]])
-PAULIS = [I, X, Y, Z]
-
-
-def generate_indices(num_points, order_desired):
-    num_indices = len(order_desired)
-    tuples = product(range(num_points), repeat=num_indices)
-    indices = [sum([num_points**(num_indices - 1 - order_desired[i]) * t[i] for i in range(num_indices)]) for t in tuples]
-    return indices
-
-
-def error_unitary(unitary, target):
-    """
-    Constructs the superoperator for the error unitary corresponding propagating forward by target,
-     and back by unitary.
-
-    :param np.array unitary: Control unitary realized in the computational basis.
-    :param np.array target: The desired unitary in the computational basis.
-    :return: The superoperator corresponding to the unitary postrotational error.
-    :rtype: numpy.array
-    """
-    error = adjoint(unitary).dot(target)
-    return np.kron(np.conj(error), error)
-
-
-def off_diagonal_projection(sop):
-    """
-    Computes a quantity proportional to the sum of the magnitudes of terms corresponding to non-stochastic evolution.
-
-    :param numpy.ndarry sop: Representation our operator as a superoperator, e.g. operating on vectorized density
-     matrices.
-    """
-    basis = PAULIS
-    for _ in range(int(np.log2(sop.shape[0]) / 2.0) - 1):
-        basis = [np.kron(base, pauli) for pauli in PAULIS for base in basis]
-    off_diagonal = 0
-    for i, base1 in enumerate(basis):
-        for j, base2 in enumerate(basis):
-            if i != j:
-                off_diagonal += np.abs(np.trace(adjoint(np.kron(base1, base2)).dot(sop))) ** 2
-    return off_diagonal
-
-
-def error_on_controls(ambient_hamiltonian, control_hamiltonians, controls, dt,
[…]

### 2019-09-19 data/one_qubit_numeric/1q_dnorm.py

@@ -1,0 +1,166 @@
+import os
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+os.environ['NUMEXPR_NUM_THREADS'] = '1'
+os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
+
+from pauli_channel_approximation import PCA
+from time import time
+import scipy
+
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+import os; os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+import pygsti
+
+import pygsti
+import numpy as np
+import itertools
+from functools import reduce
+
+multi_kron = lambda *a: reduce(np.kron, a)
+
+def change_basis(process, from_basis, to_basis):
+    """
+    PyGSTi 'std' basis is *row stacked* rather than column stacked, so need to defined a 'col' basis.
+    """
+    allowed_bases = ['col', 'std', 'gm', 'pp', 'qsim']
+    if not ((from_basis in allowed_bases) or (to_basis in allowed_bases)):
+        raise ValueError("Allowed bases are 'col', 'std', 'gm', 'pp', 'qsim' ")
+
+    n_qubits = int(np.log(len(process)) / np.log(4))
+    if from_basis == 'col' or to_basis == 'col':
+
+        if len(process) != 4**n_qubits:
+            raise ValueError('The dimension of the process matrix must be a power of 4.')
+        def matrix_unit(n,i,j):
+            unit = np.zeros([n,n], dtype='complex')
+            unit[i,j] = 1.
+            return unit
+        col_stacked_matrix_units = [matrix_unit(2**n_qubits, i, j) for j in range(2**n_qubits) for i in range(2**n_qubits)]
+
+        from pygsti.objects import ExplicitBasis
+        col = ExplicitBasis(col_stacked_matrix_units, ["myElement%d" % i for i in range(4**n_qubits)],
+                                     name='col', longname='Column=-Stacked')
+        if from_basis == 'col':
+            from_basis = col
+        if to_basis == 'col':
[…]

### 2019-09-19 data/one_qubit_numeric/2d_mpi_plot_1q.py

@@ -1,0 +1,171 @@
+# Standard imports
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+# Set the environment variables
+import os
+
+os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+
+# Initialize the parallel processing
+from mpi4py import MPI
+
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+# Additional imports
+from time import time
+import pygsti
+
+if rank == 0:
+    import matplotlib
+
+    matplotlib.use('Agg')
+    from matplotlib import pyplot as plt
+
+
+def print(*args, root=0, **kwargs):
+    if rank == root:
+        import builtins
+        return builtins.print(*args, **kwargs)
+
+
+# Import the data
+import dill
+
+filenames = {0: '0_pickled_controls5.pkl', 1: '1_pickled_controls5.pkl'}
+with open(filenames[1], 'rb') as f:
+    data = dill.load(f)
+
+
+# Divide list into n approximately equally sized chunks
+def split(n, a):
+    k, m = divmod(len(a), n)
+    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
+
+
+# Get the unitary associated with a given index
+def get_unitary(c_ind, epsilon1, delta1):
+    u = np.eye(2, dtype='complex')
+    a = epsilon1 * data.ambient_hamiltonian[0]
+    h0 = a
+    for t_ind in range(25):
+        f = (1 + delta1) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
+        g = (1 + delta1) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1]
+        ham = h0 + f + g
+        u = np.dot(slin.expm(-1.j * ham * data.dt), u)
+    return u
+
+
+# for testing:
+my_inds = split(size, np.arange(len(data.controlset)))[rank]
+
+
+# my_inds = np.array(split(size, np.arange(size)))[rank]
+
+
+# Get the process matrix for a given setting of the error parameters
[…]

### 2019-09-19 data/one_qubit_numeric/convex.py

@@ -1,174 +1,0 @@
-from scipy.misc import derivative
-from itertools import product
-from functools import reduce
-from copy import deepcopy
-from GRAPE import control_unitaries
-from scipy.linalg import logm
-import cvxpy as cp
-import numpy as np
-from scipy.linalg import norm
-
-DEFAULT_TOL = 1e-8
-
-
-def error(combo, controls, target_operator, control_hamiltonians, ambient_hamiltonian0, dt):
-    """Return the Hamiltonian that when exponentiated gives the error unitary from the target."""
-    adjoint_target = np.conj(target_operator.T)
-    newcontrols = deepcopy(controls)
-    ambient_hamiltonian = [deepcopy(ah).astype("complex") for ah in ambient_hamiltonian0]
-    combo = list(combo)
-    if len(combo) == 2:
-        combo = combo + combo[-1:]
-        assert len(combo) == 3
-    else:
-        assert len(combo) == 5
-        combo = combo[:2] + combo[2:3] * 2 + combo[3:4] * 2 + combo[4:]
-        assert len(combo) == 7
-    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
-    assert len(combo) == len(control_hamiltonians) + len(ambient_hamiltonian0)
-    for cnum, value in enumerate(combo):
-        cnum -= len(ambient_hamiltonian0)
-        if cnum >= 0:
-            newcontrols[:, cnum] = newcontrols[:, cnum] * (1 + value)
-        if cnum < 0:
-            idx = len(ambient_hamiltonian) - abs(cnum)
-            if cnum == -1 and len(combo) != 3: # not the one qubit case, in particular the uncontrolled 2q hamiltonian
-                continue
-            ambient_hamiltonian[idx] *= float(value)
-    # just check the first one
-    assert np.isclose(ambient_hamiltonian[0], np.conj(ambient_hamiltonian[0].T)).all()
-    for h in control_hamiltonians:
-        assert np.isclose(h, np.conj(h.T)).all()
-    step_unitaries = control_unitaries(ambient_hamiltonian,
-                                       control_hamiltonians,
-                                       newcontrols,
-                                       dt)
-    for u in step_unitaries:
-        assert np.isclose(np.conj(u.T).dot(u), np.eye(int(np.sqrt(target_operator.size)))).all(), np.conj(u.T).dot(u)
[…]

### 2019-09-19 data/shared_code/diamond.py

@@ -1,0 +1,102 @@
+"""
+diamond.py
+
+Compute the diamond norm of a quantum process
+
+Kevin Young
+Sandia National Laboratories
+2 September 2015
+
+------------------------------------------------------
+
+Uses the primal SDP from arXiv:1207.5726v2, Sec 3.2
+
+Maximize 1/2 ( < J(phi), X > + < J(phi).dag, X.dag > )
+Subject to  [[ I otimes rho0, X],
+            [X.dag, I otimes rho1]] >> 0
+              rho0, rho1 are density matrices
+              X is linear operator
+
+Jamiolkowski representation of the process
+  J(phi) = sum_ij Phi(Eij) otimes Eij
+
+< A, B > = Tr(A.dag B)
+"""
+
+from scipy import transpose, array, zeros
+import scipy
+from itertools import chain, repeat
+import cvxpy as cvx
+import pickle
+import numpy as np
+
+def vec(matrix_in):
+    # Stack the columns of a matrix to return a vector
+    return [b for a in transpose(matrix_in) for b in a]
+
+def unvec(vector_in):
+    # Slice a vector into columns of a matrix
+    dim = int(scipy.sqrt(len(vector_in)))
+    return transpose(array(list(zip(*[chain(vector_in, repeat(None, dim-1))]*dim))))
+
+def jamiolkowski(process, representation = 'superoperator'):
+    # Return the Choi-Jamiolkowski representation of a quantum process
+    # Add methods as necessary to accept different representations
+    process = array(process)
+    if representation == 'unitary':
+        process = np.kron(process.conj(), process)
+        representation = 'superoperator'
+    if representation == 'superoperator':
+        # Superoperator is the linear operator acting on vec(rho)
+        dimension = int(scipy.sqrt(process.shape[0]))
+        jamiolkowski_matrix = zeros([dimension**2, dimension**2], dtype='complex')
+        for i in range(dimension**2):
+            Ei_vec= zeros(dimension**2)
+            Ei_vec[i] = 1
+            output = unvec(scipy.dot(process,Ei_vec))
+            jamiolkowski_matrix += scipy.kron(output, unvec(Ei_vec))
+        return jamiolkowski_matrix
+
+def diamond_norm( jamiolkowski_matrix ):
[…]

### 2019-09-19 data/shared_code/pauli_channel_approximation.py

@@ -1,0 +1,250 @@
+import matplotlib
+matplotlib.use('Agg')
+from GRAPE import GRAPE, control_unitaries, adjoint
+import numpy as np
+import dill
+from functools import reduce
+import time as timemod
+from convex import (all_derivs, optimal_weights)
+from mpi4py import MPI
+import scipy
+import os
+from itertools import product
+
+COMM = MPI.COMM_WORLD
+
+I = np.eye(2)
+X = np.array([[0, 1], [1, 0]])
+Y = np.array([[0, -1.j], [1.j, 0]])
+Z = np.array([[1, 0], [0, -1]])
+PAULIS = [I, X, Y, Z]
+
+
+def generate_indices(num_points, order_desired):
+    num_indices = len(order_desired)
+    tuples = product(range(num_points), repeat=num_indices)
+    indices = [sum([num_points**(num_indices - 1 - order_desired[i]) * t[i] for i in range(num_indices)]) for t in tuples]
+    return indices
+
+
+def error_unitary(unitary, target):
+    """
+    Constructs the superoperator for the error unitary corresponding propagating forward by target,
+     and back by unitary.
+
+    :param np.array unitary: Control unitary realized in the computational basis.
+    :param np.array target: The desired unitary in the computational basis.
+    :return: The superoperator corresponding to the unitary postrotational error.
+    :rtype: numpy.array
+    """
+    error = adjoint(unitary).dot(target)
+    return np.kron(np.conj(error), error)
+
+
+def off_diagonal_projection(sop):
+    """
+    Computes a quantity proportional to the sum of the magnitudes of terms corresponding to non-stochastic evolution.
+
+    :param numpy.ndarry sop: Representation our operator as a superoperator, e.g. operating on vectorized density
+     matrices.
+    """
+    basis = PAULIS
+    for _ in range(int(np.log2(sop.shape[0]) / 2.0) - 1):
+        basis = [np.kron(base, pauli) for pauli in PAULIS for base in basis]
+    off_diagonal = 0
+    for i, base1 in enumerate(basis):
+        for j, base2 in enumerate(basis):
+            if i != j:
+                off_diagonal += np.abs(np.trace(adjoint(np.kron(base1, base2)).dot(sop))) ** 2
+    return off_diagonal
+
+
+def error_on_controls(ambient_hamiltonian, control_hamiltonians, controls, dt,
[…]

### 2019-09-19 data/two_qubit_numeric/2d_mpi_plot.py

@@ -1,0 +1,162 @@
+# Standard imports
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+# Set the environment variables
+import os 
+os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+
+# Initialize the parallel processing
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+# Additional imports
+from time import time
+import pygsti 
+if rank == 0:
+    import matplotlib 
+    matplotlib.use('Agg')
+    from matplotlib import pyplot as plt
+
+def print(*args, root = 0, **kwargs):
+    if rank == root:
+        return __builtin__.print(*args, **kwargs)
+
+# Import the data
+import dill
+filenames = {0: '0_pickled_controls106.pkl', 1: '1_pickled_controls106.pkl'}
+with open(filenames[0], 'rb') as f:
+    data = dill.load(f)
+
+# Divide list into n approximately equally sized chunks
+def split(n, a):
+    k, m = divmod(len(a), n)
+    return np.array(list(a[i * k + min(i, m):(i + 1) * k + min(i + 1, m)] for i in range(n)))
+
+
+# Get the unitary associated with a given index
+def get_unitary(c_ind, epsilon1, epsilon2, delta1, delta2):
+    u = np.eye(4, dtype='complex')
+    
+    a = epsilon1 * data.ambient_hamiltonian[0]
+    b = epsilon2 * data.ambient_hamiltonian[1]
+    c = data.ambient_hamiltonian[2] 
+    h0 = a+b+c
+    
+    for t_ind in range(500):
+        d = (1+delta2) * data.controlset[c_ind][t_ind][0] * data.control_hamiltonians[0]
+        e = (1+delta2) * data.controlset[c_ind][t_ind][1] * data.control_hamiltonians[1] 
+        f = (1+delta1) * data.controlset[c_ind][t_ind][2] * data.control_hamiltonians[2] 
+        g = (1+delta1) * data.controlset[c_ind][t_ind][3] * data.control_hamiltonians[3] 
+        ham = h0 + d + e + f + g
[…]

### 2019-09-19 data/two_qubit_numeric/2q_dnorm.py

@@ -1,0 +1,170 @@
+import os
+os.environ['OPENBLAS_NUM_THREADS'] = '1'
+os.environ['GOTO_NUM_THREADS'] = '1'
+os.environ['OMP_NUM_THREADS'] = '1'
+os.environ['NUMEXPR_NUM_THREADS'] = '1'
+os.environ['VECLIB_MAXIMUM_THREADS'] = '1'
+
+from pauli_channel_approximation import PCA
+from time import time
+
+from mpi4py import MPI
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+size = comm.Get_size()
+
+import numpy as np
+import scipy as sp
+import numpy.linalg as lin
+import scipy.linalg as slin
+
+import os; os.environ['PYGSTI_BACKCOMPAT_WARNING'] = '0'
+import pygsti 
+
+import pygsti
+import numpy as np
+import itertools
+from functools import reduce
+
+multi_kron = lambda *a: reduce(np.kron, a)
+
+def change_basis(process, from_basis, to_basis):
+    """
+    PyGSTi 'std' basis is *row stacked* rather than column stacked, so need to defined a 'col' basis.
+    """
+    allowed_bases = ['col', 'std', 'gm', 'pp', 'qsim']
+    if not ((from_basis in allowed_bases) or (to_basis in allowed_bases)):
+        raise ValueError("Allowed bases are 'col', 'std', 'gm', 'pp', 'qsim' ")
+
+    n_qubits = int(np.log(len(process)) / np.log(4))
+    if from_basis == 'col' or to_basis == 'col':
+
+        if len(process) != 4**n_qubits:
+            raise ValueError('The dimension of the process matrix must be a power of 4.')
+        def matrix_unit(n,i,j):
+            unit = np.zeros([n,n], dtype='complex')
+            unit[i,j] = 1.
+            return unit
+        col_stacked_matrix_units = [matrix_unit(2**n_qubits, i, j) for j in range(2**n_qubits) for i in range(2**n_qubits)]
+
+        from pygsti.objects import ExplicitBasis
+        col = ExplicitBasis(col_stacked_matrix_units, ["myElement%d" % i for i in range(4**n_qubits)],
+                                     name='col', longname='Column=-Stacked')
+        if from_basis == 'col':
+            from_basis = col
+        if to_basis == 'col':
[…]

### 2019-09-20 data/one_qubit_numeric/GRAPE.py
changing convex code to use agi and running cells in notebook that appear to show a dependence

@@ -1,0 +1,1 @@
+../shared_code/GRAPE.py

### 2019-09-20 data/one_qubit_numeric/convex.py

@@ -1,0 +1,1 @@
+../shared_code/convex.py

### 2019-09-27 decorrelation/mixed_unitaries.tex
Edits

@@
 There is a lot of literature on this, most of it inconsistent.
-Try Joel's Estimating the Coherence of Noise (terrible title) and Gottesman's paper on Maximally Sensitive States.}
+Try Joel's Estimating the Coherence of Noise (terrible title) and Gottesman's paper on Maximally Sensitive States, and Arnaud's work on the Polar Decomposition.}
 
@@
 I feel like it should be $(d + \tr(\errmat))/(d+d^2)$.
-Maybe cite Nielsen's paper, or Horodecki**3.} and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
+Maybe cite Nielsen's paper, or Horodecki**3, ** cite QUANTUM GATE FIDELITY IN TERMS OF CHOI MATRICES NATHANIEL JOHNSTON AND DAVID W.
+KRIBS
+.} and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
 \begin{align}
@@
 However this is insufficient for our purposes, as we require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends (\ref{eq:robust_minimization}):
-
-\kcy{Make the rest of this section consistent with the current notation.}
+Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
 \begin{equation}\label{eq:minimization_regularization}
 \begin{split}
-&\underset{m\in[N]}{\textbf{minimize}}\\
-&\ \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1,\\ t\geq0} ||{\mathbf{D}^{\ell}}\weight||_1 + t\\
-&\ \ \textbf{subject to: } \weight_m > \frac{\lambda}{t}\\
-&\ \ \phantom{\textbf{subject to: }} \forall n<\ell, ||\sum \weight_iD_i^n||=0
+&\underset{m\in[1..N]}{\textbf{minimize:}}\\
+&\ \ \bunderbrace{\textbf{\hspace{.2cm}minimize:\hspace{.2cm}} }{\hspace{.1cm}\weight_i\geq0, |\weight|_1=1, t\geq0} ||\mathbf{L}\cdot\vec\weight||_2 + t\\
+&\ \ \hspace{.2cm}\textbf{subject to: } \weight_m > \frac{\lambda}{t}.
 \end{split}
-\end{equation} with $\lambda\geq0$.
-As with $\eta$ in the last subsection, the optimal value of $\lambda$ is problem specific, depending on $\mathbf{D}^\ell$ and how sparse the solution needs to be.
+\end{equation}
+In this program, $\lambda > 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+
 In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
@@
 % ------------------------------------------------------------------------------
-\subsection{Single-qubit example} 
+\subsubsection{Single-qubit example} 
 \label{sub:one_qubit}
@@
 To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
-However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
+However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just \kcy{10 controls}.
 In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
@@
 % ------------------------------------------------------------------------------
-\subsection{Two-qubit example} 
+\subsubsection{Two-qubit example} 
 \label{sub:two_qubit}
@@
 \amp{This section is still tough to read, but I'm not sure of a better way to handle it.
-The constituent controls are clearly contrived, so I think it best to be explicit about how they were constructed.}In this example it was infeasible to use GRAPE to return non-trivial solutions.
+The constituent controls are clearly contrived, so I think it best to be explicit about how they were constructed.}In this example it was infeasible to use GRAPE to return non-trivial solutions (always got the same result).
 Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.

### 2019-10-01 decorrelation/mixed_unitaries.tex
Minor modifications

@@
 \end{equation}
-In this program, $\lambda > 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+Here, $\lambda > 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+Increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
 
-In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging these optimization techniques.
+In the following sections we discuss both experimental and numerical implementations of MQGs, leveraging each of these secondary optimizations.
 

### 2019-10-02 decorrelation/mixed_unitaries.tex
adding in citations, attempts at addressing some comments, and probs

@@
 Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
-\kcy{We might need more here defining coherent noise.
-There is a lot of literature on this, most of it inconsistent.
-Try Joel's Estimating the Coherence of Noise (terrible title) and Gottesman's paper on Maximally Sensitive States, and Arnaud's work on the Polar Decomposition.}
+
+\amp{Not at all a final draft, but tried to take your note about coherence of noise and write something.}In general, an error will neither be fully coherent nor Pauli stochastic, and there is significant work defining precisely how coherent arbitrary noise is \cite{CarignanDugas2019, Wallman2015}.
+In particular, the unitarity of an error map can be defined to be:
+\begin{align}
+u(\mathcal{E}) = \frac{d}{d-1}\int d\psi ||\mathbf{n}[\mathcal{E}\cdot\vectorize{\ketbra{\psi}{\psi}}] - \mathbf{n}[\mathcal{E}\cdot\vectorize{\identmat_d}/2]||^2
+\end{align}
+where the integral is taken over all pure states and \textbf{n} is the norm of the Bloch vector.
+Even if we avoid measuring this unitarity, there are protocols to detect how unitary an error is by seeing how errors accumulate on different input states\cite{1907.05950}.
+In this work, we will be content if the unitarity of our error map decreases by any of these metrics.
+%Even if we avoid measuring the unitarity explicitly, we can assess how unitary an error is from how they compound.
+In particular, coherent errors have the property that they accumulate as the square of the number of qubits.
+To this end, there are protocols such as that given in \cite{1907.05950} that will use a collection of maximally sensitive inputs to detect this scaling.
 
@@
 \end{equation}
-Two important error metrics are the average gate infidelity (AGI), $\AGI$, \kcy{We need a citation for this, and check if it's right!
-Gives weird answer if E = I.
-I feel like it should be $(d + \tr(\errmat))/(d+d^2)$.
-Maybe cite Nielsen's paper, or Horodecki**3, ** cite QUANTUM GATE FIDELITY IN TERMS OF CHOI MATRICES NATHANIEL JOHNSTON AND DAVID W.
-KRIBS
-.} and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
+Two important error metrics are the average gate infidelity (AGI), $\AGI$\cite{Johnston2011}, and the diamond distance to the target (or simply, the \emph{diamond distance}), $\dnorm$ \cite{watrous2018theory}, defined as:
 \begin{align}
@@
 the ellipsoid method \cite{wright1999numerical, khachiyan}.
-Many existing convex solver software packages are available that can solve these problems efficiently in practice.
-\kcy{Need some citations here.}
+Many existing convex solver software packages are available that can solve these problems efficiently in practice\cite{cvxpy, cvxpy_rewriting}.
 
@@
 As discussed above, Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
-\kcy{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
+\amp{Still not sure what you want here.
+In the \textit{general} case, it doesn't matter if the error is Pauli, since you could have nasty unitaries other places in the circuit.
+If all of the gates in the circuit are clifford, of course, then this helps, since now the arbitrary noise turns into just propagating some probability vector.
+Is that what you had in mind?} \kcy{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
 
@@
 Here $(\mathsf{diag}(\mathcal{A}))_{ij} = \mathcal{A}_{ij}\delta_{ij}$ sets the off-diagonal elements of a matrix to zero.
-This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$\amp{Why E?}, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$.
+This can be more transparently written as a convex program by constructing the $(d^2-d)\times m$-dimensional matrix, $\mathbf{E}$, whose $i$\textsuperscript{th} column is a vector composed of all of the off-diagonal entries of the error generators $\errmat_i$.
 \footnote{Exactly \emph{how} the off-diagonal entries are vectorized is unimportant, so long as it is consistent across error matrices.} Eq.~\eqref{eq:minimization2} is then equivalent to
@@
 \end{equation}
-Both optimizations are convex and efficiently solvable.
+Both optimizations are convex and efficiently solvable\cite{Shah2001}.
 
@@
 We model their effect on the qubit state as perfectly unitary rotations, $X_{A \pi/2} = \exp{(-i A \pi/2 \sigma_x)}$.
-These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities, \kcy{What are they?}\amp{I'll have to go hunting, I didn't save these}, respectively.
+These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
 
@@
 It performs comparably to the highly-calibrated implementation in both average survival probability and variance over random sequences.
-The reduced variance of the MQG is a tell-tale sign of reduced coherent error in the effective channel \kcy{cite Biercuk's paper}.
-}
+The reduced variance of the MQG is a tell-tale sign of reduced coherent error in the effective channel\cite{Ball2016}.}
   \label{fig:rb}

### 2019-11-25 decorrelation/mixed_unitaries.tex
commiting before leaving

@@
 \email[Email: ]{ampolloreno@gmail.com}
-\affiliation{Rigetti Computing, Berkeley, CA}
-
+\altaffiliation[Current address: ]{University of Colorado, Boulder, CO}
+\affiliation{Rigetti Computing, 2919 Seventh Street, Berkeley, CA, 94710-2704 USA}
 \author{Kevin C. Young}
@@
 But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, there are errors in the gate.
-If the device is fairly stable with time\kcy{cite drift paper} and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\actual$ acting on the Hilbert space of the target qubits.
+If the device is fairly stable with time\cite{1907.13608} and context\cite{Rudinger2019}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\actual$ acting on the Hilbert space of the target qubits.
 This map can always be written as $\actual = \error\circ\target$, where $\error = \actual\circ\target^{-1}$ is the \emph{error map}, which is itself CPTP because $\target$ is unitary.
@@
 
-\amp{Not at all a final draft, but tried to take your note about coherence of noise and write something.}In general, an error will neither be fully coherent nor Pauli stochastic, and there is significant work defining precisely how coherent arbitrary noise is \cite{CarignanDugas2019, Wallman2015}.
-In particular, the unitarity of an error map can be defined to be:
+In general an error will neither be fully coherent nor Pauli stochastic and so it is useful to define what we mean by the coherence of arbitrary noise\cite{CarignanDugas2019}.
+ One way to measure this is with a quanitiy called the unitarity\cite{Wallman2015}:
 \begin{align}
-u(\mathcal{E}) = \frac{d}{d-1}\int d\psi ||\mathbf{n}[\mathcal{E}\cdot\vectorize{\ketbra{\psi}{\psi}}] - \mathbf{n}[\mathcal{E}\cdot\vectorize{\identmat_d}/2]||^2
+u(\mathsf{E}) = \frac{d}{d-1}\int d\psi ||\mathbf{n}[\mathsf{E}(\psi)] - \mathbf{n}[\mathsf{E}(\identmat_d/2)||^2
 \end{align}
-where the integral is taken over all pure states and \textbf{n} is the norm of the Bloch vector.
-Even if we avoid measuring this unitarity, there are protocols to detect how unitary an error is by seeing how errors accumulate on different input states\cite{1907.05950}.
-In this work, we will be content if the unitarity of our error map decreases by any of these metrics.
-%Even if we avoid measuring the unitarity explicitly, we can assess how unitary an error is from how they compound.
-In particular, coherent errors have the property that they accumulate as the square of the number of qubits.
-To this end, there are protocols such as that given in \cite{1907.05950} that will use a collection of maximally sensitive inputs to detect this scaling.
+where $\mathbf{n}$ is the length of the Bloch vector, and the integral is over all pure states using the Haar measure.
+Yet another way of quantitavely describing how unitary a channel is with protocols that assess how errors accumulate on different input states\cite{1907.05950}.
+In this work, we will only discuss the relative unitarity of channels, and therefore are content if the unitarity of our error map decreases by any of these metrics.
 
@@
 % ==============================================================================
+% contrast coherent errors with stochastic where an expectation can be computed and then the circuit can be rerun, rather than having to track the the whole state.
 
@@
 Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
-As discussed above, Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
-\amp{Still not sure what you want here.
-In the \textit{general} case, it doesn't matter if the error is Pauli, since you could have nasty unitaries other places in the circuit.
-If all of the gates in the circuit are clifford, of course, then this helps, since now the arbitrary noise turns into just propagating some probability vector.
-Is that what you had in mind?} \kcy{say something more concrete here and PROVIDE CITATIONS!} Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
+While there has been significant work done investigating how to approximate different error channels as Pauli stochastic channels, and assessing the quality of these approximations\cite{Puzzuoli2014}, this technique offers another path forward.
+Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
+
+\amp{clean up} In particular, the well-known stabilizer framework \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations.
+These circuits are useful in that they give examples of quantum circuits whose performance we can test efficiently against classical simulation.
+This has motivated significant development of these techniques to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and simulating the evolution of mixtures of stabilizer states.
+\cite{Yoder, Bennink2017} An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is.
+Therefore Pauli-Exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-Stochastic errors, they will be more amenable to stabilizer simualtion.
+Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
 
@@
 
-\kcy{do something with the paragraph}
-If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
+%\kcy{do something with the paragraph}
+%If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
 As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods.
@@
 Often, however, the gates are not perfectly well characterized.
-This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \kcy{cite Tim's drift manuscript}.
+This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \cite{1907.13608}.
 In either case, the performance of the MQG will be negatively impacted.
@@
 In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
+All circuits were precompiled on the host computer and sent to be executed to the control electronics, rather than using the FPGA or lower-level firmware to sample at run-time.
+
 An RB experiment consisted of sampling and running $10$ random Clifford sequences at each of lengths $L\in\{2, 4, 8, 16, 32, 64\}$.
@@
 
-To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 100 candidate controls.
-However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just \kcy{10 controls}.
+To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls.
+However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
+Figure \ref{} shows that as $\lambda$ increases, the support of the MQG becomes more peaked, with most of their probability mass concentrating on a smaller number of controls.
 In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
@@
   \caption{\textbf{One-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
-The target is an $X_{\pi/2}$ gate on a single tunable \kcy{the model doesn't indicate that it is tunable - double check the x axis is correct} qubit.
+The target is an $X_{\pi/2}$ gate on a single qubit.
 The generator-exact MQGs dramatically outperforms both the robust MQG and any of the bare unitaries at $\delta=0$.
@@
 
-\amp{This section is still tough to read, but I'm not sure of a better way to handle it.
-The constituent controls are clearly contrived, so I think it best to be explicit about how they were constructed.}In this example it was infeasible to use GRAPE to return non-trivial solutions (always got the same result).
+In this example it was infeasible to use GRAPE to return non-trivial solutions (always got the same result).
 Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
@@
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation \kcy{this needs to be explained in the experimental section} step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 

### 2019-11-25 data/one_qubit_numeric/pauli_channel_approximation.py

@@ -1,0 +1,1 @@
+../shared_code/pauli_channel_approximation.py

### 2019-11-26 decorrelation/mixed_unitaries.tex
rough plots, and i've addressed all the points. but i think it finally has everything we want.

@@
 
+Randomized protocols have a long history of outperforming their deterministic counterparts.
+In \cite{Viola2005, Santos2006} the use of randomness is discussed in the context of dynamical decoupling.
+In particular, it is shown that both stochastic and hybrid approaches can result in better or more tractable coherent controls.
+Additionally Pauli Frame Randomization\cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
+While this routine affects a similar outcome to that of randomized compiling, it admits a hardware-efficient implementation and numerous useful extensions due to its framing as a numerical optimization problem.
+
 In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates and show that the advantages of their approach can be made robust to drift and model uncertainty.
@@
 In general an error will neither be fully coherent nor Pauli stochastic and so it is useful to define what we mean by the coherence of arbitrary noise\cite{CarignanDugas2019}.
- One way to measure this is with a quanitiy called the unitarity\cite{Wallman2015}:
+ One way to measure this is with a quantity called the unitarity\cite{Wallman2015}:
 \begin{align}
@@
 Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
-While there has been significant work done investigating how to approximate different error channels as Pauli stochastic channels, and assessing the quality of these approximations\cite{Puzzuoli2014}, this technique offers another path forward.
-Pauli-exact MQGs can be constructed with vanishing coherent error, enabling the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
+Existing work generally approximates channels as Pauli stochastic channels, and assesses the quality of these approximations\cite{Puzzuoli2014, Magesan2013}.
+Pauli frame randomization adds additional gates into circuits leave the result unchanged but randomize the nosie in such a way that it becomes a Pauli stochastic channel.
+This technique offers another path forward.
+Pauli-exact MQGs can be constructed with vanishing coherent error and without adding any additional gates or compilation time.
+Building MQGs with diminished coherent error enables the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
 
-\amp{clean up} In particular, the well-known stabilizer framework \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations.
-These circuits are useful in that they give examples of quantum circuits whose performance we can test efficiently against classical simulation.
-This has motivated significant development of these techniques to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and simulating the evolution of mixtures of stabilizer states.
+In particular, the well-known stabilizer framework \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations.
+These circuits are useful because they give examples of quantum circuits whose performance we can efficiently assess using classical simulation.
+This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and even algorithms for the simulation of arbitrary circuits.
 \cite{Yoder, Bennink2017} An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is.
-Therefore Pauli-Exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-Stochastic errors, they will be more amenable to stabilizer simualtion.
+Therefore Pauli-Exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli Stochastic errors, they will be more amenable to stabilizer simulation.
 Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
@@
 The similarity with Eq.~\ref{eq:minimization} is clear and the same methods can be used to solve both.
-
-%\kcy{do something with the paragraph}
-%If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
-As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods.
-Furthermore, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} \kcy{Why this paper?} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014}.
-This protocol can implement gates with errors that are actually Pauli stochastic.
-\kcy{Discuss randomized compiling here and in the introduction.}\amp{still rough}
+If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
+%As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods.
+Furthermore, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} \kcy{Why this paper?}
 
@@
 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
+Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli Transfer Matrices in Figure \ref{ptms}.
+\begin{figure}
+\includegraphics[scale=.5]{experimental-ptm.png}
+\caption{Pauli Transfer Matrices for a) $\mathsf{Pulse1}$ b) $\mathsf{Pulse2}$ c) $\mathsf{Pulse3}$ d) $\mathsf{Pulse4}$ e) MQG.
+The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-Exact MQG has been constructed to have minimal coherent error and therefore had dominantly diagonal elements.}
+\end{figure}
 
@@
 \label{sub:one_qubit}
-We consider the following dimensionless model for a single tunable qubit: 
+We consider the following dimensionless model for a single qubit subject to frequency drift: 
 \begin{equation}\label{eq:1Qham}
@@
 
+\begin{figure}
+\includegraphics[scale=.5]{sparisity-versus-parameter.png}
+\caption{Sparsity of MQGs as a function of the sparisty parameter, $\lambda$.
+As the parameter is increased from zero, the number of controls (y-axis) with low probability increases.
+For $\lambda=.001$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
+\label{fig:sparsity}
+\end{figure}
 To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls.
 However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
-Figure \ref{} shows that as $\lambda$ increases, the support of the MQG becomes more peaked, with most of their probability mass concentrating on a smaller number of controls.
+Fig.~\ref{fig:sparsity} shows that as $\lambda$ increases, the support of the MQG becomes more peaked, with most of their probability mass concentrating on a smaller number of controls.
 In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
@@
 \label{sub:two_qubit}
-In our two-qubit example we consider the following model for two tunable qubits coupled by a resonant exchange interaction, similar to that in \cite{McKay2016}:
+In our two-qubit example we consider a resonant exchange interaction, similar to that in \cite{McKay2016}:
 \begin{equation} \label{eq:2Qham}
@@
 
-Randomized protocols have a long history of outperforming their deterministic counterparts.
-In \cite{Viola2005, Santos2006} the use of randomness is discussed in the context of dynamical decoupling.
-In particular, it is shown that both stochastic and hybrid approaches can result in better or more tractable coherent controls.
-Additionally Pauli Frame Randomization\cite{Wallman2016} has been shown \cite{1803.01818} to reduce coherent errors by introducing randomness in a pre-compilation step.
-The techniques discussed in this paper are different from both of these approaches in that they explicitly produce incoherent errors through mixing, and that the randomness is hardware efficient for any desired gate.
-
 Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 
-That these methods depnd on accurate system models is a clear shortcoming.
+That these methods depend on accurate system models is a clear shortcoming.
 The robust MQG The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
@@
 While performing a complete optimization in this way would require full process tomography, one could instead optimize via partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
+By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ terms, one could perform optimization over fewer parameters.
 

### 2019-11-26 decorrelation/mixed_unitaries.tex
about ready to be read through again by kevin

@@
 for more than a few qubits.
-In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nelder-Mead to perform the minimization.
-While performing a complete optimization in this way would require full process tomography, one could instead optimize via partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ terms, one could perform optimization over fewer parameters.
-
-Crosstalk, two qubit gates, etc.
+In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015}.
+While performing a complete optimization in this way would require full process tomography, one could instead use partial tomography.
+By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk terms, one could perform optimization over fewer parameters.
 

### 2019-11-26 decorrelation/mixed_unitaries.tex
one more read through, then time to email kevin!

@@
 \caption{Pauli Transfer Matrices for a) $\mathsf{Pulse1}$ b) $\mathsf{Pulse2}$ c) $\mathsf{Pulse3}$ d) $\mathsf{Pulse4}$ e) MQG.
-The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-Exact MQG has been constructed to have minimal coherent error and therefore had dominantly diagonal elements.}
+The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-Exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
 \end{figure}
@@
 \includegraphics[scale=.5]{sparisity-versus-parameter.png}
-\caption{Sparsity of MQGs as a function of the sparisty parameter, $\lambda$.
-As the parameter is increased from zero, the number of controls (y-axis) with low probability increases.
-For $\lambda=.001$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
+\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$, with higher weight controls omitted to emphasize the low-weight distribution.
+Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=6.25$e-05, $\lambda_2=0.0001$, $\lambda_3=0.00025$, $\lambda_4=0.0005$.
+As the parameter is increased from zero, the number of controls with low probability increases.
+For $\lambda_4$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
 \label{fig:sparsity}

### 2019-11-27 decorrelation/mixed_unitaries.tex
trying to find the dat files

@@
 \noindent The ultimate impact of a gate error on the performance of a quantum circuit depends strongly on both the magnitude and the nature of the error.
-Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor (QIP).
+Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a quantum information processor.
 Errors of this type are correlated in time and may add up constructively or destructively, depending on details of the circuit in which they appear.
@@
 
-Randomized protocols have a long history of outperforming their deterministic counterparts.
-In \cite{Viola2005, Santos2006} the use of randomness is discussed in the context of dynamical decoupling.
-In particular, it is shown that both stochastic and hybrid approaches can result in better or more tractable coherent controls.
-Additionally Pauli Frame Randomization\cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
-While this routine affects a similar outcome to that of randomized compiling, it admits a hardware-efficient implementation and numerous useful extensions due to its framing as a numerical optimization problem.
+Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}.
+In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
+While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
 
@@
 \end{equation}
-Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented in this basis take the particularly nice form,
+Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} (PTMs) \cite{Chow2012}.  Error maps represented in this basis take the particularly nice form,
 \begin{equation}\label{eq:process_matrix}
@@
 If the error map is unitary, then the error is called \textit{coherent} and the unital submatrix $R$ is a rotation matrix.
-Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
+Importantly, if $R$ is diagonal, then the error is Pauli-stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.
 
-In general an error will neither be fully coherent nor Pauli stochastic and so it is useful to define what we mean by the coherence of arbitrary noise\cite{CarignanDugas2019}.
+In general an error will neither be fully coherent nor Pauli-stochastic and so it is useful to define what we mean by the coherence of arbitrary maps\cite{CarignanDugas2019}.
  One way to measure this is with a quantity called the unitarity\cite{Wallman2015}:
@@
 \end{align}
-where $\mathbf{n}$ is the length of the Bloch vector, and the integral is over all pure states using the Haar measure.
-Yet another way of quantitavely describing how unitary a channel is with protocols that assess how errors accumulate on different input states\cite{1907.05950}.
+where $\mathbf{n}$ is the length of the Bloch vector, and the integral is over all $d$-dimensional pure states using the Haar measure.
+Yet another way of quantitavely describing how unitary a map is with protocols that assess how errors accumulate on different input states\cite{1907.05950}.
 In this work, we will only discuss the relative unitarity of channels, and therefore are content if the unitarity of our error map decreases by any of these metrics.
@@
 \end{align}
-where $d=2^n$ and $\ident_d$ is the $d$-dimensional identity operator.
+where $d=2^n$, with $n$ being the number of qubits, and $\ident_d$ is the $d$-dimensional identity operator.
 In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\error$, in terms of its associated Pauli transfer matrix, $\errmat$.
@@
 In order to definitively eliminate these coherent errors, we could instead seek weights, $\weight^P_i$, that annihilate the off-diagonal entries of the effective error map.
-The resulting diagonal error map will be Pauli stochastic.
+The resulting diagonal error map will be Pauli-stochastic.
 For a single qubit gate, it takes the form,
@@
 The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$.
-If the error map contains non-unital components or correlated Pauli stochastic errors (such as $X+Y$), then this strict geometric condition will not hold and no Pauli-exact MQG will exist.
+If the error map contains non-unital components or correlated Pauli-stochastic errors (such as $X+Y$), then this strict geometric condition will not hold and no Pauli-exact MQG will exist.
 However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.
@@
   \begin{split}
-    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm} \dnorm\left(\sum_i\error_i \weight_i\right)
+    &\underset{\weight_i\geq0, \sum_i\weight_i=1}{\textbf{minimize}: } \hspace{.5cm} \dnorm\left(\sum_i\weight_i\error_i \right)
   \end{split}
@@
 
-As discussed in the previous section, the geometric condition illustrated in Fig.~\ref{fig:vectorspace} may not be satisfied, due perhaps to stochastic errors in the generators or possible a situation in which one has access only to $m$ distinct, precomputed gate implementations.
-In this case, we may simply wish to to identify the MQG with minimum error.
+As discussed in the previous section, the geometric condition illustrated in Fig.~\ref{fig:vectorspace} may not be satisfied, due perhaps to stochastic errors in the generators or possibly a situation in which one has access only to $m$ distinct, precomputed gate implementations.
+In this case, we may simply wish to to identify the MQG with minimal error.
 A heuristic that is efficiently computable is to minimize the Frobenius norm of the first-order effective error generator:
@@
 Coherent errors impose a particular burden on classical simulators, as the entire quantum state must be tracked continually.
-Existing work generally approximates channels as Pauli stochastic channels, and assesses the quality of these approximations\cite{Puzzuoli2014, Magesan2013}.
-Pauli frame randomization adds additional gates into circuits leave the result unchanged but randomize the nosie in such a way that it becomes a Pauli stochastic channel.
-This technique offers another path forward.
+Existing work generally approximates channels as Pauli-stochastic channels, and assesses the quality of these approximations\cite{Puzzuoli2014, Magesan2013}.
+Pauli Frame Randomization adds additional gates into circuits leaving the computation unchanged but randomizing the noise in such a way that it becomes a Pauli-stochastic channel.
+MQGs offer another path forward.
 Pauli-exact MQGs can be constructed with vanishing coherent error and without adding any additional gates or compilation time.
-Building MQGs with diminished coherent error enables the use of much more efficient Pauli stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
+Building MQGs with diminished coherent error enables the use of much more efficient Pauli-stochastic simulators that are able to model significantly more qubits than their vector-state counterparts.
 
-In particular, the well-known stabilizer framework \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations.
-These circuits are useful because they give examples of quantum circuits whose performance we can efficiently assess using classical simulation.
-This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and even algorithms for the simulation of arbitrary circuits.
+In particular, the well-known stabilizer formalism \cite{quant-ph/9807006} for quantum simluation gives a polynomial-time algorithm to compute expectation values of circuits consisting of only Clifford operations.
+These circuits are useful because they give examples of quantum circuits whose performance can be efficiently assessed using classical simulation.
+This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and linear combinations of stabilizer circuits.
 \cite{Yoder, Bennink2017} An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is.
-Therefore Pauli-Exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli Stochastic errors, they will be more amenable to stabilizer simulation.
+Therefore Pauli-exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-stochastic errors, they will be more amenable to efficient classical simulation.
+
 Like generator-exact MQGs, the optimal weights can be found efficiently by a convex optimization.
-
 As above, we assume that we have access to $m$ distinct gate implementations, each of which is associated with its own error matrix, $\errmat_i$.
@@
 Mixed quantum gates can offer significant performance improvements over bare unitary gates, but their construction requires a good knowledge of the errors experienced by the constituent gates.
-Often, however, the gates are not perfectly well characterized.
+Often, however, the gates are not perfectly well-characterized.
 This could be due to simple uncertainty about the parameters of the model used to generate the control solutions, or the system could experience some degree of drift \cite{1907.13608}.
@@
 We would like to choose the weights $\vec\weight$ so that the effective error generator vanishes to first order.
-We can cast this problem as a convex optimization problem, much as we did in Sec.~\ref{sec:introduction} for synthesizing generator-exact MQGs.
+We can cast this problem as a convex optimization problem, much as we did in Sec.~\ref{sub:first_order_generators} for synthesizing generator-exact MQGs.
 Following Eq.~\eqref{eq:minimization}, we have,
-\begin{equation}\label{eq:minimization}
+\begin{equation}
   \begin{split}
@@
 We call a gate constructed in this way a \emph{robust} generator-exact MQG.
-These techniques can easily adapted to construct robust Pauli-exact MQGs, where vectors of the off-diagonal elements of the error maps take the role of the error generators used above.
+These techniques can be easily adapted to construct robust Pauli-exact MQGs, where vectors of the off-diagonal elements of the error maps take the role of the error generators used above.
 
@@
 
-To incentive the inclusion of controls with smaller error, we may instead minimize the average gate infidelity of the mixed quantum gate, subject to the condition that any solution we find be generator-exact:
+To incentive the inclusion of controls with smaller error, we may instead minimize the average gate infidelity of the MQG, subject to the condition that any solution we find be generator-exact:
 
@@
 \caption{Pauli Transfer Matrices for a) $\mathsf{Pulse1}$ b) $\mathsf{Pulse2}$ c) $\mathsf{Pulse3}$ d) $\mathsf{Pulse4}$ e) MQG.
-The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-Exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
+The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
 \end{figure}

### 2019-11-27 decorrelation/mixed_unitaries.tex
final paper updates, ready for kevin to look at

@@
 \end{equation}
-Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices} (PTMs) \cite{Chow2012}.  Error maps represented in this basis take the particularly nice form,
+Process matrices written in this Pauli basis are often referred to as \emph{Pauli transfer matrices}\cite{Chow2012}.  Error maps represented in this basis take the particularly nice form,
 \begin{equation}\label{eq:process_matrix}
@@
 As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
-Control electronics often have a limited amount of waveform memory, and thus it is important to be able to construct MQGs as few constituent gates as possible.
+Control electronics often have a limited amount of waveform memory, and thus it is important to be able to construct MQGs with as few constituent gates as possible.
 In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions.
 Rather than penalizing the $\ell_0$ norm of the solution, which is not convex, lasso regularization penalizes the $\ell_1$, which is the convex relaxation of the $\ell_0$ norm.
-However this is insufficient for our purposes, as we require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
+However this is insufficient for our purposes, as we already require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
 Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
@@
 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
-Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli Transfer Matrices in Figure \ref{ptms}.
+Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices in Fig.
+\ref{ptms}.
+$\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
 \begin{figure}
 \includegraphics[scale=.5]{experimental-ptm.png}
-\caption{Pauli Transfer Matrices for a) $\mathsf{Pulse1}$ b) $\mathsf{Pulse2}$ c) $\mathsf{Pulse3}$ d) $\mathsf{Pulse4}$ e) MQG.
-The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli Transfer Matrices, while the Pauli-exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
+\label{ptms}
+\caption{Pauli transfer matrices for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG.
+The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices, while the Pauli-exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
 \end{figure}
@@
 We characterize the performance of the MQG using a series of randomized benchmarking (RB) experiments\cite{Magesan2011}: one for each of the miscalibrated pulses, one using the calibrated pulse, and using the MQG.
-In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were implemented directly using the relevant waveforms, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
-All circuits were precompiled on the host computer and sent to be executed to the control electronics, rather than using the FPGA or lower-level firmware to sample at run-time.
+In each case, the Clifford operations were decomposed into $X_{\pi/2}$ gates, which were implemented directly using the relevant waveform, and $Y_{\pi/2}$ gates, which were implemented by phase-shifting the relevant waveform $\pi/2$ radians.
+All circuits were precompiled on the host computer and sent to be executed on the control electronics, rather than using the FPGA or lower-level firmware to sample from $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ at run-time.
 
@@
 We emphasize that, when benchmarking the MQG, each sequence repetition used a new, randomly sampled sequence of waveforms consistent with its definition.
-Results of the standard RB analysis are discussed in Table.~\eqref{tabl:rb}.
+Results of the standard RB analysis are discussed in Table.~\ref{tabl:rb}.
 The MQG is seen to perform nearly as well as the calibrated pulse, and better than any of the constituent pulses individually.
@@
 \begin{table}[h]
-	\label{tabl:rb}
 	\centering
@@
 }
+\label{tabl:rb}
 \end{table}
@@
 Shown here is the distribution of randomized benchmarking survival probabilities at $L=64$ for each of six native gate implementations.
-The first four boxes (light blue) result four intentionally miscalibrated ${\pi/2}$ rotations.
+The first four boxes (light blue) are the results from four intentionally miscalibrated ${\pi/2}$ rotations.
 The coherent noise present in these implementations leads to large variance in the survival probability over sequences.
@@
 \caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$, with higher weight controls omitted to emphasize the low-weight distribution.
-Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=6.25$e-05, $\lambda_2=0.0001$, $\lambda_3=0.00025$, $\lambda_4=0.0005$.
+Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=6.25$e-05, $\lambda_2=0.0001$, $\lambda_3=0.00025$ and $\lambda_4=0.0005$.
 As the parameter is increased from zero, the number of controls with low probability increases.
@@
 However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
-Fig.~\ref{fig:sparsity} shows that as $\lambda$ increases, the support of the MQG becomes more peaked, with most of their probability mass concentrating on a smaller number of controls.
+Fig.~\ref{fig:sparsity} shows that as $\lambda$ (Eq.
+\eqref{eq:minimization_regularization}) increases, the support of the MQGs become more peaked, with most of their probability mass concentrating on a smaller number of controls.
 In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
@@
 
-Using controls generated in this way, the MQGs produced for $X_{\pi/2}$ and $Y_{\pi/2}$ are qualitatively similar, with the results for $X_{\pi/2}$ shown in Figure \ref{fig:YMQG}.
+Using controls generated in this way, the MQGs produced for $X_{\pi/2}$ and $Y_{\pi/2}$ are qualitatively similar, with the results for $X_{\pi/2}$ shown in Fig.
+\ref{fig:YMQG}.
 By imposing the penalty from Section \ref{sec:norm}, we sought to ensure that the algorithm preferentially selected controls with smaller errors.
-Adding this constraint increased the performance of the 0MQG by nearly an order of magnitude at the origin, and produced a 1MQG whose performance is an order of magnitude better than the 0MQG away from the origin.
+Adding this constraint increased the performance of the generator-exact MQG by nearly an order of magnitude at the origin, and produced a robust generator-exact MQG whose performance is an order of magnitude better than the generator-exact MQG away from the origin.
 Imposing this constraint allows us to trade off flatness for performance.
@@
   \includegraphics[width=\columnwidth]{figures/1q_robustness_delta.pdf}
-  \caption{\textbf{One-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
+  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
 The target is an $X_{\pi/2}$ gate on a single qubit.
-The generator-exact MQGs dramatically outperforms both the robust MQG and any of the bare unitaries at $\delta=0$.
-However, even a relatively small amplitude error leads to a regime in which the the robust MQG will yield the better gate.
+The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$.
+However, even a relatively small amplitude error leads to a regime in which the the robust generator-exact will yield the better gate.
 Similar results are obtained for drift in the qubit frequency.}
@@
 
-In this example it was infeasible to use GRAPE to return non-trivial solutions (always got the same result).
+In this example it was infeasible to use GRAPE to return non-trivial solutions, as the algorithm would tend to return similar solutions for a wide variety of initial conditions.
 Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$.
@@
 
-In this example, we find more modest improvements to performance, as shown in Figure \ref{fig:2MQG}.
+In this example, we find more modest improvements to performance, as shown in Fig.
+\ref{fig:2MQG}.
 There are now four free parameters to optimize over, and the uncontrolled entangling interaction means that there is little room for variation in the controls.
-Nonetheless, using an MQG improves performance by half an order of magnitude at the origin relative to the constituent controls, and up to an order of magnitude away from the origin.
-For all values of the drifting parameters we see that the 1MQG performs as well or better than 0MQG.
+Nonetheless, using an MQG improves performance over any of the constituent controls over a wide-range of detunings, and for all values of the detunings we see that the robust generator-exact MQG performs as well or better than generator-exact MQG.
 
@@
   \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
-  \caption{\textbf{Two-qubit robust MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).
-It is intended to models a pair of tunable qubits interacting via resonant exchange.
+  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).
+It is intended to model a pair of qubits interacting via resonant exchange.
 Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings.
-The robust MQG performs always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings.
+The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings.
 Similar results are obtained for drift in the qubit control amplitude.}
@@
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other optimization routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other control routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 
-That these methods depend on accurate system models is a clear shortcoming.
-The robust MQG The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g.
-in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system.
-Even if a model is available, it might be computationally inconvenient to simulate, i.e.
-for more than a few qubits.
-In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015}.
+Additionally while this optimal control in this work has been \textit{ex situ}, an interesting approach would be to instead use \textit{in situ} techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate the controls.
 While performing a complete optimization in this way would require full process tomography, one could instead use partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk terms, one could perform optimization over fewer parameters.
+By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk terms, one could perform optimization over fewer parameters to produce MQGs that supress specific errors.
 

### 2019-12-13 decorrelation/mixed_unitaries.tex
Minor updates

@@
 
-In general an error will neither be fully coherent nor Pauli-stochastic and so it is useful to define what we mean by the coherence of arbitrary maps\cite{CarignanDugas2019}.
- One way to measure this is with a quantity called the unitarity\cite{Wallman2015}:
-\begin{align}
-u(\mathsf{E}) = \frac{d}{d-1}\int d\psi ||\mathbf{n}[\mathsf{E}(\psi)] - \mathbf{n}[\mathsf{E}(\identmat_d/2)||^2
-\end{align}
-where $\mathbf{n}$ is the length of the Bloch vector, and the integral is over all $d$-dimensional pure states using the Haar measure.
+% In general an error will neither be fully coherent nor Pauli-stochastic and so it is useful to define what we mean by the coherence of arbitrary maps\cite{CarignanDugas2019}.
+%  One way to measure this is with a quantity called the unitarity \cite{Wallman2015}:
+% \begin{align}
+% u(\mathsf{E}) = \frac{d}{d-1}\int d\psi ||\mathbf{n}[\mathsf{E}(\psi)] - \mathbf{n}[\mathsf{E}(\identmat_d/2)||^2
+% \end{align}
+% where $\mathbf{n}$ is the length of the Bloch vector, and the integral is over all $d$-dimensional pure states using the Haar measure.
 Yet another way of quantitavely describing how unitary a map is with protocols that assess how errors accumulate on different input states\cite{1907.05950}.
@@
 Such errors always have strictly positive probabilities, so the origin can \emph{never} lie in their convex hull.
-This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators, or by replacing the exact condition with a minimization, as we discuss in Sec.~\ref{sec:mixed_unitary_processes}.
+This formalism can be adapted to such cases by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators, or by replacing the exact condition with a minimization, as we discuss in Sec.~\ref{sec:mixed_unitary_processes}.
 
@@
 The off-diagonal elements of the error map form a vector space, so we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\errmat_i$.
-If the error map contains non-unital components or correlated Pauli-stochastic errors (such as $X+Y$), then this strict geometric condition will not hold and no Pauli-exact MQG will exist.
+If the error map contains non-unital components or correlated Pauli-stochastic errors (such as $X+Y$), then this strict geometric condition may not hold and no Pauli-exact MQG would exist.
 However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.
@@
 We will begin by discussing the two broad optimization targets introduced above: i) generator-exact MQGs and ii) Pauli-exact MQGs.
-We then propose a set of secondary targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
+We then propose a set of secondary optimization targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
 
@@
 Often, the cost of generating distinct gate implementations is quite small, so large ensembles of them can be computed rather quickly.
-It is often the case that one will have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
+One may then have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
 This can lead to the the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions.
@@
 \label{sub:diamond_distance_inequality}
-Here we prove the claim of \eqref{eq:diamond_ineq} that:
+Here we prove the claim of Eq.~\eqref{eq:diamond_ineq} that:
 \begin{equation}

### 2019-12-13 decorrelation/mixed_unitaries.tex
updating alpha of robustness plots, delta -> epsilon in ylabel, spaces in the ptms, and lambda -> mu in discussion of model parameters

--- 2019-11-27 decorrelation/mixed_unitaries.tex
@@
 In either case, the performance of the MQG will be negatively impacted.
-We can describe the effect of this uncertainty by first writing the gate explicitly as a function of a vector of model parameters, $\vec\lambda$, and their nominal values, $\vec\lambda_0$.
+We can describe the effect of this uncertainty by first writing the gate explicitly as a function of a vector of model parameters, $\vec\mu$, and their nominal values, $\vec\mu_0$.
 These model parameters could include magnetic field strengths, laser or microwave intensities, coupling strengths, etc.
-If the parameters are close to their nominal values, then we can write a gate's error generator as a Taylor expansion in the deviation vector, $\vec\delta = \vec\lambda-\vec\lambda_0$:
+If the parameters are close to their nominal values, then we can write a gate's error generator as a Taylor expansion in the deviation vector, $\vec\delta = \vec\mu-\vec\mu_0$:
 \begin{equation}

### 2020-01-13 decorrelation/arxiv/mixed_unitaries.tex
adding in first version submitted to arxiv, and document now has typos fixed by earl

--- 2019-12-13 decorrelation/mixed_unitaries.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% RevTeX 4.1 LaTeX
-% Kevin C. Young
-% Scalable & Secure Systems Research (08961)
-% Thu Mar  5 15:29:19 PST 2015
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
@@
 \newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
-% \newcommand{\identmat}{{\mathbb1}}
 \newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
@@
 \newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
-% \newcommand{\note}[1]{{\color{red}[#1]}}
 \newcommand{\note}[1]{}
@@
 Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}.
-In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
+In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
 While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
@@
 For a single qubit gate, it takes the form,
-% \begin{equation}
-% 	\errmat_{eff} = 
-% 	\left(\begin{array}{@{}ccccc@{}}
-% 		\cdot & \cdot & \cdot & \cdot \\ 
-%   		\cline{1-1}\cline{3-4}
-%     	\multicolumn{1}{|c}{0} & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c}{0} & \multicolumn{1}{c|}{0} \\
-%     	\cline{2-2}\cline{3-3}		
-% 		\multicolumn{1}{|c}{0} & 0 & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c|}{0}\\
-% 		\cline{3-3}\cline{4-4}	
-% 		\multicolumn{1}{|c}{0} & 0 & 0 & \multicolumn{1}{|c}{\cdot}\\
-% 		\cline{1-3}
-% 	\end{array} 	
-% 	\right).
-% \end{equation}
+
 \begin{equation}
@@
 However, MQGs that approximate the Pauli-exact condition can be found via the convex programing techniques discussed in Sec.~\ref{sub:off_diagonals}.
-
-% In the remainder of this paper, we will formalize this process, laying out efficient convex programs to both generate a family of unitary controls \kcy{do we do this?} and compute the weights required to yield either type of MQG.
-We discuss how one might include additional desiderata, including reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the MQG.
 
@@
 We then propose a set of secondary optimization targets that can improve the performance by i) incorporating robustness to drift, ii) targeting low-error-rate solutions, and iii) reducing the number of native unitaries that contribute to the effective channel.
-
-% In the examples that were discussed, all objective functions were linear, and reduced to finding a collection of controls whose convex hull contained the origin in some high-dimensional vector space.
-In those cases, the vectors might represent a collection of error generators or the off-diagonal elements of a collection of error maps.
-As we'll see in Section \ref{sub:adding_robustness}, we can also consider the derivatives of the error generators to minimize the sensitivity of the controls to drift.
-In this way, we see that by considering the appropriate collection of vectors, we can optimize our MQG for different purposes, and which routine we choose will depend on the quantities we are trying to minimize.
 
@@
 
-%In both cases it is clear that we should select the gates with smaller error, i.e.
-$\{U_{\epsilon}, U_{-\epsilon}\}$, rather than those with larger error, to minimize the multiplicative coefficient on the error.
-Despite this, literature commonly assumes that all controls are less than some threshold value, below which differences in performance don't matter.
-\cite{Campbell2017} In realistic scenarios, some controls will have better performance than others, and it is important to select from those controls when able to.
-We will discuss numerical approaches to solving this Section \ref{sec:norm}.
-
-%Another interesting property of the MQG given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift.
-In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways.
-Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$.
-In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order.
-Given these considerations from this simple example, we will now consider a numerical strategy for generating MQGs.
-
-% subsection first_order_generators (end)
-
-% ==============================================================================
-% Section: Off-diagonals
-% ==============================================================================
-% contrast coherent errors with stochastic where an expectation can be computed and then the circuit can be rerun, rather than having to track the the whole state.
-
 \subsubsection{Pauli-exact MQGs} % (fold)
@@
 If the solver routine finds a solution for which the cost function is equal to 0, then the resulting error channel will be \textit{exactly} a Pauli channel.
-%As mentioned, circuits composed of gates with Pauli stochastic error channels can be more efficiently simulated by Monte Carlo methods.
-Furthermore, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} \kcy{Why this paper?}
 
@@
 
-% subsection adding_robustness (end)
-
 % ==============================================================================
@@
 
-% then we can instead incentivize the construction of a lowest-error MQG by including an AGI penalty directly in the
-
-% \begin{equation}\label{eq:minimization}
-%   \begin{split}
-%     &\underset{\weight_i\geq0, |\weight|_1=1}{\textbf{minimize}: } \sum_i \weight_i\; \AGI(\errmat_i)\\
-%     & \textbf{subject to}: ||\mathbf{L}\cdot\vec\weight||_2 = 0 
-%   \end{split}
-% \end{equation}
-
-% \begin{equation}\label{eq:minimization_l2}
-% \begin{split}
-% & \ \bunderbrace{\textbf{minimize}: }{\weight_i\geq0, |\weight|_1=1} ||{\mathbf{D}^{\ell}}\weight||_1+ \eta\sum\weight_i||D^0_i||_2\\
-% &\ \ \textbf{subject to: } \forall n<\ell, ||\sum \weight_iD_i^n||=0\\
-% \end{split}
-% \end{equation}
-% with $\eta \geq 0$.
-By increasing $\eta$, we can encourage the optimizer to include better controls while minimizing the diamond norm.
-The value of $\eta$ that is best for any particular problem instance will depend on the values in $\mathbf{D}^\ell$.
-
-%Naively generating the 1Q 0MQG in the previous section results in nontrivial support on all the members of the control family.
-However, as we will see in the next section, we can rewrite the minimization to impose a sparsity constraint, and the resulting 0MQG uses just five of the controls.
 % ==============================================================================
@@
 {\renewcommand{\arraystretch}{1.2}
-% \newcolumntype{d}[1]{D{.}{.}{#1}}
 \begin{table}[h]
@@
 By minimizing the off-diagonal elements of the process matrix, we expect the resulting MQG to display suppressed coherent error.
-To see that this is in fact the case, we can inspect the variance of the $RB$ survival probabilities for the MQG relative to the miscalibrated pulses.
+To see that this is in fact the case, we can inspect the variance of the RB survival probabilities for the MQG relative to the miscalibrated pulses.
 As discussed in \cite{Ball2016}, coherent errors will tend to broaden the distribution of RB survival probabilities over sequences at each length, generally manifesting as a long-tailed gamma distribution.

### 2020-01-21 decorrelation/mixed_unitaries.tex
one RB was in dolla signs
removing comments
updates before PRA

@@
 Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate.
-As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, by replacing the deterministic implementation of a quantum gate with a randomized ensemble of implementations, on can dramatically suppress coherent errors.
+As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, by replacing the deterministic implementation of a quantum gate with a randomized ensemble of implementations, one can dramatically suppress coherent errors.
 Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem.
@@
 
-Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations.
+Campbell \cite{Campbell2017,Campbell2019} and Hastings \cite{Hastings2017} have developed a technique for suppressing coherent noise by replacing deterministic gate implementations with a \emph{mixed quantum gate} (MQG) consisting of a randomly sampled ensemble of implementations.
 They focus on errors in gate compilation, such as those that arise from the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the underlying native gates are perfect.
@@
 
-While generator-exact MQGs can provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be a purely stochastic.
+While generator-exact MQGs can provide a guaranteed suppression of the diamond distance, their effective error channels are unlikely to be purely stochastic.
 Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel.
@@
 
-% In the remainder of this paper, we will formalize this process, laying out efficient convex programs to both generate a family of unitary controls \kcy{do we do this?} and compute the weights required to yield either type of MQG.
-We discuss how one might include additional desiderata, including reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the MQG.
-
 % ==============================================================================
@@
 The first is a control synthesis step, in which we construct an ensemble of gate implementations.
-Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we use utilize quantum optimal control theory.
+Campbell and Hastings draw their ensembles from various different gate compilations, but for this work we utilize quantum optimal control theory.
 Many standard control-generation algorithms, such as GRAPE \cite{Khaneja2005}, take a random initial guess for the control and iteratively improve it to yield a gate that well-approximates a target.
@@
 These circuits are useful because they give examples of quantum circuits whose performance can be efficiently assessed using classical simulation.
-This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and linear combinations of stabilizer circuits.
-\cite{Yoder, Bennink2017} An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is.
+This has motivated significant development of these techniques, including extensions to simulating stabilizer circuits with mixed state inputs\cite{Aaronson2004} and linear combinations of stabilizer circuits\cite{Yoder, Bennink2017}.
+An interesting property of such simulation techniques is that the cost of the classical simulation is proportional to how non-Clifford the circuit is.
 Therefore Pauli-exact MQGs have a clear benefit - if the error channels of a circuit can be made to look more like Pauli-stochastic errors, they will be more amenable to efficient classical simulation.
@@
 One may then have available many more distinct gate implementations than there are parameters in the relevant vector space (see Fig.~\ref{fig:vectorspace}).
-This can lead to the the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions.
+This can lead to the minimization problems discussed in the previous section being massively under-constrained, yielding a large continuous family of exact solutions.
 Secondary objectives provide a means for choosing among this family of exact MQGs those with increased performance in a desired area.
@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/1q_robustness_delta.pdf}
+  \includegraphics[width=\columnwidth]{1q_robustness_delta.pdf}
   \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
@@
   \centering
-  \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
+  \includegraphics[width=\columnwidth]{2q_robustness.pdf}
   \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).

### 2020-03-05 decorrelation/mixed_unitaries.tex
changes to sparisty section

@@
 \noindent
-As a practical consideration, we would also like to regularize our objective function to promote sparse weightings.
+As a practical consideration, we would also like to regularize our objective function to promote sparse weightings, resulting in MQGs with only a small number of gate implementations.
 Control electronics often have a limited amount of waveform memory, and thus it is important to be able to construct MQGs with as few constituent gates as possible.
-In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions.
-Rather than penalizing the $\ell_0$ norm of the solution, which is not convex, lasso regularization penalizes the $\ell_1$, which is the convex relaxation of the $\ell_0$ norm.
+In many machine learning contexts, a technique called lasso regularization \cite{tibshirani1996regression} can be used to enforce this sparsity in solutions.
+
+Rather than penalizing the $\ell_0$ norm of the solution, which counts the number of nonzero entries in a vector, lasso regularization penalizes the $\ell_1$ norm, which is a convex relaxation of the $\ell_0$ norm.
+Because the extreme points of the unit $\mathcal{L}_1$ sphere lie on the unit Cartesian vectors, solutions to the lasso regularized problem are guaranteed to be sparse.
 However this is insufficient for our purposes, as we already require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
-Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
+
+The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
 \begin{equation}\label{eq:minimization_regularization}
@@
 \end{equation}
-Here, $\lambda > 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
-Increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
+Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization}, and the outer minimization is redundant.
+If $\lambda$ is very large each inner minimization problem reduces to a MQG with a single control selected.
+Therefore the outer minimization simply selects the control whose corresponding error generator has smallest norm.
+While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
+In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
 
@@
 To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls.
-However, by imposing the sparisty constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
+However, by imposing the sparsity constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
 Fig.~\ref{fig:sparsity} shows that as $\lambda$ (Eq.

### 2020-03-05 decorrelation/mixed_unitaries.tex
all the email updates and the sparsity updates should be on the tex file. The arxiv folder is no longer faithful to arxiv version v1

@@
 In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
-While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
+While Pauli Frame Randomization shares some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
 
@@
   \includegraphics[width=\columnwidth]{1q_robustness_delta.pdf}
-  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
+  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error.
 The target is an $X_{\pi/2}$ gate on a single qubit.
 The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$.
-However, even a relatively small amplitude error leads to a regime in which the the robust generator-exact will yield the better gate.
+However, even a relatively small amplitude error leads to a regime in which the robust generator-exact will yield the better gate.
 Similar results are obtained for drift in the qubit frequency.}
@@
   \includegraphics[width=\columnwidth]{2q_robustness.pdf}
-  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).
+  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude).
 It is intended to model a pair of qubits interacting via resonant exchange.

### 2020-04-11 decorrelation/mixed_unitaries.tex
adding ptm

@@
 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
-Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices in Fig.
+Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices, minus the identity, in Fig.
 \ref{ptms}.
-$\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
+We have removed the identity from the plot to highlight the small diagonal elements of the MQG $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
 \begin{figure}
@@
 \label{ptms}
-\caption{Pauli transfer matrices for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG.
-The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices, while the Pauli-exact MQG has been constructed to have minimal coherent error and therefore has predominantly diagonal elements.}
+\caption{Pauli transfer matrices with the identity subtracted off for the error maps of a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG.
+The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices.
+The Pauli-exact MQG has been constructed to have minimal coherent error and therefore only has diagonal elements.
+}
 \end{figure}

### 2020-04-11 decorrelation/mixed_unitaries.tex
updates to paper

@@
 \subsection{Convex Programs for Constructing Mixed Quantum Gates}
+\label{sec:convex_programs}
 \subsubsection{Generator-exact MQGs} % (fold)
@@
 
-Rather than penalizing the $\ell_0$ norm of the solution, which counts the number of nonzero entries in a vector, lasso regularization penalizes the $\ell_1$ norm, which is a convex relaxation of the $\ell_0$ norm.
-Because the extreme points of the unit $\mathcal{L}_1$ sphere lie on the unit Cartesian vectors, solutions to the lasso regularized problem are guaranteed to be sparse.
+Rather than penalizing the $\ell_0$ norm of the solution, which is not convex, lasso regularization penalizes the $\ell_1$ norm, which is a convex relaxation of the $\ell_0$ norm.
 However this is insufficient for our purposes, as we already require $\weight$ to be a valid probability distribution, which constrains the $\ell_1$ norm to be equal to $1$.
@@
 The problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Eq.~\eqref{eq:minimization}:
-\begin{equation}\label{eq:minimization_regularization}
+\begin{equation}\label{eq:minimization_sparsity}
 \begin{split}
@@
 Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
-If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization}, and the outer minimization is redundant.
-If $\lambda$ is very large each inner minimization problem reduces to a MQG with a single control selected.
-Therefore the outer minimization simply selects the control whose corresponding error generator has smallest norm.
+If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant.
+If $\lambda$ is very large each inner minimization problem is minimized for an MQG with a single control.
+Therefore the outer minimization simply selects the control which has the error generator of smallest norm.
 While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
@@
 \ref{ptms}.
-We have removed the identity from the plot to highlight the small diagonal elements of the MQG $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
+We have subtracted the identity from each matrix to highlight the small diagonal elements of the MQG.
+$\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
 \begin{figure}
@@
 The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices.
-The Pauli-exact MQG has been constructed to have minimal coherent error and therefore only has diagonal elements.
+The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.
 }
@@
 
-We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed.
+This example shows that MQGs are capable of outperforming the individual gates of which they are composed.
+In particular, given a collection of controls whose miscalibration errors are known, this demonstrates that the techniques in Section \ref{sec:convex_programs} can be used to trade the coherent errors for incoherent errors.
 In future work, we hope to apply this technique to two-qubit gates, which are significantly more difficult to tune up in general and are more likely to possess lingering coherent errors.
@@
 To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls.
-However, by imposing the sparsity constraint discussed in Section \ref{sec:sparsity}, we found MQGs consisting of just 10 controls.
-Fig.~\ref{fig:sparsity} shows that as $\lambda$ (Eq.
-\eqref{eq:minimization_regularization}) increases, the support of the MQGs become more peaked, with most of their probability mass concentrating on a smaller number of controls.
+Using the results from in Section \ref{sec:sparsity} we generated MQGs that sample from only 10 of these controls.
+Fig.~\ref{fig:sparsity} shows solutions to Eq.~\eqref{eq:minimization_sparsity} for different choices of  $\lambda$.
+As $\lambda$ increases, the optimal solution contains less controls.
+
 In our implementation of the GRAPE algorithm, we use the performance function presented in \cite{Khaneja2005}, and average over different values of $\delta$ and $\epsilon$ using Gaussian quadrature when computing the gradient, so that we find controls that are naturally robust.
@@
 In addition, we have demonstrated that these approximate controls can be generated through optimal control (GRAPE), and that the minimization problem is tractable.
+By implementing four miscalibrated $X_{\frac{\pi}{2}}$ rotations on a superconducting qubit and drawing from them with optimized weights, we see that coherent over- and under- rotations can be averaged away.
 

### 2020-04-23 decorrelation/mixed_unitaries.tex
Changing PTM plot to a Hinton diagram of the error generator.

@@
 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
-Using these probabilities and pulse amplitudes we have plotted the corresponding Pauli transfer matrices, minus the identity, in Fig.
+Using these probabilities and pulse amplitudes we have plotted the corresponding error generators in Fig.
 \ref{ptms}.
-We have subtracted the identity from each matrix to highlight the small diagonal elements of the MQG.
-$\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear supression of these off-diagonal elements.
+$\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear suppression of these off-diagonal elements.
 \begin{figure}
@@
 \label{ptms}
-\caption{Pauli transfer matrices with the identity subtracted off for the error maps of a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e)a Pauli-exact MQG.
-The four constituent pulses can be seen to have coherent error from the off-diagonal components of their Pauli transfer matrices.
-The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.
-}
+\caption{Hinton diagrams representing the error generators for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e) a Pauli-exact MQG.
+White boxes correspond to positive values, black  boxes correspond to negative values, and the size of the box corresponds to the magnitude of each entry.
+The four constituent pulses can be seen to have coherent errors from the off-diagonal components of their error generators.
+The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.}
 \end{figure}

### 2020-04-28 decorrelation/resubmission/response_to_referees.txt
Added referee response

First Referee,
Thank you for the helpful suggestions. In line with your comment, we have added the following text to Secs. IIIB3 and IVB1 with Fig. 6 for readers not familiar with sparse modeling.
""

Second Referee,
Thank you for your report.

While randomized compiling is well known in the field and affects the same outcome as our strategy, it is important to note that our technique works at the hardware level, rather than the compilation level. Thus our routine does not require a precompilation step for each circuit. Additionally, as you point out, our routine has been cast as a convex optimization routine. Because of the way we have formulated our problem, we are able to augment the mixed quantum gate to have properties besides just twirling away the error. We have summarized this in the text now as:
""

We will now respond to your five bullet points.
The experiment we chose was meant to demonstrate the reduced coherent error of the channel. While it's true that any mixing of the unitaries will outperform any of the constituent unitaries as measured by RB number, the demonstration was meant to show a reduction in the coherence of the error. This is the result mentioned by Ball et al., and we have revised the text to emphasize this. Had we chosen different weights than those produced by the convex optimizer, the error bars would have been larger.
This is a great suggestion, although the presentation might be more cluttered. However, the first author no longer has access to the hardware at Rigetti Computing.
While it is true that RB randomizes errors and our technique also randomizes errors, randomized benchmarking still show cases the property of the resulting channel that we want. Namely, that the errors have minimal coherent error. Using an algorithm like QAOA would be challenging to demonstrate a decrease in the coherent error of the resulting channel. 
The two-qubit experiment is substantially harder to do. Two qubit infidelities are sufficiently high that even repeating the randomized benchmarking experiment would have very poor signal to noise, since an average clifford gate has a large number of two qubit gates. While we agree that a two-qubit demonstration would be a good addition to the manuscript, it is also the case the author no longer has access to the hardware.
The control errors need to be known to you - you can accomplish this through something like tomography. You might object - if I know my control errors, I will just fix them! It could be the case that you don't have enough samples in your DAC to do this, or that the coherent errors come from unknown interactions that are out of your control. Moreover, in the context of drift as in superconducting platforms, it is the case that you can pick out a family of controls that will all drift, but drift in different ways such that their average channel performs in a better way than any individual channel. In our experiment we have introduced the miscalibrations intentionally, since the qubits were coherence limited. We have clarified this in the text as a summary of the protocol:  ""

### 2020-04-28 decorrelation/resubmission/response_to_referees.txt
udpated response

@@
-First Referee,
-Thank you for the helpful suggestions. In line with your comment, we have added the following text to Secs. IIIB3 and IVB1 with Fig. 6 for readers not familiar with sparse modeling.
-""
+Response to referee comments for: AN11713 Robustly decorrelating errors with mixed quantum gates
 
-Second Referee,
-Thank you for your report.
+We’d like to begin by thanking the referees for their detailed comments.
+We have used their comments and criticism to improve our manuscript and are now even more confident that it is suitable for publication in Physical Review A.
+Below we include the full report of each referee (in blue italics), interspersed with our response.
+Quotes from our revised manuscript are shown in green italics.
 
-While randomized compiling is well known in the field and affects the same outcome as our strategy, it is important to note that our technique works at the hardware level, rather than the compilation level.
-Thus our routine does not require a precompilation step for each circuit.
-Additionally, as you point out, our routine has been cast as a convex optimization routine.
-Because of the way we have formulated our problem, we are able to augment the mixed quantum gate to have properties besides just twirling away the error.
-We have summarized this in the text now as:
-""
+Report of the First Referee -- AN11713/Polloreno
 
-We will now respond to your five bullet points.
-The experiment we chose was meant to demonstrate the reduced coherent error of the channel.
-While it's true that any mixing of the unitaries will outperform any of the constituent unitaries as measured by RB number, the demonstration was meant to show a reduction in the coherence of the error.
-This is the result mentioned by Ball et al., and we have revised the text to emphasize this.
-Had we chosen different weights than those produced by the convex optimizer, the error bars would have been larger.
-This is a great suggestion, although the presentation might be more cluttered. However, the first author no longer has access to the hardware at Rigetti Computing.
-While it is true that RB randomizes errors and our technique also randomizes errors, randomized benchmarking still show cases the property of the resulting channel that we want.
-Namely, that the errors have minimal coherent error.
-Using an algorithm like QAOA would be challenging to demonstrate a decrease in the coherent error of the resulting channel.
-The two-qubit experiment is substantially harder to do.
-Two qubit infidelities are sufficiently high that even repeating the randomized benchmarking experiment would have very poor signal to noise, since an average clifford gate has a large number of two qubit gates.
-While we agree that a two-qubit demonstration would be a good addition to the manuscript, it is also the case the author no longer has access to the hardware.
-The control errors need to be known to you - you can accomplish this through something like tomography.
-You might object - if I know my control errors, I will just fix them!
-It could be the case that you don't have enough samples in your DAC to do this, or that the coherent errors come from unknown interactions that are out of your control.
-Moreover, in the context of drift as in superconducting platforms, it is the case that you can pick out a family of controls that will all drift, but drift in different ways such that their average channel performs in a better way than any individual channel.
-In our experiment we have introduced the miscalibrations intentionally, since the qubits were coherence limited.
-We have clarified this in the text as a summary of the protocol:  ""
+In this paper, the authors propose novel techniques to solve the problem of coherent errors in quantum computation.
+Their techniques, which are obtained by extending previous approaches, are based on various optimization methods.
+This topic is timely and the methods proposed here will be useful in the field of quantum information science.
+So, I recommend its publication in PRA.
+
+Here I have a comment for readability.
+The presentation in Secs.
+IIIB3 and IVB1 with Fig.
+6 may be difficult to understand, especially for readers not familiar with sparse modeling.
+I recommend the improvement of the parts.
+
+We thank the referee for their positive assessment of our work, as well as for alerting us to potentially unclear sections of the manuscript.
+In line with these comments, we have added the following text to Secs.
+IIIB3 and IVB1 and modified Fig.
+6 to improve the clarity for readers not familiar with sparse optimization.
+
+Here, $\lambda\geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+If $\lambda$ is set to zero, the inner program reduces to Eq.
+(19) and the outer minimization is redundant.
+If $\lambda$  is very large each inner minimization problem is minimized for an MQG with a single control.
+Therefore the outer minimization simply selects the control which has the error generator of smallest norm.
+While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
+In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
+
+Report of the Second Referee -- AN11713/Polloreno
+
+The manuscript by Pollareno et al.
+presents a convex algorithm for compiling gates in quantum algorithms in a random fashion.
+Instead of applying a fixed gate pulse (which can have both coherent and incoherent errors), the authors pick the gates from ensembles with intentionally injected control errors.
+This procedure is meant to randomize coherent errors and mitigate any amplification of such errors in quantum circuits.
+The authors then performed a simple single-qubit RB experiment using their qubit device, where they show that the coherent errors of individual (intentionally misaligned) pulses are suppressed if the SQ gates are chosen from an ensemble of such misaligned gates.
+Some numerics are also done for two-qubit gates arguing for similar, beneficial outcomes.
+
+Randomized compiling is technique known to the QC community for quite some time now and therefore there is nothing particularly novel about the technique itself.
+What appears to be the highlight of the paper is the convex algorithm that the authors used to choose random gates and the experimental demonstration.
+While these are good steps toward a nice direction, I feel the demonstrations are not sufficiently convincing, particularly in regard to the experimental part (which the authors themselves acknowledge as being "contrived").
+Here are my main concerns:
+
+While the referee is correct that our approach is superficially similar to randomized compiling, we wish to emphasize that our technique is intended as an alternative approach to solving the problem of coherent errors in quantum information processors.
+Our method is particularly well suited for experimental implementation, as the mixed unitary gates can be implemented at the level of individual logic operations using the FPGA control hardware.
+Contrast this against the randomized compiling approach, which requires wholesale recompilation of the circuit every time it is run.
+Importantly, though, we make no claim that this broad approach is novel – in fact, we frequently cite prior foundational work in this area.
+Instead, our manuscript extends and expands the scope of this prior work, formulating the problem as an explicit convex optimization, incorporating robustness to uncertainty, and, critically, providing the first experimental demonstration of this technique on quantum information processing hardware.
+We have added the following to the text to clarify this point:
+
+MQGs are an alternative approach to solving this problem.
+Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time.
+Moreover, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.
+
+We further thank the referee for their detailed assessment of our experimental demonstration.
+We address each of the referees comments below and, in doing so, we have substantially improved our manuscript.
+
+1.
+For the experiment, it is completely trivial to me that randomly picking four faulty unitaries outperforms choosing just one of them.
+Here the only coherent errors the authors introduced are under and over-rotations to the Rabi angle.
+These over- and under-rotations would naturally build up and amplify if left by themselves.
+However, if chosen at random, they would cancel each other out and give better fidelity at the end of the sequence.
+Correct?
+I fail to see any surprise here and how the authors' lengthy algorithm even plays a role for this demonstration.
+
+The referee is correct that Rabi oscillations would be significantly (and obviously) improved by switching to a mixed quantum gate implementation.
+In fact, we found this to be so obvious as to be uninteresting, so we chose not to test such circuits experimentally.
+What we did find surprising, however, was the improved performance of randomized benchmarking circuits.
+These circuits already incorporate randomness (as the referee points out below in comment 3).
+This randomness is specifically designed to – on average -- twirl coherent errors into stochastic errors.
+But the mixed quantum gate implementation both narrowed the variance over circuits and improved the average success probability.
+The former effect is a clear signature of reduced coherent noise, while the latter has a more complicated explanation: The improvement in success probability can be traced to the compilation of the Clifford operations, which occasionally contain sequences of repeated primitive gates.
+Coherent errors in these compilations can add up, increasing the average error rate of the compiled Clifford.
+When implemented using mixed quantum gates, the coherent addition of error is suppressed and the average compiled Clifford error rate is lower, leading to an improved success probability.
+We have included new text to highlight this:
+
+While, as discussed in Sec.~\ref{sec:mqg}, the AGI of an MQG cannot be lower than any of constituent controls, the AGI of a circuit can be improved by using MQGs.
+We see from this experiment that by reducing the diamond distance of the MQG, we can improve the AGI of the total circuit.
+
+While the algorithm section of our manuscript is lengthy, it is central to our demonstration as it is used to choose the sampling weights for each of the erroneous implementations.
+If we had picked different weights, the effective channel would not be stochastic, and we would suffer a performance penalty in our demonstration.
+
+2.
+It seems to me that authors can very easily go a step further: A SQ unitary is parametrized by three angles: Rabi angle, off-diagonal and diagonal phases.
+Why not introduce coherent errors to all three phases (or at least two, such as the Rabi angle and the off-diagonal phase)?
+To me this will be much less trivial.
+
+This is an excellent suggestion, and we considered broadening the scope of the injected errors.
+However, we decided against this so that the presentation might be more streamlined.
+And while we agree that this might ultimately yield a more convincing demonstration, we no longer have the low-level access to Rigetti Computing hardware that would be required to implement it.
+
+3.
+The whole point of RB is meant to randomize coherent errors and turn them into a depolarization channel.
+It is bizarre to me that the authors chose to demonstrate their randomized compiling through an experiment that is in itself random.
+Wouldn't a structured algorithm (QAOA or anything else that is not random) be a far better candidate for demonstrating the efficacy of randomized compiling?
+
+As we discuss in our response to the referee’s first enumerated comment, randomized benchmarking circuits are sensitive to coherent errors.
+Demonstrations using metaheuristics such as QAOA, while currently en vogue, may instead confound the coherent error suppression we are attempting to illustrate.
+Full-stack QAOA requires a classical optimizer that continually tunes circuit parameters, so coherent errors can easily be suppressed by the optimizer.
+And, as we mentioned above, Rabi oscillation experiments just seemed too trivial to be interesting.
+
+4.
+Why is the two-qubit experiment not done?
+It shouldn't be that difficult to do, if the authors believe that their method works (according to numerics).
+SQ demonstrations just too trivial to show anything given their simplicity.
+
+We agree with the referee that a two-qubit gate demonstration would be significantly more impressive.
+Ultimately, we ourselves would like to see this method implemented on a two-qubit gate.
+However, the two-qubit gate available to us was dominated by large stochastic errors that severely curtailed the number of sequential gate applications before the state decohered.
+Injecting additional coherent errors would reduce this further.
+We felt that any convincing demonstration would be impossible to implement.
+
+5.
+I'm still confused about how the algorithm works.
+Suppose we have gates that have systematic errors on some unitary angles.
+These errors are, of course, not known to me.
+Now, what do I do exactly?
+I start introducing a bunch of (additional and known) random errors to the gates, then compile the quantum circuit by picking gates from this random ensemble I constructed?
+If so, what the authors seemed to have showed is that the error of the randomly compiled circuit beats that of the circuit made from any one of the faulty gates in the ensemble (which I constructed myself), NOT the coherent error in the original gate.
+This seemed rather useless, as the endgame is to suppress the original, unknown coherent error, NOT the artificial errors I introduced.
+Am I missing something?
+
+While the precise coherent errors experienced by a particular gate implementation might be unknown, it can certainly be learned fairly accurately using, for instance, a tomographic protocol.
+However, if our approach demanded such detailed knowledge it would be an operationally useless, though perhaps interesting, curiosity – you could simply calibrate away any errors you identify.
+Of course, it could be the case that the classical control hardware is sufficiently inflexible that some lingering coherent error will always remain (maybe you don't have enough samples in your DAC), or that the coherent errors come from unknown interactions that are out of your control.
+But an important enabling contribution of our work is the explicit inclusion of robustness into the optimization.
+This enables the mixed unitary gate to be protected against drift or uncertainty in the precise nature of the coherent error.
+This means that tomographic reconstruction of the error is unnecessary.
+
+In our experiment we have introduced the miscalibrations intentionally, since the qubits were coherence limited. We have clarified this in the text as a summary of the protocol:
+
+To construct an MQG, there needs to be several different realizations of the desired gate available.
+To see improved performance, these realizations need to be imperfect in different ways, from drift, miscalibration, or other sources of error.
+Because the qubit used in our demonstration was coherence-limited, and therefore did not suffer from miscalibration errors, we intentionally introduced coherent errors to showcase our technique.
+
+By implementing four miscalibrated $X_{\frac{\pi}{2}}$ rotations on a superconducting qubit and drawing from them with optimized weights, we see that coherent over- and under- rotations can be averaged away.
+
+All in all, I cannot recommend the publication of the manuscript until the authors clarify my concerns above.
+
+We believe that we have thoroughly addressed the referee’s concerns.
+We thank the referee for their observations, and we believe that responding to them has helped us to substantially improve our manuscript.

### 2020-05-06 decorrelation/resubmission/response_to_referees.txt
Updates after conversation5/6

@@
 When implemented using mixed quantum gates, the coherent addition of error is suppressed and the average compiled Clifford error rate is lower, leading to an improved success probability.
-We have included new text to highlight this:
-
-While, as discussed in Sec.~\ref{sec:mqg}, the AGI of an MQG cannot be lower than any of constituent controls, the AGI of a circuit can be improved by using MQGs.
-We see from this experiment that by reducing the diamond distance of the MQG, we can improve the AGI of the total circuit.
 

### 2020-05-06 decorrelation/mixed_unitaries.tex
Updates after conversation5/6

@@
 Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem.
-We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates.
+We then discuss a family of convex programs able to solve this problem, as well as a set of secondary objectives designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates.
 Finally, we implement these mixed quantum gates on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
@@
 Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}.
-In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step.
-While Pauli Frame Randomization shares some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.
+In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a compilation step.
+MQGs are an alternative approach to solving this problem.
+Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time, allowing them to be easily implemented in hardware.
+Moreover, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.
 
@@
 If the error channel is purely stochastic, then $\dnorm(\error) = \AGI(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \cite{1511.00727}.
-The diamond distance is subaddative \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for gates that compose the circuit \cite{aharonov1998quantum}.
+The diamond distance is subadditive \cite{watrous2018theory} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for gates that compose the circuit \cite{aharonov1998quantum}.
 
@@
 \noindent
-As a practical consideration, we would also like to regularize our objective function to promote sparse weightings, resulting in MQGs with only a small number of gate implementations.
+As a practical consideration, we would also like to regularize our objective function to promote sparse weightings, resulting in MQGs composed of only a small number of individual gate implementations.
 Control electronics often have a limited amount of waveform memory, and thus it is important to be able to construct MQGs with as few constituent gates as possible.
@@
 If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant.
-If $\lambda$ is very large each inner minimization problem is minimized for an MQG with a single control.
-Therefore the outer minimization simply selects the control which has the error generator of smallest norm.
+If $\lambda$ is very large each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm.
 While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
@@
 While this device consisted of 20 qubits with fixed couplings, we used only qubit \#8 for our demonstration.
+
+To construct an MQG, there needs to be several different realizations of the desired gate available.
+To see improved performance, these realizations need to be imperfect in different ways, from drift, miscalibration, or other sources of error.
+Because the qubit used in our demonstration was coherence-limited, and therefore did not suffer from miscalibration errors, we intentionally introduced coherent errors to showcase our technique.
 Controls were derived from a single, 10-sample, 50ns Gaussian $X_{\pi/2}$ pulse calibrated via Rabi oscillation.
@@
 We model their effect on the qubit state as perfectly unitary rotations, $X_{A \pi/2} = \exp{(-i A \pi/2 \sigma_x)}$.
+
  These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
@@
 
-This example shows that MQGs are capable of outperforming the individual gates of which they are composed.
-In particular, given a collection of controls whose miscalibration errors are known, this demonstrates that the techniques in Section \ref{sec:convex_programs} can be used to trade the coherent errors for incoherent errors.
+We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed.
 In future work, we hope to apply this technique to two-qubit gates, which are significantly more difficult to tune up in general and are more likely to possess lingering coherent errors.
@@
 \begin{figure}
-\includegraphics[scale=.5]{sparisity-versus-parameter.png}
-\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$, with higher weight controls omitted to emphasize the low-weight distribution.
-Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=6.25$e-05, $\lambda_2=0.0001$, $\lambda_3=0.00025$ and $\lambda_4=0.0005$.
-As the parameter is increased from zero, the number of controls with low probability increases.
-For $\lambda_4$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
+\includegraphics[width=\linewidth]{sparisity-versus-parameter_kcy.png}
+\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$.
+Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=0.0001$, $\lambda_2=0.00025$ and $\lambda_3=0.0005$.
+As the parameter is increased from zero, the number of controls with low probability increases (seen on the plot as the probability mass moving to the left).
+For $\lambda_3$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
 \label{fig:sparsity}
@@
 Fig.~\ref{fig:sparsity} shows solutions to Eq.~\eqref{eq:minimization_sparsity} for different choices of  $\lambda$.
-As $\lambda$ increases, the optimal solution contains less controls.
+As $\lambda$ increases, the optimal solution contains fewer controls with large support.
 
@@
 While performing a complete optimization in this way would require full process tomography, one could instead use partial tomography.
-By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk terms, one could perform optimization over fewer parameters to produce MQGs that supress specific errors.
+By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk terms, one could perform optimization over fewer parameters to produce MQGs that suppress specific errors.
 

### 2020-05-06 decorrelation/mixed_unitaries.tex
incorrect figure reference on page 7
final changes to text from anthony, regeenrated text

@@
  These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively.
-Using these probabilities and pulse amplitudes we have plotted the corresponding error generators in Fig.
-\ref{ptms}.
+Using these probabilities and pulse amplitudes we have plotted the corresponding error generators in Fig.~\ref{fig:ptms}.
 $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear suppression of these off-diagonal elements.
@@
 \includegraphics[scale=.5]{experimental-ptm.png}
-\label{ptms}
 \caption{Hinton diagrams representing the error generators for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e) a Pauli-exact MQG.
@@
 The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.}
+\label{fig:ptms}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\linewidth]{sparisity-versus-parameter_kcy.png}
+\includegraphics[width=\columnwidth]{sparisity-versus-parameter_kcy.png}
 \caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$.
@@
 Fig.~\ref{fig:sparsity} shows solutions to Eq.~\eqref{eq:minimization_sparsity} for different choices of  $\lambda$.
-As $\lambda$ increases, the optimal solution contains fewer controls with large support.
+As $\lambda$ increases, most of the weights in the optimal solution become smaller, resulting in a sparser MQG.
 
@@
 
-Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other control routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
+Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other control generation algorithms such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
 

### 2020-05-06 decorrelation/mixed_unitaries.tex
updating sparsity plot to onlt have two lamdba value

@@
 \includegraphics[width=\columnwidth]{sparisity-versus-parameter_kcy.png}
-\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$.
-Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=0.0001$, $\lambda_2=0.00025$ and $\lambda_3=0.0005$.
+\caption{Sparsity of MQGs as a function of the sparsity parameter $\lambda$, with $\lambda_0=0$ and $\lambda_1=0.0005$.
 As the parameter is increased from zero, the number of controls with low probability increases (seen on the plot as the probability mass moving to the left).
-For $\lambda_3$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
+For $\lambda_1$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
 \label{fig:sparsity}

### 2020-05-08 decorrelation/mixed_unitaries.tex
final update before resubmitting

@@
 If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant.
-If $\lambda$ is very large each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm.
+If $\lambda$ is very large, each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm.
 While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
-In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
+
+In general, increasing $\lambda$ decreases the number of controls with large weights, and by removing controls with weights below a threshold probability we can increase the sparsity of the solution.
+Truncating in this way will introduce error in the Pauli-exactness of the solution.
+For larger $\lambda$ the required threshold probability decreases, and so the error introduced from truncation can be made smaller.
+However, larger $\lambda$ will also decrease the likelihood of the optimizer returning a generator-exact solution, and so in this way, tuning $\lambda$ allows us to trade between different sources of error when constructing sparse MQGs.
 

### 2020-05-08 decorrelation/resubmission/response_to_referees.txt
udpating coloring of response

@@
 
-Here, $\lambda\geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
-If $\lambda$ is set to zero, the inner program reduces to Eq.
-(19) and the outer minimization is redundant.
-If $\lambda$  is very large each inner minimization problem is minimized for an MQG with a single control.
-Therefore the outer minimization simply selects the control which has the error generator of smallest norm.
+Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
+If $\lambda$ is set to zero, the inner program reduces to Eq.~\eqref{eq:minimization} and the outer minimization is redundant.
+If $\lambda$ is very large, each inner minimization problem is minimized for an MQG with a single control, and the outer minimization simply selects the control which has the error generator of smallest norm.
 While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
-In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
+
+In general, increasing $\lambda$ decreases the number of controls with large weights, and by removing controls with weights below a threshold probability we can increase the sparsity of the solution.
+Truncating in this way will introduce error in the Pauli-exactness of the solution.
+For larger $\lambda$ the required threshold probability decreases, and so the error introduced from truncation can be made smaller.
+However, larger $\lambda$ will also decrease the likelihood of the optimizer returning a generator-exact solution, and so in this way, tuning $\lambda$ allows us to trade between different sources of error when constructing sparse MQGs.
 

### 2020-05-08 decorrelation/mixed_unitaries.tex
a newline for an indent
okay last commit - pauli -> generator

@@
 \end{equation}
+
 Here, $\lambda \geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
@@
 In general, increasing $\lambda$ decreases the number of controls with large weights, and by removing controls with weights below a threshold probability we can increase the sparsity of the solution.
-Truncating in this way will introduce error in the Pauli-exactness of the solution.
+Truncating in this way will introduce error in the generator-exactness of the solution.
 For larger $\lambda$ the required threshold probability decreases, and so the error introduced from truncation can be made smaller.

### 2020-09-11 decorrelation/resubmission/response_to_referees.txt
and ref response...
Minor edits to referee response.

--- 2020-05-06 decorrelation/resubmission/response_to_referees.txt
@@
-Response to referee comments for: AN11713 Robustly decorrelating errors with mixed quantum gates
+First Referee,
+Thank you for the helpful suggestions. In line with your comment, we have added the following text to Secs. IIIB3 and IVB1 with Fig. 6 for readers not familiar with sparse modeling.
+""
 
-We’d like to begin by thanking the referees for their detailed comments.
-We have used their comments and criticism to improve our manuscript and are now even more confident that it is suitable for publication in Physical Review A.
-Below we include the full report of each referee (in blue italics), interspersed with our response.
-Quotes from our revised manuscript are shown in green italics.
+Second Referee,
+Thank you for your report.
 
-Report of the First Referee -- AN11713/Polloreno
+While randomized compiling is well known in the field and affects the same outcome as our strategy, it is important to note that our technique works at the hardware level, rather than the compilation level.
+Thus our routine does not require a precompilation step for each circuit.
+Additionally, as you point out, our routine has been cast as a convex optimization routine.
+Because of the way we have formulated our problem, we are able to augment the mixed quantum gate to have properties besides just twirling away the error.
+We have summarized this in the text now as:
+""
 
-In this paper, the authors propose novel techniques to solve the problem of coherent errors in quantum computation.
-Their techniques, which are obtained by extending previous approaches, are based on various optimization methods.
-This topic is timely and the methods proposed here will be useful in the field of quantum information science.
-So, I recommend its publication in PRA.
+We will now respond to your five bullet points.
 
-Here I have a comment for readability.
-The presentation in Secs.
-IIIB3 and IVB1 with Fig.
-6 may be difficult to understand, especially for readers not familiar with sparse modeling.
-I recommend the improvement of the parts.
+The experiment we chose was meant to demonstrate the reduced coherent error of the channel.
+While it's true that any mixing of the unitaries will outperform any of the constituent unitaries as measured by RB number, the demonstration was meant to show a reduction in the coherence of the error.
+This is the result mentioned by Ball et al., and we have revised the text to emphasize this.
+Had we chosen different weights than those produced by the convex optimizer, the error bars would have been larger.
 
-We thank the referee for their positive assessment of our work, as well as for alerting us to potentially unclear sections of the manuscript.
-In line with these comments, we have added the following text to Secs.
-IIIB3 and IVB1 and modified Fig.
-6 to improve the clarity for readers not familiar with sparse optimization.
+This is a great suggestion, although the presentation might be more cluttered. However, the first author no longer has access to the hardware at Rigetti Computing.
 
-Here, $\lambda\geq 0$ is a tunable parameter that can be used to control the degree of sparsity in the solution.
-If $\lambda$ is set to zero, the inner program reduces to Eq.
-(19) and the outer minimization is redundant.
-If $\lambda$  is very large each inner minimization problem is minimized for an MQG with a single control.
-Therefore the outer minimization simply selects the control which has the error generator of smallest norm.
-While this gives a maximally sparse solution, it doesn't allow for any cancellation of coherent errors.
-In particular, increasing $\lambda$ will increase the sparsity of the solution, but will generally decrease the likelihood that the solution will be generator-exact.
+While it is true that RB randomizes errors and our technique also randomizes errors, randomized benchmarking still show cases the property of the resulting channel that we want.
+Namely, that the errors have minimal coherent error.
+Using an algorithm like QAOA would be challenging to demonstrate a decrease in the coherent error of the resulting channel.
 
-Report of the Second Referee -- AN11713/Polloreno
+The two-qubit experiment is substantially harder to do.
+Two qubit infidelities are sufficiently high that even repeating the randomized benchmarking experiment would have very poor signal to noise, since an average clifford gate has a large number of two qubit gates.
+While we agree that a two-qubit demonstration would be a good addition to the manuscript, it is also the case the author no longer has access to the hardware.
 
-The manuscript by Pollareno et al.
-presents a convex algorithm for compiling gates in quantum algorithms in a random fashion.
-Instead of applying a fixed gate pulse (which can have both coherent and incoherent errors), the authors pick the gates from ensembles with intentionally injected control errors.
-This procedure is meant to randomize coherent errors and mitigate any amplification of such errors in quantum circuits.
-The authors then performed a simple single-qubit RB experiment using their qubit device, where they show that the coherent errors of individual (intentionally misaligned) pulses are suppressed if the SQ gates are chosen from an ensemble of such misaligned gates.
-Some numerics are also done for two-qubit gates arguing for similar, beneficial outcomes.
+The control errors need to be known to you - you can accomplish this through something like tomography.
+You might object - if I know my control errors, I will just fix them!
+It could be the case that you don't have enough samples in your DAC to do this, or that the coherent errors come from unknown interactions that are out of your control.
+Moreover, in the context of drift as in superconducting platforms, it is the case that you can pick out a family of controls that will all drift, but drift in different ways such that their average channel performs in a better way than any individual channel.
+In our experiment we have introduced the miscalibrations intentionally, since the qubits were coherence limited.
+We have clarified this in the text as a summary of the protocol:
 
-Randomized compiling is technique known to the QC community for quite some time now and therefore there is nothing particularly novel about the technique itself.
-What appears to be the highlight of the paper is the convex algorithm that the authors used to choose random gates and the experimental demonstration.
-While these are good steps toward a nice direction, I feel the demonstrations are not sufficiently convincing, particularly in regard to the experimental part (which the authors themselves acknowledge as being "contrived").
-Here are my main concerns:
+------
 
-While the referee is correct that our approach is superficially similar to randomized compiling, we wish to emphasize that our technique is intended as an alternative approach to solving the problem of coherent errors in quantum information processors.
-Our method is particularly well suited for experimental implementation, as the mixed unitary gates can be implemented at the level of individual logic operations using the FPGA control hardware.
-Contrast this against the randomized compiling approach, which requires wholesale recompilation of the circuit every time it is run.
-Importantly, though, we make no claim that this broad approach is novel – in fact, we frequently cite prior foundational work in this area.
-Instead, our manuscript extends and expands the scope of this prior work, formulating the problem as an explicit convex optimization, incorporating robustness to uncertainty, and, critically, providing the first experimental demonstration of this technique on quantum information processing hardware.
-We have added the following to the text to clarify this point:
-
-MQGs are an alternative approach to solving this problem.
-Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time.
-Moreover, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.
-
-We further thank the referee for their detailed assessment of our experimental demonstration.
-We address each of the referees comments below and, in doing so, we have substantially improved our manuscript.
-
-1.
-For the experiment, it is completely trivial to me that randomly picking four faulty unitaries outperforms choosing just one of them.
-Here the only coherent errors the authors introduced are under and over-rotations to the Rabi angle.
-These over- and under-rotations would naturally build up and amplify if left by themselves.
-However, if chosen at random, they would cancel each other out and give better fidelity at the end of the sequence.
-Correct?
-I fail to see any surprise here and how the authors' lengthy algorithm even plays a role for this demonstration.
-
-The referee is correct that Rabi oscillations would be significantly (and obviously) improved by switching to a mixed quantum gate implementation.
-In fact, we found this to be so obvious as to be uninteresting, so we chose not to test such circuits experimentally.
-What we did find surprising, however, was the improved performance of randomized benchmarking circuits.
-These circuits already incorporate randomness (as the referee points out below in comment 3).
-This randomness is specifically designed to – on average -- twirl coherent errors into stochastic errors.
-But the mixed quantum gate implementation both narrowed the variance over circuits and improved the average success probability.
-The former effect is a clear signature of reduced coherent noise, while the latter has a more complicated explanation: The improvement in success probability can be traced to the compilation of the Clifford operations, which occasionally contain sequences of repeated primitive gates.
-Coherent errors in these compilations can add up, increasing the average error rate of the compiled Clifford.
-When implemented using mixed quantum gates, the coherent addition of error is suppressed and the average compiled Clifford error rate is lower, leading to an improved success probability.
-
-While the algorithm section of our manuscript is lengthy, it is central to our demonstration as it is used to choose the sampling weights for each of the erroneous implementations.
-If we had picked different weights, the effective channel would not be stochastic, and we would suffer a performance penalty in our demonstration.
-
-2.
-It seems to me that authors can very easily go a step further: A SQ unitary is parametrized by three angles: Rabi angle, off-diagonal and diagonal phases.
-Why not introduce coherent errors to all three phases (or at least two, such as the Rabi angle and the off-diagonal phase)?
-To me this will be much less trivial.
-
-This is an excellent suggestion, and we considered broadening the scope of the injected errors.
-However, we decided against this so that the presentation might be more streamlined.
-And while we agree that this might ultimately yield a more convincing demonstration, we no longer have the low-level access to Rigetti Computing hardware that would be required to implement it.
-
-3.
-The whole point of RB is meant to randomize coherent errors and turn them into a depolarization channel.
-It is bizarre to me that the authors chose to demonstrate their randomized compiling through an experiment that is in itself random.
-Wouldn't a structured algorithm (QAOA or anything else that is not random) be a far better candidate for demonstrating the efficacy of randomized compiling?
-
-As we discuss in our response to the referee’s first enumerated comment, randomized benchmarking circuits are sensitive to coherent errors.
-Demonstrations using metaheuristics such as QAOA, while currently en vogue, may instead confound the coherent error suppression we are attempting to illustrate.
-Full-stack QAOA requires a classical optimizer that continually tunes circuit parameters, so coherent errors can easily be suppressed by the optimizer.
-And, as we mentioned above, Rabi oscillation experiments just seemed too trivial to be interesting.
-
-4.
-Why is the two-qubit experiment not done?
-It shouldn't be that difficult to do, if the authors believe that their method works (according to numerics).
-SQ demonstrations just too trivial to show anything given their simplicity.
-
-We agree with the referee that a two-qubit gate demonstration would be significantly more impressive.
-Ultimately, we ourselves would like to see this method implemented on a two-qubit gate.
-However, the two-qubit gate available to us was dominated by large stochastic errors that severely curtailed the number of sequential gate applications before the state decohered.
-Injecting additional coherent errors would reduce this further.
-We felt that any convincing demonstration would be impossible to implement.
-
-5.
-I'm still confused about how the algorithm works.
-Suppose we have gates that have systematic errors on some unitary angles.
-These errors are, of course, not known to me.
-Now, what do I do exactly?
-I start introducing a bunch of (additional and known) random errors to the gates, then compile the quantum circuit by picking gates from this random ensemble I constructed?
-If so, what the authors seemed to have showed is that the error of the randomly compiled circuit beats that of the circuit made from any one of the faulty gates in the ensemble (which I constructed myself), NOT the coherent error in the original gate.
-This seemed rather useless, as the endgame is to suppress the original, unknown coherent error, NOT the artificial errors I introduced.
-Am I missing something?
-
-While the precise coherent errors experienced by a particular gate implementation might be unknown, it can certainly be learned fairly accurately using, for instance, a tomographic protocol.
-However, if our approach demanded such detailed knowledge it would be an operationally useless, though perhaps interesting, curiosity – you could simply calibrate away any errors you identify.
-Of course, it could be the case that the classical control hardware is sufficiently inflexible that some lingering coherent error will always remain (maybe you don't have enough samples in your DAC), or that the coherent errors come from unknown interactions that are out of your control.
-But an important enabling contribution of our work is the explicit inclusion of robustness into the optimization.
-This enables the mixed unitary gate to be protected against drift or uncertainty in the precise nature of the coherent error.
-This means that tomographic reconstruction of the error is unnecessary.
-
-In our experiment we have introduced the miscalibrations intentionally, since the qubits were coherence limited. We have clarified this in the text as a summary of the protocol:
-
-To construct an MQG, there needs to be several different realizations of the desired gate available.
-To see improved performance, these realizations need to be imperfect in different ways, from drift, miscalibration, or other sources of error.
-Because the qubit used in our demonstration was coherence-limited, and therefore did not suffer from miscalibration errors, we intentionally introduced coherent errors to showcase our technique.
-
-By implementing four miscalibrated $X_{\frac{\pi}{2}}$ rotations on a superconducting qubit and drawing from them with optimized weights, we see that coherent over- and under- rotations can be averaged away.
-
-All in all, I cannot recommend the publication of the manuscript until the authors clarify my concerns above.
-
-We believe that we have thoroughly addressed the referee’s concerns.
-We thank the referee for their observations, and we believe that responding to them has helped us to substantially improve our manuscript.
+Kevin's Edits:

### 2020-09-11 decorrelation/resubmission/response_to_referees.txt

--- 2020-05-08 decorrelation/resubmission/response_to_referees.txt
@@
 MQGs are an alternative approach to solving this problem.
-Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time.
+Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time, allowing them to be easily implemented in hardware.
 Moreover, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.

### 2020-10-07 decorrelation/mixed_unitaries.tex
anthony made some changes before submitting

@@
 
-Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}.
-In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a compilation step.
-MQGs are an alternative approach to solving this problem.
-Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time, allowing them to be easily implemented in hardware.
-Moreover, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.
-
 In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates and show that the advantages of their approach can be made robust to drift and model uncertainty.
@@
 We further apply our methods in simulation, constructing both single- and two-qubit mixed unitary controls that are robust to drift and uncertainty in the control parameters.
+These robust MQGs are insensitive to calibration errors, but do not require the temporal overhead of coherent control techniques\cite{1203.6392}.
+
+Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}.
+In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a compilation step.
+MQGs are an alternative approach to solving this problem.
+Because they are implemented by randomly drawing from different gate realizations, they only require randomness at run-time, allowing them to be easily implemented in hardware.
+Moreover, as we will discuss, when the construction of MQGs is posed as a numerical optimization problem, numerous useful modifications can be made to augment their performance.
 
@@
 We illustrate this in Fig.~\ref{fig:vectorspace2}.
-
 We call a gate constructed in this way a \emph{robust} generator-exact MQG.
 These techniques can be easily adapted to construct robust Pauli-exact MQGs, where vectors of the off-diagonal elements of the error maps take the role of the error generators used above.
-
+An important property of these robust MQGs is their relatively short implementation times, as compared with conventional coherent control techniques.
+To see this, consider two well-known robust optimal control sequences, BB1 and SK1.\cite{Wimperis1994, Brown2004}.
+Considering specifically pulse amplitude errors, BB1 utilizes a so-called broadband sequence which requires four rotations to mitigate calibration errirs.
+In the more general case of SK1 (and SKn) pulses, we consider an arbitrary error of magnitude $\epsilon$, that we wish to supress to order $n$.
+Already, for an SK1 pulse, this technique requires three rotation.
+Contrast this with the duration of an MQG, which is at worst the duration of the longest gate in the family.
 \begin{figure}
@@
 
-\subsection{Experimental implementation } % (fold)
+\subsection{Experimental implementation} % (fold)
 \label{sub:experimental}
@@
 
-We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed.
+We note that, while this example is somewhat contrived (the calibrated gate is clearly the best), it nonetheless succeeds in demonstrating that the MQGs are capable of outperforming the individual gates of which they are composed and are able to be easily implemented on modern devices.
 In future work, we hope to apply this technique to two-qubit gates, which are significantly more difficult to tune up in general and are more likely to possess lingering coherent errors.
-Tomography or modeling can then be used to construct the process matrix estimates required to build a mixed gate.
+In this case, tomography or modeling can then be used to construct the process matrix estimates required to build a mixed gate.
+Even in the case that the errors cannot be learned tomographically or modeled accurately, the robust methods introduced in the previous section can be used to produce MQGs with improved performance.
 
@@
 Nonetheless, using an MQG improves performance over any of the constituent controls over a wide-range of detunings, and for all values of the detunings we see that the robust generator-exact MQG performs as well or better than generator-exact MQG.
-
+And, as discussed previously, the robustness comes without the temporal overhead of introducing more gates sequentially.
 \begin{figure}
@@
 The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings.
-Similar results are obtained for drift in the qubit control amplitude.}
+Similar results are obtained for drift in the qubit control amplitude.
+The insensitivity to $\epsilon$ here is reminiscent of the insensitivity to pulse amplitude in \cite{Wimperis1994}, however we emphasize that the robustness here is achieved without increasing the duration of the gate.}
   \label{fig:2MQG}
